---
title: "Map of Cities in Sample"
output:
  html_document:
    df_print: paged
---

This file makes a map that shows the cities in our sample and Brazil's regions

```{r}
knitr::opts_chunk$set(message=FALSE)
library(tidyverse)
library(glue)

library(sf)
library(rnaturalearth)
library(ggrepel)

library(here)
```

```{r}
out_dir <- here("out") 
data_dir <- here("data") 
survey_data_dir <- file.path(data_dir, 'survey')
```

```{r}
capital.coords <- read_csv(file.path(data_dir, "cities.csv"))
```

```{r}
map_pal <- 'Set1'
```

```{r}
#
# grab the brazilian states
brne <- ne_states(country='brazil', returnclass='sf')

# need to make two manual fixes where the state code 
# seems to be wrong in the naturalearth data
brne <- brne %>%
  mutate(postal = case_when(fips == 'BR01' ~ 'AC',
                            fips == 'BR24' ~ 'RO',
                            TRUE ~ postal))
```

```{r}
theme_set(theme_bw())
```

Convert the dataframe w/ info on the state capitals into an sf object;
we'll eventually use this to plot the capitals on the map below

```{r}
capitals <- st_as_sf(capital.coords,
                     coords=c('lon', 'lat'),
                     # using CRS code 4326, which is WGS84
                     # (I got this from an example online, and it looks reasonable)
                     crs = 4326,
                     remove=FALSE)
capitals <- capitals %>%
  mutate(city_state_label = glue::glue("{municipio} ({state_abbrev})"))

capitals
```

Looking at a few pages:

* [rspatial - Drawing beautiful maps programmatically with R, sf and ggplot2 — Part 1: Basics](https://www.r-spatial.org/r/2018/10/25/ggplot2-sf.html)
* [rspatial - Drawing beautiful maps programmatically with R, sf and ggplot2 — Part 2: Layers](https://www.r-spatial.org/r/2018/10/25/ggplot2-sf-2.html)
* [rspatial - Drawing beautiful maps programmatically with R, sf and ggplot2 — Part 3: Layouts](https://www.r-spatial.org/r/2018/10/25/ggplot2-sf-3.html)

```{r}
ggplot(data=brne) + geom_sf()
```

Join region info from `capital.coords.raw` info onto the `brne` object

```{r}
brne <- brne %>% 
  select(-region) %>%
  left_join(capital.coords %>% select(postal=state_abbrev, region)) 
```

```{r}
# for removing the background from ggplots
remove_background <- theme(panel.background = element_blank(),
          panel.border = element_blank(),
          panel.grid.major = element_blank(),
          axis.ticks.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.y = element_blank(),
          axis.text.y = element_blank()) 
```

```{r}
region_map <- 
  ggplot(data=brne) + 
    geom_sf(aes(fill=region), linetype=2) +
    scale_fill_brewer(palette = map_pal) +
    guides(fill = guide_legend("Region")) +
    remove_background

region_map
```

```{r, fig.width=6, fig.height=6}
sample_map <- 
  ggplot(data=brne) + 
    theme_bw(base_size=5) +
    geom_sf(aes(fill=region), 
            linetype='dotted', 
            alpha=.8) +
    scale_fill_brewer(palette = map_pal) +
    remove_background +
  geom_sf(data=capitals) +
  geom_text_repel(data=capitals,
                  aes(x=lon, y=lat, 
                      label=glue::glue("{municipio} ({state_abbrev})")),
                  size=rel(3)) +
  xlab('') + ylab('') +
  guides(fill=guide_legend("Region",
                           override.aes=list(linetype=0))) +
  theme(legend.position=c(.2,.3),
        legend.direction='vertical',
        legend.text=element_text(size=8),
        legend.title=element_text(size=8, face='bold')) +
  NULL

ggsave(filename=file.path(out_dir, "sample_map.pdf"),
       plot=sample_map,
       height=6,
       width=6)
  
sample_map
```

```{r}
brne_outline <- brne %>% st_make_valid %>% st_union()

sample_map_clean <- 
  #ggplot(data = brne) + 
  #  theme_bw(base_size = 5) +
  #  # Keep borders black and dotted
  #  geom_sf(fill = NA, 
  #          color = "black", 
  #          linetype = 'dotted', 
  #          linewidth = 0.3) +
  #  remove_background +
  ggplot() + 
    theme_bw(base_size = 5) +
    # 2. Draw ONLY the outline (the dissolved shape)
    geom_sf(data = brne_outline,
            fill = NA, 
            color = "darkgrey", 
            linetype = 'solid', # Changed to solid for a cleaner outline, but 'dotted' works too
            linewidth = 0.5) +
    remove_background +
  geom_sf(data = capitals, size = 1.2, color='red') + # The city points
  geom_text_repel(data = capitals,
                  aes(x = lon, y = lat, 
                      #label = glue::glue("{municipio} ({state_abbrev})")),
                      label = glue::glue("{municipio}")),
                  size = 6,
                  color = "black",          # Light grey text
                  segment.color = "black",  # Grey connecting lines
                  #color = "grey60",          # Light grey text
                  #segment.color = "grey60",  # Grey connecting lines
                  segment.alpha = 0.6,       # Make lines slightly transparent
                  box.padding = 0.6,
                  point.padding = 0.4,
                  min.segment.length = 0,
                  force = 3) +              # Increased force to handle larger text
  xlab('') + ylab('') +
  theme(legend.position = "none") +
  NULL

ggsave(filename=file.path(out_dir, "sample_map_clean.pdf"),
       plot=sample_map_clean,
       height=6,
       width=6)

sample_map_clean
```
```{r}
library(ggplot2)
library(ggrepel)
library(patchwork)
library(dplyr)
library(gridExtra)

# 1. Prepare the data: Add a numeric ID
capitals <- capitals %>%
  mutate(id = row_number())

# 2. Create the Map
map_plot <- 
  ggplot(data = brne) + 
    theme_bw(base_size = 5) +
    geom_sf(fill = NA, 
            color = "black", 
            linetype = 'dotted', 
            linewidth = 0.3) +
    remove_background +
    # Use geom_text_repel to put the NUMBER on the map
    geom_text_repel(data = capitals,
                    aes(x = lon, y = lat, label = id),
                    size = 5,
                    fontface = "bold",
                    color = "black", # Numbers kept black for readability
                    box.padding = 0.3,
                    point.padding = 0.5,
                    segment.color = "grey70") +
  xlab('') + ylab('') +
  theme(legend.position = "none")

# 3. Create the Table Plot
# We format the text for the legend/table
table_data <- capitals %>%
  mutate(label = glue::glue("{id}. {municipio}")) %>%
  select(label)

table_plot <- ggplot() +
  annotate("text", 
           x = 0, 
           y = rev(seq_along(table_data$label)), 
           label = table_data$label, 
           hjust = 0, 
           size = 3.5,     # Adjust size of table text here
           color = "grey40") + # Light grey as requested
  theme_void() +
  coord_cartesian(xlim = c(0, 1)) +
  NULL

# 4. Combine Map and Table using patchwork
# widths = c(3, 1) means the map takes 3/4 and the table 1/4 of the space
final_layout <- map_plot + table_plot + 
  plot_layout(widths = c(3, 1))

final_layout
```


# Make a hexgrid showing states/cities

See the geogrid package:
https://github.com/jbaileyh/geogrid

NB: this code causes some warnings - we don't need to worry about these

```{r}
cur.hex.seed <- 99 
new_cells_hex <- geogrid::calculate_grid(shape = brne, grid_type='hexagonal', seed=cur.hex.seed)
br_state_hexgrid <- geogrid::assign_polygons(brne, new_cells_hex)

# adding a small buffer seems to fix the fact that the hex tiles don't
# completely overlap
eps_buffer <- .001
br_state_hexgrid <- st_buffer(br_state_hexgrid, eps_buffer)
```

```{r, fig.width=6, fig.height=6}
sample_hexmap <- ggplot(data=br_state_hexgrid) + 
    theme_bw(base_size=5) +
    geom_sf(aes(fill=region), 
            linetype='dotted', 
            alpha=.8) +
    scale_fill_brewer(palette = map_pal) +
    remove_background +
    geom_text(aes(label=postal,
                  x=V1, y=V2)) +
  xlab('') + ylab('') +
  guides(fill=guide_legend("Region",
                           override.aes=list(linetype=0))) +
  theme(legend.position=c(.2,.3),
        legend.direction='vertical',
        legend.text=element_text(size=8),
        legend.title=element_text(size=8, face='bold')) +
  NULL

ggsave(filename=file.path(out_dir, "sample_hexmap.pdf"),
       plot=sample_hexmap,
       height=6,
       width=6)
ggsave(filename=file.path(out_dir, "sample_hexmap.png"),
       plot=sample_hexmap,
       height=6,
       width=6)
  
sample_hexmap
```

Get hexmap of regions

```{r}
br_hexgrid_outline <- st_union(br_state_hexgrid) 

br_region_hexgrid <- br_state_hexgrid %>%
  group_by(region) %>%
  summarize(geometry = st_union(geometry))
```

```{r}
sample_hex_dim <- 4

sample_region_hexmap <- ggplot(data=br_region_hexgrid) + 
    theme_bw(base_size=5) +
    geom_sf(aes(fill=region), 
            linetype='solid', 
            alpha=.8) +
    #scale_fill_brewer(palette = "Set3") +
    scale_fill_brewer(palette = map_pal) +
    # uncomment to get faint lines along state hex boundaries
    #geom_sf(aes(fill=NA),
    #        alpha=.1,
    #        data=br_state_hexgrid) +
    remove_background +
    geom_text(aes(label=postal,
                  x=V1, y=V2),
              data=br_state_hexgrid) +
  xlab('') + ylab('') +
  guides(fill=guide_legend("Region",
                           override.aes=list(linetype=0))) +
  theme(legend.position=c(.2,.3),
        legend.direction='vertical',
        legend.text=element_text(size=8),
        legend.title=element_text(size=8, face='bold')) +
  NULL

ggsave(filename=file.path(out_dir, "sample_region_hexmap.pdf"),
       plot=sample_region_hexmap,
       height=sample_hex_dim,
       width=sample_hex_dim)
ggsave(filename=file.path(out_dir, "sample_region_hexmap.png"),
       plot=sample_region_hexmap,
       height=sample_hex_dim,
       width=sample_hex_dim)
  
sample_region_hexmap
```

```{r}
saveRDS(list(map=brne, 
             capitals=capitals, 
             hexmap=br_state_hexgrid, 
             hexmap_region=br_region_hexgrid),
        file.path(out_dir, "brazil_map.rds"))
```


