---
title: "Map of Cities in Sample"
output:
  html_document:
    df_print: paged
---

This file makes a map that shows the cities in our sample and Brazil's regions

```{r}
library(tidyverse)
library(glue)

library(sf)
library(rnaturalearth)
library(ggrepel)

# has st_remove_holes()
#library(nngeo)

library(here)
```

```{r}
out_dir <- here("out") 
data_dir <- here("data") 
```

```{r}
capital.coords <- read_csv(file.path(data_dir, "cities.csv"))
```

```{r}
#map_pal <- 'Set3'
#map_pal <- 'Accent'
map_pal <- 'Set1'
```


```{r}
# see
# https://github.com/ropenscilabs/rnaturalearth
#devtools::install_github("ropensci/rnaturalearthdata@352e548")
#install.packages("rnaturalearthhires", repos = "https://packages.ropensci.org", type = "source")
```

```{r}
#
# grab the brazilian states
brne <- ne_states(country='brazil', returnclass='sf')

# need to make two manual fixes where the state code 
# seems to be wrong in the naturalearth data
brne <- brne %>%
  mutate(postal = case_when(fips == 'BR01' ~ 'AC',
                            fips == 'BR24' ~ 'RO',
                            TRUE ~ postal))
```

```{r}
theme_set(theme_bw())
```

Convert the dataframe w/ info on the state capitals into an sf object;
we'll eventually use this to plot the capitals on the map below

```{r}
capitals <- st_as_sf(capital.coords,
                     coords=c('lon', 'lat'),
                     # using CRS code 4326, which is WGS84
                     # (I got this from an example online, and it looks reasonable)
                     crs = 4326,
                     remove=FALSE)
capitals <- capitals %>%
  mutate(city_state_label = glue::glue("{municipio} ({state_abbrev})"))

capitals
```

Looking at a few pages:

* [rspatial - Drawing beautiful maps programmatically with R, sf and ggplot2 — Part 1: Basics](https://www.r-spatial.org/r/2018/10/25/ggplot2-sf.html)
* [rspatial - Drawing beautiful maps programmatically with R, sf and ggplot2 — Part 2: Layers](https://www.r-spatial.org/r/2018/10/25/ggplot2-sf-2.html)
* [rspatial - Drawing beautiful maps programmatically with R, sf and ggplot2 — Part 3: Layouts](https://www.r-spatial.org/r/2018/10/25/ggplot2-sf-3.html)

```{r}
ggplot(data=brne) + geom_sf()
```

Join region info from `capital.coords.raw` info onto the `brne` object

```{r}
brne <- brne %>% 
  select(-region) %>%
  left_join(capital.coords %>% select(postal=state_abbrev, region)) 
```

```{r}
# for removing the background from ggplots
remove_background <- theme(panel.background = element_blank(),
          panel.border = element_blank(),
          panel.grid.major = element_blank(),
          axis.ticks.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.y = element_blank(),
          axis.text.y = element_blank()) 
```

```{r}
region_map <- 
  ggplot(data=brne) + 
    geom_sf(aes(fill=region), linetype=2) +
    #scale_fill_viridis_d(name='Region') +
    #scale_fill_brewer(palette = "Set3") +
    scale_fill_brewer(palette = map_pal) +
    guides(fill = guide_legend("Region")) +
    remove_background

region_map
```

```{r, fig.width=6, fig.height=6}
sample_map <- 
  ggplot(data=brne) + 
    theme_bw(base_size=5) +
    geom_sf(aes(fill=region), 
            linetype='dotted', 
            alpha=.8) +
    #scale_fill_viridis_d(name='Region') +
    #scale_fill_brewer(palette = "Set3") +
    scale_fill_brewer(palette = map_pal) +
    remove_background +
  geom_sf(data=capitals) +
  geom_text_repel(data=capitals,
                  aes(x=lon, y=lat, 
                      label=glue::glue("{municipio} ({state_abbrev})")),
                  size=rel(3)) +
                      #label=city_state_label)) +
  xlab('') + ylab('') +
  guides(fill=guide_legend("Region",
                           override.aes=list(linetype=0))) +
  #theme(legend.position='bottom',
  #      legend.direction='horizontal',
  theme(legend.position=c(.2,.3),
        legend.direction='vertical',
        legend.text=element_text(size=8),
        legend.title=element_text(size=8, face='bold')) +
  NULL

ggsave(filename=file.path(out_dir, "sample_map.pdf"),
       plot=sample_map,
       height=6,
       width=6)
  
sample_map
```

# Make a hexgrid showing states/cities

See the geogrid package:
https://github.com/jbaileyh/geogrid

NB: this code causes some warnings - we don't need to worry about these

```{r}
cur.hex.seed <- 99 
new_cells_hex <- geogrid::calculate_grid(shape = brne, grid_type='hexagonal', seed=cur.hex.seed)
br_state_hexgrid <- geogrid::assign_polygons(brne, new_cells_hex)

# adding a small buffer seems to fix the fact that the hex tiles don't
# completely overlap
eps_buffer <- .001
br_state_hexgrid <- st_buffer(br_state_hexgrid, eps_buffer)
```

```{r, fig.width=6, fig.height=6}
sample_hexmap <- ggplot(data=br_state_hexgrid) + 
    theme_bw(base_size=5) +
    geom_sf(aes(fill=region), 
            linetype='dotted', 
            alpha=.8) +
    #scale_fill_brewer(palette = "Set3") +
    scale_fill_brewer(palette = map_pal) +
    remove_background +
    geom_text(aes(label=postal,
                  x=V1, y=V2)) +
  xlab('') + ylab('') +
  guides(fill=guide_legend("Region",
                           override.aes=list(linetype=0))) +
  theme(legend.position=c(.2,.3),
        legend.direction='vertical',
        legend.text=element_text(size=8),
        legend.title=element_text(size=8, face='bold')) +
  NULL

ggsave(filename=file.path(out_dir, "sample_hexmap.pdf"),
       plot=sample_hexmap,
       height=6,
       width=6)
ggsave(filename=file.path(out_dir, "sample_hexmap.png"),
       plot=sample_hexmap,
       height=6,
       width=6)
  
sample_hexmap
```

Get hexmap of regions

```{r}
br_hexgrid_outline <- st_union(br_state_hexgrid) 

br_region_hexgrid <- br_state_hexgrid %>%
  group_by(region) %>%
  summarize(geometry = st_union(geometry))
```

```{r}
sample_hex_dim <- 4

sample_region_hexmap <- ggplot(data=br_region_hexgrid) + 
    theme_bw(base_size=5) +
    geom_sf(aes(fill=region), 
            linetype='solid', 
            alpha=.8) +
    #scale_fill_brewer(palette = "Set3") +
    scale_fill_brewer(palette = map_pal) +
    # uncomment to get faint lines along state hex boundaries
    #geom_sf(aes(fill=NA),
    #        alpha=.1,
    #        data=br_state_hexgrid) +
    remove_background +
    geom_text(aes(label=postal,
                  x=V1, y=V2),
              data=br_state_hexgrid) +
  xlab('') + ylab('') +
  guides(fill=guide_legend("Region",
                           override.aes=list(linetype=0))) +
  theme(legend.position=c(.2,.3),
        legend.direction='vertical',
        legend.text=element_text(size=8),
        legend.title=element_text(size=8, face='bold')) +
  NULL

ggsave(filename=file.path(out_dir, "sample_region_hexmap.pdf"),
       plot=sample_region_hexmap,
       height=sample_hex_dim,
       width=sample_hex_dim)
ggsave(filename=file.path(out_dir, "sample_region_hexmap.png"),
       plot=sample_region_hexmap,
       height=sample_hex_dim,
       width=sample_hex_dim)
  
sample_region_hexmap
```





```{r}
saveRDS(list(map=brne, 
             capitals=capitals, 
             hexmap=br_state_hexgrid, 
             hexmap_region=br_region_hexgrid),
        file.path(out_dir, "brazil_map.rds"))
```


