---
title: "VR completeness"
output:
  html_document:
    df_print: paged
---

This file summarizes the estimated vital registration completeness by city.
It saves its results to `out/`

```{r}
knitr::opts_chunk$set(message=FALSE)
library(tidyverse)
library(here)
library(janitor)
library(readxl)
```

```{r}
out_dir <- here("out") 
data_dir <- here("data") 
cap_recap_dir <- file.path(data_dir, "ibge-capture-recapture")
```

```{r}
capital.coords <- read_csv(file.path(data_dir, "cities.csv"))

capital.coords
```

Read in the files w/ the results of the capture-recapture studies

```{r}

cr_res <- map_dfr(2015:2017,
                  function(year) {
                    res <- read_xlsx(file.path(cap_recap_dir, paste(year), '02obitos', 'Tabela 2.2.xlsx'),
                                        skip=1) %>%
                      janitor::clean_names()
                    
                    res <- res %>%
                      filter(codigo_municipio %in% capital.coords$municipio_code) %>%
                      mutate(year = year)
                    
                    return(res)
                  })


cr_res
```


```{r}
cr_res_avg <- cr_res %>%
  mutate(municipio_code = codigo_municipio,
         state_name = nome_uf_2,
         city_name = nome_uf_4) %>%
  group_by(municipio_code, city_name, state_name) %>%
  dplyr::summarize(mean_sim_underest_pct = mean(sub_notificacao_ms_percent),
            mean_ibge_underest_pct = mean(sub_registro_ibge_1_percent)) %>%
  ungroup() %>%
  mutate(mean_sim_cov_pct = 100 - mean_sim_underest_pct)

cr_res_avg %>% 
  select(municipio_code, city_name, state_name, 
         mean_sim_underest_pct, mean_sim_cov_pct, everything()) %>%
  arrange(desc(mean_sim_underest_pct))
```

Three cities have an average estimated undercount (from 2015, 2016, 2017) of more
than four percent:

San Luis, Maranhao (94\% coverage, MA in NE);
Salvador, Bahia (95\% coverage BA in NE);
and Macapa, Amapa (96\% coverage, AP in NO)

Save the results to a table that we can include in the pre-registration document

```{r}
cr_res_tbl <- cr_res_avg %>%
    left_join(capital.coords %>% select(municipio_code, state_abbrev, region)) %>%
    select(region, state_abbrev, state_name, city_name,  mean_sim_cov_pct) %>%
    #mutate(mean_sim_cov_pct = round(mean_sim_cov_pct, 1)) %>%
    arrange(desc(mean_sim_cov_pct))

write_csv(cr_res_tbl,
          path=file.path(out_dir, 'vr_completeness_estimates.csv'))
```

```{r}
vr.table.rendered <- pander::pandoc.table.return(cr_res_tbl,
               col.names = c('Region', 'State\ncode', 'State\nname', 'City', 'Estimated\ncompleteness of\ndeath registration\n(%)'),
               big.mark=',',
               round=2,
               keep.trailing.zeros=TRUE,
               split.cells=c(1, 1, 25, 25, 15),
               split.table=Inf,
               justify=c('center', 'center', 'left', 'left', 'right'),
               caption="(\\#tab:vrcompleteness) Estimated completeness of death registration at all ages and for both sexes in each of the 27 cities in our sample.")

cat(vr.table.rendered,
    file=file.path(out_dir, 'vr_completeness_estimates.md'))
cat(vr.table.rendered)
```

NB: this is the same conclusion we'd reach by just looking at the 2015 data

```{r}
cr_res_2015 <- cr_res %>%
  filter(year==2015) %>%
  select(year,
         municipio_code = codigo_municipio,
         city_name = nome_uf_4,
         state_name = nome_uf_2,
         sim_underest_pct = sub_notificacao_ms_percent,
         ibge_underest_pct = sub_registro_ibge_1_percent)

cr_res_2015 %>% arrange(desc(sim_underest_pct))
```


