---
title: "VR completeness"
output:
  html_document:
    df_print: paged
---

This file summarizes the estimated vital registration completeness by city.
It saves its results to `out/`

```{r}
knitr::opts_chunk$set(message=FALSE)
library(tidyverse)
library(here)
library(janitor)
library(readxl)
```

```{r}
out_dir <- here("out") 
data_dir <- here("data") 
cap_recap_dir <- file.path(data_dir, "ibge-capture-recapture")
survey_data_dir <- file.path(data_dir, 'survey')
```

```{r}
capital.coords <- read_csv(file.path(data_dir, "cities.csv"))

capital.coords
```

Read in the files w/ the results of the capture-recapture studies

```{r}

cr_res <- map_dfr(2015:2017,
                  function(year) {
                    res <- read_xlsx(file.path(cap_recap_dir, paste(year), '02obitos', 'Tabela 2.2.xlsx'),
                                        skip=1) %>%
                      janitor::clean_names()
                    
                    res <- res %>%
                      filter(codigo_municipio %in% capital.coords$municipio_code) %>%
                      mutate(year = year)
                    
                    return(res)
                  })


cr_res
```


```{r}
cr_res_avg <- cr_res %>%
  mutate(municipio_code = codigo_municipio,
         state_name = nome_uf_2,
         city_name = nome_uf_4) %>%
  group_by(municipio_code, city_name, state_name) %>%
  dplyr::summarize(mean_sim_underest_pct = mean(sub_notificacao_ms_percent),
            mean_ibge_underest_pct = mean(sub_registro_ibge_1_percent)) %>%
  ungroup() %>%
  mutate(mean_sim_cov_pct = 100 - mean_sim_underest_pct)

cr_res_avg %>% 
  select(municipio_code, city_name, state_name, 
         mean_sim_underest_pct, mean_sim_cov_pct, everything()) %>%
  arrange(desc(mean_sim_underest_pct))
```

Three cities have an average estimated undercount (from 2015, 2016, 2017) of more
than four percent:

San Luis, Maranhao (94\% coverage, MA in NE);
Salvador, Bahia (95\% coverage BA in NE);
and Macapa, Amapa (96\% coverage, AP in NO)

Save the results to a table 

```{r}
cr_res_tbl <- cr_res_avg %>%
    left_join(capital.coords %>% select(municipio_code, state_abbrev, region)) %>%
    select(region, state_abbrev, state_name, city_name,  mean_sim_cov_pct) %>%
    arrange(desc(mean_sim_cov_pct))

write_csv(cr_res_tbl,
          path=file.path(out_dir, 'vr_completeness_estimates.csv'))
```

```{r}
vr.table.rendered <- pander::pandoc.table.return(cr_res_tbl,
               col.names = c('Region', 'State\ncode', 'State\nname', 'City', 'Estimated\ncompleteness of\ndeath registration\n(%)'),
               big.mark=',',
               round=2,
               keep.trailing.zeros=TRUE,
               split.cells=c(1, 1, 25, 25, 15),
               split.table=Inf,
               justify=c('center', 'center', 'left', 'left', 'right'),
               caption="(\\#tab:vrcompleteness) Estimated completeness of death registration at all ages and for both sexes in each of the 27 cities in our sample.")

cat(vr.table.rendered,
    file=file.path(out_dir, 'vr_completeness_estimates.md'))
cat(vr.table.rendered)
```

Calculate median level of completeness for the text

```{r}
median_completeness <- quantile(cr_res_tbl$mean_sim_cov_pct, 0.5)
glue::glue("Median level of completeness: {median_completeness}")
```


NB: this is the same conclusion we'd reach by just looking at the 2015 data

```{r}
cr_res_2015 <- cr_res %>%
  filter(year==2015) %>%
  select(year,
         municipio_code = codigo_municipio,
         city_name = nome_uf_4,
         state_name = nome_uf_2,
         sim_underest_pct = sub_notificacao_ms_percent,
         ibge_underest_pct = sub_registro_ibge_1_percent)

cr_res_2015 %>% arrange(desc(sim_underest_pct))
```



## Table with sample size, response rate, and VR completeness 

These are the response rates (pasted in from code that works on the identifiable data, which
we can't release; I just copied that data frame)

```{r}
rr_dat <- structure(
  list(
    state = c("AC","AL","AM","AP","BA","CE","DF","ES","GO","MA",
              "MG","MS","MT","PA","PB","PE","PI","PR","RJ","RN",
              "RO","RR","RS","SC","SE","SP","TO"),
    RR_I = c(0.99,0.94,1.00,0.96,0.94,0.93,0.94,1.00,0.99,1.00,
             1.00,1.00,0.99,0.98,0.99,0.95,0.99,1.00,0.85,0.97,
             0.98,0.96,0.94,1.00,1.00,1.00,0.99),
    RR_II_III = c(0.55,0.63,0.80,0.75,0.50,0.52,0.54,0.40,0.72,0.70,
                  0.54,0.82,0.67,0.73,0.66,0.60,0.42,0.46,0.26,0.60,
                  0.64,0.73,0.32,0.71,0.67,0.51,0.80)
  ),
  class = "data.frame",
  row.names = c(NA, -27L)
)
```

Open up the individual survey datafile

```{r}
# load individual data
ind.dat <- read_csv(file.path(survey_data_dir, "individual.csv"))
```


Make a table with the sample size for each city

```{r}
sampsize.table <- ind.dat %>%
  group_by(state_abbrev) %>%
  summarize(num_interviews = n()) %>%
  left_join(capital.coords %>%
              select(state_abbrev, state_name, region, city_name=municipio),
            by='state_abbrev') %>%
  left_join(rr_dat %>%
              # have the response rates print nicely
              mutate(
                RR_I      = sprintf("%.2f", RR_I),
                RR_II_III = sprintf("%.2f", RR_II_III)
              ), 
    by=c('state_abbrev'='state')) %>%
  left_join(
    cr_res_tbl %>% 
      mutate(vr_completeness = sprintf('%.2f', round(mean_sim_cov_pct,2))) %>%
      select(state_abbrev, vr_completeness),
    by='state_abbrev',
  ) %>%
  #select(region, state_abbrev, state_name, city_name, num_interviews)
  select(region, state_abbrev, city_name, num_interviews, RR_I, RR_II_III, vr_completeness)

sampsize.table
```

```{r}
sampsize.table.rendered <- pander::pandoc.table.return(sampsize.table,
               #col.names = c('Region', 'State\ncode', 'State\nname', 'City', 'Number of\nInterviews'),
               col.names = c('Region', 'State\ncode', 'City', 'Number of\nInterviews', '$\\text{RR\n}_{I}$', '$\\text{RR}_{\nII/III}$', 'Estimated VR\nCompleteness (%)'),
               big.mark=',',
               split.cells=c(1, 1, 17, 12, 8, 6, 22),
               split.table=Inf,
               justify=c('center', 'center', 'left', 'right', 'right', 'right', 'right'),
               caption="(\\#tab:sampsize) Number of interviews conducted, response rates, and estimated vital registration completeness (IBGE 2018) for each of the 27 cities in our sample.")

cat(sampsize.table.rendered,
    file=file.path(out_dir, 'sample_size_table.md'))
cat(sampsize.table.rendered)
```
