---
title: "Calculate death rates from VR data"
output: html_notebook
---

This file calculates death rates for each city based on the vital registration data.

All output gets saved to `data/vr_prepped`.

```{r}
library(tidyverse)
library(here)

#devtools::install_github("tbrugz/ribge")
library(ribge)
```

```{r}
data_dir <- here("data")

popn_data_dir <- file.path(data_dir, "vr", "popn")
death_data_dir <- file.path(data_dir, "vr", "deaths")

out_dir <- here("out")
data_out_dir <- file.path(data_dir, "vr_prepped")
```

# Denominator: city populations

Grabbed tabwin files in popn/tabwin from this site:

http://tabnet.datasus.gov.br/cgi/deftohtm.exe?ibge/cnv/popbr.def


Using web interface to get data for 2012, I selected
* Linha - 'Municipio'; Colunha - 'Faixa Etaria detalhada'; Sexo - 'Masculino'
  -> it displays a table and, at the bottom, I picked 'save as .csv' -> saved as 'raw_popn_municipio_m.csv'
* I did the same for Sexo - 'Feminino' and for Sexo - 'Todas as categorias'

* editing raw files to remove header and footer info; notes at bottom of page say source is "2011-2012: IBGE - Estimativas populacionais enviadas para o TCU, estratificadas por idade e sexo pelo MS/SGEP/Datasus."

* municipio_popn_m.csv - results for males
* municipio_popn_f.csv - results for females
* municipio_popn_both.csv - results for all sexes
* note that the tool lets you query for un-specified sex ('ignorado'), but when I did that search, it said 'no records found'; we can double-check that there are no missing sex people by verifying that the number male + number female = number both

the legend at the bottom of the results page says:

    Para alguns anos, os dados aqui apresentados não são comparáveis com as estimativas populacionais fornecidas ao TCU, devido a diferenças metodológicas para estimar e projetar os contingentes populacionais. Veja a nota técnica para detalhes da metodologia.
    Legenda:

    -   - Dado numérico igual a 0 não resultante de arredondamento.
    0; 0,0      - Dado numérico igual a 0 resultante de arredondamento de um dado originalmente positivo.

I believe that means that '-' is an actual 0, while 0 or 0,0 are 0s that result from rounding




First get info on the cities in our sample

```{r}
city.dat <- read_csv(file.path(data_dir, "cities.csv"))
```


These will be helpful when recoding age groups, below

```{r}
under20_agenames <- paste(2:19, 'anos')
recode_under20 <- setNames(c(rep('[0,18)', 18),
                             '[18,25)', '[18,25)'),
                           c('Menor 1 ano', '1 ano', under20_agenames))

older_agenames <- c(paste(c('20 a 24', 
                            '25 a 29', '30 a 34', 
                            '35 a 39', '40 a 44',
                            '45 a 49', '50 a 54',
                            '55 a 59', '60 a 64',
                            '65 a 69', '70 a 74',
                            '75 a 79'),
                          'anos'),
                    '80 anos e mais')
recode_over20 <- setNames(c('[18,25)', 
                            '[25,35)', '[25,35)', 
                            '[35,45)', '[35,45)',
                            '[45,55)', '[45,55)',
                            '[55,65)', '[55,65)',
                            '[65,Inf)', '[65,Inf)',
                            '[65,Inf)',
                            '[65,Inf)'),
                          older_agenames)
```

Now load data from tabwin: first females

```{r}
munipop12_f <- read_delim(file.path(popn_data_dir, "municipio_popn_f.csv"),
                          delim=";",
                          locale=locale(encoding='latin1'))
munipop12_f <- munipop12_f %>%
  pivot_longer(-1, names_to='age', values_to='popn') %>%
  mutate(municipio_code = str_sub(Município, 1, 6),
         municipio_name = str_sub(Município, 8, -1)) %>%
  select(-Município) %>%
  mutate(agegp = dplyr::recode(age,
                               !!!recode_under20,
                               !!!recode_over20)) %>%
  group_by(municipio_name, municipio_code, agegp) %>%
  summarize(popn = sum(popn)) %>%
  mutate(sex='f')

munipop12_f
```

... then males

```{r}
munipop12_m <- read_delim(file.path(popn_data_dir, "municipio_popn_m.csv"),
                          delim=";",
                          locale=locale(encoding='latin1'))
munipop12_m <- munipop12_m %>%
  pivot_longer(-1, names_to='age', values_to='popn') %>%
  mutate(municipio_code = str_sub(Município, 1, 6),
         municipio_name = str_sub(Município, 8, -1)) %>%
  select(-Município) %>%
  mutate(agegp = dplyr::recode(age,
                               !!!recode_under20,
                               !!!recode_over20)) %>%
  group_by(municipio_name, municipio_code, agegp) %>%
  summarize(popn = sum(popn)) %>%
  mutate(sex='m')

munipop12_m
```


... and finally both

```{r}
munipop12_b <- read_delim(file.path(popn_data_dir, "municipio_popn_both.csv"),
                          delim=";",
                          locale=locale(encoding='latin1'))
munipop12_b <- munipop12_b %>%
  pivot_longer(-1, names_to='age', values_to='popn') %>%
  mutate(municipio_code = str_sub(Município, 1, 6),
         municipio_name = str_sub(Município, 8, -1)) %>%
  select(-Município) %>%
  mutate(agegp = dplyr::recode(age,
                               !!!recode_under20,
                               !!!recode_over20)) %>%
  group_by(municipio_name, municipio_code, agegp) %>%
  summarize(popn = sum(popn)) %>%
  mutate(sex='b')

munipop12_b
```

Next:

* filter to municipios we care about
* check that m+f=b

```{r}
munipop12 <- bind_rows(munipop12_f, munipop12_m, munipop12_b) %>%
  filter(municipio_code %in% city.dat$municipio_code)

munipop12
```

```{r}
munipop12_check <- munipop12 %>%
  pivot_wider(id_cols = c('municipio_name', 'municipio_code', 'agegp'),
              names_from='sex',
              values_from='popn')

munipop12_check
```

Looks good:

```{r}
all(munipop12_check$f + munipop12_check$m == munipop12_check$b)
```

```{r save-city-popns}
munipop12_tosave <- munipop12 %>% filter(sex %in% c('f', 'm'),
                                         ! agegp %in% c('[65,Inf)', '[0,18)', 'Total'))

#write_csv(munipop12_tosave, path=file.path(data_out_dir, 'dr_denom.csv'))

munipop12_tosave
```


### check municipio totals using ribge package {-}

[ribge github page](https://github.com/tbrugz/ribge)


```{r}
ribge_pop2012 <- ribge::populacao_municipios(2012, dir=data_out_dir)
```

```{r}
check_ribge <- munipop12_b %>% 
  ungroup() %>%
  filter(municipio_code != 'Total') %>%
  filter(agegp == 'Total') %>%
  left_join(ribge_pop2012 %>%
              mutate(municipio_code = paste(cod_munic6),
                     ribge_popn = populacao) %>%
              select(municipio_code, ribge_popn), 
            by='municipio_code')

check_ribge
```

```{r}
all(check_ribge$popn == check_ribge$ribge_popn)
```

```{r}
check_ribge %>% filter(popn != ribge_popn)
```

These only differ in two municipalities, and we don't care about these. So we're good.

# Numerator: city resident deaths

I went to [this page](http://www2.datasus.gov.br/DATASUS/index.php?area=0901) and selected 'SIM'.
Then I picked 'Dados'.
... and then "DO - Declaracoes de obitos - 1979 a 2018"
... I picked years 2011 - 2013
... and I selected all of the states
... and pushed go
I got a list of files, and I checked "Marcar Todos"
... this was ~235 MB. I said "download"
... and I downloaded them to Arq_333368978.zip

```{r}
# this has 2012 only
#death_archive_fn <- 'Arq_984437380'

# this has 2011-2013
death_archive_fn <- 'Arq_333368978'

raw_ddata_dir <- file.path(death_data_dir, death_archive_fn)
out_ddata_dir <- file.path(data_out_dir, "processed")
```

```{r}
cur_state <- 'AC'
cur_year <- '2012'

cur_dat <- read.dbc::read.dbc(file.path(raw_ddata_dir, 
                                        paste0('DO', cur_state, cur_year, '.DBC')))

glimpse(cur_dat)
```

```{r}
##################################################
## helper fns for some of the recodes...
## returns age in years (possibly fractional)
recode.age <- function(raw.age, max.age) {
  age <- rep(NA, length(raw.age))
  
  unit_field <- as.numeric(str_sub(raw.age, 1, 1))
  info_field <- as.numeric(str_sub(raw.age, 2, 4))
  
  ## unit_field == 0 -- 0 hours or info_field has age in minutes
  uf0 <- which(unit_field == 0)
  uf0and0 <- which(info_field == 0 & info_field == 0)
  
  # any age coded in minutes is 0 years for our purposes
  age[uf0] <- 0  
  # exception: 000 means 'idage ignorada'
  age[uf0and0] <- NA
  
  ## unit_field == 1 -- info_field has age in hours
  uf1 <- which(unit_field == 1)
  # any age coded in hours is 0 years for our purposes
  age[uf1] <- 0
  
  ## unit_field == 2 -- info_field has age in days
  uf2 <- which(unit_field == 2)
  # any age coded in days is 0 years for our purposes
  age[uf2] <- 0
  
  ## unit_field == 3 -- info_field has age in months
  uf3 <- which(unit_field == 3)
  # any age coded in months is 0 years for our purposes
  age[uf3] <- 0
  
  ## unit_field == 4 -- info_field has age in years
  uf4 <- which(unit_field == 4)
  age[uf4] <- info_field[uf4]
  
  ## unit_field == 5 -- info_field has age in years - 100
  uf5 <- which(unit_field == 5)
  age[uf5] <- info_field[uf5] + 100
  
  ## NOT COVERED IN CODE BOOK, but there are 999 values in the data
  ## by ignoring these, we assume they are missing (which seems appropriate)
  
  ## recode ages greater than max to max
  age[(! is.na(age)) & (age > max.age)] <- max.age
  
  return(age)
}

## 1 is male, 2 is female, and 0 is DK
recode.sex <- function(raw.sex) {
  sex <- rep('unknown', length(raw.sex))
  sex[ raw.sex == 1 ] <- "m"
  sex[ raw.sex == 2 ] <- "f"

  return(sex)
}
```

```{r}
years <- 2011:2013
#years <- 1996:2010
max.age <- 100

## age categories
## (these are the age categories available in the popn data...)
#age.breaks <- c(seq(from=0,to=80,by=5),max.age)
age.breaks <- c(0, 18, 25, seq(from=35,to=80,by=10), max.age)
# check age breaks
tmp <- cut(1, breaks=age.breaks, right=FALSE, ordered_result=TRUE)

agg.longres <- c()
agg.longocc <- c()

cityyr_todo <- expand.grid(this.yr=years,
                           state.idx=city.dat$state_abbrev)

##################################################
## now we want to open up each dbf file
## and get tallies of the deaths by
## age and sex (including unknown...)
agg_deaths <- pmap_dfr(cityyr_todo,
                       function(this.yr, state.idx) {
  
        this.state <- city.dat$state_abbrev[state.idx]

        this.capital <- city.dat$municipio_code[state.idx]

        cat(".......", this.state, "\n")

        # 2013 has lowercase extension (".dbc") while other years
        # have uppercase extension (".DBC")
        if (this.yr == 2013) {
          this.file <- path.expand(file.path(raw_ddata_dir,
                                             paste0("DO",
                                                    this.state,
                                                    this.yr,
                                                    ".dbc")))
        } else {
          this.file <- path.expand(file.path(raw_ddata_dir,
                                             paste0("DO",
                                                    this.state,
                                                    this.yr,
                                                    ".DBC")))
        }

        this.dbf <- read.dbc::read.dbc(this.file)

        if (any(is.na(this.dbf$CODMUNRES))) {
          warning("WARNING: ", sum(is.na(this.dbf$CODMUNRES)), " of ",
                  nrow(this.dbf), " rows in ", this.state, " have missing ",
                  "place of residence!\n")          
        }

        this.dbf$age <- recode.age(this.dbf$IDADE, max.age=max.age-1)
        this.dbf$sex <- recode.sex(this.dbf$SEXO)

        this.dbf$agecat <- paste(forcats::fct_explicit_na(cut(this.dbf$age,
                                                              breaks=age.breaks,
                                                              right=FALSE,
                                                              ordered_result=TRUE),
                                                          na_level='unknown'))

        ## DATSUS files appear to use the 7 digit municipio codes
        this.dbf$place.residence <- this.dbf$CODMUNRES
        this.dbf$place.death <- this.dbf$CODMUNOCOR

        this.dbf$death.day <- str_sub(this.dbf$DTOBITO,
                                      1, 2)
        this.dbf$death.month <- str_sub(this.dbf$DTOBITO,
                                        3,4)
        this.dbf$death.year <- str_sub(this.dbf$DTOBITO,
                                       5,8)
        
        deaths.capres <- subset(this.dbf,
                                place.residence == paste(this.capital))
        deaths.capocc <- subset(this.dbf,
                                place.death == paste(this.capital))        
        
        this.dbf.agg.res <- deaths.capres %>%
          group_by(sex, agecat, death.year) %>%
          summarize(num_deaths = n(), .groups='drop') %>%
          mutate(city = paste(this.capital),
                 year = this.yr) %>%
          ungroup()

        this.dbf.agg.occ <- deaths.capocc %>%
          group_by(sex, agecat, death.year) %>%
          summarize(num_deaths = n(), .groups='drop') %>%
          mutate(city = paste(this.capital),
                 year = this.yr) %>%
          ungroup()
        
        return(tibble(city = paste(this.capital),
                      year = this.yr,
                      deaths_by_residence  = list(this.dbf.agg.res),
                      deaths_by_occurrence = list(this.dbf.agg.occ)))
        
        })
```


```{r}
agg_deaths_by_residence <- map_dfr(agg_deaths %>% pull(deaths_by_residence), identity) %>%
  mutate(municipio_code=as.numeric(city)) %>%
  left_join(city.dat %>% select(municipio_code, state_abbrev))

#write.csv(agg_deaths_by_residence,
#          file=file.path(data_out_dir, "deaths_by_residence_raw.csv"))

agg_deaths_by_residence
```

How many deaths are missing age?

```{r}
pct_miss_age_res <- agg_deaths_by_residence %>%
  mutate(is_unk = as.numeric(agecat=='unknown')) %>%
  group_by(state_abbrev, year) %>%
  summarize(tot_deaths = sum(num_deaths),
            num_unk = sum(num_deaths * is_unk)) %>%
  mutate(pct_unk = 100 * (num_unk / tot_deaths)) %>%
  pivot_wider(id_cols = c('state_abbrev'),
              names_from='year',
              values_from='pct_unk',
              names_prefix='pct_unk_age_')

pct_miss_age_res
```

How many deaths are missing sex?

```{r}
agg_deaths_by_residence %>%
  #mutate(is_unk = as.numeric(is.na(sex))) %>%
  mutate(is_unk = as.numeric(sex=='unknown')) %>%
  group_by(state_abbrev, year) %>%
  summarize(tot_deaths = sum(num_deaths),
            num_unk = sum(num_deaths * is_unk)) %>%
  mutate(pct_unk = 100 * (num_unk / tot_deaths)) %>%
  pivot_wider(id_cols = c('state_abbrev'),
              names_from='year',
              values_from='pct_unk',
              names_prefix='pct_unk_sex_')
```

### Redistribute missing deaths

```{r}
ad2012 <-
  agg_deaths_by_residence %>%
  filter(death.year == '2012') %>%
  select(state_abbrev, sex, agecat, num_deaths_raw=num_deaths) %>%
  mutate(unk_age = as.numeric(agecat == 'unknown'),
         unk_sex = as.numeric(sex == 'unknown'),
         obs = as.numeric(agecat != 'unknown' & sex != 'unknown'))

ad2012_total_deaths <- ad2012 %>%
  group_by(state_abbrev) %>%
  summarize(tot_deaths = sum(num_deaths_raw),
            num_miss_agesex = sum(unk_age*unk_sex*num_deaths_raw))

ad2012 %>%
  group_by(state_abbrev,sex) %>%
  summarize(num_unk_age = sum(unk_age * num_deaths_raw))

ad2012 %>%
  group_by(state_abbrev,agecat) %>%
  summarize(num_unk_sex = sum(unk_sex * num_deaths_raw))

ad2012 %>%
  group_by(state_abbrev) %>%
  summarize(num_unk_both = sum(unk_sex * unk_age *num_deaths_raw))
```

Idea: redistribute in situations where we have the most specific information first

We will use some notation to describe what's going on here. In a given city, say

* $d^0_{a,m}$ - raw deaths to age $a$ among males
* $d^0_{a,f}$ - raw deaths to age $a$ among females
* $d^0_{a,u}$ - raw deaths to age $a$ among unknown
* $d^0_{u,m}$ - raw deaths among males of unknown age
* $d^0_{u,f}$ - raw deaths among females of unknown age
* $d^0_{u,u}$ - raw deaths among people of unknown gender and unknown age

**Step 1: redistribute deaths that have age but no sex equally across sexes within each age group**

Within each city and age group $a$, we calculate a weight factor for step 1, $w^0_a$:

$$
w^0_a = \frac{(d^0_{a,m} + d^0_{a,f} + d^0_{a,u})}{(d^0_{a,m} + d^0_{a,f})}.
$$

Then we'll set $d^1_{a,m} = w^0_{a} d^0_{a,m}$ and $d^1_{a,f} = w^0_a d^0_{a,f}$.
We do not change $d^0_{u,u}$, $d^0_{u,m}$ or $d^0_{u,f}$.

```{r}
# redistribute a vector proportionally, assuming that
# the last entry is the missing values
redistribute <- function(vec, labels, miss_val = 'unknown') {
  
  missidx <- which(labels == miss_val)
  
  if (length(missidx) == 0) {
    return(vec)
  } 
  
  w <- sum(vec) / sum(vec[-missidx])
  
  res <- vec
  res[-missidx] <- vec[-missidx]*w
  res[missidx] <- NA
  
  return(res)
}

```

```{r}
ad2012_step1 <- 
  ad2012 %>%
  # we won't handle deaths missing both age and sex yet
  filter(! (unk_age*unk_sex)) %>%
  group_by(state_abbrev, agecat) %>%
  mutate(num_deaths_step1 = redistribute(num_deaths_raw, sex)) %>%
  ungroup() 
  
ad2012_step1 %>%
  arrange(state_abbrev, agecat, sex)
```


**Step 2: redistribute deaths that have sex but no age equally across all age groups**

Within each city and age group $a$, we calculate a weight factor for step 1, $w^0_a$:

$$
w^0_a = \frac{(d^0_{a,m} + d^0_{a,f} + d^0_{a,u})}{(d^0_{a,m} + d^0_{a,f})}.
$$

Then we'll set $d^1_{a,m} = w^0_{a} d^0_{a,m}$ and $d^1_{a,f} = w^0_a d^0_{a,f}$.
We do not change $d^0_{u,u}$, $d^0_{u,m}$ or $d^0_{u,f}$.


```{r}
ad2012_step2 <-
  ad2012_step1 %>%
  filter(! is.na(num_deaths_step1)) %>%
  group_by(state_abbrev, sex) %>%
  mutate(num_deaths_step2 = redistribute(num_deaths_step1, agecat)) %>%
  ungroup() 

ad2012_step2
```

**Step 3: redistribute deaths that have no age or sex equally across all age sex groups**

```{r}
ad2012_redist_fact <-
  ad2012_step2 %>%
  filter(! is.na(num_deaths_step2)) %>%
  group_by(state_abbrev) %>%
  summarize(tot_deaths_step2 = sum(num_deaths_step2)) %>%
  left_join(ad2012_total_deaths, by='state_abbrev') %>%
  mutate(wboth = (tot_deaths_step2 + num_miss_agesex)/tot_deaths_step2)

# this checks out
#with(ad2012_redist_fact, all(tot_deaths_step2 + num_miss_agesex == tot_deaths))
#with(ad2012_redist_fact, which(tot_deaths_step2 + num_miss_agesex != tot_deaths))
#with(ad2012_redist_fact, tot_deaths_step2 + num_miss_agesex - tot_deaths)

ad2012_redist_fact
```

```{r}
ad2012_redist <- ad2012_step2 %>%
  filter(! is.na(num_deaths_step2)) %>%
  left_join(ad2012_redist_fact %>% select(state_abbrev, wboth)) %>%
  mutate(num_deaths = num_deaths_step2 * wboth)

ad2012_redist
```

Confirm no more missing levels

```{r}
with(ad2012_redist, table(sex, useNA='ifany'))
with(ad2012_redist, table(agecat, useNA='ifany'))
```


```{r}
chk <- ad2012_redist %>%
  group_by(state_abbrev) %>%
  summarize(tot_deaths_chk = sum(num_deaths)) %>%
  left_join(ad2012_total_deaths %>% select(state_abbrev, tot_deaths))

# these are all the same (they don't pass the 'all equal' test because of a very tiny floating point value that must be rounding error)
with(chk, max(abs(tot_deaths_chk - tot_deaths)))

chk
```

```{r}
ad2012_fornum <- ad2012_redist %>% select(state_abbrev, sex, agecat, num_deaths)
ad2012_fornum
```

## City death rates

```{r}
city.asdr <- munipop12_tosave %>%
  mutate(municipio_code = paste(municipio_code)) %>%
  left_join(city.dat %>% 
              mutate(municipio_code = paste(municipio_code)) %>%
              select(municipio_code, state_abbrev, region)) %>%
  left_join(ad2012_fornum %>% 
              filter(! agecat %in% c('[0,18)', '[65,75)', '[75,100]')) %>%
              rename(agegp=agecat), 
            by=c('state_abbrev', 'sex', 'agegp')) %>%
  mutate(asdr = num_deaths / popn,
         sex = case_when(sex == 'f' ~ 'Female',
                         sex == 'm' ~ 'Male')) %>%
  rename(agegp10=agegp)

city.asdr
```

```{r calculate-ffqf}
city.47q18 <- city.asdr %>%
  filter(agegp10 %in% c('[18,25)', '[25,35)', '[35,45)', '[45,55)', '[55,65)')) %>%
  mutate(width = ifelse(agegp10 == '[18,25)',
                        7,
                        10)) %>%
  mutate(const.mx.p = exp(-width*asdr),
         v2.mx.p = 1 - (width*asdr)/(1 + (width/2)*asdr)) %>%
  group_by(state_abbrev, sex) %>%
  summarize(q.47.18 = 1 - prod(const.mx.p),
            q.47.18.alt = 1 - prod(v2.mx.p))

city.47q18
```


Double-check that it does not make a big difference how we calculate prob
(Doesn't look like it does: mean relative difference is around 0.06%)

```{r check-ffqf-assumptions}
city.47q18.check <- city.47q18 %>%
  group_by(state_abbrev, sex) %>%
  mutate(rel_diff = (q.47.18.alt - q.47.18) / q.47.18)

summary(city.47q18.check$rel_diff)
```

## Regional death rates


```{r}
region.asdr <-
  city.asdr %>%
  group_by(region, agegp10, sex) %>%
  summarize(tot_deaths = sum(num_deaths),
            tot_popn = sum(popn)) %>%
  ungroup() %>%
  mutate(asdr = tot_deaths / tot_popn)

region.asdr
```



```{r calculate-ffqf-region}
region.47q18 <- region.asdr %>%
  filter(agegp10 %in% c('[18,25)', '[25,35)', '[35,45)', '[45,55)', '[55,65)')) %>%
  mutate(width = ifelse(agegp10 == '[18,25)',
                        7,
                        10)) %>%
  mutate(const.mx.p = exp(-width*asdr),
         v2.mx.p = 1 - (width*asdr)/(1 + (width/2)*asdr)) %>%
  group_by(region, sex) %>%
  summarize(q.47.18 = 1 - prod(const.mx.p),
            q.47.18.alt = 1 - prod(v2.mx.p))

region.47q18
```


## National death rates


```{r}
national.asdr <-
  city.asdr %>%
  group_by(agegp10, sex) %>%
  summarize(tot_deaths = sum(num_deaths),
            tot_popn = sum(popn)) %>%
  ungroup() %>%
  mutate(asdr = tot_deaths / tot_popn)

national.asdr
```



```{r calculate-ffqf-national}
national.47q18 <- national.asdr %>%
  filter(agegp10 %in% c('[18,25)', '[25,35)', '[35,45)', '[45,55)', '[55,65)')) %>%
  mutate(width = ifelse(agegp10 == '[18,25)',
                        7,
                        10)) %>%
  mutate(const.mx.p = exp(-width*asdr),
         v2.mx.p = 1 - (width*asdr)/(1 + (width/2)*asdr)) %>%
  group_by(sex) %>%
  summarize(q.47.18 = 1 - prod(const.mx.p),
            q.47.18.alt = 1 - prod(v2.mx.p))

national.47q18
```

# Save reference values

```{r save-ref-vals}
write_csv(city.asdr %>% ungroup() %>% select(state_abbrev, sex, agegp10, asdr, num_deaths, popn),
          file.path(data_out_dir, "vr_asdrs.csv"))

write_csv(region.asdr %>% ungroup() %>% select(region, sex, agegp10, asdr, num_deaths=tot_deaths, popn=tot_popn),
          file.path(data_out_dir, "vr_region_asdrs.csv"))

write_csv(national.asdr %>% ungroup() %>% select(sex, agegp10, asdr, num_deaths=tot_deaths, popn=tot_popn),
          file.path(data_out_dir, "vr_national_asdrs.csv"))

write_csv(city.47q18 %>% ungroup() %>% select(state_abbrev, sex, q.47.18),
          file.path(data_out_dir, "vr_47q18.csv"))

write_csv(region.47q18 %>% ungroup() %>% select(region, sex, q.47.18),
          file.path(data_out_dir, "vr_region_47q18.csv"))

write_csv(national.47q18 %>% ungroup() %>% select(sex, q.47.18),
          file.path(data_out_dir, "vr_national_47q18.csv"))
```

# Sensitivity results

Open up IBGE estimated VR completeness

```{r}
ibge_completeness <- read_csv(file.path(out_dir, "vr_completeness_estimates.csv")) %>%
  mutate(sim_cov = mean_sim_cov_pct / 100)
ibge_completeness
```


```{r}
city.asdr.adj <- city.asdr %>%
  left_join(ibge_completeness %>%
              select(state_abbrev, sim_cov)) %>%
  mutate(vr_asdr = asdr,
         asdr = vr_asdr / sim_cov)

city.asdr.adj
```




```{r calculate-ffqf-adj}
city.47q18.adj <- city.asdr.adj %>%
  filter(agegp10 %in% c('[18,25)', '[25,35)', '[35,45)', '[45,55)', '[55,65)')) %>%
  mutate(width = ifelse(agegp10 == '[18,25)',
                        7,
                        10)) %>%
  mutate(const.mx.p = exp(-width*asdr),
         v2.mx.p = 1 - (width*asdr)/(1 + (width/2)*asdr)) %>%
  group_by(state_abbrev, sex) %>%
  summarize(q.47.18 = 1 - prod(const.mx.p),
            q.47.18.alt = 1 - prod(v2.mx.p))

city.47q18.adj
```

Adjusted regional death rates


```{r}
region.asdr.adj <-
  city.asdr.adj %>%
  ungroup() %>%
  mutate(raw_deaths = num_deaths,
         num_deaths = num_deaths / sim_cov) %>%
  group_by(region, agegp10, sex) %>%
  summarize(tot_raw_deaths = sum(raw_deaths),
            tot_deaths = sum(num_deaths),
            tot_popn = sum(popn)) %>%
  ungroup() %>%
  mutate(asdr = tot_deaths / tot_popn,
         vr_asdr = tot_raw_deaths / tot_popn)

region.asdr.adj
```




```{r calculate-ffqf-region-adj}
region.47q18.adj <- region.asdr.adj %>%
  filter(agegp10 %in% c('[18,25)', '[25,35)', '[35,45)', '[45,55)', '[55,65)')) %>%
  mutate(width = ifelse(agegp10 == '[18,25)',
                        7,
                        10)) %>%
  mutate(const.mx.p = exp(-width*asdr),
         v2.mx.p = 1 - (width*asdr)/(1 + (width/2)*asdr)) %>%
  group_by(region, sex) %>%
  summarize(q.47.18 = 1 - prod(const.mx.p),
            q.47.18.alt = 1 - prod(v2.mx.p))

region.47q18.adj
```

Double check

```{r}
chk_region_47q18 <- region.47q18.adj %>%
  left_join(region.47q18 %>% select(region, sex, q.47.18.vr = q.47.18)) 
```


Adjusted national death rates


```{r}
national.asdr.adj <-
  city.asdr.adj %>%
  ungroup() %>%
  mutate(raw_deaths = num_deaths,
         num_deaths = num_deaths / sim_cov) %>%
  group_by(agegp10, sex) %>%
  summarize(tot_raw_deaths = sum(raw_deaths),
            tot_deaths = sum(num_deaths),
            tot_popn = sum(popn)) %>%
  ungroup() %>%
  mutate(asdr = tot_deaths / tot_popn,
         vr_asdr = tot_raw_deaths / tot_popn)

national.asdr.adj
```

Double-check

```{r}
ggplot(national.asdr.adj) +
  geom_point(aes(x=vr_asdr, y=asdr)) +
  geom_abline(intercept=0, slope=1) +
  theme_minimal()
```



```{r calculate-ffqf-national-adj}
national.47q18.adj <- national.asdr.adj %>%
  filter(agegp10 %in% c('[18,25)', '[25,35)', '[35,45)', '[45,55)', '[55,65)')) %>%
  mutate(width = ifelse(agegp10 == '[18,25)',
                        7,
                        10)) %>%
  mutate(const.mx.p = exp(-width*asdr),
         v2.mx.p = 1 - (width*asdr)/(1 + (width/2)*asdr)) %>%
  group_by(sex) %>%
  summarize(q.47.18 = 1 - prod(const.mx.p),
            q.47.18.alt = 1 - prod(v2.mx.p))

national.47q18.adj
```

Double check

```{r}
chk_national_47q18 <- national.47q18.adj %>%
  left_join(national.47q18 %>% select(sex, q.47.18.vr = q.47.18)) 

chk_national_47q18 %>%
  ggplot(.) +
  geom_point(aes(x=q.47.18.vr, y=q.47.18)) +
  geom_abline(intercept=0, slope=1) +
  theme_minimal()
```



# Save adjusted reference values

```{r save-ref-vals-adj}
write_csv(city.asdr.adj %>% ungroup() %>% select(state_abbrev, sex, agegp10, asdr, num_deaths, popn),
          file.path(data_out_dir, "vr_asdrs_adj.csv"))

write_csv(region.asdr.adj %>% ungroup() %>% select(region, sex, agegp10, asdr, num_deaths=tot_deaths, popn=tot_popn),
          file.path(data_out_dir, "vr_region_asdrs_adj.csv"))

write_csv(national.asdr.adj %>% ungroup() %>% select(sex, agegp10, asdr, num_deaths=tot_deaths, popn=tot_popn),
          file.path(data_out_dir, "vr_national_asdrs_adj.csv"))

write_csv(city.47q18.adj %>% ungroup() %>% select(state_abbrev, sex, q.47.18),
          file.path(data_out_dir, "vr_47q18_adj.csv"))

write_csv(region.47q18.adj %>% ungroup() %>% select(region, sex, q.47.18),
          file.path(data_out_dir, "vr_region_47q18_adj.csv"))

write_csv(national.47q18.adj %>% ungroup() %>% select(sex, q.47.18),
          file.path(data_out_dir, "vr_national_47q18_adj.csv"))
```


