---
title: "Design-based network estimates"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```


```{r load-packages}
library(networkreporting)
library(tidyverse)
library(here)
library(future)
library(furrr)
library(progressr)
library(tictoc)
library(logger)
```

```{r logger-setup}
log_threshold(TRACE)
logs_dir <- here::here('logs')
dir.create(logs_dir, showWarnings=FALSE)
log_file <- file.path(logs_dir, paste0("network_estimates_", format(Sys.time(), "%Y%m%d_%H%M%S"), ".log"))
log_appender(appender_tee(file = log_file))
log_info("Network estimates script started")
```


```{r setup-directories}
data_dir <- here('data')
survey_data_dir <- file.path(data_dir, 'survey')
out_dir <- here('out')
```

# Load the data

```{r load-data}
# load individual data
ego.dat <- read_csv(file.path(survey_data_dir, "individual.csv"))

# load network death data
nr.deaths.dat <- read_csv(file.path(survey_data_dir, "network_reports.csv"))

# load bootstrap weights
#boot.weights <- read_csv(file.path(survey_data_dir, "bootstrap_weights_jab1k.csv.gz"))
#boot.weights <- read_csv(file.path(survey_data_dir, "bootstrap_weights_1k.csv"))
#boot.weights <- read_csv(file.path(survey_data_dir, "bootstrap_weights_10k.csv.gz"))

boot.weights <- readRDS(file.path(survey_data_dir, "bootstrap_weights_10k.rds"))

#boot.weights <- read_csv(file.path(survey_data_dir, "bootstrap_weights_jab10k.csv.gz"))
#boot.weights <- readRDS(file.path(survey_data_dir, "bootstrap_weights_jab10k.rds"))

#boot.weights <- read_csv(file.path(survey_data_dir, "bootstrap_weights_5k.csv.gz"))
#boot.weights <- readRDS(file.path(survey_data_dir, "bootstrap_weights_5k.rds"))

# load frame population sizes
state.dat <- read_csv(file.path(data_dir, "cities.csv"))

all.states <- state.dat %>% pull(state_abbrev)
```

For this analysis, we'll only use reported deaths between the ages of 18 and 65.
We'll filter out people under 18. However, it's a little easier to run the code if we
keep reported deaths who are over 65 for the time being.

```{r drop-unused-deaths}
nr.deaths.dat <- nr.deaths.dat %>%
  filter(agegp10 != '[0,18)')
```


It will be convenient to have a list w/ dataset for each state. We'll do this for
the ego data, the network reports, the known population sizes, and the bootstrap resamples

```{r make-city-data-lists}
# ego data
state.svy <- setNames(map(all.states,
                              function(state) {
                                res <- ego.dat %>% filter(state_abbrev==state)
                                return(res)
                              }),
                      all.states)

# detailed reports about deaths
state.alter.deaths.dat <- setNames(map(all.states,
                                       function(state) {
                                         res <- nr.deaths.dat %>% filter(state_abbrev==state)
                                         return(res)
                                       }),
                                   all.states)

# total size of the known populations in each state
state.kp.tot <- setNames(map(all.states,
                             ~ state.dat %>% 
                               filter(state_abbrev==.x) %>% 
                               pull(total_kp_size)),
                             all.states)

# bootstrap weights
state.bootweights <- setNames(map(all.states,
                               function(state) {
                                 
                                 res <- boot.weights %>% 
                                   filter(state_abbrev==state) %>% 
                                   select(-state_abbrev)
                                 
                                 return(res)
                               }),
                               all.states)
```

## Calculate deaths per interview

Calculate the unweighted number of adult deaths reported per interview
First, calculate the raw (unweighted) number of adult deaths reported; this is useful for
comparing to the sibling method

```{r calculate-deaths-per-interview}
n.net <- ego.dat %>%
  group_by(state_abbrev) %>%
  summarize(num_interviews = n())

dpi.net <- nr.deaths.dat %>%
  # only count reported deaths in our age range of interest (18-64)
  filter(! agegp10 %in% c('[65,75)', '[75,Inf]', NA)) %>%
  group_by(state_abbrev) %>%
  summarize(num_reported_deaths = n()) %>%
  mutate(method='network')
```

```{r save-deaths-per-interview}
write_csv(n.net,
          path=file.path(out_dir, 'num_interviews.csv'))
write_csv(dpi.net,
          path=file.path(out_dir, 'num_deaths_unweighted_network.csv'))
```


## Get reported deaths by respondent age (who reports whom)

Note that this is unweighted -- it's just the number of deaths

```{r}
nr_wrw <- nr.deaths.dat %>%
  rename(death_sex = sex,
         death_agegp10 = agegp10) %>%
  left_join(ego.dat %>% select(ego.id = id, ego_sex = sex, ego_agegp10 = agegp10),
            by='ego.id')

write_csv(nr_wrw,
          path=file.path(out_dir, 'who_reports_who_network.csv'))

nr_wrw
```

#### TEMP

let's look at the distribution of number of deaths and of number KP known

```{r}

```



#### END TEMP

## Calculate network survival estimates from bootstrap resamples

```{r}
parallel <- TRUE
#parallel <- FALSE

num.cores <- 7
#num.cores <- 6 
#num.cores <- 3
#num.cores <- 2

if(parallel) {
  ## this is needed to avoid running out of memory errors w/ future package
  ## see
  ## https://github.com/HenrikBengtsson/future/issues/185
  #options(future.globals.maxSize = 768 * 1024^2)
  #options(future.globals.maxSize = 999 * 1024^2)
  options(future.globals.maxSize = 2000 * 1024^2)
}
options(future.globals.maxSize = 2000 * 1024^2)
options(expressions = 10000)

# progressr progress bar appearance
handlers(
  handler_progress(
    format = ":spin [:bar] :percent | :current/:total | :message",
    clear = FALSE,
    width = 80
  )
)
```

NB: 1000 bootstrap reps takes about 75 minutes on a 2020 Macbook Pro

NB: 10000 bootstrap reps takes about 49 hours on a 2023 Macbook Pro with 6 cores and 30gb memory allocated via docker

NOTE: this code produces some warnings that look like 
"Bootstrapped degree estimates have 9 out of 14000 values missing. These have been removed in the summary statistics"
These warnings come from older ages, which we don't use in this analysis.


```{r network-survival-estimates-bootstrap}
log_info("Starting network survival estimates bootstrap")
tic('network survival estimates (with bootstrap)')
if(parallel) {
  plan(multisession, workers=num.cores)
}

with_progress({
  p <- progressor(steps = length(all.states))

  netsurv.asdr <- future_map_dfr(all.states,
    function(state) {
      library(logger)
      log_threshold(TRACE)
      log_appender(appender_file(log_file))
      log_debug("Starting state: {state}")
      p(message = sprintf("Processing %s", state))  # Signal progress
      
      tic("TEMP - current state")
      cur.dat <- state.svy[[state]]
      cur.deaths.dat <- state.alter.deaths.dat[[state]]
      cur.bw <- state.bootweights[[state]] 
      # TEMP debug
      #cur.bw <- cur.bw[1, c(1, 2000:3000)]
      cur.kp.tot <- state.kp.tot[[state]]
      
      cur.ns <- network.survival.estimator_(resp.data = cur.dat,
                                       attribute.data = cur.deaths.dat,
                                       attribute.names = c('sex', 'agegp10'),
                                       known.populations = 'num_connections_to_kp',
                                       total.kp.size = cur.kp.tot,   
                                       weights = 'weight',
                                       attribute.weights = 'ego.weight',
                                       boot.weights=cur.bw,
                                       within.alter.weights='w.factor.alter',
                                       ego.id=c('id'='ego.id'), 
                                       dropmiss=TRUE,
                                       return.boot=TRUE,
                                       verbose=FALSE)$boot.estimates
      cur.ns$state_abbrev <- state
      toc()
      
      return(cur.ns)
    },
    .progress=FALSE)
})

if(parallel) {
  plan(sequential)  
}
toc()
```

Missingness comes from cases where bootstrap-resamples produce an estimate of 0 connections
to groups of known size. These all happen at ages 65+, which we don't produce estimates for anyway:

```{r summarize-missingness}
glue::glue("
           In {zerokp} cases out of {total} ({round(100*(zerokp/total),2)} percent), bootstrapped estimate of degree for a given age group is 0, leading to undefined estimated death rates.\n\n
           This table shows whether or not this affects any age groups used in the analysis below:\n
           ", 
           zerokp = sum(! is.finite(netsurv.asdr$asdr.hat)), 
           total=nrow(netsurv.asdr))

with(netsurv.asdr %>% filter(! is.finite(asdr.hat)), table(agegp10, useNA='ifany'))
```

Calculate 47q18, ie cond prob of death between 18 and 65 

```{r calculate-ffqf}
net.47q18 <- netsurv.asdr %>%
  filter(agegp10 %in% c('[18,25)', '[25,35)', '[35,45)', '[45,55)', '[55,65)')) %>%
  mutate(width = ifelse(agegp10 == '[18,25)',
                        7,
                        10),
         asdr = asdr.hat) %>%
  mutate(const.mx.p = exp(-width*asdr),
         v2.mx.p = 1 - (width*asdr)/(1 + (width/2)*asdr)) %>%
  group_by(state_abbrev, sex, boot_idx) %>%
  summarize(q.47.18 = 1 - prod(const.mx.p),
            q.47.18.alt = 1 - prod(v2.mx.p))

net.47q18.summ <- net.47q18 %>%
  group_by(state_abbrev, sex) %>%
  summarize(q.47.18.mean = mean(q.47.18),
            q.47.18.sd = sd(q.47.18), 
            q.47.18.ci.low = quantile(q.47.18, .025),
            q.47.18.ci.high = quantile(q.47.18, .975))
```

Double-check that it does not make a big difference how we calculate prob
(Doesn't look like it does: mean relative difference is around 0.07%)

```{r check-ffqf-assumptions}
net.47q18.check <- net.47q18 %>%
  group_by(state_abbrev, sex) %>%
  summarize(q.47.18.mean = mean(q.47.18),
            q.47.18.alt.mean = mean(q.47.18.alt)) %>%
  mutate(rel_diff = (q.47.18.alt.mean - q.47.18.mean) / q.47.18.mean)

summary(net.47q18.check$rel_diff)
```

Save asdrs and probs 

```{r save-asdrs}
# save point estimates and CI for ASDRs
netsurv.asdr.agg <- netsurv.asdr %>%
  ungroup() %>%
  filter(! agegp10 %in% c('[65,75)', '[75,Inf]', 'NA'))  %>%
  group_by(state_abbrev, sex, agegp10) %>%
  summarize(post_ci_high_asdr = quantile(asdr.hat, .975),
            post_ci_low_asdr = quantile(asdr.hat, .025),
            post_sd_asdr = sd(asdr.hat),
            post_mean_asdr = mean(asdr.hat)) %>%
  mutate(method = 'net_design')
write_csv(netsurv.asdr.agg, 
          file.path(out_dir, 'net_design_asdrs.csv'))

# save all bootstrap reps for ASDRs
netsurv.asdr.boot <- netsurv.asdr %>%
  ungroup() %>%
  filter(! agegp10 %in% c('[65,75)', '[75,Inf]', 'NA'))  %>%
  select(state_abbrev, sex, agegp10, boot_idx, post_mean_asdr = asdr.hat) %>%
  mutate(method = 'net_design')
write_csv(netsurv.asdr.boot, 
          file.path(out_dir, 'net_design_asdrs_boot.csv'))

# save point estimates for probabilities and CI
netsurv.47q18.agg <- net.47q18.summ %>%
  dplyr::rename(post_mean_q = q.47.18.mean,
                post_sd_q = q.47.18.sd,
                post_ci_low_q = q.47.18.ci.low,
                post_ci_high_q = q.47.18.ci.high) %>%
  mutate(method = 'net_design')
write_csv(netsurv.47q18.agg, 
          file.path(out_dir, 'net_design_probs.csv'))

# save all bootstrap reps for probabilities and CI
netsurv.47q18.boot <- net.47q18 %>%
  select(state_abbrev, sex, boot_idx, q.47.18.mean = q.47.18) %>%
  mutate(method = 'net_design')
write_csv(netsurv.47q18.boot, 
          file.path(out_dir, 'net_design_probs_boot.csv'))
```

## Aggregate death rate estimates up to region level

```{r aggregate-asdrs-to-region}
log_info("Aggregating estimates to region level")
net.region.asdr <- netsurv.asdr %>%
  mutate(ybar.F.Dcell.hat = y.F.Dcell.hat / N.F.hat,
         ybar.Fcell.kp.hat = y.Fcell.kp.hat / N.Fcell.hat) %>%
  filter(! agegp10 %in% c('[65,75)', '[75,Inf]', 'NA')) %>%
  left_join(state.dat %>% select(state_abbrev, region), by='state_abbrev')

net.region.asdr <- net.region.asdr %>%
  group_by(region, sex, agegp10, boot_idx) %>%
  summarize(y.F.Dcell.hat = sum(y.F.Dcell.hat),
            y.Fcell.kp.hat = sum(y.Fcell.kp.hat),
            N.F.hat = sum(N.F.hat),
            N.Fcell.hat = sum(N.Fcell.hat),
            total.kp.size = sum(total.kp.size)) %>%
  mutate(ybar.F.Dcell.hat = y.F.Dcell.hat / N.F.hat,
         ybar.Fcell.kp.hat = y.Fcell.kp.hat / N.Fcell.hat,
         asdr.hat = (ybar.F.Dcell.hat/ybar.Fcell.kp.hat)*(total.kp.size/N.Fcell.hat))

net.region.asdr.boot <- net.region.asdr %>%
  select(region, sex, agegp10, boot_idx, post_mean_asdr = asdr.hat)
  
net.region.asdr.agg <- net.region.asdr %>%
  group_by(region, sex, agegp10) %>%  
  summarize(post_mean_asdr = mean(asdr.hat),
            post_ci_low_asdr = quantile(asdr.hat, .025),
            post_ci_high_asdr = quantile(asdr.hat, .975),
            post_sd_asdr = sd(asdr.hat)) %>%
  mutate(method = 'net_design')
```

Calculate probabilities for regional death rate estimates

```{r ffqf-for-regions}
net.region.47q18 <- net.region.asdr %>%
  filter(agegp10 %in% c('[18,25)', '[25,35)', '[35,45)', '[45,55)', '[55,65)')) %>%
  mutate(width = ifelse(agegp10 == '[18,25)',
                        7,
                        10),
         asdr = asdr.hat) %>%
  mutate(const.mx.p = exp(-width*asdr),
         v2.mx.p = 1 - (width*asdr)/(1 + (width/2)*asdr)) %>%
  group_by(region, sex, boot_idx) %>%
  summarize(q.47.18 = 1 - prod(const.mx.p),
            q.47.18.alt = 1 - prod(v2.mx.p))

net.47q18.region.summ <- net.region.47q18 %>%
  group_by(region, sex) %>%
  summarize(post_mean_q = mean(q.47.18),
            post_sd_q = sd(q.47.18), 
            post_ci_low_q = quantile(q.47.18, .025),
            post_ci_high_q = quantile(q.47.18, .975)) %>%
  mutate(method = 'net_design')

net.47q18.region.boot <- net.region.47q18 %>%
   mutate(method = 'net_design') %>%
   select(region, sex, boot_idx, q.47.18.mean = q.47.18)
```

Double-check that it does not make a big difference how we calculate prob
(Doesn't look like it does: mean relative difference is around 0.3%)

```{r check-region-ffqf-assumption}
net.region.47q18.check <- net.region.47q18 %>%
  group_by(region, sex) %>%
  summarize(q.47.18.mean = mean(q.47.18),
            q.47.18.alt.mean = mean(q.47.18.alt)) %>%
  mutate(rel_diff = (q.47.18.alt.mean - q.47.18.mean) / q.47.18.mean)

summary(net.region.47q18.check$rel_diff)
```

Save regional results

```{r save-region-results}
write_csv(net.region.asdr.agg, 
          file.path(out_dir, 'net_design_asdrs_region.csv'))
write_csv(net.region.asdr.boot, 
          file.path(out_dir, 'net_design_asdrs_region_boot.csv'))
write_csv(net.47q18.region.summ, 
          file.path(out_dir, 'net_design_probs_region.csv'))  
write_csv(net.47q18.region.boot, 
          file.path(out_dir, 'net_design_probs_region_boot.csv'))  
```


## Aggregate death rate estimates up to national level

```{r aggregate-asdrs-to-national}
log_info("Aggregating estimates to national level")
net.national.asdr <- netsurv.asdr %>%
  mutate(ybar.F.Dcell.hat = y.F.Dcell.hat / N.F.hat,
         ybar.Fcell.kp.hat = y.Fcell.kp.hat / N.Fcell.hat) %>%
  filter(! agegp10 %in% c('[65,75)', '[75,Inf]', 'NA')) %>%
  left_join(state.dat %>% select(state_abbrev, region), by='state_abbrev')

net.national.asdr <- net.national.asdr %>%
  group_by(sex, agegp10, boot_idx) %>%
  summarize(y.F.Dcell.hat = sum(y.F.Dcell.hat),
            y.Fcell.kp.hat = sum(y.Fcell.kp.hat),
            N.F.hat = sum(N.F.hat),
            N.Fcell.hat = sum(N.Fcell.hat),
            total.kp.size = sum(total.kp.size)) %>%
  mutate(ybar.F.Dcell.hat = y.F.Dcell.hat / N.F.hat,
         ybar.Fcell.kp.hat = y.Fcell.kp.hat / N.Fcell.hat,
         asdr.hat = (ybar.F.Dcell.hat/ybar.Fcell.kp.hat)*(total.kp.size/N.Fcell.hat))

net.national.asdr.boot <- net.national.asdr %>%
  select(sex, agegp10, boot_idx, post_mean_asdr = asdr.hat)
  
net.national.asdr.agg <- net.national.asdr %>%
  group_by(sex, agegp10) %>%  
  summarize(post_mean_asdr = mean(asdr.hat),
            post_ci_low_asdr = quantile(asdr.hat, .025),
            post_ci_high_asdr = quantile(asdr.hat, .975),
            post_sd_asdr = sd(asdr.hat)) %>%
  mutate(method = 'net_design')
```

Calculate probabilities for national death rate estimates

```{r ffqf-for-national}
net.national.47q18 <- net.national.asdr %>%
  filter(agegp10 %in% c('[18,25)', '[25,35)', '[35,45)', '[45,55)', '[55,65)')) %>%
  mutate(width = ifelse(agegp10 == '[18,25)',
                        7,
                        10),
         asdr = asdr.hat) %>%
  mutate(const.mx.p = exp(-width*asdr),
         v2.mx.p = 1 - (width*asdr)/(1 + (width/2)*asdr)) %>%
  group_by(sex, boot_idx) %>%
  summarize(q.47.18 = 1 - prod(const.mx.p),
            q.47.18.alt = 1 - prod(v2.mx.p))

net.47q18.national.summ <- net.national.47q18 %>%
  group_by(sex) %>%
  summarize(post_mean_q = mean(q.47.18),
            post_sd_q = sd(q.47.18), 
            post_ci_low_q = quantile(q.47.18, .025),
            post_ci_high_q = quantile(q.47.18, .975)) %>%
  mutate(method = 'net_design')

net.47q18.national.boot <- net.national.47q18 %>%
   mutate(method = 'net_design') %>%
   select(sex, boot_idx, q.47.18.mean = q.47.18)
```

Double-check that it does not make a big difference how we calculate prob
(Doesn't look like it does: mean relative difference is around TODO%)

```{r check-national-ffqf-assumption}
net.national.47q18.check <- net.national.47q18 %>%
  group_by(sex) %>%
  summarize(q.47.18.mean = mean(q.47.18),
            q.47.18.alt.mean = mean(q.47.18.alt)) %>%
  mutate(rel_diff = (q.47.18.alt.mean - q.47.18.mean) / q.47.18.mean)

summary(net.national.47q18.check$rel_diff)
```

Save national results

```{r save-national-results}
write_csv(net.national.asdr.agg, 
          file.path(out_dir, 'net_design_asdrs_national.csv'))
write_csv(net.national.asdr.boot, 
          file.path(out_dir, 'net_design_asdrs_national_boot.csv'))
write_csv(net.47q18.national.summ, 
          file.path(out_dir, 'net_design_probs_national.csv'))  
write_csv(net.47q18.national.boot, 
          file.path(out_dir, 'net_design_probs_national_boot.csv'))  
```





