---
title: "Design-based sibling estimates"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```


```{r}
#library(networkreporting)
library(tidyverse)
#library(lubridate)
library(future)
library(furrr)
library(siblingsurvival)
library(tictoc)
library(logger)
library(here)

tic("Time to run file: ")
```

```{r}
data_dir <- here('data')
survey_data_dir <- file.path(data_dir, 'survey')
out_dir <- here('out')
```


```{r}
set.seed(10101010)
```

```{r}
parallel <- TRUE
#parallel <- FALSE

num.cores <- 7
#num.cores <- 9
#num.cores <- 2

if(parallel) {
  ## this is needed to avoid running out of memory errors w/ future package
  ## see
  ## https://github.com/HenrikBengtsson/future/issues/185
  #options(future.globals.maxSize = 768 * 1024^2)
  #options(future.globals.maxSize = 999 * 1024^2)
  options(future.globals.maxSize = 2000 * 1024^2)
}
options(future.globals.maxSize = 2000 * 1024^2)
options(expressions = 10000)
```

```{r}
# Set up logger in main process
log_threshold(TRACE)
logs_dir <- here::here('logs')
dir.create(logs_dir, showWarnings=FALSE)
log_file <- file.path(logs_dir, paste0("sibling_estimates_", format(Sys.time(), "%Y%m%d_%H%M%S"), ".log"))
log_appender(appender_tee(file = log_file))

log_info("Sibling estimates script started")

if (file.exists("../run_docker.sh")) {
  docker_run_contents <- readLines("../run_docker.sh")
  log_debug("run_docker.sh contents:\n{paste(docker_run_contents, collapse = '\n')}")
} else {
  log_warn("../run_docker.sh not found in working directory: {getwd()}")
}
```


# Load the data

```{r read-data}
bw_file <- "bootstrap_weights_jab10k.rds"
  
# load individual data
sib.dat <- read_csv(file.path(survey_data_dir, "sibling_reports.csv"))

# load individual data
ego.dat <- read_csv(file.path(survey_data_dir, "individual.csv"))

# load bootstrap weights
#boot.weights <- read_csv(file.path(survey_data_dir, "bootstrap_weights_1k.csv"))

#boot.weights <- read_csv(file.path(survey_data_dir, "bootstrap_weights_jab1k.csv.gz"))

boot.weights <- readRDS(file.path(survey_data_dir, bw_file))

#boot.weights <- read_csv(file.path(survey_data_dir, "bootstrap_weights_10k.csv.gz"))
#boot.weights <- readRDS(file.path(survey_data_dir, "bootstrap_weights_10k.rds"))
#boot.weights.fn <- "bootstrap_weights_5k.rds"

#boot.weights.fn <- "bootstrap_weights_10k.rds"

#boot.weights <- readRDS(file.path(survey_data_dir, boot.weights.fn))

log_info(glue::glue("Bootstrap weights opened: {bw_file}"))

# load city info
state.dat <- read_csv(file.path(data_dir, "cities.csv"))
all.states <- state.dat %>% pull(state_abbrev)
all.regions <- unique(state.dat$region)
```

```{r make-city-data-lists}
## It will be helpful to have a list of sibling reports, by city
city.sib.dat <- setNames(map(all.states,
                             function(state) {
                               csd <- sib.dat %>% filter(state_abbrev==state)
                               return(csd)
                             }),
                              all.states)

## Similarly, it will be helpful to have a list of bootstrap resamples, by city
city.boot.weights <- setNames(map(all.states,
                                  function(state) {
                                    cbw <- boot.weights %>% 
                                      filter(state_abbrev==state) %>% 
                                      select(-state_abbrev) %>%
                                      ## we need the id in the bootstrap data to line up with the id in the
                                      ## sibling reports
                                      rename(ego.id = id)
                                    return(cbw)
                                  }),
                              all.states)

## And it will also be helpful to have a list of sibling reports by region
region.sib.dat <- setNames(map(all.regions,
                             function(region) {
                               rsd <- sib.dat %>% 
                                 left_join(state.dat %>% select(state_abbrev, region), by='state_abbrev') %>%
                                 filter(region==!!region)
                               return(rsd)
                             }),
                              all.regions)

## ... and a list of sibling reports by region using only HQ cities
regionhq.sib.dat <- setNames(map(all.regions,
                             function(region) {
                               rsd <- sib.dat %>% 
                                 left_join(state.dat %>% select(state_abbrev, region), by='state_abbrev') %>%
                                 filter(region==!!region)
                               return(rsd)
                             }),
                              all.regions)

## Similarly, it will be helpful to have a list of bootstrap resamples, by region
region.boot.weights <- setNames(map(all.regions,
                                  function(region) {
                                    rbw <- boot.weights %>% 
                                      left_join(state.dat %>% select(state_abbrev, region), by='state_abbrev') %>%
                                      filter(region==!!region) %>% 
                                      select(-state_abbrev, -region) %>%
                                      ## we need the id in the bootstrap data to line up with the id in the
                                      ## sibling reports
                                      rename(ego.id = id)
                                    return(rbw)
                                  }),
                              all.regions)

## Finally, it will be helpful to have a list of bootstrap resamples, by region for the
## 24 high-quality comparison cities
regionhq.boot.weights <- setNames(map(all.regions,
                                  function(region) {
                                    rbw <- boot.weights %>% 
                                      left_join(state.dat %>% select(state_abbrev, region), by='state_abbrev') %>%
                                      filter(region==!!region) %>% 
                                      select(-state_abbrev, -region) %>%
                                      ## we need the id in the bootstrap data to line up with the id in the
                                      ## sibling reports
                                      rename(ego.id = id)
                                    return(rbw)
                                  }),
                              all.regions)

## And it will also be helpful to have national sibling reports 
national.sib.dat <- sib.dat %>% 
                    left_join(state.dat %>% select(state_abbrev, region), by='state_abbrev')

## Similarly, it will be helpful to have national bootstrap resamples
national.boot.weights <- boot.weights %>% 
                           left_join(state.dat %>% select(state_abbrev, region), by='state_abbrev') %>%
                           select(-state_abbrev, -region) %>%
                           ## we need the id in the bootstrap data to line up with the id in the
                           ## sibling reports
                           rename(ego.id = id)
```

```{r make-agegp-objects}
## Make age group objects

# NB: age groups to start at 18, not 15, for comparability
age.gps10 <- siblingsurvival::make.age.groups(start=18*12,
                                              widths=12*c(7, rep(10, 4)),
                                              names=c('[18,25)',
                                                      '[25,35)',
                                                      '[35,45)',
                                                      '[45,55)',
                                                      '[55,65)'))

## Make time period objects

time.periods.1yrbeforeint <- siblingsurvival::make.time.periods(start=-12,
                                                                durations=12,
                                                                names=c("0"))

time.periods.7yrbeforeint <- siblingsurvival::make.time.periods(start=-12*7,
                                                                durations=12*7,
                                                                names=c("0-6"))
```



```{r get-cell-configs}
## the default cell config has deaths 7 years before the interview
cc <- siblingsurvival::cell_config(age.groups=age.gps10, 
                                   time.periods='7yr_beforeinterview',
                                   start.obs='dob_cmc_shifted',    # date of birth
                                   end.obs='endobs_cmc_shifted',   # either the date respondent was interviewed 
                                                                   # (if sib is alive) 
                                                                   # or date of death (if sib is dead)
                                   event='dod_cmc_shifted',        # date of death (for sibs who died)
                                   age.offset='dob_cmc_shifted',   # date of birth
                                   time.offset='doi_cmc_shifted',  # date of interview
                                   exp.scale=1/12)

## we'll make another cell config with deaths 1 year before the interview
cc_12mo <- siblingsurvival::cell_config(age.groups=age.gps10, 
                                   time.periods='12mo_beforeinterview',
                                   start.obs='dob_cmc_shifted',    # date of birth
                                   end.obs='endobs_cmc_shifted',   # either the date respondent was interviewed 
                                                                   # (if sib is alive) 
                                                                   # or date of death (if sib is dead)
                                   event='dod_cmc_shifted',        # date of death (for sibs who died)
                                   age.offset='dob_cmc_shifted',   # date of birth
                                   time.offset='doi_cmc_shifted',  # date of interview
                                   exp.scale=1/12)

```


First, get unweighted point estimates 
(we use these to calculate the number of adult deaths reported per interview)

```{r unweighted-estts}

unweighted.sib.7yr.all <- purrr::imap_dfr(city.sib.dat,
                                      function(cur.sib.dat, city_name) {
                                        cur.sib.dat$constwgt <- 1
                                        cur.ests <- 
                                          sibling_estimator(sib.dat = cur.sib.dat,
                                          ego.id = 'ego.id',            # column with the respondent id
                                          sib.id = 'sib.id',            # column with sibling id 
                                                                        # (unique for each reported sibling)
                                          sib.frame.indicator = 'in.F', # indicator for sibling frame population membership
                                          sib.sex = 'sex',              # column with sibling's sex
                                          cell.config=cc,               # cell configuration we created above
                                          weights='constwgt')         # column with the respondents' sampling weights
                                        cur.ests <- cur.ests$asdr.agg
                                        cur.ests$state_abbrev <- city_name
                                        return(cur.ests)
                                      })

unweighted.sib.oneyr.all <- purrr::imap_dfr(city.sib.dat,
                                      function(cur.sib.dat, city_name) {
                                        cur.sib.dat$constwgt <- 1
                                        cur.ests <- 
                                          sibling_estimator(sib.dat = cur.sib.dat,
                                          ego.id = 'ego.id',            # column with the respondent id
                                          sib.id = 'sib.id',            # column with sibling id 
                                                                        # (unique for each reported sibling)
                                          sib.frame.indicator = 'in.F', # indicator for sibling frame population membership
                                          sib.sex = 'sex',              # column with sibling's sex
                                          cell.config=cc_12mo,          # cell configuration we created above
                                          weights='constwgt')         # column with the respondents' sampling weights
                                        cur.ests <- cur.ests$asdr.agg
                                        cur.ests$state_abbrev <- city_name
                                        return(cur.ests)
                                      })

#unweighted.sib.oneyr <- unweighted.sib.oneyr %>%
unweighted.sib.oneyr <- unweighted.sib.oneyr.all %>%
  group_by(state_abbrev) %>%
  summarize(num_reported_deaths = sum(num.hat)) %>%
  mutate(method = 'sibling_12mo')

unweighted.sib.7yr <- unweighted.sib.7yr.all %>%
  group_by(state_abbrev) %>%
  summarize(num_reported_deaths = sum(num.hat)) %>%
  mutate(method = 'sibling_7yr')
```

```{r num-deaths-per-interview}
unweighted.sib.nd <- bind_rows(unweighted.sib.oneyr, unweighted.sib.7yr)

write_csv(unweighted.sib.nd,
          file=file.path(out_dir, "num_deaths_unweighted_sibling.csv"))
```

Also get who reports whom

```{r}
sib.7yr.forwrw <- purrr::imap_dfr(city.sib.dat,
                                      function(cur.sib.dat, city_name) {
                                        cur.sib.dat$constwgt <- 1
                                        # get ego X sib X cell reports
                                        cur.ests <- 
                                          siblingsurvival:::get_esc_reports(sib.dat = cur.sib.dat,
                                                ego.id = 'ego.id',
                                                sib.id = 'sib.id',
                                                cell.config=cc)   
                                        return(cur.ests)
                                      })
```



```{r}
# rename agegroups
sib_7yr_wrw <- sib.7yr.forwrw %>%
  # only want deaths
  filter(sib.occ > 0) %>%
  rename(death_agegp10 = agelabel) %>%
  # join in ego agegroups
  left_join(ego.dat %>% 
              select(ego.id = id, ego_agegp10 = agegp10, ego_sex = sex, ego.weight=weight)) %>%
  select(-sib.exp, -sib.occ, -ego.weight, -ego.id, -sib.id, -agegroup, -time.period)

write_csv(sib_7yr_wrw,
          path=file.path(out_dir, 'who_reports_who_sibling.csv'))

# unweighted number of interviews by respondent age
resp_by_age <- ego.dat %>%
  rename(ego_agegp10 = agegp10) %>%
  group_by(ego_agegp10) %>%
  summarize(num_ego = n())

write_csv(resp_by_age,
          path=file.path(out_dir, 'num_interviews_by_age.csv'))
```

TODO - LEFT OFF HERE:

for R+R, calculate the average number of siblings, by city

- avg # sibs
- avg # adult sibs
- avg # adult sibs who contribute exposure in time window
- avg # of deaths

```{r}
sibling_summ <- function(sib.dat,
                         # the name of the id of the ego in the sibling histories
                         ego.id,
                         # the name of the id of the sib in the sibling histories
                         sib.id,
                         # the name of the indicator for whether or not each sib is on the
                         # frame
                         sib.frame.indicator,
                         cell.config) {
  
  sib.dat <- sib.dat %>%
   dplyr::mutate(.ego.id     = !!sym(ego.id),
                 .sib.id     = !!sym(sib.id))
  
  esc_dat <- siblingsurvival:::get_esc_reports(sib.dat = sib.dat,
                             ego.id='.ego.id',
                             sib.id='.sib.id',
                             cell.config=cc)
  
  sib_summ <- esc_dat %>%
    filter(sib.exp > 0 | sib.occ > 0)
  
  return(lst(num_sibs = length(unique(sib_summ$.sib.id)),
             num_deaths = sum(sib_summ$sib.occ)))
  
}

sib_summs <- purrr::imap_dfr(city.sib.dat,
                           function(cur_sib_dat, city) {
                             res <- sibling_summ(cur_sib_dat,
                                                 ego.id='ego.id',
                                                 sib.id='sib.id',
                                                 sib.frame.indicator='in.F',
                                                 cell.config=cc)
                             res$state_abbrev <- city
                             return(res)
                           }) 
```

```{r}
num_int_bycity <- ego.dat %>%
  group_by(state_abbrev) %>%
  summarize(num_interviews = n())

sib_summs_res <- sib_summs %>% 
  left_join(num_int_bycity) %>%
  mutate(deaths_per_interview = num_deaths / num_interviews,
         sibs_per_interview = num_sibs / num_interviews)

write_csv(sib_summs_res,
          path=file.path(out_dir, 'num_sibs_summary.csv'))

sib_summs_res
```


```{r, eval=FALSE}
# rename agegroups
sib_7yr_num_sibs <- sib.7yr.forwrw %>%
  filter(sib.occ > 0) %>%
  group_by(ego.id, sib.id) %>%
  summarize(any_over_18 = as.numeric(any(agegroup != 'agegroup_1')))

tmp <- ego.dat %>%
  select(id, state_abbrev) %>%
  left_join(sib_7yr_num_sibs, by=c('id'='ego.id')) %>%
  mutate(sib = case_when(is.na(any_over_18) ~ 0,
                         TRUE ~ 1)) %>%
  
  
sib_7yr_num_sibs_bycity <-
  sib_7yr_num_sibs %>%
  left_join
  
  # only want deaths
  #filter(sib.occ > 0) %>%
  rename(death_agegp10 = agelabel) %>%
  # join in ego agegroups
  left_join(ego.dat %>% 
              select(ego.id = id, ego_agegp10 = agegp10, ego_sex = sex, ego.weight=weight)) %>%
  select(-sib.exp, -sib.occ, -ego.weight, -ego.id, -sib.id, -agegroup, -time.period)

```


```{r avg-sibs-bycity, eval=FALSE}
sib_by_ego <- sib.dat %>%
  group_by(ego.id) %>%
  summarize(num_sib = n(),
            num_sib_over18 = TODO)
#write_csv(sib.47q18.boot.12mo, file.path(out_dir, 'sib_12mo_design_probs_boot.csv'))
```



### Sibling estimates by state

NB: this produces a small number of messages like
'Individual estimates have 2 out of 10000 values missing. These have been removed in the summary statistics. Beware!'
This is coming from the individual estimator (which we're not interested in here). It doesn't affect our analysis below.

NB: 100 bootstrap reps takes about 
NB: 1000 bootstrap reps takes about 6 minutes

NB: 5000 bootstrap reps takes about 24 minutes w/ return.boot = FALSE; (using 6 cores) now re-running w/ return.boot = TRUE
    ... same!
    
NB: 20251029 - GETTING WARNINGS
UNRELIABLE VALUE: Future (‘<none>’) unexpectedly generated random numbers without specifying argument '[future.]seed'. There is a risk that those random numbers are not statistically sound and the overall results might be invalid. To fix this, specify argument '[future.]seed', e.g. 'seed=TRUE'. This ensures that proper, parallel-safe random numbers are produced via the L'Ecuyer-CMRG method. To disable this check, use [future].seed=NULL, or set option 'future.rng.onMisuse' to "ignore"

```{r sibling-estimates-with-bootstrap}

log_info("Starting sibling estimates processing")
log_info("Number of states to process: {length(city.sib.dat)}")
log_info("Using {num.cores} cores")

tic("Running sibling estimates for states...")
if(parallel) {
  plan(multisession, workers=num.cores)
}

# Pass the log file path to workers
sib.asdr <- furrr::future_imap_dfr(city.sib.dat,
  function(cur.sib.dat, state) {
    # IMPORTANT: Configure logger inside each worker
    library(logger)
    log_threshold(TRACE)
    log_appender(appender_file(log_file))  # Note: using appender_file, not appender_tee
    
    log_debug("Starting state: {state}")
    log_debug("Number of observations: {nrow(cur.sib.dat)}")
    
    tic(glue::glue("Starting {state}...\n\n"))
    
    cur.bw <- city.boot.weights[[state]]
    
    cur.ests <- withCallingHandlers(
      tryCatch({
        sibling_estimator(
          sib.dat = cur.sib.dat,
          ego.id = 'ego.id',
          sib.id = 'sib.id',
          sib.frame.indicator = 'in.F',
          sib.sex = 'sex',
          cell.config = cc,
          weights = 'ego.weight',
          boot.weights = cur.bw,
          return.boot = TRUE
        )
      }, error = function(e) {
        log_error("Failed to process {state}: {e$message}")
        stop(e)
      }),
      warning = function(w) {
        log_warn("Warning in {state}: {w$message}")
        invokeRestart("muffleWarning")
      }
    )
    
    toc()
    log_info("Successfully completed {state}")
    
    cur.ests <- cur.ests$boot.asdr.agg
    cur.ests$state_abbrev <- state
    return(cur.ests)
  },
  .options = furrr_options(seed = TRUE))

if(parallel) {
  plan(sequential)  
}
toc()

log_info("Sibling estimates complete")

```

Rename a few columns 

```{r rename-res}
sib.asdr <- sib.asdr %>% 
  ungroup() %>%
  rename(agegp10 = sib.age,
         asdr = asdr.hat) %>%
  mutate(sex = ifelse(sex==1, 'male', 'female'))
```

```{r aggregate-res}
sib.asdr.agg <- sib.asdr %>%
  group_by(sex, agegp10, time.period, state_abbrev) %>%
  summarize(asdr.hat = mean(asdr),
            asdr.hat.sd = sd(asdr),
            asdr.hat.ci.low = quantile(asdr, .025),
            asdr.hat.ci.high = quantile(asdr, .975))
```

Calculate 47q18, ie cond prob of death between 18 and 65 

```{r calculate-ffqf}
sib.47q18 <- sib.asdr %>%
     mutate(width = ifelse(agegp10 == '[18,25)',
                          7,
                          10)) %>%
    mutate(const.mx.p = exp(-width*asdr),
           v2.mx.p = 1 - (width*asdr)/(1 + (width/2)*asdr)) %>%
    group_by(state_abbrev, sex, time.period, boot_idx) %>%
    summarize(q.47.18 = 1 - prod(const.mx.p),
              q.47.18.alt = 1 - prod(v2.mx.p))

sib.47q18.summ <- sib.47q18 %>%
  group_by(time.period, state_abbrev, sex) %>%
  summarize(q.47.18.mean = mean(q.47.18),
            q.47.18.sd = sd(q.47.18),
            q.47.18.ci.low = quantile(q.47.18, .025),
            q.47.18.ci.high = quantile(q.47.18, .975))
```

Double-check that it does not make a big difference how we calculate prob
(Doesn't look like it does: mean relative difference is around 0.1%)

```{r check-different-ffqf-assumptions}
sib.47q18.check <- sib.47q18 %>%
  group_by(time.period, state_abbrev, sex) %>%
  summarize(q.47.18.mean = mean(q.47.18),
            q.47.18.alt.mean = mean(q.47.18.alt)) %>%
  mutate(rel_diff = (q.47.18.alt.mean - q.47.18.mean) / q.47.18.mean)

summary(sib.47q18.check$rel_diff)
```

### Sibling estimates by region

NB: 1000 bootstrap reps takes about 4 minutes

TODO - THIS IS WHERE IT SEEMS TO CRASH...

```{r sibling-estimates-byregion-bootstrap}

log_info("Starting regional sibling estimates processing")
log_info("Number of regions to process: {length(region.sib.dat)}")
log_info("Using {num.cores} cores")

tic("Running sibling estimates for regions...")
if(parallel) {
  plan(multisession, workers=num.cores)
}

tic("Running sibling estimates for regions...")
sib.region.asdr <- furrr::future_imap_dfr(region.sib.dat,
                                      function(cur.sib.dat, region) {
                                        
                                        library(logger)
                                        log_threshold(TRACE)
                                        log_appender(appender_file(log_file))  # Note: using appender_file, not appender_tee
                                        
                                        log_debug("Starting region: {region}")
                                        log_debug("Number of observations: {nrow(cur.sib.dat)}")
                                                                       
                                        cur.bw <- region.boot.weights[[region]]
                                        
                                        cur.ests <- 
                                          sibling_estimator(sib.dat = cur.sib.dat,
                                          ego.id = 'ego.id',           # column with the respondent id
                                          sib.id = 'sib.id',           # column with sibling id 
                                                                       # (unique for each reported sibling)
                                          sib.frame.indicator = 'in.F',# sibling frame population membership
                                          sib.sex = 'sex',             # column with sibling's sex
                                          cell.config=cc,              # cell configuration we created above
                                          weights='ego.weight',        # column with the respondents' sampling weights
                                          boot.weights=cur.bw,         # bootstrap weights
                                          return.boot=TRUE)           # not returning full bootstrap results for now
                                          
                                        cur.ests <- cur.ests$boot.asdr.agg
                                        cur.ests$region <- region

                                        log_debug("Finished region: {region}")
                                        return(cur.ests)
                                      },
                                      .options = furrr_options(seed = TRUE))

if(parallel) {
  plan(sequential)  
}
toc()

log_info("Region estimates complete")
```

Rename a few columns 

```{r rename-region-res}
sib.region.asdr <- sib.region.asdr %>% 
  ungroup() %>%
  rename(agegp10 = sib.age,
         asdr = asdr.hat) %>%
  mutate(sex = ifelse(sex==1, 'male', 'female'))
```

```{r aggregate-region-res}
sib.region.asdr.agg <- sib.region.asdr %>%
  group_by(sex, agegp10, time.period, region) %>%
  summarize(asdr.hat = mean(asdr),
            asdr.hat.sd = sd(asdr),
            asdr.hat.ci.low = quantile(asdr, .025),
            asdr.hat.ci.high = quantile(asdr, .975))
```

Calculate 47q18, ie cond prob of death between 18 and 65 

```{r calculate-regional-ffqf}
sib.region.47q18 <- sib.region.asdr %>%
     mutate(width = ifelse(agegp10 == '[18,25)',
                          7,
                          10)) %>%
    mutate(const.mx.p = exp(-width*asdr),
           v2.mx.p = 1 - (width*asdr)/(1 + (width/2)*asdr)) %>%
    group_by(region, sex, time.period, boot_idx) %>%
    summarize(q.47.18 = 1 - prod(const.mx.p),
              q.47.18.alt = 1 - prod(v2.mx.p))

sib.region.47q18.summ <- sib.region.47q18 %>%
  group_by(time.period, region, sex) %>%
  summarize(q.47.18.mean = mean(q.47.18),
            q.47.18.sd = sd(q.47.18),
            q.47.18.ci.low = quantile(q.47.18, .025),
            q.47.18.ci.high = quantile(q.47.18, .975))
```

Double-check that it does not make a big difference how we calculate prob
(Doesn't look like it does: mean relative difference is around 0.05%)

```{r check-regional-ffqf-assumptions}
sib.region.47q18.check <- sib.region.47q18 %>%
  group_by(time.period, region, sex) %>%
  summarize(q.47.18.mean = mean(q.47.18),
            q.47.18.alt.mean = mean(q.47.18.alt)) %>%
  mutate(rel_diff = (q.47.18.alt.mean - q.47.18.mean) / q.47.18.mean)

summary(sib.region.47q18.check$rel_diff)
```


### Sibling estimates at national level 

```{r sibling-estimates-national-bootstrap}
log_info("Starting sibling estimates at the national level")
tic("Running sibling estimates at national level...")
sib.national.asdr <- sibling_estimator(sib.dat = national.sib.dat,
                     ego.id = 'ego.id',           # column with the respondent id
                     sib.id = 'sib.id',           # column with sibling id 
                                                  # (unique for each reported sibling)
                     sib.frame.indicator = 'in.F',# sibling frame population membership
                     sib.sex = 'sex',             # column with sibling's sex
                     cell.config=cc,              # cell configuration we created above
                     weights='ego.weight',        # column with the respondents' sampling weights
                     boot.weights=national.boot.weights,         # bootstrap weights
                     return.boot=TRUE)$boot.asdr.agg
toc()
```

Rename a few columns 

```{r rename-national-res}
sib.national.asdr <- sib.national.asdr %>% 
  ungroup() %>%
  rename(agegp10 = sib.age,
         asdr = asdr.hat) %>%
  mutate(sex = ifelse(sex==1, 'male', 'female'))
```

```{r aggregate-national-res}
sib.national.asdr.agg <- sib.national.asdr %>%
  group_by(sex, agegp10, time.period) %>%
  summarize(asdr.hat = mean(asdr),
            asdr.hat.sd = sd(asdr),
            asdr.hat.ci.low = quantile(asdr, .025),
            asdr.hat.ci.high = quantile(asdr, .975))
```

Calculate 47q18, ie cond prob of death between 18 and 65 

```{r calculate-national-ffqf}
sib.national.47q18 <- sib.national.asdr %>%
     mutate(width = ifelse(agegp10 == '[18,25)',
                          7,
                          10)) %>%
    mutate(const.mx.p = exp(-width*asdr),
           v2.mx.p = 1 - (width*asdr)/(1 + (width/2)*asdr)) %>%
    group_by(sex, time.period, boot_idx) %>%
    summarize(q.47.18 = 1 - prod(const.mx.p),
              q.47.18.alt = 1 - prod(v2.mx.p))

sib.national.47q18.summ <- sib.national.47q18 %>%
  group_by(time.period, sex) %>%
  summarize(q.47.18.mean = mean(q.47.18),
            q.47.18.sd = sd(q.47.18),
            q.47.18.ci.low = quantile(q.47.18, .025),
            q.47.18.ci.high = quantile(q.47.18, .975))
```

Double-check that it does not make a big difference how we calculate prob
(Doesn't look like it does: mean relative difference is around 0.04%)

```{r check-national-ffqf-assumptions}
sib.national.47q18.check <- sib.national.47q18 %>%
  group_by(time.period, sex) %>%
  summarize(q.47.18.mean = mean(q.47.18),
            q.47.18.alt.mean = mean(q.47.18.alt)) %>%
  mutate(rel_diff = (q.47.18.alt.mean - q.47.18.mean) / q.47.18.mean)

summary(sib.national.47q18.check$rel_diff)
```


### Save results

Save asdrs and probs in the same format as model output (so they can all be compared)

```{r save-results}
### city ASDRs
sib.tosave <- sib.asdr.agg %>% 
  dplyr::rename(post_mean_asdr=asdr.hat,
                post_sd_asdr=asdr.hat.sd,
                post_ci_high_asdr=asdr.hat.ci.high,
                post_ci_low_asdr=asdr.hat.ci.low) %>%
  mutate(method = 'sib_design')
write_csv(sib.tosave, file.path(out_dir, 'sib_design_asdrs.csv'))

### bootstraps of city ASDRs
sib.tosave.boot <- sib.asdr %>%
  select(state_abbrev, sex, agegp10, boot_idx, post_mean_asdr=asdr) %>%
  mutate(method='sib_design')
write_csv(sib.tosave.boot, file.path(out_dir, 'sib_design_asdrs_boot.csv'))

### city probs
sib.47q18.tosave <- sib.47q18.summ %>% 
  dplyr::rename(post_mean_q = q.47.18.mean,
                post_sd_q = q.47.18.sd,
                post_ci_low_q = q.47.18.ci.low,
                post_ci_high_q = q.47.18.ci.high) %>%
  mutate(method = 'sib_design')
write_csv(sib.47q18.tosave, file.path(out_dir, 'sib_design_probs.csv'))

### bootstraps of city probs
sib.47q18.boot <- sib.47q18 %>% 
  select(state_abbrev, sex, boot_idx, q.47.18) %>%
  mutate(method = 'sib_design')
write_csv(sib.47q18.boot, file.path(out_dir, 'sib_design_probs_boot.csv'))

### region ASDRs
sib.region.tosave <- sib.region.asdr.agg %>% 
  dplyr::rename(post_mean_asdr=asdr.hat,
                post_sd_asdr=asdr.hat.sd,
                post_ci_high_asdr=asdr.hat.ci.high,
                post_ci_low_asdr=asdr.hat.ci.low) %>%
  mutate(method = 'sib_design')
write_csv(sib.region.tosave, file.path(out_dir, 'sib_design_asdrs_region.csv'))

# all bootstrap resamples for regional ASDRs
sib.region.boot <- sib.region.asdr %>%
  select(region, sex, agegp10, boot_idx, post_mean_asdr=asdr) %>%
  mutate(method='sib_design')
write_csv(sib.region.boot, file.path(out_dir, 'sib_design_asdrs_region_boot.csv'))

### region probs
sib.region.47q18.tosave <- sib.region.47q18.summ %>% 
  dplyr::rename(post_mean_q = q.47.18.mean,
                post_sd_q = q.47.18.sd,
                post_ci_low_q = q.47.18.ci.low,
                post_ci_high_q = q.47.18.ci.high) %>%
  mutate(method = 'sib_design')
write_csv(sib.region.47q18.tosave, 
          file.path(out_dir, 'sib_design_probs_region.csv'))

### all bootstrap resamples for regional probs
sib.region.47q18.boot <- sib.region.47q18 %>% 
  select(region, sex, boot_idx, q.47.18) %>%
  mutate(method = 'sib_design')
write_csv(sib.region.47q18.boot, 
          file.path(out_dir, 'sib_design_probs_region_boot.csv'))

### national ASDRs
sib.national.tosave <- sib.national.asdr.agg %>% 
  dplyr::rename(post_mean_asdr=asdr.hat,
                post_sd_asdr=asdr.hat.sd,
                post_ci_high_asdr=asdr.hat.ci.high,
                post_ci_low_asdr=asdr.hat.ci.low) %>%
  mutate(method = 'sib_design')
write_csv(sib.national.tosave, file.path(out_dir, 'sib_design_asdrs_national.csv'))

# all bootstrap resamples for national ASDRs
sib.national.boot <- sib.national.asdr %>%
  select(sex, agegp10, boot_idx, post_mean_asdr=asdr) %>%
  mutate(method='sib_design')
write_csv(sib.national.boot, file.path(out_dir, 'sib_design_asdrs_national_boot.csv'))

### national probs
sib.national.47q18.tosave <- sib.national.47q18.summ %>% 
  dplyr::rename(post_mean_q = q.47.18.mean,
                post_sd_q = q.47.18.sd,
                post_ci_low_q = q.47.18.ci.low,
                post_ci_high_q = q.47.18.ci.high) %>%
  mutate(method = 'sib_design')
write_csv(sib.national.47q18.tosave, 
          file.path(out_dir, 'sib_design_probs_national.csv'))

### all bootstrap resamples for national probs
sib.national.47q18.boot <- sib.national.47q18 %>% 
  select(sex, boot_idx, q.47.18) %>%
  mutate(method = 'sib_design')
write_csv(sib.national.47q18.boot, 
          file.path(out_dir, 'sib_design_probs_national_boot.csv'))
```

## 12-month estimates


```{r sibling-estimates-with-bootstrap-12mo}
tic("Running sibling estimates for states...")

if(parallel) {
  plan(multisession, workers=num.cores)
}

#sib.asdr <- purrr::imap_dfr(city.sib.dat,
sib.asdr.12mo <- furrr::future_imap_dfr(city.sib.dat,
                                      function(cur.sib.dat, state) {
                                        
                                       library(logger)
                                       log_threshold(TRACE)
                                       log_appender(appender_file(log_file))  # Note: using appender_file, not appender_tee
                                       
                                       log_debug("Starting state 12mo estimates: {state}")
                                       log_debug("Number of observations: {nrow(cur.sib.dat)}")
    
                                        cat(glue::glue("Starting {state}...\n\n"))
                                       
                                       ## reload these weights to avoid memory errors in future... 
                                        #boot.weights <- readRDS(file.path(survey_data_dir, boot.weights.fn)) 
                                        #city.boot.weights <- setNames(map(all.states,
                                        #                                  function(state) {
                                        #                                    cbw <- boot.weights %>% 
                                        #                                      filter(state_abbrev==state) %>% 
                                        #                                      select(-state_abbrev) %>%
                                        #                                      ## we need the id in the bootstrap data to line up with the id in the
                                        #                                      ## sibling reports
                                        #                                      rename(ego.id = id)
                                        #                                    return(cbw)
                                        #                                  }),
                                        #                              all.states)
                                                                       
                                        cur.bw <- city.boot.weights[[state]]
                                        
                                        cur.ests <- 
                                          sibling_estimator(sib.dat = cur.sib.dat,
                                          ego.id = 'ego.id',           # column with the respondent id
                                          sib.id = 'sib.id',           # column with sibling id 
                                                                       # (unique for each reported sibling)
                                          sib.frame.indicator = 'in.F',# sibling frame population membership
                                          sib.sex = 'sex',             # column with sibling's sex
                                          cell.config=cc_12mo,              # cell configuration we created above
                                          weights='ego.weight',        # column with the respondents' sampling weights
                                          boot.weights=cur.bw,         # bootstrap weights
                                          return.boot=TRUE)           # not returning full bootstrap results for now
                                          
                                        cur.ests <- cur.ests$boot.asdr.agg
                                        cur.ests$state_abbrev <- state
                                        return(cur.ests)
                                      },
                                      .options = furrr_options(seed = TRUE))

if(parallel) {
  plan(sequential)  
}

toc()

log_info("12 mo. state estimates complete")
```


Rename a few columns 

```{r rename-aggregate-res-12mo}
sib.asdr.12mo <- sib.asdr.12mo %>% 
  ungroup() %>%
  rename(agegp10 = sib.age,
         asdr = asdr.hat) %>%
  mutate(sex = ifelse(sex==1, 'male', 'female'))

sib.asdr.agg.12mo <- sib.asdr.12mo %>%
  group_by(sex, agegp10, time.period, state_abbrev) %>%
  summarize(asdr.hat = mean(asdr),
            asdr.hat.sd = sd(asdr),
            asdr.hat.ci.low = quantile(asdr, .025, na.rm=TRUE),
            asdr.hat.ci.high = quantile(asdr, .975, na.rm=TRUE))
```

Calculate 47q18, ie cond prob of death between 18 and 65 

```{r calculate-ffqf-12mo}
sib.47q18.12mo <- sib.asdr.12mo %>%
     mutate(width = ifelse(agegp10 == '[18,25)',
                          7,
                          10)) %>%
    mutate(const.mx.p = exp(-width*asdr),
           v2.mx.p = 1 - (width*asdr)/(1 + (width/2)*asdr)) %>%
    group_by(state_abbrev, sex, time.period, boot_idx) %>%
    summarize(q.47.18 = 1 - prod(const.mx.p),
              q.47.18.alt = 1 - prod(v2.mx.p))

sib.47q18.summ.12mo <- sib.47q18.12mo %>%
  group_by(time.period, state_abbrev, sex) %>%
  summarize(q.47.18.mean = mean(q.47.18),
            q.47.18.sd = sd(q.47.18),
            q.47.18.ci.low = quantile(q.47.18, .025, na.rm=TRUE),
            q.47.18.ci.high = quantile(q.47.18, .975, na.rm=TRUE))
```



```{r save-results-12mo}
### city ASDRs
sib.tosave.12mo <- sib.asdr.agg.12mo %>% 
  dplyr::rename(post_mean_asdr=asdr.hat,
                post_sd_asdr=asdr.hat.sd,
                post_ci_high_asdr=asdr.hat.ci.high,
                post_ci_low_asdr=asdr.hat.ci.low) %>%
  mutate(method = 'sib_design')
write_csv(sib.tosave.12mo, file.path(out_dir, 'sib_12mo_design_asdrs.csv'))

### bootstraps of city ASDRs
sib.tosave.boot.12mo <- sib.asdr.12mo %>%
  select(state_abbrev, sex, agegp10, boot_idx, post_mean_asdr=asdr) %>%
  mutate(method='sib_design')
write_csv(sib.tosave.boot.12mo, file.path(out_dir, 'sib_12mo_design_asdrs_boot.csv'))

### city probs
sib.47q18.tosave.12mo <- sib.47q18.summ.12mo %>% 
  dplyr::rename(post_mean_q = q.47.18.mean,
                post_sd_q = q.47.18.sd,
                post_ci_low_q = q.47.18.ci.low,
                post_ci_high_q = q.47.18.ci.high) %>%
  mutate(method = 'sib_design')
write_csv(sib.47q18.tosave.12mo, file.path(out_dir, 'sib_12mo_design_probs.csv'))

### bootstraps of city probs
sib.47q18.boot.12mo <- sib.47q18.12mo %>% 
  select(state_abbrev, sex, boot_idx, q.47.18) %>%
  mutate(method = 'sib_design')
write_csv(sib.47q18.boot.12mo, file.path(out_dir, 'sib_12mo_design_probs_boot.csv'))
```


```{r}
log_info("All sibling estimates complete")
toc()
```




