---
title: "Compare survey estimates to vital registration death rates"
output: html_notebook
---

```{r}
library(here)
library(rmarkdown)
library(tictoc)
```

```{r}
code_dir <- here('code')

comparison_script_fn <- file.path(code_dir, "99_vr_comparison.Rmd")
```

NB: it takes about 25 minutes to run all 4 comparisons on Dennis's computer.

```{r}
tic("Running all 4 comparison scripts")
```

## Compare to VR

Compare to vital registration at the city level

```{r}
rmarkdown::render(comparison_script_fn,
                  output_file = "comparison_city_vr",
                  params=list(
                    comparison_name = 'vr_comparison',
                    geo_name = 'city'
                  ))
```

Compare to vital registration at the regional level

```{r}
rmarkdown::render(comparison_script_fn,
                  output_file = "comparison_region_vr",
                  params=list(
                    comparison_name = 'vr_comparison',
                    geo_name = 'region'
                  ))
```

Compare to vital registration at the national level

```{r}
rmarkdown::render(comparison_script_fn,
                  output_file = "comparison_national_vr",
                  params=list(
                    comparison_name = 'vr_comparison',
                    geo_name = 'national'
                  ))
```

## Compare to adjusted VR

Compare to adjusted vital registration at the city level

```{r}
rmarkdown::render(comparison_script_fn,
                  output_file = "comparison_city_adj_vr",
                  params=list(
                    comparison_name = 'vr_adj_comparison',
                    geo_name = 'city'
                  ))
```

Compare to adjusted vital registration at the regional level

```{r}
rmarkdown::render(comparison_script_fn,
                  output_file = "comparison_region_adj_vr",
                  params=list(
                    comparison_name = 'vr_adj_comparison',
                    geo_name = 'region'
                  ))
```

Compare to adjusted vital registration at the national level

```{r}
rmarkdown::render(comparison_script_fn,
                  output_file = "comparison_national_adj_vr",
                  params=list(
                    comparison_name = 'vr_adj_comparison',
                    geo_name = 'national'
                  ))
```


```{r}
toc()
```

