---
title: "Plots combining results"
output: html_notebook
---

TODO

- add plot with var and bias scatterplots combined

```{r}
library(here)
library(rmarkdown)
library(tidyverse)
library(patchwork)
library(latex2exp)
library(glue)
```

```{r}
code_dir <- here('code')
out_dir <- here('out')
data_dir <- here('data')
```


```{r}
vr_dir <- file.path(out_dir, 'vr_comparison')
vradj_dir <- file.path(out_dir, 'vr_adj_comparison')

vr_city_dir <- file.path(vr_dir, 'city')
vr_region_dir <- file.path(vr_dir, 'region')
vr_national_dir <- file.path(vr_dir, 'national')

vradj_city_dir <- file.path(vradj_dir, 'city')
vradj_region_dir <- file.path(vradj_dir, 'region')
vradj_national_dir <- file.path(vradj_dir, 'national')
```

```{r}
# load city info
cities <- read_csv(file.path(data_dir, "cities.csv"))
```

### Plot direct comparisons between sibling and network estimates

```{r}
p1_ca <- readRDS(file.path(vr_city_dir, 'direct_asdr_logged.rds'))
p1_cp <- readRDS(file.path(vr_city_dir, 'direct_probs_logged.rds'))
p1_ra <- readRDS(file.path(vr_region_dir, 'direct_asdr_logged.rds'))
p1_rp <- readRDS(file.path(vr_region_dir, 'direct_probs_logged.rds'))
p1_na <- readRDS(file.path(vr_national_dir, 'direct_asdr_logged.rds'))
p1_np <- readRDS(file.path(vr_national_dir, 'direct_probs_logged.rds'))
```

```{r}
design <- "
  1122
  3344
  5555
"
p1 <- (p1_cp + ggtitle("City, Probability")) + 
      (p1_ca + ggtitle("City, Age-specific death rate")) + 
      (p1_rp + ggtitle("Region, Probability")) +
      (p1_ra + ggtitle("Region, Age-specific death rate")) +
  plot_layout(guides='collect', design=design) & 
  theme(text = element_text(size=7),
        legend.position='bottom',
        legend.box='vertical',
        legend.spacing.y=unit(-.3, 'cm')) &
  guides(color=guide_legend(nrow=2, title="Age", override.aes=list(alpha=1)))

ggsave(filename=file.path(out_dir, "direct_estimates.pdf"),
       p1)
knitr::plot_crop(file.path(out_dir, "direct_estimates.pdf"))

# for talks, save individual versions of these plots
p_dim <- 4
ggsave(filename=file.path(out_dir, "direct_sib_net_city_prob.png"), p1_cp, width=p_dim, height=p_dim)
ggsave(filename=file.path(out_dir, "direct_sib_net_city_asdr.png"), p1_ca, width=p_dim, height=p_dim)
ggsave(filename=file.path(out_dir, "direct_sib_net_region_prob.png"), p1_rp, width=p_dim, height=p_dim)
ggsave(filename=file.path(out_dir, "direct_sib_net_region_asdr.png"), p1_ra, width=p_dim, height=p_dim)

p1
```


### Scatterplot w/ estimates and VR 

```{r}
p1.5_asdr_c <- readRDS(file.path(vr_city_dir, 'asdr_point_scatter_log.rds'))
p1.5_asdr_r <- readRDS(file.path(vr_region_dir, 'asdr_point_scatter_log.rds'))
p1.5_prob_c <- readRDS(file.path(vr_city_dir, 'prob_point_scatter.rds'))
p1.5_prob_r <- readRDS(file.path(vr_region_dir, 'prob_point_scatter.rds'))
```

```{r}
design <- "
  1122
  3344
"

p1.5 <- (((p1.5_prob_c + ggtitle("City, Probability")) 
          + (p1.5_asdr_c + ggtitle("City, Age-specific death rate"))) / 
           ((p1.5_prob_r + ggtitle("Region, Probability")) + 
             p1.5_asdr_r + ggtitle("Region, Age-specific death rate"))) +
  plot_layout(guides='collect') &
  theme(text = element_text(size=7),
        legend.position='bottom',
        legend.box='vertical',
        legend.spacing.y=unit(-.3, 'cm')) &
  guides(color=guide_legend(nrow=2, title="Age", override.aes=list(alpha=1)))
  #plot_layout(guides='collect', design=design) & 
#  plot_layout(guides='collect', design=design)
  #theme(text = element_text(size=7),
  #      legend.position='bottom',
  #      legend.box='vertical',
  #      legend.spacing.y=unit(-.3, 'cm')) &
  #guides(color=guide_legend(nrow=2, title="Age"))
  #theme(text = element_text(size=7))

ggsave(filename=file.path(out_dir, "est_point_scatter_log.pdf"),
       p1.5)

# for talks, save individual versions of these plots
p_dim <- 4
ggsave(filename=file.path(out_dir, "vr_compare_sib_net_city_prob.png"), p1.5_prob_c, 
       width=p_dim, height=p_dim)
ggsave(filename=file.path(out_dir, "vr_compare_sib_net_city_asdr.png"), p1.5_asdr_c, 
       width=p_dim, height=p_dim)
ggsave(filename=file.path(out_dir, "vr_compare_sib_net_region_prob.png"), p1.5_prob_r, 
       width=p_dim, height=p_dim)
ggsave(filename=file.path(out_dir, "vr_compare_sib_net_region_asdr.png"), p1.5_asdr_r, 
       width=p_dim, height=p_dim)

p1.5
```


### Bias-variance decomposition (BVD) plot

```{r}
p_bvd_as_bias <- readRDS(file.path(vr_city_dir, 'bvd_as_bias_plot.rds'))

p_bvd_as_se <- readRDS(file.path(vr_city_dir, 'bvd_as_se_plot.rds'))

p_bvd_as_rmse <- readRDS(file.path(vr_city_dir, 'bvd_as_rmse_plot.rds'))
```


```{r}
#bvd_as_city <- p_bvd_as_rmse / p_bvd_as_bias / p_bvd_as_se + 
bvd_as_city <- 
  (p_bvd_as_se + ggtitle("A")) +
  (p_bvd_as_bias + ggtitle("B")) +
  (p_bvd_as_rmse + ggtitle("C")) +
  plot_layout(guides='collect') &
  #theme(text = element_text(size=7)) &
  theme(text = element_text(size=7),
        legend.position='bottom',
        legend.box='vertical',
        legend.spacing.y=unit(-.3, 'cm')) & 
  #guides(color=guide_legend(nrow=2, title="Age"))
  guides(color=guide_legend(title="Age"))

ggsave(filename=file.path(out_dir, "bvd_as_city.pdf"),
       bvd_as_city)

bvd_as_city
```

```{r}
#bvd_as_city <- p_bvd_as_rmse / p_bvd_as_bias / p_bvd_as_se + 
vd_as_city <- 
  (p_bvd_as_se + ggtitle("A")) +
  (p_bvd_as_bias + ggtitle("B")) +
  plot_layout(guides='collect') &
  #theme(text = element_text(size=7)) &
  theme(text = element_text(size=7),
        legend.position='bottom',
        legend.box='vertical',
        legend.spacing.y=unit(-.3, 'cm')) & 
  #guides(color=guide_legend(nrow=2, title="Age"))
  guides(color=guide_legend(title="Age"))

ggsave(filename=file.path(out_dir, "vd_as_city.pdf"),
       height=6,
       vd_as_city)

vd_as_city
```

### Bias-variance decomposition (BVD) plot from VR sensitivity check


```{r}
p_bvd_as_bias_vrsens <- readRDS(file.path(vradj_city_dir, 'bvd_as_bias_plot.rds'))

p_bvd_as_se_vrsens <- readRDS(file.path(vradj_city_dir, 'bvd_as_se_plot.rds'))

p_bvd_as_rmse_vrsens <- readRDS(file.path(vradj_city_dir, 'bvd_as_rmse_plot.rds'))
```


```{r}
bvd_as_city_vrsens <- 
  p_bvd_as_se_vrsens +
  p_bvd_as_bias_vrsens +
  p_bvd_as_rmse_vrsens +
  #p_bvd_as_se /
  #p_bvd_as_bias /     
  #p_bvd_as_rmse +
  plot_layout(guides='collect') &
  #theme(text = element_text(size=7)) &
  theme(text = element_text(size=7),
        legend.position='bottom',
        legend.box='vertical',
        legend.spacing.y=unit(-.3, 'cm')) & 
  #guides(color=guide_legend(nrow=2, title="Age"))
  guides(color=guide_legend(title="Age"))

ggsave(filename=file.path(out_dir, "bvd_as_city_vrsens.pdf"),
       bvd_as_city_vrsens)

bvd_as_city_vrsens
```


### Error difference pointrange figure

The city asdr boot estimates have the average asdr error across 27 cities for each bootstrap rep (as well as results for prob)
The region asdr boot estimates have the average region asdr error across 5 regions for each bootstrap rep (as well as results for prob)
et cetera

```{r}
errs_cv <- read_csv(file.path(vr_city_dir, 'err_diffs_boot.csv'))
errs_rv <- read_csv(file.path(vr_region_dir, 'err_diffs_boot.csv'))
errs_nv <- read_csv(file.path(vr_national_dir, 'err_diffs_boot.csv'))

errs_ca <- read_csv(file.path(vradj_city_dir, 'err_diffs_boot.csv'))
errs_ra <- read_csv(file.path(vradj_region_dir, 'err_diffs_boot.csv'))
errs_na <- read_csv(file.path(vradj_national_dir, 'err_diffs_boot.csv'))
```

### Err diffs boot

```{r}
err_diffs_boot <- bind_rows(errs_cv,
                            errs_rv,
                            errs_nv,
                            errs_ca,
                            errs_ra,
                            errs_na)

err_diffs_summ <- err_diffs_boot %>%
  group_by(comparison_name, geo_name, qty, loss) %>%
  summarize(diff_nminuss_mean = mean(err.n.minus.s),
            diff_nminuss_ci_low = quantile(err.n.minus.s, .025),
            diff_nminuss_ci_high = quantile(err.n.minus.s, .975),
            network_err = mean(err.n),
            network_err_ci_low = quantile(err.n, .025),
            network_err_ci_high = quantile(err.n, .975),
            network_err_sd = sd(err.n),
            network_err_ci_width = quantile(err.n, .975) - quantile(err.n, .025),
            sibling_err = mean(err.s),
            sibling_err_ci_low = quantile(err.s, .025),
            sibling_err_ci_high = quantile(err.s, .975),
            sibling_err_sd = sd(err.s),
            sibling_err_ci_width = quantile(err.s, .975) - quantile(err.s, .025),
            .groups='drop')

err_diffs_summ
```

```{r}
recode_loss <- c('mare'='MARE', 'mse'='MSE', 'rmse'='RMSE')
recode_qty <- c('asdr'='Age-specifc\ndeath rates', 'prob'='Probability of\ndying at\nadult ages')
recode_geo <- c('city'='City-level\nestimates', 
                'region'='Pooled\nregion-level\nestimates', 
                'national'='Pooled\nnational-level\nestimates')

scale_linetype_values <- setNames(c("solid", "dashed", "dashed"),
                                  paste(recode_geo))

scale_shape_values <- setNames(c(19, 1, 1),
                               paste(recode_geo))

annrelsize <- 3 

mare_prob_annheight <- 0.15
mare_asdr_annheight <- .22

mse_prob_annheight <- 0.0035
mse_asdr_annheight <- 8 

rmse_prob_annheight <- .025 
rmse_asdr_annheight <- 1 

#shade_rect_color <- 'lightgrey'
shade_rect_color <- '#EEEEEE'
shade_rect_alpha <- .05

for_pr_plot_base <- err_diffs_summ %>%
  mutate(loss = dplyr::recode(loss, !!!recode_loss)) %>%
  mutate(qty= dplyr::recode(qty, !!!recode_qty)) %>%
  mutate(geo_name= dplyr::recode_factor(geo_name, !!!recode_geo))

for_pr_plot <- for_pr_plot_base %>%
  filter(comparison_name == 'vr_comparison')

for_pr_vrsens_plot <- for_pr_plot_base %>%
  filter(comparison_name == 'vr_adj_comparison')

make_pr_plot <- function(for_pr_df) {
    
  pr_asdr_mare <- 
    for_pr_df %>%
    filter(loss == 'MARE', qty==recode_qty['asdr']) %>%
    ggplot(.) +
    geom_hline(aes(yintercept = 0), color='darkgrey') +
    geom_pointrange(aes(x=geo_name,
                        y=diff_nminuss_mean,
                        ymin=diff_nminuss_ci_low,
                        ymax=diff_nminuss_ci_high,
                        shape = geo_name,
                        linetype = geo_name)) +
    theme_bw() +
    geom_rect(aes(xmin=1.5,
                  xmax=Inf,
                  ymin=-Inf,
                  ymax=Inf),
              color=shade_rect_color,
              alpha=shade_rect_alpha) +
    #theme_minimal() +
    ylab("Network MARE- Sibling MARE") +
    xlab("") +
    annotate(geom='text', 
             label="Sibling is better ->", 
             y=mare_asdr_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    annotate(geom='text', 
             label="<- Network is better ", 
             y=-mare_asdr_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    scale_y_continuous(labels = scales::percent_format(),
                       limits = c(-.45, .45)) +
    scale_linetype_manual(values=scale_linetype_values, guide = "none") +
    scale_shape_manual(values=scale_shape_values, guide = "none") +
    NULL
  
  pr_prob_mare <- 
    for_pr_df %>%
    filter(loss == 'MARE', qty==recode_qty['prob']) %>%
    ggplot(.) +
    geom_hline(aes(yintercept = 0), color='darkgrey') +
    geom_pointrange(aes(x=geo_name,
                        y=diff_nminuss_mean,
                        ymin=diff_nminuss_ci_low,
                        ymax=diff_nminuss_ci_high,
                        shape = geo_name,
                        linetype=geo_name)) +
    theme_bw() +
    geom_rect(aes(xmin=1.5,
                  xmax=Inf,
                  ymin=-Inf,
                  ymax=Inf),
              color=shade_rect_color,
              alpha=shade_rect_alpha) +
    #theme_minimal() +
    ylab("Network MARE- Sibling MARE") +
    xlab("") +
    annotate(geom='text', 
             label="Sibling is better ->", 
             y=mare_prob_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    annotate(geom='text', 
             label="<- Network is better ", 
             y=-mare_prob_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    scale_y_continuous(labels = scales::percent_format(),
                       limits=c(-.3, .3)) +
    scale_shape_manual(values=scale_shape_values, guide = "none") +
    scale_linetype_manual(values=scale_linetype_values, guide = "none") +
    NULL
    
  pr_prob_mse <- 
    for_pr_df %>%
    filter(loss == 'MSE', qty==recode_qty['prob']) %>%
    ggplot(.) +
    geom_hline(aes(yintercept = 0), color='darkgrey') +
    geom_pointrange(aes(x=geo_name,
                        y=diff_nminuss_mean,
                        ymin=diff_nminuss_ci_low,
                        ymax=diff_nminuss_ci_high,
                        shape = geo_name,
                        linetype=geo_name)) +
    theme_bw() +
    geom_rect(aes(xmin=1.5,
                  xmax=Inf,
                  ymin=-Inf,
                  ymax=Inf),
              color=shade_rect_color,
              alpha=shade_rect_alpha) +
    #theme_minimal() +
    ylab("Network MSE - Sibling MSE") +
    xlab("") +
    annotate(geom='text', 
             label="Sibling is better ->", 
             y=mse_prob_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    annotate(geom='text', 
             label="<- Network is better ", 
             y=-mse_prob_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    scale_y_continuous(limits=c(-.008, .008)) +
    scale_shape_manual(values=scale_shape_values, guide = "none") +
    scale_linetype_manual(values=scale_linetype_values, guide = "none") +
    NULL
    
  pr_asdr_mse <- 
    for_pr_df %>%
    filter(loss == 'MSE', qty==recode_qty['asdr']) %>%
    ggplot(.) +
    geom_hline(aes(yintercept = 0), color='darkgrey') +
    geom_pointrange(aes(x=geo_name,
                        y=diff_nminuss_mean,
                        ymin=diff_nminuss_ci_low,
                        ymax=diff_nminuss_ci_high,
                        shape = geo_name,
                        linetype=geo_name)) +
    theme_bw() +
    geom_rect(aes(xmin=1.5,
                  xmax=Inf,
                  ymin=-Inf,
                  ymax=Inf),
              color=shade_rect_color,
              alpha=shade_rect_alpha) +
    #theme_minimal() +
    ylab("Network MSE - Sibling MSE") +
    xlab("") +
    annotate(geom='text', 
             label="Sibling is better ->", 
             y=mse_asdr_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    annotate(geom='text', 
             label="<- Network is better ", 
             y=-mse_asdr_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    scale_y_continuous(limits=c(-15, 15)) +
    scale_shape_manual(values=scale_shape_values, guide = "none") +
    scale_linetype_manual(values=scale_linetype_values, guide = "none") +
    NULL
  
  pr_prob_rmse <- 
    for_pr_df %>%
    filter(loss == 'RMSE', qty==recode_qty['prob']) %>%
    ggplot(.) +
    geom_hline(aes(yintercept = 0), color='darkgrey') +
    geom_pointrange(aes(x=geo_name,
                        y=diff_nminuss_mean,
                        ymin=diff_nminuss_ci_low,
                        ymax=diff_nminuss_ci_high,
                        shape = geo_name,
                        linetype=geo_name)) +
    theme_bw() +
    geom_rect(aes(xmin=1.5,
                  xmax=Inf,
                  ymin=-Inf,
                  ymax=Inf),
              color=shade_rect_color,
              alpha=shade_rect_alpha) +
    #theme_minimal() +
    ylab("Network RMSE - Sibling RMSE") +
    xlab("") +
    annotate(geom='text', 
             label="Sibling is better ->", 
             y=rmse_prob_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    annotate(geom='text', 
             label="<- Network is better ", 
             y=-rmse_prob_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    scale_y_continuous(limits=c(-.05, .05)) +
    scale_linetype_manual(values=scale_linetype_values, guide = "none") +
    scale_shape_manual(values=scale_shape_values, guide = "none") +
    NULL
  
  pr_asdr_rmse <- 
    for_pr_df %>%
    filter(loss == 'RMSE', qty==recode_qty['asdr']) %>%
    ggplot(.) +
    geom_hline(aes(yintercept = 0), color='darkgrey') +
    geom_pointrange(aes(x=geo_name,
                        y=diff_nminuss_mean,
                        ymin=diff_nminuss_ci_low,
                        ymax=diff_nminuss_ci_high,
                        shape = geo_name,
                        linetype=geo_name)) +
    theme_bw() +
    geom_rect(aes(xmin=1.5,
                  xmax=Inf,
                  ymin=-Inf,
                  ymax=Inf),
              color=shade_rect_color,
              alpha=shade_rect_alpha) +
    #theme_minimal() +
    ylab("Network RMSE - Sibling RMSE") +
    xlab("") +
    annotate(geom='text', 
             label="Sibling is better ->", 
             y=rmse_asdr_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    annotate(geom='text', 
             label="<- Network is better ", 
             y=-rmse_asdr_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    scale_y_continuous(limits=c(-2, 2)) +
    scale_shape_manual(values=scale_shape_values, guide = "none") +
    scale_linetype_manual(values=scale_linetype_values, guide = "none") +
    NULL
    
  #pr_asdr_mare
  #pr_prob_mare
  #pr_prob_mse
  #pr_asdr_mse
  #pr_prob_rmse
  #pr_asdr_rmse
  
  meta_layout <- "
  #cccddd
  aeeefff
  bggghhh
  "
  
  row1_title <- ggplot() + annotate(geom='text', 
                                    x=1,y=1, 
                                    label='bold(underline(ASDR))', 
                                    angle=90,
                                    parse=TRUE) +  theme_void()
  row2_title <- ggplot() + annotate(geom='text', 
                                    x=1,y=1, 
                                    label='bold(underline(Probability~of~Death))', 
                                    angle=90,
                                    parse=TRUE) + theme_void()
  col1_title <- ggplot() + annotate(geom='text', 
                                    x=1,y=1, 
                                    label='bold(underline(MARE))',
                                    parse=TRUE) + theme_void()
  col2_title <- ggplot() + annotate(geom='text', 
                                    x=1,y=1, 
                                    #label='bold(underline(MSE))',
                                    label='bold(underline(RMSE))',
                                    parse=TRUE) + theme_void()
  
  plotlist <- list(a=row1_title,
                   b=row2_title,
                   c=col1_title,
                   d=col2_title,
                   e=pr_asdr_mare,
                   #f=pr_asdr_mse,
                   f=pr_asdr_rmse,
                   g=pr_prob_mare,
                   h=pr_prob_rmse)
                   #h=pr_prob_mse)
    
  final_plot <- wrap_plots(
       plotlist,
       guides='collect',
       design=meta_layout,
       widths=c(2,10,10),
       heights=c(2,10,10))
    
  
  return(final_plot)
}

final_err_compare <- make_pr_plot(for_pr_plot)
  
saveRDS(final_err_compare, file.path(out_dir, "err_compare_all.rds"))
fec.size <- 8 
ggsave(filename=file.path(out_dir, "err_compare_all.pdf"),
       plot=final_err_compare,
       height=fec.size,
       width=fec.size)
ggsave(filename=file.path(out_dir, "err_compare_all.png"),
       plot=final_err_compare,
       height=fec.size,
       width=fec.size)

tmp_rmse <- for_pr_plot %>% filter(qty=="Age-specifc\ndeath rates", 
                                   loss=="RMSE", 
                                   geo_name == "City-level\nestimates")
tmp_mare <- for_pr_plot %>% filter(qty=="Age-specifc\ndeath rates", 
                                   loss=="MARE", 
                                   geo_name == "City-level\nestimates")

glue::glue("
           
           On average, network estimates were about {tmp_rmse$diff_nminuss_mean} RMSE units better than sibling estimates.  
           This difference is {tmp_mare$diff_nminuss_mean} percent using MARE.
           
           ")

final_err_compare
```


Simple barplot with RMSE comparison at city level

```{r}
barplot_asdr_rmse_df <- 
    for_pr_plot %>%
    filter(loss == 'RMSE', str_detect(geo_name, 'City-level'), qty==recode_qty['asdr']) %>%
  select(comparison_name, geo_name, qty, loss, network_err, sibling_err) %>%
  pivot_longer(cols=c('network_err', 'sibling_err'),
               names_to='method',
               values_to='RMSE') %>%
  mutate(method = recode(method,
                         network_err='Network', 
                         sibling_err='Sibling'))

barplot_asdr_rmse <- barplot_asdr_rmse_df %>%
  ggplot(.) +
  geom_bar(aes(x=method, y=RMSE), stat='identity') +
  theme_minimal() +
  xlab("") +
  ylab("Root Mean Squared Error")

saveRDS(barplot_asdr_rmse, file.path(out_dir, "rmse_barplot.rds"))
fec.size <- 3
ggsave(filename=file.path(out_dir, "rmse_barplot.pdf"),
       plot=barplot_asdr_rmse,
       height=fec.size,
       width=fec.size)
ggsave(filename=file.path(out_dir, "rmse_barplot.png"),
       plot=barplot_asdr_rmse,
       height=fec.size,
       width=fec.size)

net_rmse_tot <- barplot_asdr_rmse_df %>% filter(method=='Network') %>% pull(RMSE)
sib_rmse_tot <- barplot_asdr_rmse_df %>% filter(method=='Sibling') %>% pull(RMSE)

glue::glue("
           Sibling RMSE is {round(100 * (sib_rmse_tot - net_rmse_tot)/net_rmse_tot,3)} percent higher than network RMSE
           Network RMSE is {round(100*  (net_rmse_tot - sib_rmse_tot)/sib_rmse_tot,3)} percent lower than sibling RMSE
           ")
```


## VR sensitivity version of figure above

```{r}
vrsens_err_compare <- make_pr_plot(for_pr_vrsens_plot)
  
saveRDS(vrsens_err_compare, file.path(out_dir, "err_compare_all_vrsens.rds"))
fec.size <- 8 
ggsave(filename=file.path(out_dir, "err_compare_all_vrsens.pdf"),
       plot=vrsens_err_compare,
       height=fec.size,
       width=fec.size)
ggsave(filename=file.path(out_dir, "err_compare_all_vrsens.png"),
       plot=vrsens_err_compare,
       height=fec.size,
       width=fec.size)

vrsens_err_compare
```



