---
title: "Plots combining results"
output: html_notebook
---


```{r}
library(here)
library(rmarkdown)
library(tidyverse)
library(patchwork)
library(latex2exp)
library(glue)
```

```{r}
code_dir <- here('code')
out_dir <- here('out')
data_dir <- here('data')
```


```{r}
vr_dir <- file.path(out_dir, 'vr_comparison')
vradj_dir <- file.path(out_dir, 'vr_adj_comparison')

vr_city_dir <- file.path(vr_dir, 'city')
vr_region_dir <- file.path(vr_dir, 'region')
vr_national_dir <- file.path(vr_dir, 'national')

vradj_city_dir <- file.path(vradj_dir, 'city')
vradj_region_dir <- file.path(vradj_dir, 'region')
vradj_national_dir <- file.path(vradj_dir, 'national')
```

```{r}
# load city info
cities <- read_csv(file.path(data_dir, "cities.csv"))
```

### Plot direct comparisons between sibling and network estimates

```{r}
p1_ca <- readRDS(file.path(vr_city_dir, 'direct_asdr_logged.rds'))
p1_cp <- readRDS(file.path(vr_city_dir, 'direct_probs_logged.rds'))
p1_ra <- readRDS(file.path(vr_region_dir, 'direct_asdr_logged.rds'))
p1_rp <- readRDS(file.path(vr_region_dir, 'direct_probs_logged.rds'))
p1_na <- readRDS(file.path(vr_national_dir, 'direct_asdr_logged.rds'))
p1_np <- readRDS(file.path(vr_national_dir, 'direct_probs_logged.rds'))
```

```{r}
design <- "
  1122
  3344
  5555
"
p1 <- (p1_cp + ggtitle("City, Probability")) + 
      (p1_ca + ggtitle("City, Age-specific death rate")) + 
      (p1_rp + ggtitle("Region, Probability")) +
      (p1_ra + ggtitle("Region, Age-specific death rate")) +
  plot_layout(guides='collect', design=design) & 
  theme(text = element_text(size=7),
        legend.position='bottom',
        legend.box='vertical',
        legend.spacing.y=unit(-.3, 'cm')) &
  guides(color=guide_legend(nrow=2, title="Age"))

ggsave(filename=file.path(out_dir, "direct_estimates.pdf"),
       p1)
knitr::plot_crop(file.path(out_dir, "direct_estimates.pdf"))

# for talks, save individual versions of these plots
p_dim <- 4
ggsave(filename=file.path(out_dir, "direct_sib_net_city_prob.png"), p1_cp, width=p_dim, height=p_dim)
ggsave(filename=file.path(out_dir, "direct_sib_net_city_asdr.png"), p1_ca, width=p_dim, height=p_dim)
ggsave(filename=file.path(out_dir, "direct_sib_net_region_prob.png"), p1_rp, width=p_dim, height=p_dim)
ggsave(filename=file.path(out_dir, "direct_sib_net_region_asdr.png"), p1_ra, width=p_dim, height=p_dim)

p1
```


### Scatterplot w/ estimates and VR 

```{r}
p1.5_asdr_c <- readRDS(file.path(vr_city_dir, 'asdr_point_scatter_log.rds'))
p1.5_asdr_r <- readRDS(file.path(vr_region_dir, 'asdr_point_scatter_log.rds'))
p1.5_prob_c <- readRDS(file.path(vr_city_dir, 'prob_point_scatter.rds'))
p1.5_prob_r <- readRDS(file.path(vr_region_dir, 'prob_point_scatter.rds'))
```

```{r}
design <- "
  1122
  3344
"

p1.5 <- (((p1.5_prob_c + ggtitle("City, Probability")) 
          + (p1.5_asdr_c + ggtitle("City, Age-specific death rate"))) / 
           ((p1.5_prob_r + ggtitle("Region, Probability")) + 
             p1.5_asdr_r + ggtitle("Region, Age-specific death rate"))) +
  plot_layout(guides='collect') &
  theme(text = element_text(size=7),
        legend.position='bottom',
        legend.box='vertical',
        legend.spacing.y=unit(-.3, 'cm')) &
  guides(color=guide_legend(nrow=2, title="Age"))
  #plot_layout(guides='collect', design=design) & 
#  plot_layout(guides='collect', design=design)
  #theme(text = element_text(size=7),
  #      legend.position='bottom',
  #      legend.box='vertical',
  #      legend.spacing.y=unit(-.3, 'cm')) &
  #guides(color=guide_legend(nrow=2, title="Age"))
  #theme(text = element_text(size=7))

ggsave(filename=file.path(out_dir, "est_point_scatter_log.pdf"),
       p1.5)

# for talks, save individual versions of these plots
p_dim <- 4
ggsave(filename=file.path(out_dir, "vr_compare_sib_net_city_prob.png"), p1.5_prob_c, 
       width=p_dim, height=p_dim)
ggsave(filename=file.path(out_dir, "vr_compare_sib_net_city_asdr.png"), p1.5_asdr_c, 
       width=p_dim, height=p_dim)
ggsave(filename=file.path(out_dir, "vr_compare_sib_net_region_prob.png"), p1.5_prob_r, 
       width=p_dim, height=p_dim)
ggsave(filename=file.path(out_dir, "vr_compare_sib_net_region_asdr.png"), p1.5_asdr_r, 
       width=p_dim, height=p_dim)

p1.5
```
### Scatterplot w/ estimates and VR 

```{r}
p1.6_asdr_c <- readRDS(file.path(vr_city_dir, 'asdr_pointrange_scatter_log.rds'))
p1.6_asdr_r <- readRDS(file.path(vr_region_dir, 'asdr_pointrange_scatter_log.rds'))
p1.6_prob_c <- readRDS(file.path(vr_city_dir, 'prob_pointrange_scatter.rds'))
p1.6_prob_r <- readRDS(file.path(vr_region_dir, 'prob_pointrange_scatter.rds'))
```

```{r}
design <- "
  1122
  3344
"

p1.6 <- (((  p1.6_prob_c + ggtitle("City, Probability")) 
          + (p1.6_asdr_c + ggtitle("City, Age-specific death rate"))) / 
           ((p1.6_prob_r + ggtitle("Region, Probability")) + 
             p1.6_asdr_r + ggtitle("Region, Age-specific death rate"))) +
  plot_layout(guides='collect') &
  theme(text = element_text(size=7),
        legend.position='bottom',
        legend.box='vertical',
        legend.spacing.y=unit(-.3, 'cm')) &
  guides(color=guide_legend(nrow=2, title="Age"))
  #plot_layout(guides='collect', design=design) & 
#  plot_layout(guides='collect', design=design)
  #theme(text = element_text(size=7),
  #      legend.position='bottom',
  #      legend.box='vertical',
  #      legend.spacing.y=unit(-.3, 'cm')) &
  #guides(color=guide_legend(nrow=2, title="Age"))
  #theme(text = element_text(size=7))

ggsave(filename=file.path(out_dir, "est_pointrange_scatter_log.pdf"),
       p1.6)

# for talks, save individual versions of these plots
#p_dim <- 4
#ggsave(filename=file.path(out_dir, "vr_compare_sib_net_city_prob.png"), p1.5_prob_c, 
#       width=p_dim, height=p_dim)
#ggsave(filename=file.path(out_dir, "vr_compare_sib_net_city_asdr.png"), p1.5_asdr_c, 
#       width=p_dim, height=p_dim)
#ggsave(filename=file.path(out_dir, "vr_compare_sib_net_region_prob.png"), p1.5_prob_r, 
#       width=p_dim, height=p_dim)
#ggsave(filename=file.path(out_dir, "vr_compare_sib_net_region_asdr.png"), p1.5_asdr_r, 
#       width=p_dim, height=p_dim)

p1.6
```
### Bias-variance decomposition (BVD) plot

```{r}
p_bvd_as_bias <- readRDS(file.path(vr_city_dir, 'bvd_as_bias_plot.rds'))

p_bvd_as_se <- readRDS(file.path(vr_city_dir, 'bvd_as_se_plot.rds'))

p_bvd_as_rmse <- readRDS(file.path(vr_city_dir, 'bvd_as_rmse_plot.rds'))
```


```{r}
#bvd_as_city <- p_bvd_as_rmse / p_bvd_as_bias / p_bvd_as_se + 
bvd_as_city <- 
  p_bvd_as_se +
  p_bvd_as_bias +
  p_bvd_as_rmse +
  plot_layout(guides='collect') &
  #theme(text = element_text(size=7)) &
  theme(text = element_text(size=7),
        legend.position='bottom',
        legend.box='vertical',
        legend.spacing.y=unit(-.3, 'cm')) & 
  #guides(color=guide_legend(nrow=2, title="Age"))
  guides(color=guide_legend(title="Age"))

ggsave(filename=file.path(out_dir, "bvd_as_city.pdf"),
       bvd_as_city)

bvd_as_city
```

### Bias-variance decomposition (BVD) plot from VR sensitivity check


```{r}
p_bvd_as_bias_vrsens <- readRDS(file.path(vradj_city_dir, 'bvd_as_bias_plot.rds'))

p_bvd_as_se_vrsens <- readRDS(file.path(vradj_city_dir, 'bvd_as_se_plot.rds'))

p_bvd_as_rmse_vrsens <- readRDS(file.path(vradj_city_dir, 'bvd_as_rmse_plot.rds'))
```


```{r}
bvd_as_city_vrsens <- 
  p_bvd_as_se_vrsens +
  p_bvd_as_bias_vrsens +
  p_bvd_as_rmse_vrsens +
  #p_bvd_as_se /
  #p_bvd_as_bias /     
  #p_bvd_as_rmse +
  plot_layout(guides='collect') &
  #theme(text = element_text(size=7)) &
  theme(text = element_text(size=7),
        legend.position='bottom',
        legend.box='vertical',
        legend.spacing.y=unit(-.3, 'cm')) & 
  #guides(color=guide_legend(nrow=2, title="Age"))
  guides(color=guide_legend(title="Age"))

ggsave(filename=file.path(out_dir, "bvd_as_city_vrsens.pdf"),
       bvd_as_city)

bvd_as_city_vrsens
```

### Error difference pointrange figure

The city asdr boot estimates have the average asdr error across 27 cities for each bootstrap rep (as well as results for prob)
The region asdr boot estimates have the average region asdr error across 5 regions for each bootstrap rep (as well as results for prob)
et cetera

```{r}
errs_cv <- read_csv(file.path(vr_city_dir, 'err_diffs_boot.csv'))
errs_rv <- read_csv(file.path(vr_region_dir, 'err_diffs_boot.csv'))
errs_nv <- read_csv(file.path(vr_national_dir, 'err_diffs_boot.csv'))

errs_ca <- read_csv(file.path(vradj_city_dir, 'err_diffs_boot.csv'))
errs_ra <- read_csv(file.path(vradj_region_dir, 'err_diffs_boot.csv'))
errs_na <- read_csv(file.path(vradj_national_dir, 'err_diffs_boot.csv'))
```

### Err diffs boot

```{r}
err_diffs_boot <- bind_rows(errs_cv,
                            errs_rv,
                            errs_nv,
                            errs_ca,
                            errs_ra,
                            errs_na)

err_diffs_summ <- err_diffs_boot %>%
  group_by(comparison_name, geo_name, qty, loss) %>%
  summarize(diff_nminuss_mean = mean(err.n.minus.s),
            diff_nminuss_ci_low = quantile(err.n.minus.s, .025),
            diff_nminuss_ci_high = quantile(err.n.minus.s, .975),
            network_err = mean(err.n),
            network_err_ci_low = quantile(err.n, .025),
            network_err_ci_high = quantile(err.n, .975),
            network_err_sd = sd(err.n),
            network_err_ci_width = quantile(err.n, .975) - quantile(err.n, .025),
            sibling_err = mean(err.s),
            sibling_err_ci_low = quantile(err.s, .025),
            sibling_err_ci_high = quantile(err.s, .975),
            sibling_err_sd = sd(err.s),
            sibling_err_ci_width = quantile(err.s, .975) - quantile(err.s, .025),
            .groups='drop')

err_diffs_summ
```


```{r}
recode_loss <- c('mare'='MARE', 'mse'='MSE', 'rmse'='RMSE')
recode_qty <- c('asdr'='Age-specifc\ndeath rates', 'prob'='Probability of\ndying at\nadult ages')
recode_geo <- c('city'='City-level\nestimates', 
                'region'='Pooled\nregion-level\nestimates', 
                'national'='Pooled\nnational-level\nestimates')

scale_linetype_values <- setNames(c("solid", "dashed", "dashed"),
                                  paste(recode_geo))

scale_shape_values <- setNames(c(19, 1, 1),
                               paste(recode_geo))

annrelsize <- 3 

mare_prob_annheight <- 0.15
mare_asdr_annheight <- .22

mse_prob_annheight <- 0.0035
mse_asdr_annheight <- 8 

rmse_prob_annheight <- .025 
rmse_asdr_annheight <- 1 

#shade_rect_color <- 'lightgrey'
shade_rect_color <- '#EEEEEE'
shade_rect_alpha <- .05

for_pr_plot_base <- err_diffs_summ %>%
  mutate(loss = dplyr::recode(loss, !!!recode_loss)) %>%
  mutate(qty= dplyr::recode(qty, !!!recode_qty)) %>%
  mutate(geo_name= dplyr::recode_factor(geo_name, !!!recode_geo))

for_pr_plot <- for_pr_plot_base %>%
  filter(comparison_name == 'vr_comparison')

for_pr_vrsens_plot <- for_pr_plot_base %>%
  filter(comparison_name == 'vr_adj_comparison')

make_pr_plot <- function(for_pr_df) {
    
  pr_asdr_mare <- 
    for_pr_df %>%
    filter(loss == 'MARE', qty==recode_qty['asdr']) %>%
    ggplot(.) +
    geom_hline(aes(yintercept = 0), color='darkgrey') +
    geom_pointrange(aes(x=geo_name,
                        y=diff_nminuss_mean,
                        ymin=diff_nminuss_ci_low,
                        ymax=diff_nminuss_ci_high,
                        shape = geo_name,
                        linetype = geo_name)) +
    theme_bw() +
    geom_rect(aes(xmin=1.5,
                  xmax=Inf,
                  ymin=-Inf,
                  ymax=Inf),
              color=shade_rect_color,
              alpha=shade_rect_alpha) +
    #theme_minimal() +
    ylab("Network MARE- Sibling MARE") +
    xlab("") +
    annotate(geom='text', 
             label="Sibling is better ->", 
             y=mare_asdr_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    annotate(geom='text', 
             label="<- Network is better ", 
             y=-mare_asdr_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    scale_y_continuous(labels = scales::percent_format(),
                       limits = c(-.45, .45)) +
    scale_linetype_manual(values=scale_linetype_values, guide = "none") +
    scale_shape_manual(values=scale_shape_values, guide = "none") +
    NULL
  
  pr_prob_mare <- 
    for_pr_df %>%
    filter(loss == 'MARE', qty==recode_qty['prob']) %>%
    ggplot(.) +
    geom_hline(aes(yintercept = 0), color='darkgrey') +
    geom_pointrange(aes(x=geo_name,
                        y=diff_nminuss_mean,
                        ymin=diff_nminuss_ci_low,
                        ymax=diff_nminuss_ci_high,
                        shape = geo_name,
                        linetype=geo_name)) +
    theme_bw() +
    geom_rect(aes(xmin=1.5,
                  xmax=Inf,
                  ymin=-Inf,
                  ymax=Inf),
              color=shade_rect_color,
              alpha=shade_rect_alpha) +
    #theme_minimal() +
    ylab("Network MARE- Sibling MARE") +
    xlab("") +
    annotate(geom='text', 
             label="Sibling is better ->", 
             y=mare_prob_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    annotate(geom='text', 
             label="<- Network is better ", 
             y=-mare_prob_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    scale_y_continuous(labels = scales::percent_format(),
                       limits=c(-.3, .3)) +
    scale_shape_manual(values=scale_shape_values, guide = "none") +
    scale_linetype_manual(values=scale_linetype_values, guide = "none") +
    NULL
    
  pr_prob_mse <- 
    for_pr_df %>%
    filter(loss == 'MSE', qty==recode_qty['prob']) %>%
    ggplot(.) +
    geom_hline(aes(yintercept = 0), color='darkgrey') +
    geom_pointrange(aes(x=geo_name,
                        y=diff_nminuss_mean,
                        ymin=diff_nminuss_ci_low,
                        ymax=diff_nminuss_ci_high,
                        shape = geo_name,
                        linetype=geo_name)) +
    theme_bw() +
    geom_rect(aes(xmin=1.5,
                  xmax=Inf,
                  ymin=-Inf,
                  ymax=Inf),
              color=shade_rect_color,
              alpha=shade_rect_alpha) +
    #theme_minimal() +
    ylab("Network MSE - Sibling MSE") +
    xlab("") +
    annotate(geom='text', 
             label="Sibling is better ->", 
             y=mse_prob_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    annotate(geom='text', 
             label="<- Network is better ", 
             y=-mse_prob_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    scale_y_continuous(limits=c(-.008, .008)) +
    scale_shape_manual(values=scale_shape_values, guide = "none") +
    scale_linetype_manual(values=scale_linetype_values, guide = "none") +
    NULL
    
  pr_asdr_mse <- 
    for_pr_df %>%
    filter(loss == 'MSE', qty==recode_qty['asdr']) %>%
    ggplot(.) +
    geom_hline(aes(yintercept = 0), color='darkgrey') +
    geom_pointrange(aes(x=geo_name,
                        y=diff_nminuss_mean,
                        ymin=diff_nminuss_ci_low,
                        ymax=diff_nminuss_ci_high,
                        shape = geo_name,
                        linetype=geo_name)) +
    theme_bw() +
    geom_rect(aes(xmin=1.5,
                  xmax=Inf,
                  ymin=-Inf,
                  ymax=Inf),
              color=shade_rect_color,
              alpha=shade_rect_alpha) +
    #theme_minimal() +
    ylab("Network MSE - Sibling MSE") +
    xlab("") +
    annotate(geom='text', 
             label="Sibling is better ->", 
             y=mse_asdr_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    annotate(geom='text', 
             label="<- Network is better ", 
             y=-mse_asdr_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    scale_y_continuous(limits=c(-15, 15)) +
    scale_shape_manual(values=scale_shape_values, guide = "none") +
    scale_linetype_manual(values=scale_linetype_values, guide = "none") +
    NULL
  
  pr_prob_rmse <- 
    for_pr_df %>%
    filter(loss == 'RMSE', qty==recode_qty['prob']) %>%
    ggplot(.) +
    geom_hline(aes(yintercept = 0), color='darkgrey') +
    geom_pointrange(aes(x=geo_name,
                        y=diff_nminuss_mean,
                        ymin=diff_nminuss_ci_low,
                        ymax=diff_nminuss_ci_high,
                        shape = geo_name,
                        linetype=geo_name)) +
    theme_bw() +
    geom_rect(aes(xmin=1.5,
                  xmax=Inf,
                  ymin=-Inf,
                  ymax=Inf),
              color=shade_rect_color,
              alpha=shade_rect_alpha) +
    #theme_minimal() +
    ylab("Network RMSE - Sibling RMSE") +
    xlab("") +
    annotate(geom='text', 
             label="Sibling is better ->", 
             y=rmse_prob_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    annotate(geom='text', 
             label="<- Network is better ", 
             y=-rmse_prob_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    scale_y_continuous(limits=c(-.05, .05)) +
    scale_linetype_manual(values=scale_linetype_values, guide = "none") +
    scale_shape_manual(values=scale_shape_values, guide = "none") +
    NULL
  
  pr_asdr_rmse <- 
    for_pr_df %>%
    filter(loss == 'RMSE', qty==recode_qty['asdr']) %>%
    ggplot(.) +
    geom_hline(aes(yintercept = 0), color='darkgrey') +
    geom_pointrange(aes(x=geo_name,
                        y=diff_nminuss_mean,
                        ymin=diff_nminuss_ci_low,
                        ymax=diff_nminuss_ci_high,
                        shape = geo_name,
                        linetype=geo_name)) +
    theme_bw() +
    geom_rect(aes(xmin=1.5,
                  xmax=Inf,
                  ymin=-Inf,
                  ymax=Inf),
              color=shade_rect_color,
              alpha=shade_rect_alpha) +
    #theme_minimal() +
    ylab("Network RMSE - Sibling RMSE") +
    xlab("") +
    annotate(geom='text', 
             label="Sibling is better ->", 
             y=rmse_asdr_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    annotate(geom='text', 
             label="<- Network is better ", 
             y=-rmse_asdr_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    scale_y_continuous(limits=c(-2, 2)) +
    scale_shape_manual(values=scale_shape_values, guide = "none") +
    scale_linetype_manual(values=scale_linetype_values, guide = "none") +
    NULL
    
  #pr_asdr_mare
  #pr_prob_mare
  #pr_prob_mse
  #pr_asdr_mse
  #pr_prob_rmse
  #pr_asdr_rmse
  
  meta_layout <- "
  #cccddd
  aeeefff
  bggghhh
  "
  
  row1_title <- ggplot() + annotate(geom='text', 
                                    x=1,y=1, 
                                    label='bold(underline(ASDR))', 
                                    angle=90,
                                    parse=TRUE) +  theme_void()
  row2_title <- ggplot() + annotate(geom='text', 
                                    x=1,y=1, 
                                    label='bold(underline(Probability~of~Death))', 
                                    angle=90,
                                    parse=TRUE) + theme_void()
  col1_title <- ggplot() + annotate(geom='text', 
                                    x=1,y=1, 
                                    label='bold(underline(MARE))',
                                    parse=TRUE) + theme_void()
  col2_title <- ggplot() + annotate(geom='text', 
                                    x=1,y=1, 
                                    #label='bold(underline(MSE))',
                                    label='bold(underline(RMSE))',
                                    parse=TRUE) + theme_void()
  
  plotlist <- list(a=row1_title,
                   b=row2_title,
                   c=col1_title,
                   d=col2_title,
                   e=pr_asdr_mare,
                   #f=pr_asdr_mse,
                   f=pr_asdr_rmse,
                   g=pr_prob_mare,
                   h=pr_prob_rmse)
                   #h=pr_prob_mse)
    
  final_plot <- wrap_plots(
       plotlist,
       guides='collect',
       design=meta_layout,
       widths=c(2,10,10),
       heights=c(2,10,10))
    
  
  return(final_plot)
}

final_err_compare <- make_pr_plot(for_pr_plot)
  
saveRDS(final_err_compare, file.path(out_dir, "err_compare_all.rds"))
fec.size <- 8 
ggsave(filename=file.path(out_dir, "err_compare_all.pdf"),
       plot=final_err_compare,
       height=fec.size,
       width=fec.size)
ggsave(filename=file.path(out_dir, "err_compare_all.png"),
       plot=final_err_compare,
       height=fec.size,
       width=fec.size)

final_err_compare
```

## VR sensitivity version of figure above

```{r}
vrsens_err_compare <- make_pr_plot(for_pr_vrsens_plot)
  
saveRDS(vrsens_err_compare, file.path(out_dir, "err_compare_all_vrsens.rds"))
fec.size <- 8 
ggsave(filename=file.path(out_dir, "err_compare_all_vrsens.pdf"),
       plot=vrsens_err_compare,
       height=fec.size,
       width=fec.size)
ggsave(filename=file.path(out_dir, "err_compare_all_vrsens.png"),
       plot=vrsens_err_compare,
       height=fec.size,
       width=fec.size)

vrsens_err_compare
```


# Confidence Interval width


```{r}
ci_city <- readRDS(file.path(vr_city_dir, 'ci_width.rds')) %>%
  mutate(geo_name = 'city')
ci_region <- readRDS(file.path(vr_region_dir, 'ci_width.rds')) %>%
  mutate(geo_name = 'region')
ci_national <- readRDS(file.path(vr_national_dir, 'ci_width.rds')) %>%
  mutate(geo_name = 'national')

ci_df <- bind_rows(ci_city,
                   ci_region,
                   ci_national)

ci_df
```


```{r}
ci_df_wide <- ci_df %>%
  pivot_wider(names_from = 'geo_name',
              values_from = c(mean_ci_width_sibling,
                              mean_ci_width_network,
                              avg_sibci_over_netci,
                              pct_over_1,
                              mean_rel_ci_width_sibling,
                              mean_rel_ci_width_network,
                              avg_rel_sibci_over_netci,
                              pct_rel_over_1),
              names_glue = "{.value}_{geo_name}") %>%
  mutate(ci_width_region_over_city_sibling = mean_ci_width_sibling_region / mean_ci_width_sibling_city,
         ci_width_region_over_city_network = mean_ci_width_network_region / mean_ci_width_network_city
         )

saveRDS(ci_df_wide, file.path(out_dir, "ci_df_wide.rds"))

ci_df_wide
```

Four-panel plot with histogram of CI width ratios

```{r}
ci_ratio_asdr_c <- readRDS(file.path(vr_city_dir,   'asdr_ci_width.rds')) + 
  expand_limits(x=c(0,13)) + ggtitle("City, Age-specific death rate")
ci_ratio_prob_c <- readRDS(file.path(vr_city_dir,   'prob_ci_width.rds')) + 
  expand_limits(x=c(0,5)) + ggtitle("City, Probability")
ci_ratio_asdr_r <- readRDS(file.path(vr_region_dir, 'asdr_ci_width.rds')) + 
  expand_limits(x=c(0,13)) + ggtitle("Region, Age-specific death rate")
ci_ratio_prob_r <- readRDS(file.path(vr_region_dir, 'prob_ci_width.rds')) + 
  expand_limits(x=c(0,5)) + ggtitle("Region, Probability")
ci_ratio_asdr_n <- readRDS(file.path(vr_national_dir, 'asdr_ci_width.rds')) + 
  expand_limits(x=c(0,13)) + ggtitle("National, Age-specific death rate")
ci_ratio_prob_n <- readRDS(file.path(vr_national_dir, 'prob_ci_width.rds')) + 
  expand_limits(x=c(0,5)) + ggtitle("National, Probability")
```

```{r}
ci_ratio_hists <- ((ci_ratio_prob_c + ci_ratio_asdr_c) / 
                   (ci_ratio_prob_r + ci_ratio_asdr_r) / 
                   (ci_ratio_prob_n + ci_ratio_asdr_n )) &
  theme(text = element_text(size=7))

ggsave(filename=file.path(out_dir, "ci_width_ratio_hists.pdf"),
       ci_ratio_hists)

ci_ratio_hists
```


Four-panel plot with CI coverage 

Note: since there's only one national estimate here, we don't use national-level
results to estimate CI coverage

```{r}
ci_ratio_c <- readRDS(file.path(vr_city_dir,   'comp_ci_coverage.rds'))
ci_ratio_r <- readRDS(file.path(vr_region_dir, 'comp_ci_coverage.rds'))

ci_ratio_df <- bind_rows(ci_ratio_c,
                         ci_ratio_r)
```



```{r}
recode_qty <- c('asdr'='Age-specifc\ndeath rates', 'prob'='Probability of\ndying at\nadult ages')
recode_geo <- c('city'='City level estimates', 'region'='Region level estimates')
recode_method <- c('network'='Network', 'sibling'='Sibling')

ci_coverage_plot_ignz <-
  ci_ratio_df %>%
  mutate(qty = dplyr::recode(qty, !!!recode_qty)) %>%
  mutate(geo = dplyr::recode_factor(geo, !!!recode_geo)) %>%
  ggplot(.) +
  geom_point(aes(x=sex,
                 y=empirical_ci_coverage_ignorezero,
                 color=method,
                 shape=geo),
             position=position_dodge(width=.25)) +
  facet_grid(~ qty) +
  scale_color_viridis_d("Method") +
  scale_shape_discrete(name='Geography') +
  scale_y_continuous(labels=scales::percent) +
  expand_limits(y=c(0,1)) +
  theme_minimal(base_size=6) +
  xlab("") +
  ylab("Approximate Empirical 95% CI Coverage\n(Ignoring zero estimates)") +
  theme(legend.position='bottom')

ci_coverage_plot <-
  ci_ratio_df %>%
  mutate(qty = dplyr::recode(qty, !!!recode_qty)) %>%
  mutate(geo = dplyr::recode_factor(geo, !!!recode_geo)) %>%
  ggplot(.) +
  geom_point(aes(x=sex,
                 y=empirical_ci_coverage,
                 color=method,
                 shape=geo),
             position=position_dodge(width=.25)) +
  facet_grid(~ qty) +
  scale_color_viridis_d("Method") +
  scale_shape_discrete(name='Geography') +
  scale_y_continuous(labels=scales::percent) +
  expand_limits(y=c(0,1)) +
  theme_minimal(base_size=6) +
  xlab("") +
  ylab("Approximate Empirical 95% CI Coverage") +
  theme(legend.position='bottom')

ggsave(filename=file.path(out_dir, "ci_coverage_plot_ignorezero.pdf"),
       ci_coverage_plot_ignz)
ggsave(filename=file.path(out_dir, "ci_coverage_plot.pdf"),
       ci_coverage_plot)

ci_coverage_plot_ignz
ci_coverage_plot

ci_coverage_plot_both <- (ci_coverage_plot / ci_coverage_plot_ignz) +
  plot_layout(guides='collect') &
  theme(legend.position='bottom')

ggsave(filename=file.path(out_dir, "ci_coverage_plot_both.pdf"),
       ci_coverage_plot_both)

ci_coverage_plot_both
```


## Deaths per interview

```{r}
ni <- read_csv(file.path(out_dir, "num_interviews.csv"))
dpi_sib <- read_csv(file.path(out_dir, "num_deaths_unweighted_sibling.csv"))
dpi_net <- read_csv(file.path(out_dir, "num_deaths_unweighted_network.csv"))
```

```{r}
nd <- bind_rows(dpi_sib, dpi_net) %>%
  left_join(cities %>% select(state_abbrev, region)) %>%
  left_join(ni) %>%
  mutate(deaths_per_interview = num_reported_deaths / num_interviews)

nd_wide <- nd %>%
  select(state_abbrev, method, num_reported_deaths) %>%
  pivot_wider(names_from = 'method',
              values_from = 'num_reported_deaths') %>%
  mutate(sib7_over_net = sibling_7yr / network,
         net_over_sib7= network / sibling_7yr)

nd_wide_dpi <- nd %>%
  pivot_wider(id_cols = c('state_abbrev', 'region'),
              names_from = 'method',
              values_from = 'deaths_per_interview')

nd_region <- nd %>%
  group_by(region, method) %>%
  summarize(num_reported_deaths = sum(num_reported_deaths))

nd_region_wide <- nd_region %>%
  select(region, method, num_reported_deaths) %>%
  pivot_wider(names_from = 'method',
              values_from = 'num_reported_deaths') %>%
  mutate(sib7_over_net = sibling_7yr / network,
         net_over_sib7= network / sibling_7yr)

nd_national <- nd %>%
  group_by(method) %>%
  summarize(num_reported_deaths = sum(num_reported_deaths))

nd_national_wide <- nd_national %>%
  select(method, num_reported_deaths) %>%
  pivot_wider(names_from = 'method',
              values_from = 'num_reported_deaths') %>%
  mutate(sib7_over_net = sibling_7yr / network,
         net_over_sib7= network / sibling_7yr)
```

Some calculations for the text

```{r}
avg_city_net_over_sib7 <- mean(nd_wide$net_over_sib7)

glue::glue("Across all cities, on average the network method produced {round(avg_city_net_over_sib7,2)} more deaths than the 7-year sibling method. (This weights each city equally.)")
```

```{r}
avg_sib7_over_sib1 <- sum(nd_wide$sibling_7yr)/sum(nd_wide$sibling_12mo)
avg_net_over_sib7 <- sum(nd_wide$network)/sum(nd_wide$sibling_7yr)
avg_net_over_sib1 <- sum(nd_wide$network)/sum(nd_wide$sibling_12mo)

glue::glue("Over all respondents, the 7-year sibling method produced {round(avg_sib7_over_sib1,2)} more deaths than the 1-year sibling method. (This weights each respondent equally.)")

glue::glue("Over all respondents, the network method produced {round(avg_net_over_sib1,2)} more deaths than the 1-year sibling method. (This weights each respondent equally.)")

glue::glue("Over all respondents, the network method produced {round(avg_net_over_sib7,2)} more deaths than the 7-year sibling method. (This weights each respondent equally.)")
```


```{r}
method_pretty_names <- c('network'='Network\n(12 months)',
                         'sibling_7yr' = 'Sibling\n(7 years)',
                         'sibling_12mo' = 'Sibling\n(12 months)')

dpi_bar_data <- nd %>%
  left_join(ni) %>%
  group_by(method) %>%
  summarize(dpi = sum(num_reported_deaths) / sum(num_interviews)) %>%
  mutate(method = fct_reorder(method, -dpi)) 

dpi_bar <- dpi_bar_data %>%
  mutate(method = recode_factor(method, !!!method_pretty_names)) %>%
  ggplot(.) +
  geom_bar(aes(x=method, y=dpi), stat='identity') +
  theme_bw() +
  xlab("") + ylab("Average number of adult deaths\nreported per interview")
  
ggsave(filename=file.path(out_dir, "deaths_reported_perinterview.pdf"),
       height=4, width=4,
       dpi_bar)
ggsave(filename=file.path(out_dir, "deaths_reported_perinterview.png"),
       height=4, width=4,
       dpi_bar)

dpi_bar
```


```{r}
deaths_reported_bycity <- nd_wide_dpi %>%
  ggplot(.) +
  #geom_abline(intercept=0, slope = 10, lty='dotted') +
  geom_text(aes(x=sibling_7yr, 
                y=network,
                label=state_abbrev)) +
  theme_bw() +
  #xlim(0,.8) + ylim(0, .8) + 
  #coord_equal() +
  xlab("Number of deaths reported among siblings\n(Over 7 years before interview)") +
  ylab("Number of deaths reported in network\n(Over 12 months before interview)")

glue::glue("Across cities, the 7-year sibling method dpi was correlated with the network dpi at rho =  {round(cur_cor,2)}",
           cur_cor = with(nd_wide_dpi, cor(sibling_7yr, network)))

ggsave(filename=file.path(out_dir, "deaths_reported_bycity.pdf"),
       height=4, width=4,
       deaths_reported_bycity)

deaths_reported_bycity
```




