---
title: "Plots combining results"
output: html_notebook
---

```{r}
## NB: error=FALSE matters here. This renders as an html_notebook, and
##     html_notebook sets error=TRUE by default -- so without this, a chunk that
##     fails is silently embedded in the .nb.html, every later chunk that depends
##     on it also fails, and the render still exits 0 while quietly producing no
##     figures. Halt loudly instead.
knitr::opts_chunk$set(message=FALSE, error=FALSE)
library(here)
library(rmarkdown)
library(tidyverse)
library(patchwork)
library(latex2exp)
library(glue)
```

```{r}
code_dir <- here('code')
out_dir <- here('out')
data_dir <- here('data')
```


```{r}
vr_dir <- file.path(out_dir, 'vr_comparison')
vradj_dir <- file.path(out_dir, 'vr_adj_comparison')

vr_city_dir <- file.path(vr_dir, 'city')
vr_region_dir <- file.path(vr_dir, 'region')
vr_national_dir <- file.path(vr_dir, 'national')

vradj_city_dir <- file.path(vradj_dir, 'city')
vradj_region_dir <- file.path(vradj_dir, 'region')
vradj_national_dir <- file.path(vradj_dir, 'national')
```

```{r}
# load city info
cities <- read_csv(file.path(data_dir, "cities.csv"))
```

### Plot direct comparisons between sibling and network estimates

```{r}
p1_ca <- readRDS(file.path(vr_city_dir, 'direct_asdr_logged.rds'))
p1_cp <- readRDS(file.path(vr_city_dir, 'direct_probs_logged.rds'))
p1_ra <- readRDS(file.path(vr_region_dir, 'direct_asdr_logged.rds'))
p1_rp <- readRDS(file.path(vr_region_dir, 'direct_probs_logged.rds'))
p1_na <- readRDS(file.path(vr_national_dir, 'direct_asdr_logged.rds'))
p1_np <- readRDS(file.path(vr_national_dir, 'direct_probs_logged.rds'))
```

```{r}
design <- "
  1122
  3344
  5555
"
p1 <- (p1_cp + ggtitle("      City, Probability")) + 
      (p1_ca + ggtitle("      City, Age-specific death rate")) + 
      (p1_rp + ggtitle("      Region, Probability")) +
      (p1_ra + ggtitle("      Region, Age-specific death rate")) +
  plot_layout(guides='collect', design=design) & 
  theme(text = element_text(size=7),
        axis.title = element_text(size=6),
        legend.position='bottom',
        legend.box='vertical',
        legend.spacing.y=unit(-.3, 'cm')) &
  guides(color=guide_legend(nrow=2, title="Age", override.aes=list(alpha=1)))

ggsave(filename=file.path(out_dir, "direct_estimates.pdf"),
       p1)
knitr::plot_crop(file.path(out_dir, "direct_estimates.pdf"))

# for talks, save individual versions of these plots
p_dim <- 4
ggsave(filename=file.path(out_dir, "direct_sib_net_city_prob.png"), p1_cp, width=p_dim, height=p_dim)
ggsave(filename=file.path(out_dir, "direct_sib_net_city_asdr.png"), p1_ca, width=p_dim, height=p_dim)
ggsave(filename=file.path(out_dir, "direct_sib_net_region_prob.png"), p1_rp, width=p_dim, height=p_dim)
ggsave(filename=file.path(out_dir, "direct_sib_net_region_asdr.png"), p1_ra, width=p_dim, height=p_dim)

p1
```


### Scatterplot w/ estimates and VR 

```{r}
p1.5_asdr_c <- readRDS(file.path(vr_city_dir, 'asdr_point_scatter_log.rds'))
p1.5_asdr_r <- readRDS(file.path(vr_region_dir, 'asdr_point_scatter_log.rds'))
p1.5_prob_c <- readRDS(file.path(vr_city_dir, 'prob_point_scatter.rds'))
p1.5_prob_r <- readRDS(file.path(vr_region_dir, 'prob_point_scatter.rds'))
```

```{r}
design <- "
  1122
  3344
"

p1.5 <- (((p1.5_prob_c + ggtitle("City, Probability")) 
          + (p1.5_asdr_c + ggtitle("City, Age-specific death rate"))) / 
           ((p1.5_prob_r + ggtitle("Region, Probability")) + 
             p1.5_asdr_r + ggtitle("Region, Age-specific death rate"))) +
  plot_layout(guides='collect') &
  theme(text = element_text(size=7),
        legend.position='bottom',
        legend.box='vertical',
        legend.spacing.y=unit(-.3, 'cm')) &
  guides(color=guide_legend(nrow=2, title="Age", override.aes=list(alpha=1)))
  #plot_layout(guides='collect', design=design) & 
#  plot_layout(guides='collect', design=design)
  #theme(text = element_text(size=7),
  #      legend.position='bottom',
  #      legend.box='vertical',
  #      legend.spacing.y=unit(-.3, 'cm')) &
  #guides(color=guide_legend(nrow=2, title="Age"))
  #theme(text = element_text(size=7))

ggsave(filename=file.path(out_dir, "est_point_scatter_log.pdf"),
       p1.5)

# for talks, save individual versions of these plots
p_dim <- 4
ggsave(filename=file.path(out_dir, "vr_compare_sib_net_city_prob.png"), p1.5_prob_c, 
       width=p_dim, height=p_dim)
ggsave(filename=file.path(out_dir, "vr_compare_sib_net_city_asdr.png"), p1.5_asdr_c, 
       width=p_dim, height=p_dim)
ggsave(filename=file.path(out_dir, "vr_compare_sib_net_region_prob.png"), p1.5_prob_r, 
       width=p_dim, height=p_dim)
ggsave(filename=file.path(out_dir, "vr_compare_sib_net_region_asdr.png"), p1.5_asdr_r, 
       width=p_dim, height=p_dim)

p1.5
```



### Error difference pointrange figure

The city asdr boot estimates have the average asdr error across 27 cities for each bootstrap rep (as well as results for prob)
The region asdr boot estimates have the average region asdr error across 5 regions for each bootstrap rep (as well as results for prob)
et cetera

```{r}
errs_cv <- read_csv(file.path(vr_city_dir, 'err_diffs_jab.csv'))
errs_rv <- read_csv(file.path(vr_region_dir, 'err_diffs_jab.csv'))
errs_nv <- read_csv(file.path(vr_national_dir, 'err_diffs_jab.csv'))

errs_ca <- read_csv(file.path(vradj_city_dir, 'err_diffs_jab.csv'))
errs_ra <- read_csv(file.path(vradj_region_dir, 'err_diffs_jab.csv'))
errs_na <- read_csv(file.path(vradj_national_dir, 'err_diffs_jab.csv'))
```

### Err diffs boot

```{r}
scale_1000x <- function(x) { 1000*x }

err_diffs_summ <- bind_rows(errs_cv,
                           errs_rv,
                           errs_nv,
                           errs_ca,
                           errs_ra,
                           errs_na) %>%
  select(-var_jab) %>%
  filter(loss %in% c('mare', 'rmse')) %>%
  filter(metric == 'diff') %>%
  # make RMSE values x 1,000 (like death rates typically are)
  #mutate(point_est = ifelse(qty == 'asdr' & loss == 'rmse', scale_1000x(point_est), point_est)) %>%
  #mutate(se_jab = ifelse(qty == 'asdr' & loss == 'rmse', scale_1000x(se_jab), se_jab)) %>%
  mutate(ci_low = point_est - (se_jab * 1.96),
         ci_high = point_est + (se_jab * 1.96))

err_diffs_summ
```

Plot w/ pooling for RMSE / ASDR

```{r}
recode_loss <- c('mare'='MARE', 'rmse'='RMSE')
recode_qty <- c('asdr'='Age-specifc\ndeath rates', 'prob'='Probability of\ndying at\nadult ages')
recode_geo <- c('city'='City-level\nestimates', 
                'region'='Pooled\nregion-level\nestimates', 
                'national'='Pooled\nnational-level\nestimates')

scale_linetype_values <- setNames(c("solid", "dashed", "dashed"),
                                  paste(recode_geo))

scale_shape_values <- setNames(c(19, 1, 1),
                               paste(recode_geo))

annrelsize <- 4 

mare_prob_annheight <- 0.15
mare_asdr_annheight <- .22

rmse_prob_annheight <- .025 
rmse_asdr_annheight <- 1 

#shade_rect_color <- 'lightgrey'
shade_rect_color <- '#EEEEEE'
shade_rect_alpha <- .05

pr_asdr_rmse <- 
  err_diffs_summ %>%
  mutate(loss = dplyr::recode(loss, !!!recode_loss)) %>%
  mutate(qty= dplyr::recode(qty, !!!recode_qty)) %>%
  mutate(geo_name= dplyr::recode_factor(geo_name, !!!recode_geo)) %>%
  filter(comparison_name == 'vr_comparison') %>%
  filter(loss == 'RMSE', qty==recode_qty['asdr']) %>%
  ggplot(.) +
  geom_hline(aes(yintercept = 0), color='darkgrey') +
  geom_pointrange(aes(x=geo_name,
                      y=point_est,
                      ymin=ci_low,
                      ymax=ci_high,
                      shape = geo_name,
                      linetype=geo_name)) +
  theme_bw() +
  geom_rect(aes(xmin=1.5,
                xmax=Inf,
                ymin=-Inf,
                ymax=Inf),
            color=shade_rect_color,
            alpha=shade_rect_alpha) +
  #theme_minimal() +
  ylab("Network RMSE - Sibling RMSE") +
  xlab("") +
  annotate(geom='text', 
           label="Sibling is better ->", 
           y=rmse_asdr_annheight, 
           x=0.5, 
           size=rel(annrelsize),
           color='black', 
           angle=90) +
  annotate(geom='text', 
           label="<- Network is better ", 
           y=-rmse_asdr_annheight, 
           x=0.5, 
           size=rel(annrelsize),
           color='black', 
           angle=90) +
  scale_y_continuous(limits=c(-2, 2)) +
  scale_shape_manual(values=scale_shape_values, guide = "none") +
  scale_linetype_manual(values=scale_linetype_values, guide = "none") +
  theme_bw(base_size = 16) +
  theme(
    axis.text  = element_text(size = 14),
    axis.title = element_text(size = 16),
    plot.title = element_text(size = 18)
  )
  NULL
  
pr_asdr_rmse

fec.size <- 5 
ggsave(filename=file.path(out_dir, "pooling_rmse.pdf"),
       plot=pr_asdr_rmse,
       height=fec.size,
       width=fec.size)
```



```{r}
recode_loss <- c('mare'='MARE', 'rmse'='RMSE')
recode_qty <- c('asdr'='Age-specifc\ndeath rates', 'prob'='Probability of\ndying at\nadult ages')
recode_geo <- c('city'='City-level\nestimates', 
                'region'='Pooled\nregion-level\nestimates', 
                'national'='Pooled\nnational-level\nestimates')

scale_linetype_values <- setNames(c("solid", "dashed", "dashed"),
                                  paste(recode_geo))

scale_shape_values <- setNames(c(19, 1, 1),
                               paste(recode_geo))

annrelsize <- 3 

mare_prob_annheight <- 0.15
mare_asdr_annheight <- .22

rmse_prob_annheight <- .025 
rmse_asdr_annheight <- 1 

#shade_rect_color <- 'lightgrey'
shade_rect_color <- '#EEEEEE'
shade_rect_alpha <- .05

for_pr_plot_base <- err_diffs_summ %>%
  mutate(loss = dplyr::recode(loss, !!!recode_loss)) %>%
  mutate(qty= dplyr::recode(qty, !!!recode_qty)) %>%
  mutate(geo_name= dplyr::recode_factor(geo_name, !!!recode_geo))

for_pr_plot <- for_pr_plot_base %>%
  filter(comparison_name == 'vr_comparison')

for_pr_vrsens_plot <- for_pr_plot_base %>%
  filter(comparison_name == 'vr_adj_comparison')

make_pr_plot <- function(for_pr_df) {
    
  pr_asdr_mare <- 
    for_pr_df %>%
    filter(loss == 'MARE', qty==recode_qty['asdr']) %>%
    ggplot(.) +
    geom_hline(aes(yintercept = 0), color='darkgrey') +
    geom_pointrange(aes(x=geo_name,
                        y=point_est,
                        ymin=ci_low,
                        ymax=ci_high,
                        shape = geo_name,
                        linetype = geo_name)) +
    theme_bw() +
    geom_rect(aes(xmin=1.5,
                  xmax=Inf,
                  ymin=-Inf,
                  ymax=Inf),
              color=shade_rect_color,
              alpha=shade_rect_alpha) +
    #theme_minimal() +
    ylab("Network MARE- Sibling MARE") +
    xlab("") +
    annotate(geom='text', 
             label="Sibling is better ->", 
             y=mare_asdr_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    annotate(geom='text', 
             label="<- Network is better ", 
             y=-mare_asdr_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    scale_y_continuous(labels = scales::percent_format(),
                       limits = c(-.5, .5)) +
    scale_linetype_manual(values=scale_linetype_values, guide = "none") +
    scale_shape_manual(values=scale_shape_values, guide = "none") +
    NULL
  
  pr_prob_mare <- 
    for_pr_df %>%
    filter(loss == 'MARE', qty==recode_qty['prob']) %>%
    ggplot(.) +
    geom_hline(aes(yintercept = 0), color='darkgrey') +
    geom_pointrange(aes(x=geo_name,
                        y=point_est,
                        ymin=ci_low,
                        ymax=ci_high,
                        shape = geo_name,
                        linetype=geo_name)) +
    theme_bw() +
    geom_rect(aes(xmin=1.5,
                  xmax=Inf,
                  ymin=-Inf,
                  ymax=Inf),
              color=shade_rect_color,
              alpha=shade_rect_alpha) +
    #theme_minimal() +
    ylab("Network MARE- Sibling MARE") +
    xlab("") +
    annotate(geom='text', 
             label="Sibling is better ->", 
             y=mare_prob_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    annotate(geom='text', 
             label="<- Network is better ", 
             y=-mare_prob_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    scale_y_continuous(labels = scales::percent_format(),
                       limits=c(-.3, .3)) +
    scale_shape_manual(values=scale_shape_values, guide = "none") +
    scale_linetype_manual(values=scale_linetype_values, guide = "none") +
    NULL
    
  pr_prob_rmse <- 
    for_pr_df %>%
    filter(loss == 'RMSE', qty==recode_qty['prob']) %>%
    ggplot(.) +
    geom_hline(aes(yintercept = 0), color='darkgrey') +
    geom_pointrange(aes(x=geo_name,
                        y=point_est,
                        ymin=ci_low,
                        ymax=ci_high,
                        shape = geo_name,
                        linetype=geo_name)) +
    theme_bw() +
    geom_rect(aes(xmin=1.5,
                  xmax=Inf,
                  ymin=-Inf,
                  ymax=Inf),
              color=shade_rect_color,
              alpha=shade_rect_alpha) +
    #theme_minimal() +
    ylab("Network RMSE - Sibling RMSE") +
    xlab("") +
    annotate(geom='text', 
             label="Sibling is better ->", 
             y=rmse_prob_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    annotate(geom='text', 
             label="<- Network is better ", 
             y=-rmse_prob_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    scale_y_continuous(limits=c(-.05, .05)) +
    scale_linetype_manual(values=scale_linetype_values, guide = "none") +
    scale_shape_manual(values=scale_shape_values, guide = "none") +
    NULL
  
  pr_asdr_rmse <- 
    for_pr_df %>%
    filter(loss == 'RMSE', qty==recode_qty['asdr']) %>%
    ggplot(.) +
    geom_hline(aes(yintercept = 0), color='darkgrey') +
    geom_pointrange(aes(x=geo_name,
                        y=point_est,
                        ymin=ci_low,
                        ymax=ci_high,
                        shape = geo_name,
                        linetype=geo_name)) +
    theme_bw() +
    geom_rect(aes(xmin=1.5,
                  xmax=Inf,
                  ymin=-Inf,
                  ymax=Inf),
              color=shade_rect_color,
              alpha=shade_rect_alpha) +
    #theme_minimal() +
    ylab("Network RMSE - Sibling RMSE") +
    xlab("") +
    annotate(geom='text', 
             label="Sibling is better ->", 
             y=rmse_asdr_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    annotate(geom='text', 
             label="<- Network is better ", 
             y=-rmse_asdr_annheight, 
             x=0.5, 
             size=rel(annrelsize),
             color='red', 
             angle=90) +
    scale_y_continuous(limits=c(-2, 2)) +
    scale_shape_manual(values=scale_shape_values, guide = "none") +
    scale_linetype_manual(values=scale_linetype_values, guide = "none") +
    NULL
    
  #pr_asdr_mare
  #pr_prob_mare
  #pr_prob_rmse
  #pr_asdr_rmse
  
  meta_layout <- "
  #cccddd
  aeeefff
  bggghhh
  "
  
  row1_title <- ggplot() + annotate(geom='text', 
                                    x=1,y=1, 
                                    label='bold(underline(ASDR))', 
                                    angle=90,
                                    parse=TRUE) +  theme_void()
  row2_title <- ggplot() + annotate(geom='text', 
                                    x=1,y=1, 
                                    label='bold(underline(Probability~of~Death))', 
                                    angle=90,
                                    parse=TRUE) + theme_void()
  col1_title <- ggplot() + annotate(geom='text', 
                                    x=1,y=1, 
                                    label='bold(underline(MARE))',
                                    parse=TRUE) + theme_void()
  col2_title <- ggplot() + annotate(geom='text', 
                                    x=1,y=1, 
                                    label='bold(underline(RMSE))',
                                    parse=TRUE) + theme_void()
  
  plotlist <- list(a=row1_title,
                   b=row2_title,
                   c=col1_title,
                   d=col2_title,
                   e=pr_asdr_mare,
                   f=pr_asdr_rmse,
                   g=pr_prob_mare,
                   h=pr_prob_rmse)
    
  final_plot <- wrap_plots(
       plotlist,
       guides='collect',
       design=meta_layout,
       widths=c(2,10,10),
       heights=c(2,10,10))
    
  
  return(final_plot)
}

final_err_compare <- make_pr_plot(for_pr_plot)
  
saveRDS(final_err_compare, file.path(out_dir, "err_compare_all.rds"))
fec.size <- 8 
ggsave(filename=file.path(out_dir, "err_compare_all.pdf"),
       plot=final_err_compare,
       height=fec.size,
       width=fec.size)
ggsave(filename=file.path(out_dir, "err_compare_all.png"),
       plot=final_err_compare,
       height=fec.size,
       width=fec.size)

tmp_rmse <- for_pr_plot %>% filter(qty=="Age-specifc\ndeath rates", 
                                   loss=="RMSE", 
                                   geo_name == "City-level\nestimates")
tmp_mare <- for_pr_plot %>% filter(qty=="Age-specifc\ndeath rates", 
                                   loss=="MARE", 
                                   geo_name == "City-level\nestimates")

#glue::glue("
#           Average network RMSE: {tmp_rmse$network_err}
#           Average sibling RMSE: {tmp_rmse$sibling_err}
#           On average, network estimates were about {tmp_rmse$diff_nminuss_mean} RMSE units better than sibling estimates.  
#           This difference is {tmp_mare$diff_nminuss_mean} percent using MARE.
#           
#           ")

final_err_compare
```



```{r, message=TRUE}
## Everything below this point is parked work-in-progress and is NOT run:
## knit_exit() ends the render here (added in 75c6bbb, "exit before some unused
## stuff"). Say so out loud -- otherwise a render that stops a third of the way
## through the file exits 0 and looks like a complete one.
skipped <- c("rmse_barplot.{rds,pdf,png}", "err_compare_all_vrsens.{rds,pdf,png}")
cat("\n06_plots.Rmd: stopping early at knit_exit().\n",
    "  The sections below are parked work-in-progress and were NOT run.\n",
    "  Outputs deliberately not produced: ", paste(skipped, collapse=", "), "\n",
    "  Remove the knit_exit() chunk to run them.\n", sep="")
## NB: knitr captures stdout and message() into the rendered document, so
##     neither reaches the terminal. Only a direct write to stderr escapes the
##     capture -- needed so a batch render (e.g. from 00_run_all.R) shows it too.
cat("06_plots.Rmd: stopped early at knit_exit(); these were NOT produced: ",
    paste(skipped, collapse=", "), "\n", sep="", file = stderr())
knitr::knit_exit()
```


TODO - LEFT OFF HERE...

Simple barplot with RMSE comparison at city level

```{r}
barplot_asdr_rmse_df <- 
    for_pr_plot %>%
    filter(loss == 'RMSE', str_detect(geo_name, 'City-level'), qty==recode_qty['asdr']) %>%
  select(comparison_name, geo_name, qty, loss, network_err, sibling_err) %>%
  pivot_longer(cols=c('network_err', 'sibling_err'),
               names_to='method',
               values_to='RMSE') %>%
  mutate(method = recode(method,
                         network_err='Network', 
                         sibling_err='Sibling'))

barplot_q_rmse_df <- 
    for_pr_plot %>%
    filter(loss == 'RMSE', str_detect(geo_name, 'City-level'), qty==recode_qty['prob']) %>%
  select(comparison_name, geo_name, qty, loss, network_err, sibling_err) %>%
  pivot_longer(cols=c('network_err', 'sibling_err'),
               names_to='method',
               values_to='RMSE') %>%
  mutate(method = recode(method,
                         network_err='Network', 
                         sibling_err='Sibling'))

barplot_asdr_rmse <- barplot_asdr_rmse_df %>%
  ggplot(.) +
  geom_bar(aes(x=method, y=RMSE), stat='identity') +
  theme_minimal() +
  xlab("") +
  ylab("Root Mean Squared Error")

saveRDS(barplot_asdr_rmse, file.path(out_dir, "rmse_barplot.rds"))
fec.size <- 3
ggsave(filename=file.path(out_dir, "rmse_barplot.pdf"),
       plot=barplot_asdr_rmse,
       height=fec.size,
       width=fec.size)
ggsave(filename=file.path(out_dir, "rmse_barplot.png"),
       plot=barplot_asdr_rmse,
       height=fec.size,
       width=fec.size)

net_rmse_tot <- barplot_asdr_rmse_df %>% filter(method=='Network') %>% pull(RMSE)
sib_rmse_tot <- barplot_asdr_rmse_df %>% filter(method=='Sibling') %>% pull(RMSE)

net_q_tot <- barplot_q_rmse_df %>% filter(method=='Network') %>% pull(RMSE)
sib_q_tot <- barplot_q_rmse_df %>% filter(method=='Sibling') %>% pull(RMSE)

glue::glue("
           Sibling ASDR RMSE is {round(100 * (sib_rmse_tot - net_rmse_tot)/net_rmse_tot,3)} percent higher than network RMSE
           Network ASDR RMSE is {round(100*  (net_rmse_tot - sib_rmse_tot)/sib_rmse_tot,3)} percent lower than sibling RMSE
           
           Sibling 47q18 RMSE is {round(100 * (sib_q_tot - net_q_tot)/net_q_tot,3)} percent higher than network RMSE
           Network 47q18 RMSE is {round(100*  (net_q_tot - sib_q_tot)/sib_q_tot,3)} percent lower than sibling RMSE
           
           ")
```


20250501 - CI for the 15% figure

QUICK SUMMARY: I think if you look at the plot, that's basically what we see here
The ASDR RMSE shows that network estimates are about 15% more accurate, but the CI includes 0
The 47q18 RMSE - which is more aggregated - shows that network estimates are about 


```{r}
for_pr_plot %>%
  filter(loss == 'RMSE',
         geo_name == 'City-level\nestimates',
         qty == 'Age-specifc\ndeath rates') %>% glimpse()

```

```{r}

```


## VR sensitivity version of figure above

```{r}
vrsens_err_compare <- make_pr_plot(for_pr_vrsens_plot)
  
saveRDS(vrsens_err_compare, file.path(out_dir, "err_compare_all_vrsens.rds"))
fec.size <- 8 
ggsave(filename=file.path(out_dir, "err_compare_all_vrsens.pdf"),
       plot=vrsens_err_compare,
       height=fec.size,
       width=fec.size)
ggsave(filename=file.path(out_dir, "err_compare_all_vrsens.png"),
       plot=vrsens_err_compare,
       height=fec.size,
       width=fec.size)

vrsens_err_compare
```














