---
title: "Vital registration comparison"
params:
  ## comparison_name - are we comparing to VR to the adjusted VR?
  comparison_name: "vr_comparison"
  #comparison_name: "vr_adj_comparison"
  ## geo_name - are we analyzing at the city, region, or national level?
  geo_name: "city"
  #geo_name: "region"
  #geo_name: "national"
  ## do_12mo: if true, run the sibling 12-month estimates
  do_12mo: true
output:
  html_document:
    df_print: paged
---

This file makes the comparison between the two survey-based estimates
(sibling and network) and the vital registration data.

It uses parameters to choose whether the comparison is at the state or regional level,
and to choose whether the comparison is to the adjusted or unadjusted vital registration.

For replication, this file is not supposed to be run directly; it is run by another
notebook.

```{r}
options(knitr.duplicate.label = "allow")
```

```{r}
library(tidyverse)
library(geofacet)
#devtools::install_github("dgrtwo/drlib")
library(drlib) # has reorder_within / scale_x_reordered for plots

library(gtable) # for customizing map
library(ggplotify) # for customizing map

library(ggforce) # for paginating faceted output
library(latex2exp)
library(broom)

library(gridExtra)

library(demogR)

library(ggrepel)
library(patchwork)
library(tictoc)
library(glue)

## this has coord_obs_pred, which is helpful for plots
library(tune)

# for calculating moran's I
# (spatial autocorrelation)
library(spdep)

# this has color scale
library(viridis)

# to avoid issues w/ spherical geometry (minor detail in making maps)
# see
# https://gis.stackexchange.com/questions/404385/r-sf-some-edges-are-crossing-in-a-multipolygon-how-to-make-it-valid-when-using
sf_use_s2(FALSE)

# has a helper function for symmetric y axis
# devtools::install_github("stefanedwards/lemon")
# (on 20230613)
library(lemon)

library(here)
```

```{r}
comparison_name <- params$comparison_name 

geo_name <- params$geo_name 
```

```{r}
out_dir <- here('out')
data_dir <- here('data')

vr_dir <- file.path(data_dir, 'vr_prepped')

comp_out_dir0 <- file.path(out_dir, comparison_name)
comp_out_dir <- file.path(comp_out_dir0, geo_name)
dir.create(comp_out_dir0, showWarnings = FALSE)
dir.create(comp_out_dir, showWarnings = FALSE)
```

```{r}
tic(glue::glue("Running comparison for {comparison_name} / {geo_name}"))
```


## Some aesthetics for the plots

```{r}
color_sib <- "#FC4E07"
color_net <- "#00AFBB"
color_gs <- "black"

shape_sib <- 0
shape_net <- 5
shape_gs  <- 16

region_pal <- tribble(~ region, ~ color,
                      'NO', 'blue',
                      'NE', 'orange',
                      'CW', 'red',
                      'SE', 'green',
                      'SO', 'purple')

age_scale_color <- scale_color_viridis(discrete=TRUE, direction=-1)
```

## Open up the estimates

Load vital registration reference estimates

```{r}
if(comparison_name == 'vr_comparison') {
  
  if(geo_name == 'city') {
    gs_asdrs <- read_csv(file.path(vr_dir, 
                                   "vr_asdrs.csv")) %>%
      rename(geo = state_abbrev)
    
    gs_probs <- read_csv(file.path(vr_dir, 
                                   "vr_47q18.csv")) %>%
      rename(geo = state_abbrev)
    
  } else if(geo_name == 'region') {

    gs_asdrs <- read_csv(file.path(vr_dir, 
                                   "vr_region_asdrs.csv")) %>%
      rename(geo = region)
    
    gs_probs <- read_csv(file.path(vr_dir, 
                                   "vr_region_47q18.csv")) %>%
      rename(geo = region)
    
  } else if (geo_name == 'national') {
    
    gs_asdrs <- read_csv(file.path(vr_dir, 
                                   "vr_national_asdrs.csv")) %>%
      mutate(geo = 'national')
    
    gs_probs <- read_csv(file.path(vr_dir, 
                                   "vr_national_47q18.csv")) %>%
      mutate(geo = 'national')
    
  }
  
} else if (comparison_name == 'vr_adj_comparison') {
  
  if(geo_name == 'city') {
    gs_asdrs <- read_csv(file.path(vr_dir, 
                                   "vr_asdrs_adj.csv"))  %>%
      rename(geo = state_abbrev)
    
    gs_probs <- read_csv(file.path(vr_dir, 
                                   "vr_47q18_adj.csv")) %>%
      rename(geo = state_abbrev)
    
  } else if (geo_name == 'region') {
  
    gs_asdrs <- read_csv(file.path(vr_dir, 
                                   "vr_region_asdrs_adj.csv")) %>%
      rename(geo = region)
    
    gs_probs <- read_csv(file.path(vr_dir, 
                                   "vr_region_47q18_adj.csv")) %>%
      rename(geo = region)
    
  } else if (geo_name == 'national') {
    
    gs_asdrs <- read_csv(file.path(vr_dir, 
                                   "vr_national_asdrs_adj.csv")) %>%
      mutate(geo = 'national')
    
    gs_probs <- read_csv(file.path(vr_dir, 
                                   "vr_national_47q18_adj.csv")) %>%
      mutate(geo = 'national')
    
  }
}
```

Load sibling estimates

```{r}
if(geo_name == 'city') {
  
  sib_asdrs <- read_csv(file.path(out_dir, 
                                  'sib_design_asdrs.csv')) %>%
    rename(geo = state_abbrev)
  
  sib_probs <- read_csv(file.path(out_dir, 
                                  'sib_design_probs.csv')) %>%
    rename(geo = state_abbrev)
  
  sib_asdrs_boot <- read_csv(file.path(out_dir, 
                                       'sib_design_asdrs_boot.csv')) %>%
    rename(geo = state_abbrev)
  
  sib_probs_boot <- read_csv(file.path(out_dir, 
                                       'sib_design_probs_boot.csv')) %>%
    rename(geo = state_abbrev)
  
  if(params$do_12mo) {
    
    sib_asdrs_12mo <- read_csv(file.path(out_dir, 
                                         'sib_12mo_design_asdrs.csv')) %>%
      rename(geo = state_abbrev)
    
    sib_probs_12mo <- read_csv(file.path(out_dir, 
                                    'sib_12mo_design_probs.csv')) %>%
      rename(geo = state_abbrev)
    
    sib_asdrs_boot_12mo <- read_csv(file.path(out_dir, 
                                         'sib_12mo_design_asdrs_boot.csv')) %>%
      rename(geo = state_abbrev)
    
    sib_probs_boot_12mo <- read_csv(file.path(out_dir, 
                                              'sib_12mo_design_probs_boot.csv')) %>%
      rename(geo = state_abbrev)
  
  }

} else if (geo_name == 'region') {
  
  sib_asdrs <- read_csv(file.path(out_dir, 
                                  'sib_design_asdrs_region.csv')) %>%
    rename(geo = region)
  
  sib_probs <- read_csv(file.path(out_dir, 
                                  'sib_design_probs_region.csv')) %>%
    rename(geo = region)
  
  sib_asdrs_boot <- read_csv(file.path(out_dir, 
                                       'sib_design_asdrs_region_boot.csv')) %>%
    rename(geo = region)
  
  sib_probs_boot <- read_csv(file.path(out_dir, 
                                       'sib_design_probs_region_boot.csv')) %>%
    rename(geo = region)
  
} else if (geo_name == 'national') {
  
  sib_asdrs <- read_csv(file.path(out_dir, 
                                  'sib_design_asdrs_national.csv')) %>%
    mutate(geo = 'national')
  
  sib_probs <- read_csv(file.path(out_dir, 
                                  'sib_design_probs_national.csv')) %>%
    mutate(geo = 'national')
  
  sib_asdrs_boot <- read_csv(file.path(out_dir, 
                                       'sib_design_asdrs_national_boot.csv')) %>%
    mutate(geo = 'national')
  
  sib_probs_boot <- read_csv(file.path(out_dir, 
                                       'sib_design_probs_national_boot.csv')) %>%
    mutate(geo = 'national')
  
}
```

Load network estimates

```{r}
if(geo_name == 'city') {
  
  net_asdrs <- read_csv(file.path(out_dir, 
                                  'net_design_asdrs.csv')) %>%
    rename(geo = state_abbrev)
  
  net_probs <- read_csv(file.path(out_dir, 
                                  'net_design_probs.csv')) %>%
    rename(geo = state_abbrev)
  
  net_asdrs_boot <- read_csv(file.path(out_dir, 
                                       'net_design_asdrs_boot.csv')) %>% 
    mutate(method='net_design') %>%
    rename(geo = state_abbrev)
  
  net_probs_boot <- read_csv(file.path(out_dir, 
                                       'net_design_probs_boot.csv')) %>% 
    mutate(method='net_design') %>%
    rename(geo = state_abbrev,
           q.47.18 = q.47.18.mean)
  
} else if (geo_name == 'region') {

  net_asdrs <- read_csv(file.path(out_dir, 
                                  'net_design_asdrs_region.csv')) %>%
    rename(geo = region)
  
  net_probs <- read_csv(file.path(out_dir, 
                                  'net_design_probs_region.csv')) %>%
    rename(geo = region)
  
  net_asdrs_boot <- read_csv(file.path(out_dir, 
                                       'net_design_asdrs_region_boot.csv')) %>%
    mutate(method='net_design') %>%
    rename(geo = region)
  
  net_probs_boot <- read_csv(file.path(out_dir, 
                                       'net_design_probs_region_boot.csv')) %>%
    mutate(method='net_design') %>%
    rename(geo = region,
           q.47.18 = q.47.18.mean)

} else if (geo_name == 'national') {
  
  net_asdrs <- read_csv(file.path(out_dir, 
                                  'net_design_asdrs_national.csv')) %>%
    mutate(geo = 'national')
  
  net_probs <- read_csv(file.path(out_dir, 
                                  'net_design_probs_national.csv')) %>%
    mutate(geo = 'national')
  
  net_asdrs_boot <- read_csv(file.path(out_dir, 
                                       'net_design_asdrs_national_boot.csv')) %>%
    mutate(method='net_design') %>%
    mutate(geo = 'national')
  
  net_probs_boot <- read_csv(file.path(out_dir, 
                                       'net_design_probs_national_boot.csv')) %>%
    mutate(method='net_design') %>%
    mutate(geo = 'national') %>%
    rename(q.47.18 = q.47.18.mean)
  
}
```

Load estimated VR completeness

```{r}
if(geo_name == 'city') {
  ibge_vr_completeness <- read_csv(file.path(out_dir, 
                                             'vr_completeness_estimates.csv')) %>%
    rename(geo = state_abbrev)
}
```


## Assemble the different results in one place

```{r}
est_asdrs <- bind_rows(sib_asdrs,
                       net_asdrs) %>%
  filter(agegp10 != '[65,75)') %>%
  mutate(method = recode(method,
                         'sib_design'='Sibling',
                         'net_design'='Network')) %>%
  mutate(sex = recode(sex,
                      'male'='Male',
                      'female'='Female'))

est_asdrs_boot <- bind_rows(sib_asdrs_boot,
                            net_asdrs_boot) %>%
  filter(agegp10 != '[65,75)') %>%
  mutate(method = recode(method,
                         'sib_design'='Sibling',
                         'net_design'='Network')) %>%
  mutate(sex = recode(sex,
                      'male'='Male',
                      'female'='Female'))

est_probs <- bind_rows(sib_probs,
                       net_probs) %>%
  mutate(method = recode(method,
                         'sib_design'='Sibling',
                         'net_design'='Network')) %>%
  mutate(sex = recode(sex,
                      'male'='Male',
                      'female'='Female'))

est_probs_boot <- bind_rows(sib_probs_boot,
                            net_probs_boot) %>%
  mutate(method = recode(method,
                         'sib_design'='Sibling',
                         'net_design'='Network')) %>%
  mutate(sex = recode(sex,
                      'male'='Male',
                      'female'='Female'))
```

Assemble 12 mo sib results too

```{r}
if(params$do_12mo) {
  est_asdrs_with12mo <- bind_rows(sib_asdrs,
                         sib_asdrs_12mo %>% mutate(method = 'Sibling12mo'),
                         net_asdrs) %>%
    filter(agegp10 != '[65,75)') %>%
    mutate(method = recode(method,
                           'sib_design'='Sibling',
                           'net_design'='Network')) %>%
    mutate(sex = recode(sex,
                        'male'='Male',
                        'female'='Female'))
  
  est_asdrs_boot_with12mo <- bind_rows(sib_asdrs_boot,
                              sib_asdrs_boot_12mo %>% mutate(method = 'Sibling12mo'),
                              net_asdrs_boot) %>%
    filter(agegp10 != '[65,75)') %>%
    mutate(method = recode(method,
                           'sib_design'='Sibling',
                           'net_design'='Network')) %>%
    mutate(sex = recode(sex,
                        'male'='Male',
                        'female'='Female'))
  
  est_probs_with12mo <- bind_rows(sib_probs,
                         sib_probs_12mo %>% mutate(method = 'Sibling12mo'),
                         net_probs) %>%
    mutate(method = recode(method,
                           'sib_design'='Sibling',
                           'net_design'='Network')) %>%
    mutate(sex = recode(sex,
                        'male'='Male',
                        'female'='Female'))
  
  est_probs_boot_with12mo <- bind_rows(sib_probs_boot,
                              sib_probs_boot_12mo %>% mutate(method = 'Sibling12mo'),
                              net_probs_boot) %>%
    mutate(method = recode(method,
                           'sib_design'='Sibling',
                           'net_design'='Network')) %>%
    mutate(sex = recode(sex,
                        'male'='Male',
                        'female'='Female'))  
}
```

## Quantitative summaries

MSE on natural scale

```{r}
calc_errors <- function(df, ci = TRUE) {
  res <- df %>%
    mutate(delta = 1000*(post_mean_asdr - gs_asdr),
           delta2 = delta*delta,
           ## NB: delta_rel is the absolute relative error
           ##     and delta_rel_notabs is the relative error w/out taking absolute value
           delta_rel = abs(delta)/(1000*gs_asdr),
           delta_rel_notabs = delta/(1000*gs_asdr))
  if(ci) {
    res <- res %>%
      mutate(ci_covered = as.numeric(gs_asdr >= post_ci_low_asdr & gs_asdr <= post_ci_high_asdr))
  }
  
  return(res)
}

calc_errors_probs <- function(df, ci = TRUE) {
  res <- df %>%
    mutate(delta = post_mean_q - gs_prob,
           delta2 = delta*delta,
           delta_rel = abs(delta)/gs_prob,
           delta_rel_notabs = delta/gs_prob)
  if(ci) {
  res <- res %>% mutate(ci_covered = as.numeric(gs_prob >= post_ci_low_q & gs_prob <= post_ci_high_q))
  }
  return(res)
}
```

```{r}
comp_asdrs <- est_asdrs %>%
  left_join(gs_asdrs %>% dplyr::rename(gs_asdr=asdr)) %>%
  calc_errors()

comp_asdrs_boot <- est_asdrs_boot %>%
  left_join(gs_asdrs %>% dplyr::rename(gs_asdr=asdr)) %>%
  calc_errors(ci=FALSE)


comp_asdrs_wide_boot <- comp_asdrs_boot %>%
  select(-gs_asdr, -post_mean_asdr) %>%
  pivot_wider(names_from=method, values_from=c(delta, delta2, delta_rel, delta_rel_notabs)) %>%
  mutate(delta2.n.minus.s = delta2_Network - delta2_Sibling,
         delta_rel.n.minus.s = delta_rel_Network - delta_rel_Sibling)

comp_probs <- est_probs %>%
  left_join(gs_probs %>% dplyr::rename(gs_prob=q.47.18)) %>%
  calc_errors_probs()

comp_probs_boot <- est_probs_boot %>%
  dplyr::rename(post_mean_q = q.47.18) %>%
  left_join(gs_probs %>% dplyr::rename(gs_prob=q.47.18)) %>%
  calc_errors_probs(ci=FALSE)


comp_probs_wide_boot <- comp_probs_boot %>%
  select(-gs_prob, -post_mean_q, -time.period) %>%
  pivot_wider(names_from=method, values_from=c(delta, delta2, delta_rel, delta_rel_notabs)) %>%
  mutate(delta2.n.minus.s = delta2_Network - delta2_Sibling,
         delta_rel.n.minus.s = delta_rel_Network - delta_rel_Sibling)
```

Errors for 12mo sib ests

```{r}
if(params$do_12mo) {
  
  comp_asdrs_with12mo <- est_asdrs_with12mo %>%
    left_join(gs_asdrs %>% dplyr::rename(gs_asdr=asdr)) %>%
    calc_errors()
  
  # quick table comparing squared error for net / sib / sib 12mo
  errs_with_12mo <- comp_asdrs_with12mo %>%
    group_by(method) %>%
    summarize(mean_delta2 = mean(delta2),
              mean_delta_rel = mean(delta_rel))
  
  write_csv(errs_with_12mo,
            file.path(comp_out_dir, "avg_errs_with_sib12mo.csv"))
  saveRDS(errs_with_12mo,
            file.path(comp_out_dir, "avg_errs_with_sib12mo.rds"))
  
  errs_with_12mo
}
```

## Plots directly comparing estimates at the level of geography (state or region)

```{r plot-compare-ests}
direct_comp_est_asdrs <- 
  est_asdrs %>%
    select(-time.period) %>%
    tidyr::pivot_wider(id_cols=c('sex', 'agegp10', 'geo'),
                       values_from=c('post_mean_asdr'),
                       names_from=c('method')) 

cur_range <- range(log(direct_comp_est_asdrs$Network),
                   log(direct_comp_est_asdrs$Sibling),
                   finite=TRUE)

alpha.val <- .6

# logged
direct_plot_logged <-  direct_comp_est_asdrs %>%
  ggplot(.) +
  geom_abline(intercept=0, slope=1) +
  geom_point(aes(x=log(Network), 
                 y=log(Sibling),
                 color=agegp10,
                 shape=sex), 
             alpha=alpha.val) +
  coord_equal() +
  xlim(cur_range) + ylim(cur_range) +
  guides(color=guide_legend(override.aes=list(alpha=1),
                            title='Age'),
         shape=guide_legend(override.aes=list(alpha=1),
                            title='')) +
  ylab("log(Sibling death rate est.)") +
  xlab("log(Network death rate est.)") +
  age_scale_color +
  theme_bw()

# NB: this is used in paper
saveRDS(direct_plot_logged, file.path(comp_out_dir, "direct_asdr_logged.rds"))
ggsave(filename=file.path(comp_out_dir, "direct_asdr_logged.pdf"),
       plot=direct_plot_logged,
       height=3.5,
       width=3.5)
direct_plot_logged

```

```{r plot-compare-ests-probs}
direct_comp_est_probs <- 
  est_probs %>%
    select(-time.period) %>%
    tidyr::pivot_wider(id_cols=c('sex', 'geo'),
                       values_from=c('post_mean_q'),
                       names_from=c('method')) 
```


```{r}
cur_range <- range(log(direct_comp_est_probs$Network),
                   log(direct_comp_est_probs$Sibling),
                   finite=TRUE)

alpha.val <- .6 
  
# logged
direct_plot_probs_logged <-  direct_comp_est_probs %>%
  ggplot(.) +
  geom_abline(intercept=0, slope=1) +
  geom_point(aes(x=log(Network), 
                 y=log(Sibling),
                 shape=sex), 
             alpha=alpha.val) +
  coord_equal() +
  xlim(cur_range) + ylim(cur_range) +
  guides(shape=guide_legend(override.aes=list(alpha=1),
                            title='')) +
  ylab("log(Sibling prob. of death est.)") +
  xlab("log(Network prob. of death est.)") +
  theme_bw()

# NB: this is used in paper
saveRDS(direct_plot_probs_logged, file.path(comp_out_dir, "direct_probs_logged.rds"))
ggsave(filename=file.path(comp_out_dir, "direct_probs_logged.pdf"),
       plot=direct_plot_probs_logged,
       height=3.5,
       width=3.5)
direct_plot_probs_logged

```

## Plots by geography

### Error summaries across geography

#### ASDRS

All ests, by geography

```{r calculate-errs-in-asdrs-by-geo}
comp_asdrs_bygeo <- comp_asdrs %>%
  group_by(method, geo) %>%
  summarize(geo_mse = mean(delta2),
            #geo_are = sum(abs(delta_rel))) 
            # this should be the mean, right?
            geo_are = mean(abs(delta_rel))) 

comp_asdrs_bygeo_boot <- comp_asdrs_boot %>%
  group_by(method, geo, boot_idx) %>%
  summarize(geo_mse = mean(delta2),
            #geo_are = sum(abs(delta_rel))) 
            # this should be the mean, right?
            geo_are = mean(abs(delta_rel))) 

# difference in MSE (network - sibling)
comp_asdrs_bygeo_wide <- comp_asdrs_bygeo %>%
  select(-geo_are) %>%
  pivot_wider(names_from=method, values_from=geo_mse)  %>%
  mutate(n.minus.s = Network - Sibling)

comp_asdrs_bygeo_wide_boot <- comp_asdrs_bygeo_boot %>%
  select(-geo_are) %>%
  pivot_wider(names_from=method, values_from=geo_mse)  %>%
  mutate(n.minus.s = Network - Sibling)

# difference in ARE (network - sibling)
comp_rel_asdrs_bygeo_wide <- comp_asdrs_bygeo %>%
  select(-geo_mse) %>%
  pivot_wider(names_from=method, values_from=geo_are) %>%
  mutate(n.minus.s = Network - Sibling)

comp_rel_asdrs_bygeo_wide_boot <- comp_asdrs_bygeo_boot %>%
  select(-geo_mse) %>%
  pivot_wider(names_from=method, values_from=geo_are) %>%
  mutate(n.minus.s = Network - Sibling)
```


By age/sex/geography

```{r asdr-errs-by-age-sex-geo}
comp_asdrs_bygeoas <- comp_asdrs %>%
  group_by(method, geo, sex, agegp10) %>%
  summarize(geo_mse = mean(delta2),
            # this should be the mean, right?
            geo_are = mean(abs(delta_rel)),
            # not absolute relative error (so, can be negative)
            geo_re = mean(delta_rel_notabs)) %>%
  ungroup() %>%
  mutate(geo_rmse = sqrt(geo_mse))

# difference in MSE (network - sibling)
comp_asdrs_bygeoas_wide <- comp_asdrs_bygeoas %>%
  select(-geo_are, -geo_re, -geo_rmse) %>%
  pivot_wider(names_from=method, values_from=geo_mse)  %>%
  mutate(n.minus.s = Network - Sibling)

# difference in RMSE (network - sibling)
comp_rmse_asdrs_bygeoas_wide <- comp_asdrs_bygeoas %>%
  select(-geo_are, -geo_re, -geo_mse) %>%
  pivot_wider(names_from=method, values_from=geo_rmse)  %>%
  mutate(n.minus.s = Network - Sibling)
  # alternate approach:
  # square root of difference in MSE (network - sibling)
  # that is,
  #   sign(MSE(net) - MSE(sib)) * sqrt(MSE(net) - MSE(sib))
  #mutate(n.minus.s = sign(Network - Sibling) * sqrt(abs(Network - Sibling)))

# difference in ARE (network - sibling)
comp_rel_asdrs_bygeoas_wide <- comp_asdrs_bygeoas %>%
  select(-geo_mse, -geo_re, -geo_rmse) %>%
  pivot_wider(names_from=method, values_from=geo_are) %>%
  mutate(n.minus.s = Network - Sibling)
```

By age/sex

```{r asdr-errs-by-age-sex}
comp_asdrs_byas <- comp_asdrs %>%
  group_by(method, sex, agegp10) %>%
  summarize(as_mse = mean(delta2),
            as_are = mean(abs(delta_rel)),
            # not absolute relative error (so, can be negative)
            as_re = mean(delta_rel_notabs))  

# with bootstraps
comp_asdrs_byas_boot <- comp_asdrs_boot %>%
  group_by(method, sex, agegp10, boot_idx) %>%
  summarize(as_mse = mean(delta2),
            as_are = mean(abs(delta_rel)),
            # not absolute relative error (so, can be negative)
            as_re = mean(delta_rel_notabs),
            .groups='drop') %>%
  group_by(method, sex, agegp10) %>%
  summarize(as_mse_ci_low = quantile(as_mse, .025),
            as_mse_ci_high = quantile(as_mse, .975),
            as_mse = mean(as_mse),
            as_are_ci_low = quantile(as_are, .025),
            as_are_ci_high = quantile(as_are, .975),
            as_are = mean(as_are),
            # not absolute relative error (so, can be negative)
            as_re_ci_low = quantile(as_re, .025),
            as_re_ci_high = quantile(as_re, .975),
            as_re = mean(as_re))

# difference in MSE (network - sibling)
comp_asdrs_byas_wide <- comp_asdrs_byas %>%
  select(-as_are, -as_re) %>%
  pivot_wider(names_from=method, values_from=as_mse)  %>%
  mutate(n.minus.s = Network - Sibling)

# difference in ARE (network - sibling)
comp_rel_asdrs_byas_wide <- comp_asdrs_byas %>%
  select(-as_mse, -as_re) %>%
  pivot_wider(names_from=method, values_from=as_are) %>%
  mutate(n.minus.s = Network - Sibling)
```

#### Probabilities

All ests, by geography (probs)

```{r calculate-errs-in-probs-by-geo}
comp_probs_bygeo <- comp_probs %>%
  group_by(method, geo) %>%
  summarize(geo_mse = mean(delta2),
            #geo_are = sum(abs(delta_rel))) 
            # this should be the mean, right?
            geo_are = mean(abs(delta_rel))) 

comp_probs_bygeo_boot <- comp_probs_boot %>%
  group_by(method, geo, boot_idx) %>%
  summarize(geo_mse = mean(delta2),
            #geo_are = sum(abs(delta_rel))) 
            # this should be the mean, right?
            geo_are = mean(abs(delta_rel))) 

# difference in MSE (network - sibling)
comp_probs_bygeo_wide <- comp_probs_bygeo %>%
  select(-geo_are) %>%
  pivot_wider(names_from=method, values_from=geo_mse)  %>%
  mutate(n.minus.s = Network - Sibling)

comp_probs_bygeo_wide_boot <- comp_probs_bygeo_boot %>%
  select(-geo_are) %>%
  pivot_wider(names_from=method, values_from=geo_mse)  %>%
  mutate(n.minus.s = Network - Sibling)

# difference in ARE (network - sibling)
comp_rel_probs_bygeo_wide <- comp_probs_bygeo %>%
  select(-geo_mse) %>%
  pivot_wider(names_from=method, values_from=geo_are) %>%
  mutate(n.minus.s = Network - Sibling)

comp_rel_probs_bygeo_wide_boot <- comp_probs_bygeo_boot %>%
  select(-geo_mse) %>%
  pivot_wider(names_from=method, values_from=geo_are) %>%
  mutate(n.minus.s = Network - Sibling)
```


By age/sex/geography (probs)

```{r prob-errs-by-age-sex-geo}
comp_probs_bygeos <- comp_probs %>%
  group_by(method, geo, sex) %>%
  summarize(geo_mse = mean(delta2),
            #geo_are = sum(abs(delta_rel))) 
            # this should be the mean, right?
            geo_are = mean(abs(delta_rel)))  

# difference in MSE (network - sibling)
comp_probs_bygeos_wide <- comp_probs_bygeos %>%
  select(-geo_are) %>%
  pivot_wider(names_from=method, values_from=geo_mse)  %>%
  mutate(n.minus.s = Network - Sibling)

# difference in ARE (network - sibling)
comp_rel_probs_bygeos_wide <- comp_probs_bygeos %>%
  select(-geo_mse) %>%
  pivot_wider(names_from=method, values_from=geo_are) %>%
  mutate(n.minus.s = Network - Sibling)
```

Plot the difference between the two methods against the estimated completeness

Plot the difference between the two methods (MSE) against the estimated completeness

```{r comp-errs-mse-vrcompleteness, fig.height=3.5, fig.width=3.5}
## NB: only have completeness at the state level...
if(geo_name == 'city') {

# difference in MSE
comp_df <- comp_asdrs_bygeo_wide

comp_df_withvr <- comp_df %>%
  left_join(ibge_vr_completeness %>%
              select(geo, ibge_est_vrcov = mean_sim_cov_pct))

biggestdiff <- max(abs(comp_df_withvr$n.minus.s))
xrange <- c(-biggestdiff, biggestdiff)

## controls how far out annotations go
annscale <- .6

geo_err_mse_vr_comp <-
  comp_df_withvr %>%
        mutate(geo = fct_reorder(geo, n.minus.s)) %>%
  ggplot(.) +
  geom_text(aes(y=n.minus.s,
                x=ibge_est_vrcov,
                label=geo)) +
  #geom_vline(xintercept=0, color='dark grey') +
  #geom_point(aes(y=state_abbrev, x=n.minus.s)) +
  theme_minimal() +
  ylab("Network estimate MSE - Sibling estimate MSE") +
  xlab("Estimated VR completeness") +
  expand_limits(y=xrange) +
  annotate(geom='text',
           label="<- Network is better ",
           #x='SE',
           x=100,
           y=-biggestdiff*annscale,
           size=rel(3),
           color='red',
           angle=90) +
  annotate(geom='text',
           label="Sibling is better ->",
           #x='SE',
           x=100,
           y=biggestdiff*annscale,
           size=rel(3),
           color='red',
           angle=90) +
  theme(axis.title.x=element_text(size=rel(.8))) +
  ## see
  ## https://stackoverflow.com/questions/12409960/ggplot2-annotate-outside-of-plot
  ## for how this helps plot not clip annotations
  coord_cartesian(clip='off') +
  NULL


ggsave(filename=file.path(comp_out_dir, "geo_err_summ_mse_vrsens.pdf"),
       plot=geo_err_mse_vr_comp,
       height=3.5,
       width=3.5)
knitr::plot_crop(file.path(comp_out_dir, "geo_err_summ_mse_vrsens.pdf"))

geo_err_mse_vr_comp

}
```


Scatter plot with all death rates

```{r}
method_facet_names <- c('Sibling' = 'Sibling Estimates',
                        'Network' = 'Network Estimates')

asdr_point_scatter_df <- est_asdrs %>%
  left_join(gs_asdrs) %>% 
  mutate(method = dplyr::recode(method, !!!method_facet_names))

cur_range <- range(c(asdr_point_scatter_df$post_mean_asdr,
                     asdr_point_scatter_df$asdr),
                   finite = TRUE)

asdr_point_scatter <- asdr_point_scatter_df %>%
  ggplot(.) +
  theme_bw(base_size=5) +
  geom_abline(intercept=0, slope=1) +
  #geom_pointrange(aes(x=asdr, 
  geom_point(aes(x=asdr, 
                      y=post_mean_asdr, 
                      #ymin=post_ci_low_asdr,
                      #ymax=post_ci_high_asdr,
                      color=agegp10,
                      shape=sex),
                  alpha=.5) +
                  #size=rel(rel.point.size),
                  #stroke=point.stroke) +
  xlim(cur_range) + ylim(cur_range) +
  scale_x_log10() + 
  scale_y_log10() +
  facet_grid(~ method) +
  ylab("log(Estimated age-specific death rate)") +
  xlab("log(VR age-specific death rate)") +
  guides(color=guide_legend(title='Age', override.aes=list(alpha=1)),
         shape=guide_legend(title='', override.aes=list(alpha=1))) +
  coord_equal() +
  age_scale_color +
  NULL

# NB: this is used in paper
ggsave(filename=file.path(comp_out_dir, "asdr_point_scatter_log.pdf"),
       plot=asdr_point_scatter,
       height=4,
       width=6)
saveRDS(asdr_point_scatter, 
        file.path(comp_out_dir, "asdr_point_scatter_log.rds"))

asdr_point_scatter
```

Make a plot that has a matrix of VR/Sibling/Network

```{r splom-sib-net-vr}
direct_comp_all_asdrs_df <- 
  est_asdrs %>%
    bind_rows(gs_asdrs %>% rename(post_mean_asdr=asdr) %>% mutate(method='VR')) %>%
    select(-time.period) %>%
    tidyr::pivot_wider(id_cols=c('sex', 'agegp10', 'geo'),
                       values_from=c('post_mean_asdr'),
                       names_from=c('method')) 

cur_range <- with(direct_comp_all_asdrs_df,
                  range(log(Sibling),
                        log(Network),
                        log(VR),
                        finite=TRUE))


alpha.val <- 0.6

splom_sn <- direct_comp_all_asdrs_df %>%
  ggplot(.) +
  geom_abline(intercept=0, slope=1) +
  geom_point(aes(x=log(Sibling), 
                 y=log(Network),
                 color=agegp10,
                 shape=sex), 
             alpha=alpha.val) +
  coord_equal() +
  xlim(cur_range) + ylim(cur_range) +
  guides(color=guide_legend(override.aes=list(alpha=1),
                            title='Age'),
         shape=guide_legend(override.aes=list(alpha=1),
                            title='')) +
  xlab("log(Sibling death rate est.)") +
  ylab("log(Network death rate est.)") +
  ggtitle("A") +
  age_scale_color +
  theme_bw() 



splom_vn <- direct_comp_all_asdrs_df %>%
  ggplot(.) +
  geom_abline(intercept=0, slope=1) +
  geom_point(aes(x=log(VR), 
                 y=log(Network),
                 color=agegp10,
                 shape=sex), 
             alpha=alpha.val) +
  coord_equal() +
  xlim(cur_range) + ylim(cur_range) +
  guides(color=guide_legend(override.aes=list(alpha=1),
                            title='Age'),
         shape=guide_legend(override.aes=list(alpha=1),
                            title='')) +
  ylab("log(Network death rate est.)") +
  xlab("log(VR death rate)") +
  ggtitle("B") +
  age_scale_color +
  theme_bw() 

splom_vs <- direct_comp_all_asdrs_df %>%
  ggplot(.) +
  geom_abline(intercept=0, slope=1) +
  geom_point(aes(x=log(VR), 
                 y=log(Sibling),
                 color=agegp10,
                 shape=sex), 
             alpha=alpha.val) +
  coord_equal() +
  xlim(cur_range) + ylim(cur_range) +
  guides(color=guide_legend(override.aes=list(alpha=1),
                            title='Age'),
         shape=guide_legend(override.aes=list(alpha=1),
                            title='')) +
  ylab("log(Sibling death rate est.)") +
  xlab("log(VR death rate)") +
  ggtitle("C") +
  age_scale_color +
  theme_bw() 


splom_all <- splom_sn + 
             splom_vn +
             guide_area() +
             splom_vs + 
  plot_layout(guides='collect', nrow=2, byrow=TRUE)

meta_layout <- "
#cccddd
aeeefff
aeeefff
bggghhh
bggghhh
"

row1_title <- ggplot() + annotate(geom='text', 
                                  x=1,y=1, 
                                  label='bold(underline(Network))', 
                                  angle=90,
                                  parse=TRUE) +  theme_void()
row2_title <- ggplot() + annotate(geom='text', 
                                  x=1,y=1, 
                                  label='bold(underline(Sibling))', 
                                  angle=90,
                                  parse=TRUE) + theme_void()
col1_title <- ggplot() + annotate(geom='text', 
                                  x=1,y=1, 
                                  label='bold(underline(Sibling))',
                                  parse=TRUE) + theme_void()
col2_title <- ggplot() + annotate(geom='text', 
                                  x=1,y=1, 
                                  label='bold(underline(VR))',
                                  parse=TRUE) + theme_void()

plotlist <- list(a=row1_title,
                 b=row2_title,
                 c=col1_title,
                 d=col2_title,
                 e=splom_sn,
                 f=splom_vn,
                 g=guide_area(),
                 h=splom_vs)
  
final_splom <- wrap_plots(
     plotlist,
     guides='collect',
     design=meta_layout,
     widths=c(2,10,10)) & 
  theme(legend.box='horizontal')
  #theme(legend.box='horizontal', legend.position='bottom')

fig_height <-7 
fig_width <- fig_height

saveRDS(final_splom, file.path(comp_out_dir, "splom_asdr.rds"))
ggsave(filename=file.path(comp_out_dir, "splom_asdr.pdf"),
       plot=final_splom,
       height=fig_height,
       width=fig_width)
ggsave(filename=file.path(comp_out_dir, "splom_asdr.png"),
       plot=final_splom,
       height=fig_height,
       width=fig_width)
final_splom

# the network/sib comparison alone
# scale saved figure by this amount
lone_fac <- 0.5
splom_sn_tosave <- splom_sn + ggtitle("")
saveRDS(splom_sn_tosave, file.path(comp_out_dir, "net_vs_sib_asdr.rds"))
ggsave(filename=file.path(comp_out_dir, "net_vs_sib_asdr.pdf"),
       plot=splom_sn_tosave,
       height=fig_height*lone_fac,
       width=fig_width*lone_fac)
ggsave(filename=file.path(comp_out_dir, "net_vs_sib_asdr.png"),
       plot=splom_sn_tosave,
       height=fig_height*lone_fac,
       width=fig_width*lone_fac)
final_splom


```


Version of the direct ASDR comparison between network + sibling,
faceted by age/sex group

```{r}
cur_range <- with(direct_comp_all_asdrs_df,
                  range(log(Sibling),
                        log(Network),
                        log(VR),
                        finite=TRUE))


alpha.val <- 1

splom_sn_faceted <- direct_comp_all_asdrs_df %>%
  ggplot(.) +
  geom_abline(intercept=0, slope=1) +
  geom_point(aes(x=log(Sibling), 
                 y=log(Network),
                 color=agegp10,
                 shape=sex), 
             alpha=alpha.val) +
  coord_equal() +
  xlim(cur_range) + ylim(cur_range) +
  guides(color=guide_legend(override.aes=list(alpha=1),
                            title='Age'),
         shape=guide_legend(override.aes=list(alpha=1),
                            title='')) +
  xlab("log(Sibling death rate est.)") +
  ylab("log(Network death rate est.)") +
  age_scale_color +
  theme_bw() +
  facet_grid(sex ~ agegp10) +
  theme(legend.position='bottom',
        legend.box='vertical')

fig_height <- 4 
fig_width <- 8

saveRDS(splom_sn_faceted, file.path(comp_out_dir, "net_vs_sib_asdr_faceted.rds"))
ggsave(filename=file.path(comp_out_dir, "net_vs_sib_asdr_faceted.pdf"),
       plot=splom_sn_faceted,
       height=fig_height,
       width=fig_width)

splom_sn_faceted
```


# Direct comparison - probs


Scatter plot with the probs

```{r}
direct_comp_est_probs <- 
  est_probs %>%
    select(-time.period) %>%
    tidyr::pivot_wider(id_cols=c('sex', 'geo'),
                       values_from=c('post_mean_q'),
                       names_from=c('method')) 

cur_range <- range(log(direct_comp_est_probs$Network),
                   log(direct_comp_est_probs$Sibling),
                   finite=TRUE)

```


```{r}
method_facet_names <- c('Sibling' = 'Sibling Estimates',
                        'Network' = 'Network Estimates')

prob_point_scatter_df <- est_probs %>%
  left_join(gs_probs %>% select(geo, sex, q.47.18)) %>% 
  mutate(method = dplyr::recode(method, !!!method_facet_names))

cur_range <- range(c(prob_point_scatter_df$post_mean_q,
                     prob_point_scatter_df$q.47.18),
                   finite = TRUE)

prob_point_scatter <- prob_point_scatter_df %>%
  ggplot(.) +
  theme_bw(base_size=5) +
  geom_abline(intercept=0, slope=1) +
  geom_point(aes(x=q.47.18, 
                 y=post_mean_q, 
                 shape=sex),
                 alpha=.5) +
  coord_equal() +
  xlim(cur_range) + ylim(cur_range) +
  facet_grid(~ method) +
  ylab("Estimated probability of adult death") +
  xlab("VR probability of adult death") +
  guides(shape=guide_legend(title='', override.aes=list(alpha=1))) +
  NULL

# NB: this is used in paper
ggsave(filename=file.path(comp_out_dir, "prob_point_scatter.pdf"),
       plot=prob_point_scatter,
       height=4,
       width=6)
saveRDS(prob_point_scatter, 
        file.path(comp_out_dir, "prob_point_scatter.rds"))

prob_point_scatter
```


### Estimates from both sources + VR values


```{r plot-asdrs-ref, fig.width=3.5, fig.height=10}

rel.point.size <- .3
point.stroke <- .2

asdr_point_plot <- 
  est_asdrs %>%
  left_join(gs_asdrs) %>% 
  group_by(sex, geo) %>%
  # order facets by state difficulty
  mutate(delta = post_mean_asdr - asdr,
         state_difficulty = sum(abs(delta))) %>%
  ungroup() %>%
  mutate(geo = as_factor(geo),
         geo = forcats::fct_reorder(geo, state_difficulty)) %>%
         #geo = drlib::reorder_within(geo, state_difficulty, sex)) %>%
  # end new 
  ggplot(.) +
  theme_bw(base_size=5) +
  geom_pointrange(aes(x=agegp10, 
                      y=post_mean_asdr, 
                      ymin=post_ci_low_asdr,
                      ymax=post_ci_high_asdr,
                      color=method,
                      shape=method),
                  position=position_dodge(width=.5),
                  size=rel(rel.point.size),
                  stroke=point.stroke) +
  geom_point(aes(x=agegp10,
                 y=asdr,
                 color='Vital registration',
                 shape='Vital registration'),
             size=rel(rel.point.size),
             stroke=1) +
  ylab("Age-specific death rate") +
  xlab("") +
  theme(strip.background=element_rect(fill=NA)) +
  guides(color=guide_legend(title='Method', override.aes=list(linetype=c(1,1,0))),
  #guides(color=guide_legend(title='Method'),
         shape=guide_legend(title='Method')) +
  scale_shape_manual(values=c('Sibling'=shape_sib, 'Network'=shape_net, 'Vital registration'=shape_gs))+
  scale_color_manual(values=c('Sibling'=color_sib, 'Network'=color_net, 'Vital registration'=color_gs)) +
  theme(legend.position='bottom',
        legend.direction='horizontal')
   
asdr_point_plot_log_onepage <- asdr_point_plot + 
  facet_grid(geo ~ sex) +
  scale_y_log10()

ggsave(filename=file.path(comp_out_dir, "asdr_pointrange_log.pdf"),
       plot=asdr_point_plot_log_onepage,
       height=10,
       width=3.5)
knitr::plot_crop(file.path(comp_out_dir, "asdr_pointrange_log.pdf"))

asdr_point_plot_log_multipage <- asdr_point_plot + 
  facet_grid_paginate(geo ~ sex, 
                      ncol=3, nrow=3) +
  scale_y_log10()


pdf(file.path(comp_out_dir, "asdr_pointrange_log_multipage.pdf"), onefile = TRUE)
for (i in 1:n_pages(asdr_point_plot_log_multipage)) {
    tmp <- asdr_point_plot_log_multipage + 
    facet_grid_paginate(geo ~ sex, 
                        ncol=3, nrow=3,
                        page=i) +
    scale_y_log10() 
    print(tmp)
}
dev.off()
knitr::plot_crop(file.path(comp_out_dir, "asdr_pointrange_log_multipage.pdf"))

asdr_point_plot_log_onepage
```

Specific example used in paper

```{r}
# TODO
if(params$geo_name == 'city') {
  
  spec_geo <- 'RJ'
  
  asdr_point_example <- 
  est_asdrs %>%
  left_join(gs_asdrs) %>% 
  #group_by(sex, geo) %>%
  # order facets by state difficulty
  #mutate(delta = post_mean_asdr - asdr,
  #       state_difficulty = sum(abs(delta))) %>%
  #ungroup() %>%
  #mutate(geo = as_factor(geo),
  #       geo = forcats::fct_reorder(geo, state_difficulty)) %>%
         #geo = drlib::reorder_within(geo, state_difficulty, sex)) %>%
  # end new 
  filter(geo == spec_geo) %>%
  ggplot(.) +
  theme_bw(base_size=5) +
  geom_pointrange(aes(x=agegp10, 
                      y=post_mean_asdr, 
                      ymin=post_ci_low_asdr,
                      ymax=post_ci_high_asdr,
                      color=method,
                      shape=method),
                  position=position_dodge(width=.5),
                  size=rel(rel.point.size),
                  stroke=point.stroke) +
  geom_point(aes(x=agegp10,
                 y=asdr,
                 color='Vital registration',
                 shape='Vital registration'),
             size=rel(rel.point.size),
             stroke=1) +
  ylab("Log(Age-specific death rate)") +
  xlab("") +
  theme(strip.background=element_rect(fill=NA)) +
  guides(color=guide_legend(title='Method', override.aes=list(linetype=c(1,1,0))),
  #guides(color=guide_legend(title='Method'),
         shape=guide_legend(title='Method')) +
  scale_shape_manual(values=c('Sibling'=shape_sib, 'Network'=shape_net, 'Vital registration'=shape_gs))+
  scale_color_manual(values=c('Sibling'=color_sib, 'Network'=color_net, 'Vital registration'=color_gs)) +
  theme(legend.position='bottom',
        legend.direction='horizontal') +
  scale_y_log10() +
  #facet_grid(. ~ sex)
  facet_grid(sex ~ .)
  
  
  ggsave(filename=file.path(comp_out_dir, "asdr_pointrange_example.pdf"),
       plot=asdr_point_example,
       height=6,
       width=3)
   knitr::plot_crop(file.path(comp_out_dir, "asdr_pointrange_example.pdf"))
 
  asdr_point_example 
}
```




```{r}
asdr_point_plot_opp <- asdr_point_plot + 
  ggforce::facet_grid_paginate(geo ~ sex, ncol=2, nrow=1)

np <- n_pages(asdr_point_plot_opp)

pdf(file.path(comp_out_dir, "asdr_pointrange_opp.pdf"),
    width=7, height=3.5)
for(i in 1:np) {
  print(asdr_point_plot + ggforce::facet_grid_paginate(geo ~ sex, ncol=2, nrow=1, page=i))
}
dev.off()

asdr_point_plot_opp <- asdr_point_plot + 
   ggforce::facet_grid_paginate(geo ~ sex, ncol=2, nrow=1) +
  scale_y_log10()

np <- n_pages(asdr_point_plot_opp)

pdf(file.path(comp_out_dir, "asdr_pointrange_log_opp.pdf"),
    width=7, height=3.5)
for(i in 1:np) {
  print(asdr_point_plot + 
          ggforce::facet_grid_paginate(geo ~ sex, ncol=2, nrow=1, page=i) +
          scale_y_log10())
}
dev.off()
```

```{r}
if(params$geo_name == 'city') {
  
## get Coale-Demeny model life table values
## (these come from the demogR package)

cd.f.raw <- cdmltw(sex='F')
cd.m.raw <- cdmltw(sex='M')

cd <- purrr::map_dfr(1:25,
              function(idx) {
                cur_level_f <- tibble(sex='f',
                                      level.idx=idx,
                                      age=cd.f.raw$age,
                                      width=cd.f.raw$width,
                                      e10=cd.f.raw$e10[idx],
                                      lx=cd.f.raw$lx[idx,],
                                      nqx=cd.f.raw$nqx[idx,],
                                      nax=cd.f.raw$nax[idx,],
                                      ndx=cd.f.raw$ndx[idx,],
                                      nLx=cd.f.raw$nLx[idx,],
                                      nmx=cd.f.raw$nmx[idx,],
                                      Tx=cd.f.raw$Tx[idx,],
                                      ex=cd.f.raw$ex[idx,])
                
                cur_level_m <- tibble(sex='m',
                                      level.idx=idx,
                                      age=cd.m.raw$age,
                                      width=cd.m.raw$width,
                                      e10=cd.m.raw$e10[idx],
                                      lx=cd.m.raw$lx[idx,],
                                      nqx=cd.m.raw$nqx[idx,],
                                      nax=cd.m.raw$nax[idx,],
                                      ndx=cd.m.raw$ndx[idx,],
                                      nLx=cd.m.raw$nLx[idx,],
                                      nmx=cd.m.raw$nmx[idx,],
                                      Tx=cd.m.raw$Tx[idx,],
                                      ex=cd.m.raw$ex[idx,])
                                         
                return(bind_rows(cur_level_f, cur_level_m))
              })

grab_cd_comparison <- function(level) {
  
 cd_forcomp_fine <- cd %>% 
  filter(level.idx==level) %>% 
  filter(age >=15, age < 65)

cd_forcomp <- cd_forcomp_fine %>%
  group_by(sex) %>%
  ## for age 15, we'll make this into age gp 18-19 by:
  ##    * taking .75d1 + .25d2 where d1 is 15-19 asdr and d2 is 20-24 asdr
  ##    * changing 'width' of age gp to 2
  ##    * renaming age gp '18'
  mutate(nLx = case_when(
    age==15 ~ .75*nLx + .25*nLx[age==20],
    TRUE ~ nLx
  )) %>%
  mutate(ndx = case_when(
    age==15 ~ .75*ndx + .25*ndx[age==20],
    TRUE ~ ndx
  )) %>%
  mutate(width = case_when(
    age==15 ~ 2,
    TRUE    ~ width
  )) %>%
  mutate(age = case_when(
    age==15 ~ 18,
    TRUE    ~ age
  ))

cd_forcomp <- cd_forcomp %>%
  group_by(sex) %>%
  mutate(agg.asdr = case_when(
    age == 18 ~ (ndx + ndx[age==20])/(nLx + nLx[age==20]),
    age == 25 ~ (ndx + ndx[age==30])/(nLx + nLx[age==30]),
    age == 35 ~ (ndx + ndx[age==40])/(nLx + nLx[age==40]),
    age == 45 ~ (ndx + ndx[age==50])/(nLx + nLx[age==50]),
    age == 55 ~ (ndx + ndx[age==60])/(nLx + nLx[age==60]),
    TRUE ~ NA_real_
  ))  

cd_forcomp <- cd_forcomp %>%
  filter(!is.na(agg.asdr))

cd_forcomp <- cd_forcomp %>%
  mutate(agegp10=paste(cut(as.numeric(age),
                           breaks=c(18,25,35,45,55,65,75,Inf),
                           right=FALSE,
                           include.lowest=TRUE)))

return(cd_forcomp)

}

cd_level23_raw <- grab_cd_comparison(level=23) %>%
  select(sex, agegp10, post_mean_asdr = agg.asdr) %>%
  mutate(sex = case_when(sex == 'f' ~ 'Female',
                         TRUE ~ 'Male')) %>%
  mutate(geo = 'CD')

cd_comparison <-
  bind_rows(cd_level23_raw %>% mutate(method='Network'),
            cd_level23_raw %>% mutate(method='Sibling'))

}
```


Plot with plausibility comparison: asdrs for sib/net side by side


```{r plot-asdrs-plaus, fig.width=6, fig.height=6}
if(params$geo_name == 'city') {
  

rel.point.size <- .3
point.stroke <- .2

spec_geo <- "RJ"
spec_geo_df <- est_asdrs %>% filter(geo == spec_geo)

est_lty <- 'solid'
mlt_lty <- 'twodash' 

est_color <- 'black'
mlt_color <- 'blue'

est_alpha <- 0.3
mlt_alpha <- 0.6 

asdr_plaus_plot <- 
  est_asdrs %>%
  ggplot(.) +
  theme_bw(base_size=5) +
  ###
  ## ESTIMATES
  ###
  geom_line(aes(x=agegp10, 
                y=post_mean_asdr,
                color=est_color,
                linetype=est_lty,
                group=interaction(method,sex,geo)),
            alpha=est_alpha) +  
  #geom_line(aes(x=agegp10, 
  #              y=post_mean_asdr,
  #              group=interaction(method,sex,geo)),
  #          alpha=.5,
  #          data = spec_geo_df,
  #          color=est_color,
  #          lty=est_lty,
  #          lwd=1.5) +  
  #geom_text_repel(aes(x=agegp10, 
  #              y=post_mean_asdr,
  #              group=interaction(method,sex,geo),
  #              label=geo),
  #              data = spec_geo_df %>% filter(agegp10 == "[55,65)"),
  #              color=est_color,
  #              nudge_x=2,
  #              size=1.5) +  
  ###
  ## MODEL LIFE TABLE
  ###
  geom_line(aes(x=agegp10, 
                y=post_mean_asdr,
                color=mlt_color,
                lty=mlt_lty,
                group=interaction(method,sex,geo)),
            #alpha=.5,
            data = cd_comparison,
            #color=mlt_color,
            #lty = mlt_lty,
            lwd=1.5) +    
  #geom_text_repel(aes(x=agegp10, 
  #              y=post_mean_asdr,
  #              group=interaction(method,sex,geo),
  #              label=geo),
  #              data = cd_comparison %>% filter(agegp10 == "[55,65)"),
  #              color='blue',
  #              nudge_x=2,
  #              size=1.5) +
  facet_grid(sex ~ method) +
  scale_color_identity(guide = 'legend',
                       name = "",
                       breaks = c(mlt_color, est_color),
                       labels = c("Model Life Table", "Estimate"))  +
  scale_linetype_identity(guide = 'legend',
                          name = "",
                          breaks = c(mlt_lty, est_lty),
                          labels = c("Model Life Table", "Estimate"))  +
  #scale_y_log10() +
  ylab("Age-specific death rate") +
  xlab("") +
  theme(strip.background=element_rect(fill=NA),
        legend.position='bottom')

asdr_plaus_plot_log <- asdr_plaus_plot + scale_y_log10() + ylab("Log(Age-specific death rate)") +

ggsave(filename=file.path(comp_out_dir, "asdr_plaus.pdf"),
       plot=asdr_plaus_plot,
       height=4,
       width=4)
knitr::plot_crop(file.path(comp_out_dir, "asdr_plaus.pdf"))

ggsave(filename=file.path(comp_out_dir, "asdr_plaus_log.pdf"),
       plot=asdr_plaus_plot_log,
       height=4,
       width=4)
knitr::plot_crop(file.path(comp_out_dir, "asdr_plaus_log.pdf"))


asdr_plaus_plot

}
```

NEW VERSION OF THE EXAMPLE PLOT

```{r spec-geo-valid-plot}
# TODO
if(params$geo_name == 'city') {
  
  #gs_lty <- 'dotted'
  gs_lty <- 'solid'
  est_lty <- 'dotdash' 
  #est_lty <- 'solid' 
  mlt_lty <- 'longdash' 
  
  gs_color <- 'red'
  est_color <- 'black'
  mlt_color <- 'blue'
  
  gs_alpha <- 1
  est_alpha <- 0.5
  mlt_alpha <- 0.5
  
  
  spec_geo <- 'RJ'
  
  spec_geo_df <- est_asdrs %>% filter(geo == spec_geo)
  
  asdr_rj_example <- 
    est_asdrs %>%
    left_join(gs_asdrs) %>% 
    filter(geo == spec_geo) %>%
    ggplot(.) +    
    theme_bw(base_size=12) +
    ##########
    ## vital registration/gold standard
    ##########
    geom_line(aes(x=agegp10, 
                  y=asdr,
                  group=interaction(method,sex,geo),
                  linetype=gs_lty,
                  color=gs_color),
              alpha=gs_alpha,
              lwd=1.5) +  
    #geom_point(aes(x=agegp10, 
    #              y=asdr,
    #              color=gs_color,
    #              group=interaction(method,sex,geo))) +  
    ##########
    ## survey-based estimates
    ##########
    geom_line(aes(x=agegp10, 
                  y=post_mean_asdr,
                  color=est_color,
                  linetype=est_lty,
                  group=interaction(method,sex,geo)),
            alpha=est_alpha,
            data = spec_geo_df,
            lwd=1) +  
    geom_pointrange(aes(x=agegp10, 
                        y=post_mean_asdr,
                        color=est_color,
                        ymin=post_ci_low_asdr,
                        ymax=post_ci_high_asdr),
                    key_glyph = draw_key_blank,
            alpha=est_alpha,
            data = spec_geo_df) +  
    facet_grid(sex ~ method) +
    scale_y_log10() +
    ylab("Log(Age-specific death rate)") +
    xlab("") +
    theme(strip.background=element_rect(fill=NA)) +
    # see
    # https://aosmith.rbind.io/2020/07/09/ggplot2-override-aes/
    scale_color_identity(guide = 'legend',
                         name = "",
                         breaks = c(gs_color, est_color),
                         labels = c("Vital Registration", "Estimate")) +
    scale_linetype_identity(guide = 'legend',
                         name = "",
                         breaks = c(gs_lty, est_lty),
                         labels = c("Vital Registration", "Estimate"))  +    
    theme(legend.position = 'bottom')
  
  ggsave(filename=file.path(comp_out_dir, "asdr_vr_rj_example.pdf"),
       plot=asdr_rj_example,
       height=6,
       width=6)
   knitr::plot_crop(file.path(comp_out_dir, "asdr_vr_rj_example.pdf"))
 
   asdr_rj_example 
}
```



### Minimum detectable effects

```{r}
##
## se - standard error for difference in two means
mde_onesided <- function(se, alpha=.05, beta=.2) {
  return(se * (qnorm(1-(alpha/2)) - qnorm(beta)))  
}

mde_asdrs <- est_asdrs %>% 
  group_by(method, agegp10, sex, time.period) %>% 
  summarize(mean_se = mean(post_sd_asdr), 
            mean_asdr=mean(post_mean_asdr)) %>% 
  mutate(cv_asdr = mean_se/mean_asdr, 
         ## NB: if two estimates both have std err sigma and are independent
         ##     then their difference will have std err sqrt(2)*sigma
         mde = mde_onesided((sqrt(2)*mean_se))) %>%
  mutate(rel_mde = mde / mean_asdr)

mde_probs <- est_probs %>% 
  group_by(method, sex, time.period) %>% 
  summarize(mean_se = mean(post_sd_q), 
            mean_prob = mean(post_mean_q)) %>% 
  mutate(cv_prob = mean_se/mean_prob, 
         ## NB: if two estimates both have std err sigma and are independent
         ##     then their difference will have std err sqrt(2)*sigma
         mde = mde_onesided(sqrt(2)*(mean_se))) %>%
  mutate(rel_mde = mde / mean_prob)

mde_asdrs
mde_probs
```


### CI width 

CI width for asdrs

```{r}
est_asdrs_ci_width <- est_asdrs %>%
  mutate(ci_width = post_ci_high_asdr - post_ci_low_asdr,
         rel_ci_width = ci_width / post_mean_asdr) %>%
  select(method, geo, agegp10, sex, ci_width, rel_ci_width) %>%
  pivot_wider(values_from = c('ci_width', 'rel_ci_width'),
              names_from = 'method',
              names_glue = "{.value}_{tolower(method)}") %>%
  # don't count cases w/ 0 deaths
  filter(ci_width_sibling != 0, ci_width_network != 0) %>%
  mutate(sib_over_net_ci_width = ci_width_sibling / ci_width_network,
         sib_over_net_rel_ci_width = rel_ci_width_sibling / rel_ci_width_network)
```


CI width for probabilities 

```{r}
est_probs_ci_width <- est_probs %>%
  mutate(ci_width = post_ci_high_q - post_ci_low_q,
         rel_ci_width = ci_width / post_mean_q) %>%
  select(method, geo, sex, ci_width, rel_ci_width) %>%
  pivot_wider(values_from = c('ci_width', 'rel_ci_width'),
              names_from = 'method',
              names_glue = "{.value}_{tolower(method)}") %>%
  # don't count cases w/ 0 deaths
  filter(ci_width_sibling != 0, ci_width_network != 0) %>%
  mutate(sib_over_net_ci_width = ci_width_sibling / ci_width_network,
         sib_over_net_rel_ci_width = rel_ci_width_sibling / rel_ci_width_network)
```

Save a dataframe with the CI properties

```{r}
# NB: this is used

all_ci_widths <-
  bind_rows(est_asdrs_ci_width %>% 
              mutate(qoi = 'asdr'),
            est_probs_ci_width %>% 
              mutate(qoi = 'prob')) %>%
  group_by(qoi) %>%
  summarize(mean_ci_width_sibling = mean(ci_width_sibling),
            mean_ci_width_network = mean(ci_width_network),
            avg_sibci_over_netci = mean(sib_over_net_ci_width),
            pct_over_1 = 100*mean(sib_over_net_ci_width > 1),
            # same quantities for relative CI
            mean_rel_ci_width_sibling = mean(rel_ci_width_sibling),
            mean_rel_ci_width_network = mean(rel_ci_width_network),
            avg_rel_sibci_over_netci = mean(sib_over_net_rel_ci_width),
            pct_rel_over_1 = 100*mean(sib_over_net_rel_ci_width > 1))

saveRDS(all_ci_widths,
        file=file.path(comp_out_dir, "ci_width.rds"))

all_ci_widths
```


Error distn for file

```{r}
mse_diff_hist <- comp_asdrs_wide_boot %>%
  group_by(boot_idx) %>%
  summarize(mean.delta2.n.minus.s = mean(delta2.n.minus.s),
            mean.delta2.n = mean(delta2_Network),
            mean.delta2.s = mean(delta2_Sibling))

errs_boot_asdr_mse <- mse_diff_hist  %>% 
  rename(err.n.minus.s = mean.delta2.n.minus.s,
         err.n = mean.delta2.n,
         err.s = mean.delta2.s) %>%
  bind_cols(loss = 'mse',
            qty = 'asdr',
            comparison_name = params$comparison_name,
            geo_name = params$geo_name)

mse_diff_probs_hist <- comp_probs_wide_boot %>%
  group_by(boot_idx) %>%
  summarize(mean.delta2.n.minus.s = mean(delta2.n.minus.s),
            mean.delta2.n = mean(delta2_Network),
            mean.delta2.s = mean(delta2_Sibling))

errs_boot_probs_mse <- mse_diff_probs_hist  %>% 
  rename(err.n.minus.s = mean.delta2.n.minus.s,
         err.n = mean.delta2.n,
         err.s = mean.delta2.s) %>%
  bind_cols(loss = 'mse',
            qty = 'prob',
            comparison_name = params$comparison_name,
            geo_name = params$geo_name)

rel_diff_hist <- comp_asdrs_wide_boot %>%
  group_by(boot_idx) %>%
  summarize(mean.err = mean(delta_rel.n.minus.s),
            mean.net.err = mean(delta_rel_Network),
            mean.sib.err = mean(delta_rel_Sibling))
  
errs_boot_asdr_mare <- rel_diff_hist  %>% 
  rename(err.n.minus.s = mean.err,
         err.n = mean.net.err,
         err.s = mean.sib.err) %>%
  bind_cols(loss = 'mare',
            qty = 'asdr',
            comparison_name = params$comparison_name,
            geo_name = params$geo_name)

rel_diff_prob_hist <- comp_probs_wide_boot %>%
  group_by(boot_idx) %>%
  summarize(mean.err = mean(delta_rel.n.minus.s),
            mean.err.n = mean(delta_rel_Network),
            mean.err.s = mean(delta_rel_Sibling))
  

errs_boot_probs_mare <- rel_diff_prob_hist  %>% 
  rename(err.n.minus.s = mean.err,
         err.n = mean.err.n,
         err.s = mean.err.s) %>%
  bind_cols(loss = 'mare',
            qty = 'prob',
            comparison_name = params$comparison_name,
            geo_name = params$geo_name)
```


```{r}
# convert MSE results to RMSE
errs_boot_asdr_rmse <- errs_boot_asdr_mse %>% 
  mutate(err.n = sqrt(err.n),
         err.s = sqrt(err.s),
         err.n.minus.s = err.n - err.s,
         loss = 'rmse')
errs_boot_probs_rmse <- errs_boot_probs_mse %>% 
  mutate(err.n = sqrt(err.n),
         err.s = sqrt(err.s),
         err.n.minus.s = err.n - err.s,
         loss = 'rmse')

errs_boot_both_rmse <-
  bind_rows(errs_boot_asdr_rmse,
            errs_boot_probs_rmse)

err_diffs_boot <- bind_rows(errs_boot_asdr_mare, 
                            errs_boot_asdr_mse, 
                            errs_boot_probs_mare, 
                            errs_boot_probs_mse)

# NB: this file is used
write_csv(bind_rows(err_diffs_boot,
                    errs_boot_both_rmse),
          file.path(comp_out_dir, "err_diffs_boot.csv"))

err_diffs_boot
```

# Correlations between different sets of estimates

Summarize relationship between sibling and network probability of death estimates with correlation matrix


```{r}
direct_comp_all_probs_df <- 
  est_probs %>%
    bind_rows(gs_probs %>% rename(post_mean_q = q.47.18) %>% mutate(method='VR')) %>%
    select(-time.period) %>%
    tidyr::pivot_wider(id_cols=c('sex', 'geo'),
                       values_from=c('post_mean_q'),
                       names_from=c('method')) 

cat("\n\nCorrelation between probabilities, not on log scale\n")
# not on log scale
print(
  cor(direct_comp_all_probs_df %>% 
           select(Sibling, Network, VR))
)
```

Summarize relationship between sibling and network death rate estimates with correlation matrix


```{r}

cat("\n\nCorrelation between ASDRs, not on log scale\n")
# not on log scale
print(
  cor(direct_comp_all_asdrs_df %>% 
                select(Sibling, Network, VR))
  )
cat("\n\n")

cat("\n\nCorrelation between log(ASDR)s, log(0) mapped to tiny value:\n")
# log scale, replace log(0) with log(1e-8)
print(cor(direct_comp_all_asdrs_df %>% 
      select(Sibling, Network, VR) %>% 
      mutate(across(everything(),log)) %>%
      mutate(Sibling = ifelse(! is.finite(Sibling), log(1e-8), Sibling))))
cat("\n\n")

cat("\n\nCorrelation between log(ASDR)s, dropping rows where sibling estimates are 0\n")
# log scale, drop rows where sibling ests are 0
print(cor(
  direct_comp_all_asdrs_df %>% 
      select(Sibling, Network, VR) %>% 
      mutate(across(everything(),log)) %>%
      #filter(if_all(everything(), ~ is.finite(.x)))
      filter_all(all_vars(is.finite(.)))  
    ))
```


# National and regional analyses ends here

```{r}
if(geo_name %in% c('national', 'region')) {
  toc()
  knitr::knit_exit()
}
```

## Bias-Variance Decomposition

Check bias-variance decomposition w/in city/age/sex group:
MSE = bias^2 + var

```{r}
fp.var <- function(x) {
  return(mean((x - mean(x))^2))
}

bvd_check <- comp_asdrs_boot %>%
  group_by(geo, sex, agegp10, method) %>%
  summarize(estimand = mean(post_mean_asdr),
            gs = mean(gs_asdr),
            mse = mean((post_mean_asdr - gs_asdr)^2),
            # NB: the mse var in comp_asdrs_boot is based on delta = (est - truth)*1000
            #mse = mean(delta2/(1000^2)),
            bias = mean(post_mean_asdr - gs_asdr),
            var = var(post_mean_asdr)) %>%
            #var = fp.var(post_mean_asdr)) %>%
            #var = mean((post_mean_asdr - estimand)^2)) %>%
  mutate(check = mse - (bias^2 + var))

# sanity check that bias-variance decomposition holds
bvd_check %>%
  ggplot(.) +
  geom_abline(intercept=0, slope=1, color='grey') +
  geom_point(aes(x = bias^2 + var,
                 y = mse)) +
  theme_minimal() +
  coord_equal()

bvd_check
```

```{r}
bvd_check_long <- bvd_check %>%
  pivot_longer(cols=c('mse', 'bias', 'var')) %>%
  select(-estimand, -check) %>%
  rename(qty = name) %>%
  pivot_wider(names_from = c('method'),
              values_from = 'value')

bvd_check_long
```

Aggregate up to age/sex groups (across cities)

```{r}
bvd_as_rmse_plot <- bvd_check_long %>%
  #filter(qty %in% c('bias', 'var')) %>%
  filter(qty == 'mse') %>%
  group_by(sex, agegp10) %>%
  # we take the average of the MSE; when we plot,
  # we'll take the square root to make it a little more interpretable - but
  # the quantity being averaged is the MS E
  summarize(Network = mean(Network),
            Sibling=mean(Sibling)) %>%
  ggplot(.) +
  geom_abline(intercept=0, slope=1, color='grey', lty=2) +
  geom_point(aes(x=sqrt(Network), y=sqrt(Sibling), color=agegp10, shape=sex)) +
  guides(color=guide_legend(override.aes=list(alpha=1),
                            title='Age'),
         shape=guide_legend(override.aes=list(alpha=1),
                            title='')) +
  #xlab("Network variance") + ylab("Sibling variance") +
  xlab("Square root of\nNetwork average MSE") +
  ylab("Square root of\nSibling average MSE") +
  expand_limits(x=0, y=0) +
  #coord_equal() +
  tune::coord_obs_pred() +
  age_scale_color +
  theme_minimal() 


# NB: this one is used
saveRDS(bvd_as_rmse_plot, file.path(comp_out_dir, "bvd_as_rmse_plot.rds"))
ggsave(file.path(comp_out_dir, "bvd_as_rmse.pdf"),
       bvd_as_rmse_plot,
       width=5, height=4)

## symbol size and font size for 'alone' plots
alone_size <- 4
alone_text_size <- 14
alone_fig_size <- 6

# NB: this one is used
bvd_as_rmse_plot_alone <- bvd_check_long %>%
  #filter(qty %in% c('bias', 'var')) %>%
  filter(qty == 'mse') %>%
  group_by(sex, agegp10) %>%
  # we take the average of the MSE; when we plot,
  # we'll take the square root to make it a little more interpretable - but
  # the quantity being averaged is the MS E
  summarize(Network = mean(Network),
            Sibling=mean(Sibling)) %>%
  ggplot(.) +
  geom_abline(intercept=0, slope=1, color='grey', lty=2, lwd=1.5) +
  geom_point(aes(x=sqrt(Network), y=sqrt(Sibling), color=agegp10, shape=sex), size = alone_size) +
  guides(color=guide_legend(override.aes=list(alpha=1),
                            title='Age'),
         shape=guide_legend(override.aes=list(alpha=1),
                            title='')) +
  xlab("Square root of\nNetwork average MSE") +
  ylab("Square root of\nSibling average MSE") +
  expand_limits(x=0, y=0) +
  #coord_equal() +
  tune::coord_obs_pred() +
  age_scale_color +
  #theme_minimal() + 
  theme_bw() + 
  theme(legend.position='right',
        text=element_text(size=alone_text_size))


ggsave(file.path(comp_out_dir, "bvd_as_rmse_alone.pdf"),
       bvd_as_rmse_plot_alone,
       width=alone_fig_size, height=alone_fig_size)

         #guides(color=guide_legend(nrow=2,byrow=TRUE)) +
         #theme(legend.position='bottom', 
        #       legend.direction='horizontal',
        #       legend.box='vertical',
        #       legend.margin=margin()),

bvd_as_rmse_plot_alone
```

Same as above, but as a bar plot

```{r}

bvd_as_rmse_bar_plot <- bvd_check_long %>%
  #filter(qty %in% c('bias', 'var')) %>%
  filter(qty == 'mse') %>%
  group_by(sex, agegp10) %>%
  # we take the average of the MSE; when we plot,
  # we'll take the square root to make it a little more interpretable - but
  # the quantity being averaged is the MS E
  summarize(Network = mean(Network),
            Sibling=mean(Sibling)) %>%
  pivot_longer(cols=c('Network', 'Sibling'), names_to='estimator', values_to='mse') %>%
  ggplot(.) +
  geom_bar(aes(y=agegp10, x=1000*sqrt(mse), fill=estimator), stat='identity', position='dodge') +
  #geom_abline(intercept=0, slope=1, color='grey', lty=2) +
  #geom_point(aes(x=sqrt(Network), y=sqrt(Sibling), color=agegp10, shape=sex)) +
  #guides(color=guide_legend(override.aes=list(alpha=1),
  #                          title='Age'),
  #       shape=guide_legend(override.aes=list(alpha=1),
  #                          title='')) +
  ##xlab("Network variance") + ylab("Sibling variance") +
  #xlab("Square root of\nNetwork average MSE") +
  #ylab("Square root of\nSibling average MSE") +
  #expand_limits(x=0, y=0) +
  ##coord_equal() +
  #tune::coord_obs_pred() +
  #age_scale_color +
  xlab("RMSE") + ylab("") +
  facet_wrap(~ sex) +
  theme_minimal() 

ggsave(file.path(comp_out_dir, "bvd_as_rmse_bar.pdf"),
       bvd_as_rmse_bar_plot,
       width=6, height=6)

bvd_as_rmse_bar_plot
```


Sqrt of the variance

```{r}
bvd_as_se_plot <- bvd_check_long %>%
  #filter(qty %in% c('bias', 'var')) %>%
  filter(qty == 'var') %>%
  group_by(sex, agegp10) %>%
  ## we average the variance across cities,
  ## then we take the square root to make it easier to read
  ## but the quantity being averaged is the variance
  summarize(Network = mean(Network),
            Sibling=mean(Sibling)) %>%
  ggplot(.) +
  geom_abline(intercept=0, slope=1, color='grey', lty=2) +
  geom_point(aes(x=sqrt(Network), y=sqrt(Sibling), color=agegp10, shape=sex)) +
  guides(color=guide_legend(override.aes=list(alpha=1),
                            title='Age'),
         shape=guide_legend(override.aes=list(alpha=1),
                            title='')) +
  #xlab("Network variance") + ylab("Sibling variance") +
  #xlab(TeX(r'(Network average $\sqrt{var}$)')) + 
  #ylab(TeX(r'(Sibling average $\sqrt{var}$)')) + 
  xlab("Square root of\nNetwork average variance") +
  ylab("Square root of\nSibling average variance") +
  #coord_equal() +
  tune::coord_obs_pred() +
  theme_minimal() +
  age_scale_color +
  expand_limits(x = 0, y = 0)

# NB: this one is used
saveRDS(bvd_as_se_plot, file.path(comp_out_dir, "bvd_as_se_plot.rds"))
ggsave(file.path(comp_out_dir, "bvd_as_se.pdf"),
       bvd_as_se_plot,
       width=5, height=4)

bvd_as_se_plot_alone <- bvd_check_long %>%
  #filter(qty %in% c('bias', 'var')) %>%
  filter(qty == 'var') %>%
  group_by(sex, agegp10) %>%
  ## we average the variance across cities,
  ## then we take the square root to make it easier to read
  ## but the quantity being averaged is the variance
  summarize(Network = mean(Network),
            Sibling=mean(Sibling)) %>%
  ggplot(.) +
  geom_abline(intercept=0, slope=1, color='grey', lty=2, lwd=1.5) +
  geom_point(aes(x=sqrt(Network), y=sqrt(Sibling), color=agegp10, shape=sex), size=alone_size) +
  guides(color=guide_legend(override.aes=list(alpha=1),
                            title='Age'),
         shape=guide_legend(override.aes=list(alpha=1),
                            title='')) +
  #xlab("Network variance") + ylab("Sibling variance") +
  #xlab(TeX(r'(Network average $\sqrt{var}$)')) + 
  #ylab(TeX(r'(Sibling average $\sqrt{var}$)')) + 
  xlab("Square root of\nNetwork average variance") +
  ylab("Square root of\nSibling average variance") +
  #coord_equal() +
  tune::coord_obs_pred() +
  #theme_minimal() +
  theme_bw() +
  age_scale_color +
  expand_limits(x = 0, y = 0) +
  theme(legend.position='right',
        text=element_text(size=alone_text_size))

# NB: this one is used
saveRDS(bvd_as_se_plot_alone, file.path(comp_out_dir, "bvd_as_se_plot_alone.rds"))
ggsave(file.path(comp_out_dir, "bvd_as_se_alone.pdf"),
       bvd_as_se_plot_alone,
       width=alone_fig_size, height=alone_fig_size)

bvd_as_se_plot_alone
```

Bias

```{r}
bvd_as_bias_plot <- bvd_check_long %>%
  #filter(qty %in% c('bias', 'var')) %>%
  filter(qty == 'bias') %>%
  group_by(sex, agegp10) %>%
  summarize(Network = mean(Network),
            Sibling=mean(Sibling)) %>%
  ggplot(.) +
  #geom_abline(intercept=0, slope=1, color='grey', linetype=2) +
  geom_vline(xintercept=0, color='grey') +
  geom_hline(yintercept=0, color='grey') +
  geom_point(aes(x=Network, y=Sibling, color=agegp10, shape=sex)) +
  guides(color=guide_legend(override.aes=list(alpha=1),
                            title='Age'),
         shape=guide_legend(override.aes=list(alpha=1),
                            title='')) +
  xlab("Network bias") + ylab("Sibling bias") +
  #coord_equal() +
  tune::coord_obs_pred() +
  lemon::scale_y_symmetric(mid=0) +
  lemon::scale_x_symmetric(mid=0) +
  age_scale_color +
  theme_minimal() 

# NB: this one is used
saveRDS(bvd_as_bias_plot, file.path(comp_out_dir, "bvd_as_bias_plot.rds"))

ggsave(file.path(comp_out_dir, "bvd_as_bias.pdf"),
       bvd_as_bias_plot,
       width=5, height=4)

bvd_as_bias_plot_alone <- bvd_check_long %>%
  #filter(qty %in% c('bias', 'var')) %>%
  filter(qty == 'bias') %>%
  group_by(sex, agegp10) %>%
  summarize(Network = mean(Network),
            Sibling=mean(Sibling)) %>%
  ggplot(.) +
  #geom_abline(intercept=0, slope=1, color='grey', linetype=2) +
  geom_vline(xintercept=0, color='grey') +
  geom_hline(yintercept=0, color='grey') +
  geom_point(aes(x=Network, y=Sibling, color=agegp10, shape=sex), size=alone_size) +
  guides(color=guide_legend(override.aes=list(alpha=1),
                            title='Age'),
         shape=guide_legend(override.aes=list(alpha=1),
                            title='')) +
  xlab("Network bias") + ylab("Sibling bias") +
  #coord_equal() +
  tune::coord_obs_pred() +
  lemon::scale_y_symmetric(mid=0) +
  lemon::scale_x_symmetric(mid=0) +
  age_scale_color +
  #theme_minimal() +
  theme_bw() +
  theme(legend.position='right',
        text=element_text(size=alone_text_size))

# NB: this one is used
saveRDS(bvd_as_bias_plot_alone, file.path(comp_out_dir, "bvd_as_bias_plot_alone.rds"))

ggsave(file.path(comp_out_dir, "bvd_as_bias_alone.pdf"),
       bvd_as_bias_plot_alone,
       width=alone_fig_size, height=alone_fig_size)

bvd_as_bias_plot_alone
```


Same as above, but as a bar plot

```{r}

bvd_as_bias_bar_plot <- bvd_check_long %>%
  filter(qty == 'bias') %>%
  group_by(sex, agegp10) %>%
  summarize(Network = mean(Network),
            Sibling=mean(Sibling)) %>%
  pivot_longer(cols=c('Network', 'Sibling'), names_to='estimator', values_to='bias') %>%
  ggplot(.) +
  #### vertical version
  #geom_bar(aes(y=agegp10, x=bias, fill=estimator), stat='identity', position='dodge') +
  #lemon::scale_x_symmetric(mid=0) +
  #geom_vline(xintercept=0) +
  #xlab("Bias") + ylab("") +
  #facet_wrap(~ sex) +
  #### horizontal version
  geom_bar(aes(x=agegp10, y=bias, fill=estimator, pattern=estimator), stat='identity', position='dodge') +
  lemon::scale_y_symmetric(mid=0) +
  geom_hline(yintercept=0) +
  ylab("Average Bias\n(Estimate - Gold Standard)") + xlab("") +
  #annotate("text",
  #         #label = "Estimate is too high -->",
  #         label = "Estimate is\ntoo high -->",
  #         x=5.5, y=0.001,
  #         size=3,
  #         hjust=0,
  #         col='red',
  #         angle = 90) +
  facet_grid(sex ~ .) +
  scale_fill_manual(breaks=c('Network', 'Sibling'),
                    values = c(color_net, color_sib)) +
  guides(fill = guide_legend(title="")) +
  theme_bw() +
  theme(strip.background =element_rect(fill="white"))
  #theme_minimal() 


saveRDS(bvd_as_bias_bar_plot, file.path(comp_out_dir, "bvd_as_bias_bar_plot.rds"))
ggsave(file.path(comp_out_dir, "bvd_as_bias_bar_alone.pdf"),
       bvd_as_bias_bar_plot,
       #width=6, height=8)
       width=8, height=5)

bvd_as_bias_bar_plot
```

Count number of age/sex groups for which magnitude of net bias is bigger
than magnitude of sibling bias

```{r}
check_ns_mag_bias <- bvd_check_long %>%
  #filter(qty %in% c('bias', 'var')) %>%
  filter(qty == 'bias') %>%
  group_by(sex, agegp10) %>%
  summarize(Network = mean(Network),
            Sibling=mean(Sibling)) %>%
  mutate(net_bias_mag_bigger = as.numeric(abs(Network) > abs(Sibling)))

glue::glue("
           The bias of the network method is bigger in magnitude for
           {sum(check_ns_mag_bias$net_bias_mag_bigger)} out of {nrow(check_ns_mag_bias)} age-sex groups
           ")

check_ns_mag_bias
```

# Maps

```{r}
city.dat <- read_csv(file.path(data_dir, "cities.csv"))

# join in city names for titles
state.city.map <- city.dat %>% select(state_abbrev, region, state_name, city_name=municipio)
state.city.map <- state.city.map %>%
  mutate(title = paste0(city_name, " (", state_abbrev, ")")) %>%
  mutate(geo = state_abbrev)
  #mutate(title = paste0(city_name, ",\n", state_name))

#br_customgrid <- br_grid1 %>% 
br_customgrid <- br_states_grid1 %>% 
  select(-name) %>%
  left_join(state.city.map %>% select(code=state_abbrev, name=title))
```

## Hexgrid maps

Helper fn 

```{r city-method-mare-map, fig.height=4.5, fig.width=3}
  
comp_df <- comp_rel_asdrs_bygeo_wide
  
##
## data - dataset to use, already filtered (so either males or females)
##        needs a column called 'geo'
## qoivar - the value to plot
## name - the label for the qoi
br_compare_choro_map <- function(data, qoivar, name, 
                                 title=NULL, 
                                 labels=TRUE, 
                                 fillscale=NULL,
                                 logfill=FALSE,
                                 hex=TRUE) {
    
  mapobj <- readRDS(file.path(out_dir, "brazil_map.rds"))
  
  # should we plot a hex map? or a political map?
  if(hex) {
    # hexmap
    if(geo_name == 'region') {
      basemap <- mapobj$hexmap_region
    } else {
      basemap <- mapobj$hexmap
    }
    # political map
  } else {
    basemap <- mapobj$map
  }
  
  if(geo_name == 'city') {
    mapraw <- basemap %>%
      mutate(geo = postal) 
  } else {
    mapraw <- basemap %>%
      mutate(geo = region) 
  }
  
  mapdat <- mapraw %>%
    left_join(data %>% rename(qoi = qoivar))
  
  capdat <- mapobj$capitals
  
  if(is.null(fillscale)) {
    # default fill scale
    plot_fill_scale <- scale_fill_distiller(name=name, type='div')
  } else {
    plot_fill_scale <- fillscale
  }
  
  if (logfill) {
    plot_fill_scale <- plot_fill_scale + scale_color_continuous(trans=log10)
  }
  

  # for removing the background from ggplots
  remove_background <- theme(panel.background = element_blank(),
            panel.border = element_blank(),
            panel.grid.major = element_blank(),
            axis.ticks.x = element_blank(),
            axis.text.x = element_blank(),
            axis.ticks.y = element_blank(),
            axis.text.y = element_blank()) 
  
  cur_map <- 
    ggplot(data=mapdat) + 
      theme_bw(base_size=5) +
      geom_sf(aes(fill=qoi), 
              linetype='dotted', 
              alpha=.8) +
    plot_fill_scale +
    #log_scale_fill +
    remove_background  +
    xlab('') + ylab('') +
    theme(legend.position=c(.2,.3),
          legend.direction='vertical',
          legend.text=element_text(size=8),
          legend.title=element_text(size=8, face='bold')) +
    NULL
  
  if(labels) {
    cur_map <- cur_map +
      geom_sf(data=capdat) +
      geom_text_repel(data=capdat,
                      aes(x=lon, y=lat, 
                          label=glue::glue("{municipio} ({state_abbrev})")),
                      size=rel(3))
  }
  
  if(! is.null(title)) {
    cur_map <- cur_map + ggtitle(title)
  }
  
  return(cur_map)
}

# see 
# https://github.com/tidyverse/ggplot2/issues/1012
scale_fill_log10 <- function(...) {
  scale_fill_continuous(..., trans = scales::log10_trans())
}

# make maps for each age/sex group and assemble
# them into one figure
br_hexgrid_map <- function(qoivar,
                           qoiname,
                           scale_lims=NULL,
                           fillscale=NULL,
                           logfill=FALSE) {
  
  # TODO 
  if(! is.null(scale_lims)) {
    cur_lims <- scale_lims*1.05 
  } else {
    cur_lims <- NULL
  }
  
  if(logfill) {
    plot_logfill <- scale_fill_log10()
  } else {
    plot_logfill <- NULL
  }
  
  if(! is.null(fillscale)) {
    plot_fillscale <- fillscale
  } else {
    plot_fillscale <- scale_fill_distiller(name=qoiname, 
                                           palette = 'Spectral',
                                           limits=cur_lims,
                                           oob=scales::squish,
                                           type='div') 
  }
  
  maps_indiv <- comp_asdrs_bygeoas %>%
    group_by(sex, method, agegp10) %>%
    group_modify(function(cur_df, key) {
      
      cur_sex <- key$sex[1]
      cur_agegp10 <- key$agegp10[1]
      cur_method <- key$method[1]
      
      cur_map_errs <- br_compare_choro_map(cur_df,
                                           qoivar=qoivar,
                                           title=glue::glue('{cur_method}: {cur_sex}, {cur_agegp10}'),
                                           name=glue::glue('{cur_method} {qoiname}'),
                                           labels=FALSE,
                                           fillscale=plot_fillscale,
                                           hex=TRUE) +
        plot_logfill
      return(tibble(map_errs=list(cur_map_errs)))
      
    })
  
  layout <- "
  AF#KP
  BG#LQ
  CH#MR
  DI#NS
  EJ#OT
  "
  
  ppw <- 4 # plot panel width (relative)
  spw <- 1 # space panel width (relative)
  
  
  maps_array <- maps_indiv %>% 
    pull(map_errs) %>%
    wrap_plots(design=layout,
               widths=c(ppw, ppw, spw, ppw, ppw)) +
    plot_layout(guides='collect') &
    theme(legend.position='bottom',
          legend.direction='horizontal',
          plot.title=element_text(hjust=0.5)) 
  
  
  meta_layout <- "
  ##FF###MM##
  #NNSS#TTUU#
  APPPPPPPPPV
  BPPPPPPPPPW
  CPPPPPPPPPX
  DPPPPPPPPPY
  EPPPPPPPPPZ
  "
  
  final_maps <- wrap_plots(
     A=wrap_elements(grid::textGrob("18-24")), 
     B=wrap_elements(grid::textGrob("25-34")), 
     C=wrap_elements(grid::textGrob("35-44")), 
     D=wrap_elements(grid::textGrob("45-54")), 
     E=wrap_elements(grid::textGrob("55-64")), 
     V=wrap_elements(grid::textGrob("18-24")), 
     W=wrap_elements(grid::textGrob("25-34")), 
     X=wrap_elements(grid::textGrob("35-44")), 
     Y=wrap_elements(grid::textGrob("45-54")), 
     Z=wrap_elements(grid::textGrob("55-64")), 
     F=wrap_elements(grid::textGrob("Female")),
     M=wrap_elements(grid::textGrob("Male")),
     N=wrap_elements(grid::textGrob("Network")),
     T=wrap_elements(grid::textGrob("Network")),
     S=wrap_elements(grid::textGrob("Sibling")),
     U=wrap_elements(grid::textGrob("Sibling")),
     P=maps_array,
     design=meta_layout,
   heights=c(1,1,rep(6,5))) +
   plot_annotation(caption="Values outside of limits squished to limits.")
  
  return(final_maps)
}
```

Plot age/sex RMSE for estimates

```{r method_map_as_rmse}
method_rmse_as_maps <- br_hexgrid_map(qoivar='geo_rmse',
                                      qoiname='RMSE',
                                      scale_lims=c(0,10))
      
saveRDS(method_rmse_as_maps, file.path(comp_out_dir, "method_rmse_agesex_map.rds"))
ggsave(filename=file.path(comp_out_dir, "method_rmse_agesex_map.pdf"),
       plot=method_rmse_as_maps,
       height=10,
       width=8)
ggsave(filename=file.path(comp_out_dir, "method_rmse_agesex_map.png"),
       plot=method_rmse_as_maps,
       height=10,
       width=8)

method_rmse_as_maps
```

## Summarize Geographical relationships with Moran's I

Helper function to calculate Moran's I

```{r}

calculate_moran_I <- function(qoi_df, 
                              qoi_var, 
                              alternative = 'two.sided',
                              # other args for spdep::moran.test
                              ...) {

  mapobj <- readRDS(file.path(out_dir, "brazil_map.rds"))
  
  if(geo_name == 'city') {
    mapraw <- mapobj$map %>%
      mutate(geo = postal) 
  } else {
    mapraw <- mapobj$map %>%
      mutate(geo = region) %>%
      group_by(geo) %>%
      summarize() %>%
      ungroup()
  }
  
  # see
  # https://mgimond.github.io/Spatial/spatial-autocorrelation-in-r.html
  neighbors <- spdep::poly2nb(mapraw) 
  neighbors_weight <- spdep::nb2listw(neighbors, style="W", zero.policy=TRUE)
  
  #comp_rel_asdrs_bygeo_wide,
  #qoivar='n.minus.s'
                                        
  mapdat <- mapraw %>%
    left_join(qoi_df %>% rename(qoi = all_of(qoi_var)))
  
  res <- spdep::moran.test(mapdat[['qoi']], 
                           listw=neighbors_weight,
                           alternative=alternative,
                           ...)
  
  res$moran_I <- round(res$estimate[1],2)
  res$p_value <- round(res$p.value, 2)
  res$desc <- glue::glue("Moran's I, p-value calculated based on {alternative}",
                         .envir = res)
    
  # rename 'method' slot, since we use that for something else
  res$moran_method <- res$method
  res$method <- NULL
  
  return(res)
}

# helper function to coerce results of Moran's I calculation
# to a tibble row
moran_I_to_tibble <- function(res, ...) {
  class(res) <- NULL
  res$estimate <- list(res$estimate)
  return(as_tibble_row(c(res, ...)))
}

```

### Moran's I for MSE values

Calculate Moran's I for MSE values

```{r}
mse_moran_I <- comp_asdrs_bygeoas_wide %>%
  rename(diff = 'n.minus.s') %>%
  pivot_longer(cols=c('Network', 'Sibling', 'diff'),
               names_to = 'method',
               values_to = 'value') %>%
  ungroup() %>%
  group_by(geo, method) %>%
  summarize(value = mean(value)) %>%
  group_by(method) %>%
  group_map(function(cur_df, key) {
    
    cur_method <- key$method[1]
    
    res <- calculate_moran_I(cur_df, 'value')
    
    res$sex <- 'both'
    res$agegp10 <- 'all'
    res$method <- cur_method
    
    return(res)
    
  })

spatial_res_mse <- map_dfr(mse_moran_I,
                           ~ moran_I_to_tibble(.x,
                                               qty = 'MSE'))
```

Calculate Moran's I for MSE values by age/sex group

```{r}
mse_as_moran_I <- comp_asdrs_bygeoas_wide %>%
  rename(diff = 'n.minus.s') %>%
  pivot_longer(cols=c('Network', 'Sibling', 'diff'),
               names_to = 'method',
               values_to = 'value') %>%
  ungroup() %>%
  group_by(sex, method, agegp10) %>%
  group_map(function(cur_df, key) {
    
    cur_sex <- key$sex[1]
    cur_agegp10 <- key$agegp10[1]
    cur_method <- key$method[1]
    
    res <- calculate_moran_I(cur_df, 'value')
    
    res$sex <- cur_sex
    res$agegp10 <- cur_agegp10
    res$method <- cur_method
    
    return(res)
    
  })

spatial_res_mse_as <- map_dfr(mse_as_moran_I,
                              ~ moran_I_to_tibble(.x,
                                                  qty = 'MSE'))
```

```{r}
moran_I_df <- bind_rows(spatial_res_mse,
                        spatial_res_mse_as)


write_csv(moran_I_df %>% unnest_wider(estimate) %>% arrange(p_value),
          file.path(comp_out_dir, "moran_I.csv"))
```

Moran's I values that are significant at $p=0.05$ level

```{r}
moran_I_df %>% filter(p_value < 0.05)
```

## Heatmap figures 

Create a dataset `all_err_diffs_boot`
which has a row for each geo/sex/agegp/boot_idx that has, for Sibling and Network
  - delta = (estimate - truth) [diff between estimate and truth]
  - delta2 = (estimate - truth)^2 [delta squared - used in calculating MSE and RMSE]
  - delta_rel = |estimate - truth| / truth [absolute relative diff between estimate and truth]
  - delta_rel_notabs = (estimate - truth) / truth [relative diff between estimate and truth, with no absolute value taken]
  - estimate (the actual estimate)
  - gs_asdr (the gold standard value)
  
```{r}
all_err_diffs_boot <- comp_asdrs_boot %>%
  rename(estimate = post_mean_asdr) %>%
  pivot_wider(id_cols = c('geo', 'sex', 'agegp10', 'boot_idx', 'gs_asdr'),
              names_from=method,
              values_from=c(starts_with('delta'), 'estimate'))
```

Create a dataset `geo_err_diffs_boot` which summarizes errors within each geographical area;
it has a row for each geo/boot_idx that has, for Network/Sibling
  - mean_delta
  - mean_delta2
  - mean_delta_rel
it also has differences:
  - mean_diff_rel
  - mean_diff_mse
  - mean_diff_rmse = sqrt(mean_delta2_Network) - sqrt(mean_delta2_Sibling)
  
```{r}
## given a dataset assumed to be grouped in some way 
## aggregate errors and calculate rmse after aggregating
summ_estimate_errs <- function(df) {
  df %>%
    summarize(# sibling
              mean_delta_Sibling = mean(delta_Sibling),
              mean_delta2_Sibling = mean(delta2_Sibling),
              mean_delta_rel_Sibling = mean(delta_rel_Sibling),
              mean_delta_rel_notabs_Sibling = mean(delta_rel_notabs_Sibling), 
              # network 
              mean_delta_Network = mean(delta_Network),
              mean_delta2_Network = mean(delta2_Network),
              mean_delta_rel_Network = mean(delta_rel_Network),
              mean_delta_rel_notabs_Network = mean(delta_rel_notabs_Network)) %>%
    ungroup() %>%
    mutate(mean_diff_rel = mean_delta_rel_Network - mean_delta_rel_Sibling,
           mean_diff_rel_notabs = mean_delta_rel_notabs_Network - mean_delta_rel_notabs_Sibling,
           mean_diff_mse = mean_delta2_Network - mean_delta2_Sibling,
           mean_diff_rmse = sqrt(mean_delta2_Network) - sqrt(mean_delta2_Sibling),
           mean_diff_raw = mean_delta_Network - mean_delta_Sibling)
}

## given a summarized and grouped dataset,
## calculate summaries (point ests + cis) for network, sibling, and diffs
calc_ci_errs <- function(df) {
  df %>%
  summarize(
            ## sibling
            sib_mare = mean(mean_delta_rel_Sibling),
            sib_mare_ci_low = quantile(mean_delta_rel_Sibling, .025),
            sib_mare_ci_high = quantile(mean_delta_rel_Sibling, .975),
            sib_mse = mean(mean_delta2_Sibling),
            sib_mse_ci_low = quantile(mean_delta2_Sibling, .025),
            sib_mse_ci_high = quantile(mean_delta2_Sibling, .975),
            sib_rmse = sqrt(mean(mean_delta2_Sibling)),
            sib_rmse_ci_low = sqrt(quantile(mean_delta2_Sibling, .025)),
            sib_rmse_ci_high = sqrt(quantile(mean_delta2_Sibling, .975)),
            sib_raw = mean(mean_delta_Sibling),
            sib_raw_ci_low = quantile(mean_delta_Sibling, .025),
            sib_raw_ci_high = quantile(mean_delta_Sibling, .975),
            sib_rel_notabs = mean(mean_delta_rel_notabs_Sibling),
            sib_rel_notabs_ci_low = quantile(mean_delta_rel_notabs_Sibling, .025),
            sib_rel_notabs_ci_high = quantile(mean_delta_rel_notabs_Sibling, .975),
            ## network 
            net_mare = mean(mean_delta_rel_Network),
            net_mare_ci_low = quantile(mean_delta_rel_Network, .025),
            net_mare_ci_high = quantile(mean_delta_rel_Network, .975),
            net_mse = mean(mean_delta2_Network),
            net_mse_ci_low = quantile(mean_delta2_Network, .025),
            net_mse_ci_high = quantile(mean_delta2_Network, .975),
            net_rmse = sqrt(mean(mean_delta2_Network)),
            net_rmse_ci_low = sqrt(quantile(mean_delta2_Network, .025)),
            net_rmse_ci_high = sqrt(quantile(mean_delta2_Network, .975)),
            net_raw = mean(mean_delta_Network),
            net_raw_ci_low = quantile(mean_delta_Network, .025),
            net_raw_ci_high = quantile(mean_delta_Network, .975),
            net_rel_notabs = mean(mean_delta_rel_notabs_Network),
            net_rel_notabs_ci_low = quantile(mean_delta_rel_notabs_Network, .025),
            net_rel_notabs_ci_high = quantile(mean_delta_rel_notabs_Network, .975),
            ## differences    
            diff_mare = mean(mean_diff_rel),
            diff_mare_ci_low = quantile(mean_diff_rel, .025),
            diff_mare_ci_high = quantile(mean_diff_rel, .975),
            diff_mse = mean(mean_diff_mse),
            diff_mse_ci_low = quantile(mean_diff_mse, .025),
            diff_mse_ci_high = quantile(mean_diff_mse, .975),
            diff_rmse = mean(mean_diff_rmse),
            diff_rmse_ci_low = quantile(mean_diff_rmse, .025),
            diff_rmse_ci_high = quantile(mean_diff_rmse, .975),
            diff_raw = mean(mean_diff_raw),
            diff_raw_ci_low = quantile(mean_diff_raw, .025),
            diff_raw_ci_high = quantile(mean_diff_raw, .975),
            diff_rel_notabs = mean(mean_diff_rel_notabs),
            diff_rel_notabs_ci_low = quantile(mean_diff_rel_notabs, .025),
            diff_rel_notabs_ci_high = quantile(mean_diff_rel_notabs, .975)
            )
}

## given df with errors and grouping vars,
## calculate point ests and cis for those grouping vars,
## based on the general principle of calculating aggregates within
## each bootstrap rep, then summarizing across bootstrap reps
##
## example:
##   if groups is age and sex, then
##       1) calculate mare and rmse for each age and sex group within each boot rep
##       2) then calculate average and 95% CI of these age/sex mare and rmse values across boot reps
calc_summ_errs <- function(df, groups) {
  df %>%
    ## calculate rmse, mare, etc within groups and boot rep
    group_by(across({{groups}}), boot_idx) %>%
    summ_estimate_errs() %>%
    ## now summarize across boot reps, within groups
    group_by(across({{groups}})) %>%
    calc_ci_errs()
}
```

```{r}
geo_err_diffs_summ <-
  all_err_diffs_boot %>%
  calc_summ_errs(geo)

agesex_err_diffs_summ <-
  all_err_diffs_boot %>%
  calc_summ_errs(c(sex, agegp10))

geo_agesex_err_diffs_summ <-
  all_err_diffs_boot %>%
  calc_summ_errs(c(geo, sex, agegp10))

## this should calculate errs across cities for each bootstrap rep,
## then take ci, etc, over bootstrap reps
tot_err_diffs_summ <- all_err_diffs_boot %>%
  group_by(boot_idx) %>%
  summ_estimate_errs() %>%
  mutate(dummy=1) %>%
  group_by(dummy) %>%
  calc_ci_errs() %>%
  ungroup()
```

```{r}
# see
# https://stackoverflow.com/questions/60016390/set-axes-limits-in-patchwork-when-combining-ggplot2-objects
apply_consistent_y_lims <- function(this_plot){
    num_plots <- length(this_plot$layers)
    y_lims <- lapply(1:num_plots, function(x) ggplot_build(this_plot[[x]])$layout$panel_scales_y[[1]]$range$range)
    min_y <- min(unlist(y_lims))
    max_y <- max(unlist(y_lims))
    this_plot & ylim(min_y, max_y)
}
```


```{r}
## NB: this fn assumes that the environment has
##   geo_err_diffs_summ
##   agesex_err_diffs_summ
##   geo_agesex_err_diffs_summ
err_breakdown_plot <- function(err_metric, 
                               err_metric_name, 
                               diff = FALSE) {
  
  if (diff) {
    fill_scale <- scale_fill_gradient2(low='yellow', high='red', midpoint=0)
    vline <- geom_vline(xintercept = 0, color='grey')
    hline <- geom_hline(yintercept = 0, color='grey')
    symm_x <- lemon::scale_x_symmetric(mid=0)
  } else {
    fill_scale <- scale_fill_gradient(low='white', high='red')
    vline <- NULL
    hline <- NULL
    symm_x <- NULL
  }
  
  ## age-sex plot
  as_plot <- agesex_err_diffs_summ %>%
    ## rename current error
    rename_with(~ str_replace(.x, err_metric, 'err'),
                .cols=starts_with(err_metric)) %>%
    ggplot(.) +
    geom_pointrange(aes(x=agegp10, 
                        ymin=err_ci_low,
                        ymax=err_ci_high,
                        y=err)) +
    facet_wrap(~ sex) +
    theme_minimal() +
    xlab("") +
    expand_limits(y = 0) +
    hline + 
    ylab(err_metric_name)

   geo_err_diffs_summ_forplot <- geo_err_diffs_summ %>%
    ## rename current error
    rename_with(~ str_replace(.x, err_metric, 'err'),
                .cols=starts_with(err_metric)) %>%
     mutate(geo = factor(geo)) %>%
     mutate(geo = fct_reorder(geo, err))
   
   geo_lev_order <- levels(geo_err_diffs_summ_forplot$geo)
   
   city_plot <- geo_err_diffs_summ_forplot %>%
     ggplot(.) +
     geom_pointrange(aes(x=err, 
                         xmin=err_ci_low,
                         xmax=err_ci_high,
                         y=geo)) +
     theme_minimal() +
     xlab(err_metric_name) +
     expand_limits(x = 0) +
     symm_x +
     vline +
     ylab("")
   
   ## summarize errors across bootstrap reps within each city/age/sex gp
   hm <- geo_agesex_err_diffs_summ %>%
    ## rename current error
    rename_with(~ str_replace(.x, err_metric, 'err'),
                .cols=starts_with(err_metric)) %>%
     mutate(geo = factor(geo)) %>%
     mutate(geo = fct_relevel(geo, geo_lev_order)) %>%
     ggplot(.) +
     geom_tile(aes(x=agegp10, y=geo, fill=err)) +
     facet_wrap(~ sex) +
     theme_minimal() +
     xlab("") +
     ylab("") +
     theme(legend.position = 'bottom') +
     fill_scale +
     expand_limits(fill = 0) +
     #coord_equal() +
     guides(fill = guide_colorbar(title = err_metric_name,
                                  title.position="top"))
     #scale_fill_gradient(low='black', high='red')   
  
  # 1 : heatmap
  # 2 : city agg errs
  # 3 : age-sex errs
  design <- "
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    333333333334444
    333333333334444
    333333333334444
    333333333334444
  "
  #p1 <- (hm + ggtitle("City, Probability")) + 
  #      (city_plot + ggtitle("City, Age-specific death rate")) + 
  #      (as_plot + ggtitle("Region, Probability")) +
  test <- (hm + ggtitle("A")) + 
        (city_plot + ggtitle("B")) + 
        (as_plot + ggtitle("C")) +
        guide_area() +
    plot_layout(guides='collect', design=design)   
  
  return(test)
}

```


```{r}
# height / width for saved plots
pheight <- 10
pwidth <- 7.5
```


### MARE

Network MARE

```{r}
err_breakdown_mare_net <- err_breakdown_plot('net_mare', 
                                             'Network\nMARE')

#saveRDS(err_breakdown_mare_net, 
#        file.path(comp_out_dir, "err_breakdown_mare_net.rds"))
ggsave(filename=file.path(comp_out_dir, "err_breakdown_mare_net.pdf"),
       plot=err_breakdown_mare_net,
       height=pheight,
       width=pwidth)

err_breakdown_mare_net
```

Sibling MARE

```{r}
err_breakdown_mare_sib <- err_breakdown_plot('sib_mare', 
                                             'Sibling\nMARE')

#saveRDS(err_breakdown_mare_sib, 
#        file.path(comp_out_dir, "err_breakdown_mare_sib.rds"))
ggsave(filename=file.path(comp_out_dir, "err_breakdown_mare_sib.pdf"),
       plot=err_breakdown_mare_sib,
       height=pheight,
       width=pwidth)

err_breakdown_mare_sib
```

### RMSE


Network RMSE

```{r}
err_breakdown_rmse_net <- err_breakdown_plot('net_rmse', 
                                             'Network\nRMSE')

#saveRDS(err_breakdown_rmse_net, 
#        file.path(comp_out_dir, "err_breakdown_rmse_net.rds"))
ggsave(filename=file.path(comp_out_dir, "err_breakdown_rmse_net.pdf"),
       plot=err_breakdown_rmse_net,
       height=pheight,
       width=pwidth)

err_breakdown_rmse_net
```

Sibling RMSE

```{r}
err_breakdown_rmse_sib <- err_breakdown_plot('sib_rmse', 
                                             'Sibling\nRMSE')

#saveRDS(err_breakdown_rmse_sib, 
#        file.path(comp_out_dir, "err_breakdown_rmse_sib.rds"))
ggsave(filename=file.path(comp_out_dir, "err_breakdown_rmse_sib.pdf"),
       plot=err_breakdown_rmse_sib,
       height=pheight,
       width=pwidth)

err_breakdown_rmse_sib
```


```{r}
toc()
```


