---
title: "Vital registration comparison"
params:
  ## comparison_name - are we comparing to VR to the adjusted VR?
  comparison_name: "vr_comparison"
  #comparison_name: "vr_adj_comparison"
  ## geo_name - are we analyzing at the city, region, or national level?
  geo_name: "city"
  #geo_name: "region"
  #geo_name: "national"
  ## do_12mo: if true, run the sibling 12-month estimates
  do_12mo: true
output:
  html_document:
    df_print: paged
---

This file makes the comparison between the two survey-based estimates
(sibling and network) and the vital registration data.

It uses parameters to choose whether the comparison is at the state or regional level,
and to choose whether the comparison is to the adjusted or unadjusted vital registration.

For replication, this file is not supposed to be run directly; it is run by another
notebook.

```{r}
library(tidyverse)
library(geofacet)
#devtools::install_github("dgrtwo/drlib")
library(drlib) # has reorder_within / scale_x_reordered for plots

library(gtable) # for customizing map
library(ggplotify) # for customizing map

library(ggforce) # for paginating faceted output
library(latex2exp)
library(broom)

library(ggrepel)
library(patchwork)
library(tictoc)
library(glue)

## this has coord_obs_pred, which is helpful for plots
library(tune)

# for calculating moran's I
# (spatial autocorrelation)
library(spdep)

# this has color scale
library(viridis)

# to avoid issues w/ spherical geometry (minor detail in making maps)
# see
# https://gis.stackexchange.com/questions/404385/r-sf-some-edges-are-crossing-in-a-multipolygon-how-to-make-it-valid-when-using
sf_use_s2(FALSE)

# has a helper function for symmetric y axis
# devtools::install_github("stefanedwards/lemon")
# (on 20230613)
library(lemon)

library(here)
```

```{r}
comparison_name <- params$comparison_name 

geo_name <- params$geo_name 
```

```{r}
out_dir <- here('out')
data_dir <- here('data')

vr_dir <- file.path(data_dir, 'vr_prepped')

comp_out_dir0 <- file.path(out_dir, comparison_name)
comp_out_dir <- file.path(comp_out_dir0, geo_name)
dir.create(comp_out_dir0, showWarnings = FALSE)
dir.create(comp_out_dir, showWarnings = FALSE)
```

```{r}
tic(glue::glue("Running comparison for {comparison_name} / {geo_name}"))
```


## Some aesthetics for the plots

```{r}
color_sib <- "#FC4E07"
color_net <- "#00AFBB"
color_gs <- "black"

shape_sib <- 0
shape_net <- 5
shape_gs  <- 16

region_pal <- tribble(~ region, ~ color,
                      'NO', 'blue',
                      'NE', 'orange',
                      'CW', 'red',
                      'SE', 'green',
                      'SO', 'purple')

age_scale_color <- scale_color_viridis(discrete=TRUE, direction=-1)
```

## Cities to use in comparison

## Open up the estimates

Load vital registration reference estimates

```{r}
if(comparison_name == 'vr_comparison') {
  
  if(geo_name == 'city') {
    gs_asdrs <- read_csv(file.path(vr_dir, 
                                   "vr_asdrs.csv")) %>%
      rename(geo = state_abbrev)
    
    gs_probs <- read_csv(file.path(vr_dir, 
                                   "vr_47q18.csv")) %>%
      rename(geo = state_abbrev)
    
  } else if(geo_name == 'region') {

    gs_asdrs <- read_csv(file.path(vr_dir, 
                                   "vr_region_asdrs.csv")) %>%
      rename(geo = region)
    
    gs_probs <- read_csv(file.path(vr_dir, 
                                   "vr_region_47q18.csv")) %>%
      rename(geo = region)
    
  } else if (geo_name == 'national') {
    
    gs_asdrs <- read_csv(file.path(vr_dir, 
                                   "vr_national_asdrs.csv")) %>%
      mutate(geo = 'national')
    
    gs_probs <- read_csv(file.path(vr_dir, 
                                   "vr_national_47q18.csv")) %>%
      mutate(geo = 'national')
    
  }
  
} else if (comparison_name == 'vr_adj_comparison') {
  
  if(geo_name == 'city') {
    gs_asdrs <- read_csv(file.path(vr_dir, 
                                   "vr_asdrs_adj.csv"))  %>%
      rename(geo = state_abbrev)
    
    gs_probs <- read_csv(file.path(vr_dir, 
                                   "vr_47q18_adj.csv")) %>%
      rename(geo = state_abbrev)
    
  } else if (geo_name == 'region') {
  
    gs_asdrs <- read_csv(file.path(vr_dir, 
                                   "vr_region_asdrs_adj.csv")) %>%
      rename(geo = region)
    
    gs_probs <- read_csv(file.path(vr_dir, 
                                   "vr_region_47q18_adj.csv")) %>%
      rename(geo = region)
    
  } else if (geo_name == 'national') {
    
    gs_asdrs <- read_csv(file.path(vr_dir, 
                                   "vr_national_asdrs_adj.csv")) %>%
      mutate(geo = 'national')
    
    gs_probs <- read_csv(file.path(vr_dir, 
                                   "vr_national_47q18_adj.csv")) %>%
      mutate(geo = 'national')
    
  }
}
```

Load sibling estimates

```{r}
if(geo_name == 'city') {
  
  sib_asdrs <- read_csv(file.path(out_dir, 
                                  'sib_design_asdrs.csv')) %>%
    rename(geo = state_abbrev)
  
  sib_probs <- read_csv(file.path(out_dir, 
                                  'sib_design_probs.csv')) %>%
    rename(geo = state_abbrev)
  
  sib_asdrs_boot <- read_csv(file.path(out_dir, 
                                       'sib_design_asdrs_boot.csv')) %>%
    rename(geo = state_abbrev)
  
  sib_probs_boot <- read_csv(file.path(out_dir, 
                                       'sib_design_probs_boot.csv')) %>%
    rename(geo = state_abbrev)
  
  if(params$do_12mo) {
    
    sib_asdrs_12mo <- read_csv(file.path(out_dir, 
                                         'sib_12mo_design_asdrs.csv')) %>%
      rename(geo = state_abbrev)
    
    sib_probs_12mo <- read_csv(file.path(out_dir, 
                                    'sib_12mo_design_probs.csv')) %>%
      rename(geo = state_abbrev)
    
    sib_asdrs_boot_12mo <- read_csv(file.path(out_dir, 
                                         'sib_12mo_design_asdrs_boot.csv')) %>%
      rename(geo = state_abbrev)
    
    sib_probs_boot_12mo <- read_csv(file.path(out_dir, 
                                              'sib_12mo_design_probs_boot.csv')) %>%
      rename(geo = state_abbrev)
  
  }

} else if (geo_name == 'region') {
  
  sib_asdrs <- read_csv(file.path(out_dir, 
                                  'sib_design_asdrs_region.csv')) %>%
    rename(geo = region)
  
  sib_probs <- read_csv(file.path(out_dir, 
                                  'sib_design_probs_region.csv')) %>%
    rename(geo = region)
  
  sib_asdrs_boot <- read_csv(file.path(out_dir, 
                                       'sib_design_asdrs_region_boot.csv')) %>%
    rename(geo = region)
  
  sib_probs_boot <- read_csv(file.path(out_dir, 
                                       'sib_design_probs_region_boot.csv')) %>%
    rename(geo = region)
  
} else if (geo_name == 'national') {
  
  sib_asdrs <- read_csv(file.path(out_dir, 
                                  'sib_design_asdrs_national.csv')) %>%
    mutate(geo = 'national')
  
  sib_probs <- read_csv(file.path(out_dir, 
                                  'sib_design_probs_national.csv')) %>%
    mutate(geo = 'national')
  
  sib_asdrs_boot <- read_csv(file.path(out_dir, 
                                       'sib_design_asdrs_national_boot.csv')) %>%
    mutate(geo = 'national')
  
  sib_probs_boot <- read_csv(file.path(out_dir, 
                                       'sib_design_probs_national_boot.csv')) %>%
    mutate(geo = 'national')
  
}
```

Load network estimates

```{r}
if(geo_name == 'city') {
  
  net_asdrs <- read_csv(file.path(out_dir, 
                                  'net_design_asdrs.csv')) %>%
    rename(geo = state_abbrev)
  
  net_probs <- read_csv(file.path(out_dir, 
                                  'net_design_probs.csv')) %>%
    rename(geo = state_abbrev)
  
  net_asdrs_boot <- read_csv(file.path(out_dir, 
                                       'net_design_asdrs_boot.csv')) %>% 
    mutate(method='net_design') %>%
    rename(geo = state_abbrev)
  
  net_probs_boot <- read_csv(file.path(out_dir, 
                                       'net_design_probs_boot.csv')) %>% 
    mutate(method='net_design') %>%
    rename(geo = state_abbrev,
           q.47.18 = q.47.18.mean)
  
} else if (geo_name == 'region') {

  net_asdrs <- read_csv(file.path(out_dir, 
                                  'net_design_asdrs_region.csv')) %>%
    rename(geo = region)
  
  net_probs <- read_csv(file.path(out_dir, 
                                  'net_design_probs_region.csv')) %>%
    rename(geo = region)
  
  net_asdrs_boot <- read_csv(file.path(out_dir, 
                                       'net_design_asdrs_region_boot.csv')) %>%
    mutate(method='net_design') %>%
    rename(geo = region)
  
  net_probs_boot <- read_csv(file.path(out_dir, 
                                       'net_design_probs_region_boot.csv')) %>%
    mutate(method='net_design') %>%
    rename(geo = region,
           q.47.18 = q.47.18.mean)

} else if (geo_name == 'national') {
  
  net_asdrs <- read_csv(file.path(out_dir, 
                                  'net_design_asdrs_national.csv')) %>%
    mutate(geo = 'national')
  
  net_probs <- read_csv(file.path(out_dir, 
                                  'net_design_probs_national.csv')) %>%
    mutate(geo = 'national')
  
  net_asdrs_boot <- read_csv(file.path(out_dir, 
                                       'net_design_asdrs_national_boot.csv')) %>%
    mutate(method='net_design') %>%
    mutate(geo = 'national')
  
  net_probs_boot <- read_csv(file.path(out_dir, 
                                       'net_design_probs_national_boot.csv')) %>%
    mutate(method='net_design') %>%
    mutate(geo = 'national') %>%
    rename(q.47.18 = q.47.18.mean)
  
}
```

Load estimated VR completeness

```{r}
if(geo_name == 'city') {
  ibge_vr_completeness <- read_csv(file.path(out_dir, 
                                             'vr_completeness_estimates.csv')) %>%
    rename(geo = state_abbrev)
}
```


Assemble the different results in one place

```{r}
est_asdrs <- bind_rows(sib_asdrs,
                       net_asdrs) %>%
  filter(agegp10 != '[65,75)') %>%
  mutate(method = recode(method,
                         'sib_design'='Sibling',
                         'net_design'='Network')) %>%
  mutate(sex = recode(sex,
                      'male'='Male',
                      'female'='Female'))

est_asdrs_boot <- bind_rows(sib_asdrs_boot,
                            net_asdrs_boot) %>%
  filter(agegp10 != '[65,75)') %>%
  mutate(method = recode(method,
                         'sib_design'='Sibling',
                         'net_design'='Network')) %>%
  mutate(sex = recode(sex,
                      'male'='Male',
                      'female'='Female'))

est_probs <- bind_rows(sib_probs,
                       net_probs) %>%
  mutate(method = recode(method,
                         'sib_design'='Sibling',
                         'net_design'='Network')) %>%
  mutate(sex = recode(sex,
                      'male'='Male',
                      'female'='Female'))

est_probs_boot <- bind_rows(sib_probs_boot,
                            net_probs_boot) %>%
  mutate(method = recode(method,
                         'sib_design'='Sibling',
                         'net_design'='Network')) %>%
  mutate(sex = recode(sex,
                      'male'='Male',
                      'female'='Female'))
```

Assemble 12 mo sib results too

```{r}
if(params$do_12mo) {
  est_asdrs_with12mo <- bind_rows(sib_asdrs,
                         sib_asdrs_12mo %>% mutate(method = 'Sibling12mo'),
                         net_asdrs) %>%
    filter(agegp10 != '[65,75)') %>%
    mutate(method = recode(method,
                           'sib_design'='Sibling',
                           'net_design'='Network')) %>%
    mutate(sex = recode(sex,
                        'male'='Male',
                        'female'='Female'))
  
  est_asdrs_boot_with12mo <- bind_rows(sib_asdrs_boot,
                              sib_asdrs_boot_12mo %>% mutate(method = 'Sibling12mo'),
                              net_asdrs_boot) %>%
    filter(agegp10 != '[65,75)') %>%
    mutate(method = recode(method,
                           'sib_design'='Sibling',
                           'net_design'='Network')) %>%
    mutate(sex = recode(sex,
                        'male'='Male',
                        'female'='Female'))
  
  est_probs_with12mo <- bind_rows(sib_probs,
                         sib_probs_12mo %>% mutate(method = 'Sibling12mo'),
                         net_probs) %>%
    mutate(method = recode(method,
                           'sib_design'='Sibling',
                           'net_design'='Network')) %>%
    mutate(sex = recode(sex,
                        'male'='Male',
                        'female'='Female'))
  
  est_probs_boot_with12mo <- bind_rows(sib_probs_boot,
                              sib_probs_boot_12mo %>% mutate(method = 'Sibling12mo'),
                              net_probs_boot) %>%
    mutate(method = recode(method,
                           'sib_design'='Sibling',
                           'net_design'='Network')) %>%
    mutate(sex = recode(sex,
                        'male'='Male',
                        'female'='Female'))  
}
```


Count the number of estimates that is exactly 0

```{r}
num_zero_ests <- est_asdrs %>%
  group_by(method) %>%
  summarize(num_zero = sum(post_mean_asdr == 0),
            total = n())

write_csv(num_zero_ests,
          file.path(comp_out_dir, "num_zero_ests.csv"))

num_zero_ests
```

## Quantitative summaries

MSE on natural scale

```{r}
calc_errors <- function(df, ci = TRUE) {
  res <- df %>%
    mutate(delta = 1000*(post_mean_asdr - gs_asdr),
           delta2 = delta*delta,
           ## NB: delta_rel is the absolute relative error
           ##     and delta_rel_notabs is the relative error w/out taking absolute value
           delta_rel = abs(delta)/(1000*gs_asdr),
           delta_rel_notabs = delta/(1000*gs_asdr))
  if(ci) {
    res <- res %>%
      mutate(ci_covered = as.numeric(gs_asdr >= post_ci_low_asdr & gs_asdr <= post_ci_high_asdr))
  }
  
  return(res)
}

calc_errors_probs <- function(df, ci = TRUE) {
  res <- df %>%
    mutate(delta = post_mean_q - gs_prob,
           delta2 = delta*delta,
           delta_rel = abs(delta)/gs_prob,
           delta_rel_notabs = delta/gs_prob)
  if(ci) {
  res <- res %>% mutate(ci_covered = as.numeric(gs_prob >= post_ci_low_q & gs_prob <= post_ci_high_q))
  }
  return(res)
}

comp_asdrs <- est_asdrs %>%
  left_join(gs_asdrs %>% dplyr::rename(gs_asdr=asdr)) %>%
  calc_errors()

comp_asdrs_boot <- est_asdrs_boot %>%
  left_join(gs_asdrs %>% dplyr::rename(gs_asdr=asdr)) %>%
  calc_errors(ci=FALSE)

write_csv(comp_asdrs_boot %>%
          rename(estimate_asdr = post_mean_asdr) %>%
          mutate(estimate_asdr_1000 = estimate_asdr * 1000) %>%
          bind_cols(comparison_name = params$comparison_name,
                    geo_name = params$geo_name),
          file.path(comp_out_dir, "comp_asdrs_boot.csv"))

comp_asdrs_wide_boot <- comp_asdrs_boot %>%
  select(-gs_asdr, -post_mean_asdr) %>%
  pivot_wider(names_from=method, values_from=c(delta, delta2, delta_rel, delta_rel_notabs)) %>%
  mutate(delta2.n.minus.s = delta2_Network - delta2_Sibling,
         delta_rel.n.minus.s = delta_rel_Network - delta_rel_Sibling)

comp_probs <- est_probs %>%
  left_join(gs_probs %>% dplyr::rename(gs_prob=q.47.18)) %>%
  calc_errors_probs()

comp_probs_boot <- est_probs_boot %>%
  dplyr::rename(post_mean_q = q.47.18) %>%
  left_join(gs_probs %>% dplyr::rename(gs_prob=q.47.18)) %>%
  calc_errors_probs(ci=FALSE)

write_csv(comp_probs_boot %>%
          rename(estimate_prob = post_mean_q) %>%
          bind_cols(comparison_name = params$comparison_name,
                    geo_name = params$geo_name),
          file.path(comp_out_dir, "comp_probs_boot.csv"))

comp_probs_wide_boot <- comp_probs_boot %>%
  select(-gs_prob, -post_mean_q, -time.period) %>%
  pivot_wider(names_from=method, values_from=c(delta, delta2, delta_rel, delta_rel_notabs)) %>%
  mutate(delta2.n.minus.s = delta2_Network - delta2_Sibling,
         delta_rel.n.minus.s = delta_rel_Network - delta_rel_Sibling)
```

Errors for 12mo sib ests

```{r}
if(params$do_12mo) {
  
  comp_asdrs_with12mo <- est_asdrs_with12mo %>%
    left_join(gs_asdrs %>% dplyr::rename(gs_asdr=asdr)) %>%
    calc_errors()
  
  # quick table comparing squared error for net / sib / sib 12mo
  errs_with_12mo <- comp_asdrs_with12mo %>%
    group_by(method) %>%
    summarize(mean_delta2 = mean(delta2),
              mean_delta_rel = mean(delta_rel))
  
  write_csv(errs_with_12mo,
            file.path(comp_out_dir, "avg_errs_with_sib12mo.csv"))
  saveRDS(errs_with_12mo,
            file.path(comp_out_dir, "avg_errs_with_sib12mo.rds"))
  
  errs_with_12mo
}
```

## Plots directly comparing estimates at the level of geography (state or region)

```{r plot-compare-ests}
direct_comp_est_asdrs <- 
  est_asdrs %>%
    select(-time.period) %>%
    tidyr::pivot_wider(id_cols=c('sex', 'agegp10', 'geo'),
                       values_from=c('post_mean_asdr'),
                       names_from=c('method')) 

cur_range <- range(log(direct_comp_est_asdrs$Network),
                   log(direct_comp_est_asdrs$Sibling),
                   finite=TRUE)

alpha.val <- .6

# logged
direct_plot_logged <-  direct_comp_est_asdrs %>%
  ggplot(.) +
  geom_abline(intercept=0, slope=1) +
  geom_point(aes(x=log(Network), 
                 y=log(Sibling),
                 color=agegp10,
                 shape=sex), 
             alpha=alpha.val) +
  coord_equal() +
  xlim(cur_range) + ylim(cur_range) +
  guides(color=guide_legend(override.aes=list(alpha=1),
                            title='Age'),
         shape=guide_legend(override.aes=list(alpha=1),
                            title='')) +
  ylab("log(Sibling death rate est.)") +
  xlab("log(Network death rate est.)") +
  age_scale_color +
  theme_bw()

# NB: this is used in paper
saveRDS(direct_plot_logged, file.path(comp_out_dir, "direct_asdr_logged.rds"))
ggsave(filename=file.path(comp_out_dir, "direct_asdr_logged.pdf"),
       plot=direct_plot_logged,
       height=3.5,
       width=3.5)
direct_plot_logged

```

```{r plot-compare-ests-probs}
direct_comp_est_probs <- 
  est_probs %>%
    select(-time.period) %>%
    tidyr::pivot_wider(id_cols=c('sex', 'geo'),
                       values_from=c('post_mean_q'),
                       names_from=c('method')) 
```


```{r}
cur_range <- range(log(direct_comp_est_probs$Network),
                   log(direct_comp_est_probs$Sibling),
                   finite=TRUE)

alpha.val <- .6 
  
# logged
direct_plot_probs_logged <-  direct_comp_est_probs %>%
  ggplot(.) +
  geom_abline(intercept=0, slope=1) +
  geom_point(aes(x=log(Network), 
                 y=log(Sibling),
                 shape=sex), 
             alpha=alpha.val) +
  coord_equal() +
  xlim(cur_range) + ylim(cur_range) +
  guides(shape=guide_legend(override.aes=list(alpha=1),
                            title='')) +
  ylab("log(Sibling prob. of death est.)") +
  xlab("log(Network prob. of death est.)") +
  theme_bw()

# NB: this is used in paper
saveRDS(direct_plot_probs_logged, file.path(comp_out_dir, "direct_probs_logged.rds"))
ggsave(filename=file.path(comp_out_dir, "direct_probs_logged.pdf"),
       plot=direct_plot_probs_logged,
       height=3.5,
       width=3.5)
direct_plot_probs_logged

```
## Plots by geography

ASDRs w/ ref est

```{r plot-asdrs-ref, fig.width=3.5, fig.height=10}

rel.point.size <- .3
point.stroke <- .2

asdr_point_plot <- 
  est_asdrs %>%
  left_join(gs_asdrs) %>% 
  group_by(sex, geo) %>%
  # order facets by state difficulty
  mutate(delta = post_mean_asdr - asdr,
         state_difficulty = sum(abs(delta))) %>%
  ungroup() %>%
  mutate(geo = as_factor(geo),
         geo = forcats::fct_reorder(geo, state_difficulty)) %>%
         #geo = drlib::reorder_within(geo, state_difficulty, sex)) %>%
  # end new 
  ggplot(.) +
  theme_bw(base_size=5) +
  geom_pointrange(aes(x=agegp10, 
                      y=post_mean_asdr, 
                      ymin=post_ci_low_asdr,
                      ymax=post_ci_high_asdr,
                      color=method,
                      shape=method),
                  position=position_dodge(width=.5),
                  size=rel(rel.point.size),
                  stroke=point.stroke) +
  geom_point(aes(x=agegp10,
                 y=asdr,
                 color='Vital registration',
                 shape='Vital registration'),
             size=rel(rel.point.size),
             stroke=1) +
  ylab("Age-specific death rate") +
  xlab("") +
  theme(strip.background=element_rect(fill=NA)) +
  guides(color=guide_legend(title='Method', override.aes=list(linetype=c(1,1,0))),
  #guides(color=guide_legend(title='Method'),
         shape=guide_legend(title='Method')) +
  scale_shape_manual(values=c('Sibling'=shape_sib, 'Network'=shape_net, 'Vital registration'=shape_gs))+
  scale_color_manual(values=c('Sibling'=color_sib, 'Network'=color_net, 'Vital registration'=color_gs)) +
  theme(legend.position='bottom',
        legend.direction='horizontal')
   
asdr_point_plot_onepage <- asdr_point_plot + facet_grid(geo ~ sex)

ggsave(filename=file.path(comp_out_dir, "asdr_pointrange.pdf"),
       plot=asdr_point_plot_onepage,
       height=10,
       width=3.5)
knitr::plot_crop(file.path(comp_out_dir, "asdr_pointrange.pdf"))

asdr_point_plot_onepage
```


Log-scale ASDRs all on one big page

```{r plot-state-asdr-log, fig.width=3.5, fig.height=10}
asdr_point_plot_log_onepage <-
  asdr_point_plot_onepage +
  ##coord_trans(y='log10')
  scale_y_log10()

ggsave(filename=file.path(comp_out_dir, "asdr_pointrange_log.pdf"),
       plot=asdr_point_plot_log_onepage,
       height=10,
       width=3.5)
knitr::plot_crop(file.path(comp_out_dir, "asdr_pointrange_log.pdf"))

asdr_point_plot_log_onepage
```

### Error summaries across geography

#### ASDRS

All ests, by geography

```{r calculate-errs-in-asdrs-by-geo}
comp_asdrs_bygeo <- comp_asdrs %>%
  group_by(method, geo) %>%
  summarize(geo_mse = mean(delta2),
            #geo_are = sum(abs(delta_rel))) 
            # this should be the mean, right?
            geo_are = mean(abs(delta_rel))) 

comp_asdrs_bygeo_boot <- comp_asdrs_boot %>%
  group_by(method, geo, boot_idx) %>%
  summarize(geo_mse = mean(delta2),
            #geo_are = sum(abs(delta_rel))) 
            # this should be the mean, right?
            geo_are = mean(abs(delta_rel))) 

# difference in MSE (network - sibling)
comp_asdrs_bygeo_wide <- comp_asdrs_bygeo %>%
  select(-geo_are) %>%
  pivot_wider(names_from=method, values_from=geo_mse)  %>%
  mutate(n.minus.s = Network - Sibling)

comp_asdrs_bygeo_wide_boot <- comp_asdrs_bygeo_boot %>%
  select(-geo_are) %>%
  pivot_wider(names_from=method, values_from=geo_mse)  %>%
  mutate(n.minus.s = Network - Sibling)

# difference in ARE (network - sibling)
comp_rel_asdrs_bygeo_wide <- comp_asdrs_bygeo %>%
  select(-geo_mse) %>%
  pivot_wider(names_from=method, values_from=geo_are) %>%
  mutate(n.minus.s = Network - Sibling)

comp_rel_asdrs_bygeo_wide_boot <- comp_asdrs_bygeo_boot %>%
  select(-geo_mse) %>%
  pivot_wider(names_from=method, values_from=geo_are) %>%
  mutate(n.minus.s = Network - Sibling)
```


By age/sex/geography

```{r asdr-errs-by-age-sex-geo}
comp_asdrs_bygeoas <- comp_asdrs %>%
  group_by(method, geo, sex, agegp10) %>%
  summarize(geo_mse = mean(delta2),
            # this should be the mean, right?
            geo_are = mean(abs(delta_rel)),
            # not absolute relative error (so, can be negative)
            geo_re = mean(delta_rel_notabs)) %>%
  ungroup() %>%
  mutate(geo_rmse = sqrt(geo_mse))

# difference in MSE (network - sibling)
comp_asdrs_bygeoas_wide <- comp_asdrs_bygeoas %>%
  select(-geo_are, -geo_re, -geo_rmse) %>%
  pivot_wider(names_from=method, values_from=geo_mse)  %>%
  mutate(n.minus.s = Network - Sibling)

# difference in RMSE (network - sibling)
comp_rmse_asdrs_bygeoas_wide <- comp_asdrs_bygeoas %>%
  select(-geo_are, -geo_re, -geo_mse) %>%
  pivot_wider(names_from=method, values_from=geo_rmse)  %>%
  mutate(n.minus.s = Network - Sibling)
  # alternate approach:
  # square root of difference in MSE (network - sibling)
  # that is,
  #   sign(MSE(net) - MSE(sib)) * sqrt(MSE(net) - MSE(sib))
  #mutate(n.minus.s = sign(Network - Sibling) * sqrt(abs(Network - Sibling)))

# difference in ARE (network - sibling)
comp_rel_asdrs_bygeoas_wide <- comp_asdrs_bygeoas %>%
  select(-geo_mse, -geo_re, -geo_rmse) %>%
  pivot_wider(names_from=method, values_from=geo_are) %>%
  mutate(n.minus.s = Network - Sibling)
```

By age/sex

```{r asdr-errs-by-age-sex}
comp_asdrs_byas <- comp_asdrs %>%
  group_by(method, sex, agegp10) %>%
  summarize(as_mse = mean(delta2),
            as_are = mean(abs(delta_rel)),
            # not absolute relative error (so, can be negative)
            as_re = mean(delta_rel_notabs))  

# with bootstraps
comp_asdrs_byas_boot <- comp_asdrs_boot %>%
  group_by(method, sex, agegp10, boot_idx) %>%
  summarize(as_mse = mean(delta2),
            as_are = mean(abs(delta_rel)),
            # not absolute relative error (so, can be negative)
            as_re = mean(delta_rel_notabs),
            .groups='drop') %>%
  group_by(method, sex, agegp10) %>%
  summarize(as_mse_ci_low = quantile(as_mse, .025),
            as_mse_ci_high = quantile(as_mse, .975),
            as_mse = mean(as_mse),
            as_are_ci_low = quantile(as_are, .025),
            as_are_ci_high = quantile(as_are, .975),
            as_are = mean(as_are),
            # not absolute relative error (so, can be negative)
            as_re_ci_low = quantile(as_re, .025),
            as_re_ci_high = quantile(as_re, .975),
            as_re = mean(as_re))

# difference in MSE (network - sibling)
comp_asdrs_byas_wide <- comp_asdrs_byas %>%
  select(-as_are, -as_re) %>%
  pivot_wider(names_from=method, values_from=as_mse)  %>%
  mutate(n.minus.s = Network - Sibling)

# difference in ARE (network - sibling)
comp_rel_asdrs_byas_wide <- comp_asdrs_byas %>%
  select(-as_mse, -as_re) %>%
  pivot_wider(names_from=method, values_from=as_are) %>%
  mutate(n.minus.s = Network - Sibling)
```

#### Probabilities

All ests, by geography (probs)

```{r calculate-errs-in-probs-by-geo}
comp_probs_bygeo <- comp_probs %>%
  group_by(method, geo) %>%
  summarize(geo_mse = mean(delta2),
            #geo_are = sum(abs(delta_rel))) 
            # this should be the mean, right?
            geo_are = mean(abs(delta_rel))) 

comp_probs_bygeo_boot <- comp_probs_boot %>%
  group_by(method, geo, boot_idx) %>%
  summarize(geo_mse = mean(delta2),
            #geo_are = sum(abs(delta_rel))) 
            # this should be the mean, right?
            geo_are = mean(abs(delta_rel))) 

# difference in MSE (network - sibling)
comp_probs_bygeo_wide <- comp_probs_bygeo %>%
  select(-geo_are) %>%
  pivot_wider(names_from=method, values_from=geo_mse)  %>%
  mutate(n.minus.s = Network - Sibling)

comp_probs_bygeo_wide_boot <- comp_probs_bygeo_boot %>%
  select(-geo_are) %>%
  pivot_wider(names_from=method, values_from=geo_mse)  %>%
  mutate(n.minus.s = Network - Sibling)

# difference in ARE (network - sibling)
comp_rel_probs_bygeo_wide <- comp_probs_bygeo %>%
  select(-geo_mse) %>%
  pivot_wider(names_from=method, values_from=geo_are) %>%
  mutate(n.minus.s = Network - Sibling)

comp_rel_probs_bygeo_wide_boot <- comp_probs_bygeo_boot %>%
  select(-geo_mse) %>%
  pivot_wider(names_from=method, values_from=geo_are) %>%
  mutate(n.minus.s = Network - Sibling)
```


By age/sex/geography (probs)

```{r prob-errs-by-age-sex-geo}
comp_probs_bygeos <- comp_probs %>%
  group_by(method, geo, sex) %>%
  summarize(geo_mse = mean(delta2),
            #geo_are = sum(abs(delta_rel))) 
            # this should be the mean, right?
            geo_are = mean(abs(delta_rel)))  

# difference in MSE (network - sibling)
comp_probs_bygeos_wide <- comp_probs_bygeos %>%
  select(-geo_are) %>%
  pivot_wider(names_from=method, values_from=geo_mse)  %>%
  mutate(n.minus.s = Network - Sibling)

# difference in ARE (network - sibling)
comp_rel_probs_bygeos_wide <- comp_probs_bygeos %>%
  select(-geo_mse) %>%
  pivot_wider(names_from=method, values_from=geo_are) %>%
  mutate(n.minus.s = Network - Sibling)
```

Plot the difference between the two methods against the estimated completeness

```{r comp-errs-vrcompleteness, fig.height=3.5, fig.width=3.5}
## NB: only have completeness at the state level...
if(geo_name == 'city') {

#comp_df <- comp_asdrs_bygeo_wide
comp_df <- comp_rel_asdrs_bygeo_wide

comp_df_withvr <- comp_df %>%
  left_join(ibge_vr_completeness %>%
              select(geo, ibge_est_vrcov = mean_sim_cov_pct))

biggestdiff <- max(abs(comp_df_withvr$n.minus.s))
xrange <- c(-biggestdiff, biggestdiff)

## controls how far out annotations go
annscale <- .6

geo_err_vr_comp <-
  comp_df_withvr %>%
        mutate(geo = fct_reorder(geo, n.minus.s)) %>%
  ggplot(.) +
  geom_text(aes(y=n.minus.s, 
                x=ibge_est_vrcov, 
                label=geo)) +
  #geom_vline(xintercept=0, color='dark grey') +
  #geom_point(aes(y=state_abbrev, x=n.minus.s)) +
  theme_minimal() +
  ylab("Network estimate MARE - Sibling estimate MARE") +
  xlab("Estimated VR completeness") +
  expand_limits(y=xrange) +
  annotate(geom='text', 
           label="<- Network is better ", 
           #x='SE', 
           x=100, 
           y=-biggestdiff*annscale, 
           size=rel(3),
           color='red', 
           angle=90) +
  annotate(geom='text', 
           label="Sibling is better ->", 
           #x='SE', 
           x=100, 
           y=biggestdiff*annscale, 
           size=rel(3),
           color='red', 
           angle=90) +
  theme(axis.title.x=element_text(size=rel(.8))) +
  ## see
  ## https://stackoverflow.com/questions/12409960/ggplot2-annotate-outside-of-plot
  ## for how this helps plot not clip annotations
  coord_cartesian(clip='off') +
  NULL
  

ggsave(filename=file.path(comp_out_dir, "geo_err_summ_vrsens.pdf"),
       plot=geo_err_vr_comp,
       height=3.5,
       width=3.5)
knitr::plot_crop(file.path(comp_out_dir, "geo_err_summ_vrsens.pdf"))

geo_err_vr_comp

}
```


Scatter plot with all death rates

```{r}
method_facet_names <- c('Sibling' = 'Sibling Estimates',
                        'Network' = 'Network Estimates')

asdr_point_scatter_df <- est_asdrs %>%
  left_join(gs_asdrs) %>% 
  mutate(method = dplyr::recode(method, !!!method_facet_names))

cur_range <- range(c(asdr_point_scatter_df$post_mean_asdr,
                     asdr_point_scatter_df$asdr),
                   finite = TRUE)

asdr_point_scatter <- asdr_point_scatter_df %>%
  ggplot(.) +
  theme_bw(base_size=5) +
  geom_abline(intercept=0, slope=1) +
  #geom_pointrange(aes(x=asdr, 
  geom_point(aes(x=asdr, 
                      y=post_mean_asdr, 
                      #ymin=post_ci_low_asdr,
                      #ymax=post_ci_high_asdr,
                      color=agegp10,
                      shape=sex),
                  alpha=.5) +
                  #size=rel(rel.point.size),
                  #stroke=point.stroke) +
  xlim(cur_range) + ylim(cur_range) +
  scale_x_log10() + 
  scale_y_log10() +
  facet_grid(~ method) +
  ylab("log(Estimated age-specific death rate)") +
  xlab("log(VR age-specific death rate)") +
  guides(color=guide_legend(title='Age', override.aes=list(alpha=1)),
         shape=guide_legend(title='', override.aes=list(alpha=1))) +
  coord_equal() +
  age_scale_color +
  NULL

# NB: this is used in paper
ggsave(filename=file.path(comp_out_dir, "asdr_point_scatter_log.pdf"),
       plot=asdr_point_scatter,
       height=4,
       width=6)
saveRDS(asdr_point_scatter, 
        file.path(comp_out_dir, "asdr_point_scatter_log.rds"))

asdr_point_scatter
```

Make a plot that has a matrix of VR/Sibling/Network

```{r splom-sib-net-vr}
direct_comp_all_asdrs_df <- 
  est_asdrs %>%
    bind_rows(gs_asdrs %>% rename(post_mean_asdr=asdr) %>% mutate(method='VR')) %>%
    select(-time.period) %>%
    tidyr::pivot_wider(id_cols=c('sex', 'agegp10', 'geo'),
                       values_from=c('post_mean_asdr'),
                       names_from=c('method')) 

cur_range <- with(direct_comp_all_asdrs_df,
                  range(log(Sibling),
                        log(Network),
                        log(VR),
                        finite=TRUE))


alpha.val <- 0.6

splom_sn <- direct_comp_all_asdrs_df %>%
  ggplot(.) +
  geom_abline(intercept=0, slope=1) +
  geom_point(aes(x=log(Sibling), 
                 y=log(Network),
                 color=agegp10,
                 shape=sex), 
             alpha=alpha.val) +
  coord_equal() +
  xlim(cur_range) + ylim(cur_range) +
  guides(color=guide_legend(override.aes=list(alpha=1),
                            title='Age'),
         shape=guide_legend(override.aes=list(alpha=1),
                            title='')) +
  xlab("log(Sibling death rate est.)") +
  ylab("log(Network death rate est.)") +
  ggtitle("A") +
  age_scale_color +
  theme_bw() 


splom_vn <- direct_comp_all_asdrs_df %>%
  ggplot(.) +
  geom_abline(intercept=0, slope=1) +
  geom_point(aes(x=log(VR), 
                 y=log(Network),
                 color=agegp10,
                 shape=sex), 
             alpha=alpha.val) +
  coord_equal() +
  xlim(cur_range) + ylim(cur_range) +
  guides(color=guide_legend(override.aes=list(alpha=1),
                            title='Age'),
         shape=guide_legend(override.aes=list(alpha=1),
                            title='')) +
  ylab("log(Network death rate est.)") +
  xlab("log(VR death rate)") +
  ggtitle("B") +
  age_scale_color +
  theme_bw() 

splom_vs <- direct_comp_all_asdrs_df %>%
  ggplot(.) +
  geom_abline(intercept=0, slope=1) +
  geom_point(aes(x=log(VR), 
                 y=log(Sibling),
                 color=agegp10,
                 shape=sex), 
             alpha=alpha.val) +
  coord_equal() +
  xlim(cur_range) + ylim(cur_range) +
  guides(color=guide_legend(override.aes=list(alpha=1),
                            title='Age'),
         shape=guide_legend(override.aes=list(alpha=1),
                            title='')) +
  ylab("log(Sibling death rate est.)") +
  xlab("log(VR death rate)") +
  ggtitle("C") +
  age_scale_color +
  theme_bw() 


splom_all <- splom_sn + 
             splom_vn +
             guide_area() +
             splom_vs + 
  plot_layout(guides='collect', nrow=2, byrow=TRUE)

meta_layout <- "
#cccddd
aeeefff
aeeefff
bggghhh
bggghhh
"

row1_title <- ggplot() + annotate(geom='text', 
                                  x=1,y=1, 
                                  label='bold(underline(Network))', 
                                  angle=90,
                                  parse=TRUE) +  theme_void()
row2_title <- ggplot() + annotate(geom='text', 
                                  x=1,y=1, 
                                  label='bold(underline(Sibling))', 
                                  angle=90,
                                  parse=TRUE) + theme_void()
col1_title <- ggplot() + annotate(geom='text', 
                                  x=1,y=1, 
                                  label='bold(underline(Sibling))',
                                  parse=TRUE) + theme_void()
col2_title <- ggplot() + annotate(geom='text', 
                                  x=1,y=1, 
                                  label='bold(underline(VR))',
                                  parse=TRUE) + theme_void()

plotlist <- list(a=row1_title,
                 b=row2_title,
                 c=col1_title,
                 d=col2_title,
                 e=splom_sn,
                 f=splom_vn,
                 g=guide_area(),
                 h=splom_vs)
  
final_splom <- wrap_plots(
     plotlist,
     guides='collect',
     design=meta_layout,
     widths=c(2,10,10)) & 
  theme(legend.box='horizontal')
  #theme(legend.box='horizontal', legend.position='bottom')

fig_height <-7 
fig_width <- fig_height

saveRDS(final_splom, file.path(comp_out_dir, "splom_asdr.rds"))
ggsave(filename=file.path(comp_out_dir, "splom_asdr.pdf"),
       plot=final_splom,
       height=fig_height,
       width=fig_width)
ggsave(filename=file.path(comp_out_dir, "splom_asdr.png"),
       plot=final_splom,
       height=fig_height,
       width=fig_width)
final_splom

```

Version w/ CI

```{r}
asdr_point_scatter_df <- est_asdrs %>%
  left_join(gs_asdrs) %>% 
  mutate(method = dplyr::recode(method, !!!method_facet_names))

#cur_range <- range(c(asdr_point_scatter_df$post_ci_low_asdr,
#                     asdr_point_scatter_df$post_ci_high_asdr,
#                     asdr_point_scatter_df$asdr),
#                   finite = TRUE)
cur_range <- range(c(asdr_point_scatter_df$post_mean_asdr,
                     asdr_point_scatter_df$asdr),
                   finite = TRUE)

asdr_pointrange_scatter <- asdr_point_scatter_df %>%
  ggplot(.) +
  theme_bw(base_size=5) +
  geom_abline(intercept=0, slope=1) +
  geom_pointrange(aes(x=asdr, 
                      y=post_mean_asdr, 
                      ymin=post_ci_low_asdr,
                      ymax=post_ci_high_asdr,
                      color=agegp10,
                      shape=sex),
                  alpha=.25) +
  xlim(cur_range) + ylim(cur_range) +
  scale_x_log10() + scale_y_log10() +
  facet_grid(~ method) +
  ylab("log(Estimated age-specific death rate)") +
  xlab("log(VR age-specific death rate)") +
  guides(color=guide_legend(title='Age', override.aes=list(alpha=1)),
         shape=guide_legend(title='', override.aes=list(alpha=1))) +
  coord_equal() +
  age_scale_color +
  NULL

# NB: this is used in paper
ggsave(filename=file.path(comp_out_dir, "asdr_pointrange_scatter_log.pdf"),
       plot=asdr_pointrange_scatter,
       height=4,
       width=4)
ggsave(filename=file.path(comp_out_dir, "asdr_pointrange_scatter_log.png"),
       plot=asdr_pointrange_scatter,
       height=4,
       width=4)


saveRDS(asdr_pointrange_scatter, 
        file.path(comp_out_dir, "asdr_pointrange_scatter_log.rds"))

asdr_pointrange_scatter
```

CI width for age-specific death rates

```{r}
est_asdrs_ci_width <- est_asdrs %>%
  mutate(ci_width = post_ci_high_asdr - post_ci_low_asdr,
         rel_ci_width = ci_width / post_mean_asdr) %>%
  select(method, geo, agegp10, sex, ci_width, rel_ci_width) %>%
  pivot_wider(values_from = c('ci_width', 'rel_ci_width'),
              names_from = 'method',
              names_glue = "{.value}_{tolower(method)}") %>%
  # don't count cases w/ 0 deaths
  filter(ci_width_sibling != 0, ci_width_network != 0) %>%
  mutate(sib_over_net_ci_width = ci_width_sibling / ci_width_network,
         sib_over_net_rel_ci_width = rel_ci_width_sibling / rel_ci_width_network)

asdr_ci_width_plot <- ggplot(est_asdrs_ci_width) +
  geom_histogram(aes(x=sib_over_net_ci_width), binwidth=.5,boundary=0) +
  geom_vline(aes(xintercept=1), color='red', linetype='dotted') +
  theme_minimal() +
  xlab("Width(Sibling CI) / Width(Network CI)") +
  ylab("Number of estimated death rates")

ggsave(filename=file.path(comp_out_dir, "asdr_ci_width.pdf"),
       plot=asdr_ci_width_plot,
       height=4,
       width=4)
ggsave(filename=file.path(comp_out_dir, "asdr_ci_width.png"),
       plot=asdr_ci_width_plot,
       height=4,
       width=4)

## NB: this is used
saveRDS(asdr_ci_width_plot, 
        file.path(comp_out_dir, "asdr_ci_width.rds"))

ci_pct_over_1_asdr <- 100*mean(est_asdrs_ci_width$sib_over_net_ci_width > 1)
ci_ratio_asdr <- mean(est_asdrs_ci_width$sib_over_net_ci_width)

cat(glue::glue("
               {round(ci_pct_over_1_asdr)} percent of estimated ASDRs have bigger CI for sibling than for network
               On average, CI are about {round(ci_ratio_asdr,1)} times wider for the sibling method. 
               "))

asdr_ci_width_plot
```


# Direct comparison - probs


Scatter plot with the probs

```{r}
direct_comp_est_probs <- 
  est_probs %>%
    select(-time.period) %>%
    tidyr::pivot_wider(id_cols=c('sex', 'geo'),
                       values_from=c('post_mean_q'),
                       names_from=c('method')) 

cur_range <- range(log(direct_comp_est_probs$Network),
                   log(direct_comp_est_probs$Sibling),
                   finite=TRUE)

```


```{r}
method_facet_names <- c('Sibling' = 'Sibling Estimates',
                        'Network' = 'Network Estimates')

prob_point_scatter_df <- est_probs %>%
  left_join(gs_probs %>% select(geo, sex, q.47.18)) %>% 
  mutate(method = dplyr::recode(method, !!!method_facet_names))

cur_range <- range(c(prob_point_scatter_df$post_mean_q,
                     prob_point_scatter_df$q.47.18),
                   finite = TRUE)

prob_point_scatter <- prob_point_scatter_df %>%
  ggplot(.) +
  theme_bw(base_size=5) +
  geom_abline(intercept=0, slope=1) +
  geom_point(aes(x=q.47.18, 
                 y=post_mean_q, 
                 shape=sex),
                 alpha=.5) +
  coord_equal() +
  xlim(cur_range) + ylim(cur_range) +
  facet_grid(~ method) +
  ylab("Estimated probability of adult death") +
  xlab("VR probability of adult death") +
  guides(shape=guide_legend(title='', override.aes=list(alpha=1))) +
  NULL

# NB: this is used in paper
ggsave(filename=file.path(comp_out_dir, "prob_point_scatter.pdf"),
       plot=prob_point_scatter,
       height=4,
       width=6)
saveRDS(prob_point_scatter, 
        file.path(comp_out_dir, "prob_point_scatter.rds"))

prob_point_scatter
```


```{r}
method_facet_names <- c('Sibling' = 'Sibling Estimates',
                        'Network' = 'Network Estimates')

prob_pointrange_scatter_df <- est_probs %>%
  left_join(gs_probs %>% select(geo, sex, q.47.18)) %>% 
  mutate(method = dplyr::recode(method, !!!method_facet_names))

cur_range <- range(c(prob_pointrange_scatter_df$post_ci_low_q,
                     prob_pointrange_scatter_df$post_ci_high_q,
                     prob_pointrange_scatter_df$q.47.18),
                   finite = TRUE)

prob_pointrange_scatter <- prob_pointrange_scatter_df %>%
  ggplot(.) +
  theme_bw(base_size=5) +
  geom_abline(intercept=0, slope=1) +
  geom_pointrange(aes(x=q.47.18, 
                      y=post_mean_q, 
                      ymin=post_ci_low_q,
                      ymax=post_ci_high_q,
                      shape=sex),
                      alpha=.5) +
  coord_equal() +
  xlim(cur_range) + ylim(cur_range) +
  facet_grid(~ method) +
  ylab("Estimated probability of adult death") +
  xlab("VR probability of adult death") +
  guides(shape=guide_legend(title='', override.aes=list(alpha=1))) +
  NULL

# NB: this is used in paper
ggsave(filename=file.path(comp_out_dir, "prob_pointrange_scatter.pdf"),
       plot=prob_pointrange_scatter,
       height=4,
       width=6)
saveRDS(prob_pointrange_scatter, 
        file.path(comp_out_dir, "prob_pointrange_scatter.rds"))

prob_pointrange_scatter
```


### minimum detectable effects

```{r}
##
## se - standard error for difference in two means
mde_onesided <- function(se, alpha=.05, beta=.2) {
  return(se * (qnorm(1-(alpha/2)) - qnorm(beta)))  
}

mde_asdrs <- est_asdrs %>% 
  group_by(method, agegp10, sex, time.period) %>% 
  summarize(mean_se = mean(post_sd_asdr), 
            mean_asdr=mean(post_mean_asdr)) %>% 
  mutate(cv_asdr = mean_se/mean_asdr, 
         ## NB: if two estimates both have std err sigma and are independent
         ##     then their difference will have std err sqrt(2)*sigma
         mde = mde_onesided((sqrt(2)*mean_se))) %>%
  mutate(rel_mde = mde / mean_asdr)

mde_probs <- est_probs %>% 
  group_by(method, sex, time.period) %>% 
  summarize(mean_se = mean(post_sd_q), 
            mean_prob = mean(post_mean_q)) %>% 
  mutate(cv_prob = mean_se/mean_prob, 
         ## NB: if two estimates both have std err sigma and are independent
         ##     then their difference will have std err sqrt(2)*sigma
         mde = mde_onesided(sqrt(2)*(mean_se))) %>%
  mutate(rel_mde = mde / mean_prob)

mde_asdrs
mde_probs
```


### CI width for probabilities

CI width for probabilities 

```{r}
est_probs_ci_width <- est_probs %>%
  mutate(ci_width = post_ci_high_q - post_ci_low_q,
         rel_ci_width = ci_width / post_mean_q) %>%
  select(method, geo, sex, ci_width, rel_ci_width) %>%
  pivot_wider(values_from = c('ci_width', 'rel_ci_width'),
              names_from = 'method',
              names_glue = "{.value}_{tolower(method)}") %>%
  # don't count cases w/ 0 deaths
  filter(ci_width_sibling != 0, ci_width_network != 0) %>%
  mutate(sib_over_net_ci_width = ci_width_sibling / ci_width_network,
         sib_over_net_rel_ci_width = rel_ci_width_sibling / rel_ci_width_network)

prob_ci_width_plot <- ggplot(est_probs_ci_width) +
  geom_histogram(aes(x=sib_over_net_ci_width), binwidth=.5,boundary=0) +
  geom_vline(aes(xintercept=1), color='red', linetype='dotted') +
  theme_minimal() +
  xlab("Width(Sibling CI) / Width(Network CI)") +
  ylab("Number of estimated probabilities of death")

ggsave(filename=file.path(comp_out_dir, "prob_ci_width.pdf"),
       plot=prob_ci_width_plot,
       height=4,
       width=4)
ggsave(filename=file.path(comp_out_dir, "prob_ci_width.png"),
       plot=prob_ci_width_plot,
       height=4,
       width=4)

## NB: this is used
saveRDS(prob_ci_width_plot, 
        file.path(comp_out_dir, "prob_ci_width.rds"))

ci_pct_over_1_prob <- 100*mean(est_probs_ci_width$sib_over_net_ci_width > 1)
ci_ratio_prob <- mean(est_probs_ci_width$sib_over_net_ci_width)

cat(glue::glue("
               {round(ci_pct_over_1_prob)} percent of estimated probabilities have bigger CI for sibling than for network
               On average, CI are about {round(ci_ratio_prob,1)} times wider for the sibling method. 
               "))


prob_ci_width_plot
```

Save a dataframe with the CI properties

```{r}
# NB: this is used

all_ci_widths <-
  bind_rows(est_asdrs_ci_width %>% 
              mutate(qoi = 'asdr'),
            est_probs_ci_width %>% 
              mutate(qoi = 'prob')) %>%
  group_by(qoi) %>%
  summarize(mean_ci_width_sibling = mean(ci_width_sibling),
            mean_ci_width_network = mean(ci_width_network),
            avg_sibci_over_netci = mean(sib_over_net_ci_width),
            pct_over_1 = 100*mean(sib_over_net_ci_width > 1),
            # same quantities for relative CI
            mean_rel_ci_width_sibling = mean(rel_ci_width_sibling),
            mean_rel_ci_width_network = mean(rel_ci_width_network),
            avg_rel_sibci_over_netci = mean(sib_over_net_rel_ci_width),
            pct_rel_over_1 = 100*mean(sib_over_net_rel_ci_width > 1))

saveRDS(all_ci_widths,
        file=file.path(comp_out_dir, "ci_width.rds"))

all_ci_widths
```


Error distn for file

```{r}
mse_diff_hist <- comp_asdrs_wide_boot %>%
  group_by(boot_idx) %>%
  summarize(mean.delta2.n.minus.s = mean(delta2.n.minus.s),
            mean.delta2.n = mean(delta2_Network),
            mean.delta2.s = mean(delta2_Sibling))

errs_boot_asdr_mse <- mse_diff_hist  %>% 
  rename(err.n.minus.s = mean.delta2.n.minus.s,
         err.n = mean.delta2.n,
         err.s = mean.delta2.s) %>%
  bind_cols(loss = 'mse',
            qty = 'asdr',
            comparison_name = params$comparison_name,
            geo_name = params$geo_name)

mse_diff_probs_hist <- comp_probs_wide_boot %>%
  group_by(boot_idx) %>%
  summarize(mean.delta2.n.minus.s = mean(delta2.n.minus.s),
            mean.delta2.n = mean(delta2_Network),
            mean.delta2.s = mean(delta2_Sibling))

errs_boot_probs_mse <- mse_diff_probs_hist  %>% 
  rename(err.n.minus.s = mean.delta2.n.minus.s,
         err.n = mean.delta2.n,
         err.s = mean.delta2.s) %>%
  bind_cols(loss = 'mse',
            qty = 'prob',
            comparison_name = params$comparison_name,
            geo_name = params$geo_name)

rel_diff_hist <- comp_asdrs_wide_boot %>%
  group_by(boot_idx) %>%
  summarize(mean.err = mean(delta_rel.n.minus.s),
            mean.net.err = mean(delta_rel_Network),
            mean.sib.err = mean(delta_rel_Sibling))
  
errs_boot_asdr_mare <- rel_diff_hist  %>% 
  rename(err.n.minus.s = mean.err,
         err.n = mean.net.err,
         err.s = mean.sib.err) %>%
  bind_cols(loss = 'mare',
            qty = 'asdr',
            comparison_name = params$comparison_name,
            geo_name = params$geo_name)

rel_diff_prob_hist <- comp_probs_wide_boot %>%
  group_by(boot_idx) %>%
  summarize(mean.err = mean(delta_rel.n.minus.s),
            mean.err.n = mean(delta_rel_Network),
            mean.err.s = mean(delta_rel_Sibling))
  

errs_boot_probs_mare <- rel_diff_prob_hist  %>% 
  rename(err.n.minus.s = mean.err,
         err.n = mean.err.n,
         err.s = mean.err.s) %>%
  bind_cols(loss = 'mare',
            qty = 'prob',
            comparison_name = params$comparison_name,
            geo_name = params$geo_name)
```


```{r}
# convert MSE results to RMSE
errs_boot_asdr_rmse <- errs_boot_asdr_mse %>% 
  mutate(err.n = sqrt(err.n),
         err.s = sqrt(err.s),
         err.n.minus.s = err.n - err.s,
         loss = 'rmse')
errs_boot_probs_rmse <- errs_boot_probs_mse %>% 
  mutate(err.n = sqrt(err.n),
         err.s = sqrt(err.s),
         err.n.minus.s = err.n - err.s,
         loss = 'rmse')

errs_boot_both_rmse <-
  bind_rows(errs_boot_asdr_rmse,
            errs_boot_probs_rmse)

err_diffs_boot <- bind_rows(errs_boot_asdr_mare, 
                            errs_boot_asdr_mse, 
                            errs_boot_probs_mare, 
                            errs_boot_probs_mse)

# NB: this file is used
write_csv(bind_rows(err_diffs_boot,
                    errs_boot_both_rmse),
          file.path(comp_out_dir, "err_diffs_boot.csv"))

err_diffs_boot
```

# Correlations between different sets of estimates

Summarize relationship between sibling and network probability of death estimates with correlation matrix


```{r}
direct_comp_all_probs_df <- 
  est_probs %>%
    bind_rows(gs_probs %>% rename(post_mean_q = q.47.18) %>% mutate(method='VR')) %>%
    select(-time.period) %>%
    tidyr::pivot_wider(id_cols=c('sex', 'geo'),
                       values_from=c('post_mean_q'),
                       names_from=c('method')) 

cat("\n\nCorrelation between probabilities, not on log scale\n")
# not on log scale
print(
  cor(direct_comp_all_probs_df %>% 
           select(Sibling, Network, VR))
)
```

Summarize relationship between sibling and network death rate estimates with correlation matrix


```{r}

cat("\n\nCorrelation between ASDRs, not on log scale\n")
# not on log scale
print(
  cor(direct_comp_all_asdrs_df %>% 
                select(Sibling, Network, VR))
  )
cat("\n\n")

cat("\n\nCorrelation between log(ASDR)s, log(0) mapped to tiny value:\n")
# log scale, replace log(0) with log(1e-8)
print(cor(direct_comp_all_asdrs_df %>% 
      select(Sibling, Network, VR) %>% 
      mutate(across(everything(),log)) %>%
      mutate(Sibling = ifelse(! is.finite(Sibling), log(1e-8), Sibling))))
cat("\n\n")

cat("\n\nCorrelation between log(ASDR)s, dropping rows where sibling estimates are 0\n")
# log scale, drop rows where sibling ests are 0
print(cor(
  direct_comp_all_asdrs_df %>% 
      select(Sibling, Network, VR) %>% 
      mutate(across(everything(),log)) %>%
      filter(if_all(everything(), ~ is.finite(.x)))
    ))
```

Method-specific errors in ASDR estimates across age groups, aggregating over cities

NOTE: the bars here are the first and third quartile of cities (so the length is inter-quartile range);
these are not 95% CI

```{r err-within-method-by-age}
err_within_method_byage <- 
  comp_asdrs %>%
  group_by(method, sex, agegp10) %>%
  summarize(delta_rel_mean = mean(delta_rel),
            delta_rel_ci_low = quantile(delta_rel, .25),
            delta_rel_ci_high = quantile(delta_rel, .75),
            delta_mean = mean(delta),
            delta_ci_low = quantile(delta, .25),
            delta_ci_high = quantile(delta, .75),
            .groups='drop')

err_within_method_byage_plot <- 
err_within_method_byage %>%
  ggplot(.) +
  #geom_point(aes(x=agegp10,
  geom_pointrange(aes(x=agegp10,
                      y=delta_mean,
                      ymin = delta_ci_low,
                      ymax = delta_ci_high,
                      color = method,
                      shape = sex),
                  position=position_dodge(width=.5)) +
  theme_minimal() +
  ylab("Average error\nin estimated death rate") +
  xlab("") +
  labs(caption="NB: Bars show estimated inter-quartile range across the cities")

# NB: this is used
ggsave(filename=file.path(comp_out_dir, "asdr_err_within_method_byage.pdf"),
       plot=err_within_method_byage_plot)
```

### CI covereage

How many estimates have no CI?

```{r}
comp_asdrs %>%
  mutate(zero_ci = as.numeric(post_sd_asdr==0)) %>%
  group_by(method, sex, zero_ci) %>%
  summarize(count=n()) %>%
  pivot_wider(names_from=c(method,sex), values_from=count)
```

Note that this is CI coverage with zero estimates removed -- in other words, when the sibling
method produces a point estimate of 0, we don't include it in this summary

```{r coverage-table}
comp_ci_coverage_asdr <- 
  comp_asdrs %>%
    mutate(zero_ci = as.numeric(post_sd_asdr==0)) %>%
    # if no CI b/c zero reported deaths, count as not covered
    mutate(ci_covered = ifelse(zero_ci, 0, ci_covered)) %>%
    group_by(method, sex) %>%
    summarize(empirical_ci_coverage = mean(ci_covered),
              # this version doesn't count zero cis
              empirical_ci_coverage_ignorezero = sum((1-zero_ci) * ci_covered) / sum(1-zero_ci)) %>%
    mutate(qty = 'asdr')

comp_ci_coverage_probs <- 
  comp_probs %>%
    mutate(zero_ci = as.numeric(post_sd_q==0)) %>%
    # if no CI b/c zero reported deaths, count as not covered
    mutate(ci_covered = ifelse(zero_ci, 0, ci_covered)) %>%
    group_by(method, sex) %>%
    summarize(empirical_ci_coverage = mean(ci_covered),
              # this version doesn't count zero cis
              empirical_ci_coverage_ignorezero = sum((1-zero_ci) * ci_covered) / sum(1-zero_ci)) %>%
    mutate(qty = 'prob')

comp_ci_coverage <- bind_rows(comp_ci_coverage_asdr,
                              comp_ci_coverage_probs) %>%
                    mutate(geo = params$geo,
                           comparison_name = params$comparison_name) 

## NB: this is used

saveRDS(comp_ci_coverage,
        file.path(comp_out_dir, "comp_ci_coverage.rds"))
```

# National analysis ends here

```{r}
if(geo_name == 'national') {
  toc()
  knitr::knit_exit()
}
```



## Bias-Variance Decomposition

Check bias-variance decomposition w/in city/age/sex group:
MSE = bias^2 + var

```{r}
fp.var <- function(x) {
  return(mean((x - mean(x))^2))
}

bvd_check <- comp_asdrs_boot %>%
  group_by(geo, sex, agegp10, method) %>%
  summarize(estimand = mean(post_mean_asdr),
            gs = mean(gs_asdr),
            mse = mean((post_mean_asdr - gs_asdr)^2),
            # NB: the mse var in comp_asdrs_boot is based on delta = (est - truth)*1000
            #mse = mean(delta2/(1000^2)),
            bias = mean(post_mean_asdr - gs_asdr),
            var = var(post_mean_asdr)) %>%
            #var = fp.var(post_mean_asdr)) %>%
            #var = mean((post_mean_asdr - estimand)^2)) %>%
  mutate(check = mse - (bias^2 + var))

bvd_check %>%
  ggplot(.) +
  geom_abline(intercept=0, slope=1, color='grey') +
  geom_point(aes(x = bias^2 + var,
                 y = mse)) +
  theme_minimal() +
  coord_equal()

bvd_check
```
```{r}
bvd_check_long <- bvd_check %>%
  pivot_longer(cols=c('mse', 'bias', 'var')) %>%
  select(-estimand, -check) %>%
  rename(qty = name) %>%
  pivot_wider(names_from = c('method'),
              values_from = 'value')

bvd_check_long
```

Aggregate up to age/sex groups (across cities)

```{r}
bvd_as_rmse_plot <- bvd_check_long %>%
  #filter(qty %in% c('bias', 'var')) %>%
  filter(qty == 'mse') %>%
  group_by(sex, agegp10) %>%
  # we take the average of the MSE; when we plot,
  # we'll take the square root to make it a little more interpretable - but
  # the quantity being averaged is the MS E
  summarize(Network = mean(Network),
            Sibling=mean(Sibling)) %>%
  ggplot(.) +
  geom_abline(intercept=0, slope=1, color='grey', lty=2) +
  geom_point(aes(x=sqrt(Network), y=sqrt(Sibling), color=agegp10, shape=sex)) +
  guides(color=guide_legend(override.aes=list(alpha=1),
                            title='Age'),
         shape=guide_legend(override.aes=list(alpha=1),
                            title='')) +
  #xlab("Network variance") + ylab("Sibling variance") +
  xlab("Square root of\nNetwork average MSE") +
  ylab("Square root of\nSibling average MSE") +
  expand_limits(x=0, y=0) +
  #coord_equal() +
  tune::coord_obs_pred() +
  age_scale_color +
  theme_minimal() 


# NB: this one is used
saveRDS(bvd_as_rmse_plot, file.path(comp_out_dir, "bvd_as_rmse_plot.rds"))
ggsave(file.path(comp_out_dir, "bvd_as_rmse.pdf"),
       bvd_as_rmse_plot,
       width=5, height=4)

bvd_as_rmse_plot
```

Sqrt of the variance

```{r}
bvd_as_se_plot <- bvd_check_long %>%
  #filter(qty %in% c('bias', 'var')) %>%
  filter(qty == 'var') %>%
  group_by(sex, agegp10) %>%
  ## we average the variance across cities,
  ## then we take the square root to make it easier to read
  ## but the quantity being averaged is the variance
  summarize(Network = mean(Network),
            Sibling=mean(Sibling)) %>%
  ggplot(.) +
  geom_abline(intercept=0, slope=1, color='grey', lty=2) +
  geom_point(aes(x=sqrt(Network), y=sqrt(Sibling), color=agegp10, shape=sex)) +
  guides(color=guide_legend(override.aes=list(alpha=1),
                            title='Age'),
         shape=guide_legend(override.aes=list(alpha=1),
                            title='')) +
  #xlab("Network variance") + ylab("Sibling variance") +
  #xlab(TeX(r'(Network average $\sqrt{var}$)')) + 
  #ylab(TeX(r'(Sibling average $\sqrt{var}$)')) + 
  xlab("Square root of\nNetwork average variance") +
  ylab("Square root of\nSibling average variance") +
  #coord_equal() +
  tune::coord_obs_pred() +
  theme_minimal() +
  age_scale_color +
  expand_limits(x = 0, y = 0)

# NB: this one is used
saveRDS(bvd_as_se_plot, file.path(comp_out_dir, "bvd_as_se_plot.rds"))
ggsave(file.path(comp_out_dir, "bvd_as_se.pdf"),
       bvd_as_se_plot,
       width=5, height=4)

bvd_as_se_plot
```

Bias

```{r}
bvd_as_bias_plot <- bvd_check_long %>%
  #filter(qty %in% c('bias', 'var')) %>%
  filter(qty == 'bias') %>%
  group_by(sex, agegp10) %>%
  summarize(Network = mean(Network),
            Sibling=mean(Sibling)) %>%
  ggplot(.) +
  #geom_abline(intercept=0, slope=1, color='grey', linetype=2) +
  geom_vline(xintercept=0, color='grey') +
  geom_hline(yintercept=0, color='grey') +
  geom_point(aes(x=Network, y=Sibling, color=agegp10, shape=sex)) +
  guides(color=guide_legend(override.aes=list(alpha=1),
                            title='Age'),
         shape=guide_legend(override.aes=list(alpha=1),
                            title='')) +
  xlab("Network bias") + ylab("Sibling bias") +
  #coord_equal() +
  tune::coord_obs_pred() +
  lemon::scale_y_symmetric(mid=0) +
  lemon::scale_x_symmetric(mid=0) +
  age_scale_color +
  theme_minimal() 

# NB: this one is used
saveRDS(bvd_as_bias_plot, file.path(comp_out_dir, "bvd_as_bias_plot.rds"))

ggsave(file.path(comp_out_dir, "bvd_as_bias.pdf"),
       bvd_as_bias_plot,
       width=5, height=4)

bvd_as_bias_plot
```

Count number of age/sex groups for which magnitude of net bias is bigger
than magnitude of sibling bias

```{r}
check_ns_mag_bias <- bvd_check_long %>%
  #filter(qty %in% c('bias', 'var')) %>%
  filter(qty == 'bias') %>%
  group_by(sex, agegp10) %>%
  summarize(Network = mean(Network),
            Sibling=mean(Sibling)) %>%
  mutate(net_bias_mag_bigger = as.numeric(abs(Network) > abs(Sibling)))

glue::glue("
           The bias of the network method is bigger in magnitude for
           {sum(check_ns_mag_bias$net_bias_mag_bigger)} out of {nrow(check_ns_mag_bias)} age-sex groups
           ")

check_ns_mag_bias
```

# Maps

```{r}
city.dat <- read_csv(file.path(data_dir, "cities.csv"))

# join in city names for titles
state.city.map <- city.dat %>% select(state_abbrev, region, state_name, city_name=municipio)
state.city.map <- state.city.map %>%
  mutate(title = paste0(city_name, " (", state_abbrev, ")")) %>%
  mutate(geo = state_abbrev)
  #mutate(title = paste0(city_name, ",\n", state_name))

#br_customgrid <- br_grid1 %>% 
br_customgrid <- br_states_grid1 %>% 
  select(-name) %>%
  left_join(state.city.map %>% select(code=state_abbrev, name=title))
```

## Hexgrid maps

Helper fn 

```{r city-method-mare-map, fig.height=4.5, fig.width=3}
  
comp_df <- comp_rel_asdrs_bygeo_wide
  
##
## data - dataset to use, already filtered (so either males or females)
##        needs a column called 'geo'
## qoivar - the value to plot
## name - the label for the qoi
br_compare_choro_map <- function(data, qoivar, name, 
                                 title=NULL, 
                                 labels=TRUE, 
                                 fillscale=NULL,
                                 logfill=FALSE,
                                 hex=TRUE) {
    
  mapobj <- readRDS(file.path(out_dir, "brazil_map.rds"))
  
  # should we plot a hex map? or a political map?
  if(hex) {
    # hexmap
    if(geo_name == 'region') {
      basemap <- mapobj$hexmap_region
    } else {
      basemap <- mapobj$hexmap
    }
    # political map
  } else {
    basemap <- mapobj$map
  }
  
  if(geo_name == 'city') {
    mapraw <- basemap %>%
      mutate(geo = postal) 
  } else {
    mapraw <- basemap %>%
      mutate(geo = region) 
  }
  
  mapdat <- mapraw %>%
    left_join(data %>% rename(qoi = qoivar))
  
  capdat <- mapobj$capitals
  
  if(is.null(fillscale)) {
    # default fill scale
    plot_fill_scale <- scale_fill_distiller(name=name, type='div')
  } else {
    plot_fill_scale <- fillscale
  }
  
  if (logfill) {
    plot_fill_scale <- plot_fill_scale + scale_color_continuous(trans=log10)
  }
  

  # for removing the background from ggplots
  remove_background <- theme(panel.background = element_blank(),
            panel.border = element_blank(),
            panel.grid.major = element_blank(),
            axis.ticks.x = element_blank(),
            axis.text.x = element_blank(),
            axis.ticks.y = element_blank(),
            axis.text.y = element_blank()) 
  
  cur_map <- 
    ggplot(data=mapdat) + 
      theme_bw(base_size=5) +
      geom_sf(aes(fill=qoi), 
              linetype='dotted', 
              alpha=.8) +
    plot_fill_scale +
    #log_scale_fill +
    remove_background  +
    xlab('') + ylab('') +
    theme(legend.position=c(.2,.3),
          legend.direction='vertical',
          legend.text=element_text(size=8),
          legend.title=element_text(size=8, face='bold')) +
    NULL
  
  if(labels) {
    cur_map <- cur_map +
      geom_sf(data=capdat) +
      geom_text_repel(data=capdat,
                      aes(x=lon, y=lat, 
                          label=glue::glue("{municipio} ({state_abbrev})")),
                      size=rel(3))
  }
  
  if(! is.null(title)) {
    cur_map <- cur_map + ggtitle(title)
  }
  
  return(cur_map)
}

# see 
# https://github.com/tidyverse/ggplot2/issues/1012
scale_fill_log10 <- function(...) {
  scale_fill_continuous(..., trans = scales::log10_trans())
}

# make maps for each age/sex group and assemble
# them into one figure
br_hexgrid_map <- function(qoivar,
                           qoiname,
                           scale_lims=NULL,
                           fillscale=NULL,
                           logfill=FALSE) {
  
  # TODO 
  if(! is.null(scale_lims)) {
    cur_lims <- scale_lims*1.05 
  } else {
    cur_lims <- NULL
  }
  
  if(logfill) {
    plot_logfill <- scale_fill_log10()
  } else {
    plot_logfill <- NULL
  }
  
  if(! is.null(fillscale)) {
    plot_fillscale <- fillscale
  } else {
    plot_fillscale <- scale_fill_distiller(name=qoiname, 
                                           palette = 'Spectral',
                                           limits=cur_lims,
                                           oob=scales::squish,
                                           type='div') 
  }
  
  maps_indiv <- comp_asdrs_bygeoas %>%
    group_by(sex, method, agegp10) %>%
    group_modify(function(cur_df, key) {
      
      cur_sex <- key$sex[1]
      cur_agegp10 <- key$agegp10[1]
      cur_method <- key$method[1]
      
      cur_map_errs <- br_compare_choro_map(cur_df,
                                           qoivar=qoivar,
                                           title=glue::glue('{cur_method}: {cur_sex}, {cur_agegp10}'),
                                           name=glue::glue('{cur_method} {qoiname}'),
                                           labels=FALSE,
                                           fillscale=plot_fillscale,
                                           hex=TRUE) +
        plot_logfill
      return(tibble(map_errs=list(cur_map_errs)))
      
    })
  
  layout <- "
  AF#KP
  BG#LQ
  CH#MR
  DI#NS
  EJ#OT
  "
  
  ppw <- 4 # plot panel width (relative)
  spw <- 1 # space panel width (relative)
  
  
  maps_array <- maps_indiv %>% 
    pull(map_errs) %>%
    wrap_plots(design=layout,
               widths=c(ppw, ppw, spw, ppw, ppw)) +
    plot_layout(guides='collect') &
    theme(legend.position='bottom',
          legend.direction='horizontal',
          plot.title=element_text(hjust=0.5)) 
  
  
  meta_layout <- "
  ##FF###MM##
  #NNSS#TTUU#
  APPPPPPPPPV
  BPPPPPPPPPW
  CPPPPPPPPPX
  DPPPPPPPPPY
  EPPPPPPPPPZ
  "
  
  final_maps <- wrap_plots(
     A=wrap_elements(grid::textGrob("18-24")), 
     B=wrap_elements(grid::textGrob("25-34")), 
     C=wrap_elements(grid::textGrob("35-44")), 
     D=wrap_elements(grid::textGrob("45-54")), 
     E=wrap_elements(grid::textGrob("55-64")), 
     V=wrap_elements(grid::textGrob("18-24")), 
     W=wrap_elements(grid::textGrob("25-34")), 
     X=wrap_elements(grid::textGrob("35-44")), 
     Y=wrap_elements(grid::textGrob("45-54")), 
     Z=wrap_elements(grid::textGrob("55-64")), 
     F=wrap_elements(grid::textGrob("Female")),
     M=wrap_elements(grid::textGrob("Male")),
     N=wrap_elements(grid::textGrob("Network")),
     T=wrap_elements(grid::textGrob("Network")),
     S=wrap_elements(grid::textGrob("Sibling")),
     U=wrap_elements(grid::textGrob("Sibling")),
     P=maps_array,
     design=meta_layout,
   heights=c(1,1,rep(6,5))) +
   plot_annotation(caption="Values outside of limits squished to limits.")
  
  return(final_maps)
}
```

Plot age/sex MARE for estimates

```{r method_map_as_mare}
method_mare_as_maps <- br_hexgrid_map(qoivar='geo_are',
                                      qoiname='MARE',
                                      scale_lims=c(0,2))
                                     #fillscale=scale_fill_gradient(name='MARE',
                                     #                               #type='div',
                                     #                               #palette='RdBu',
                                     #                               low='black',
                                     #                               high='red',
                                     #                               oob=scales::squish,
                                     #                               limits=c(0,2)))
      
saveRDS(method_mare_as_maps, file.path(comp_out_dir, "method_mare_agesex_map.rds"))
ggsave(filename=file.path(comp_out_dir, "method_mare_agesex_map.pdf"),
       plot=method_mare_as_maps,
       height=10,
       width=8)
ggsave(filename=file.path(comp_out_dir, "method_mare_agesex_map.png"),
       plot=method_mare_as_maps,
       height=10,
       width=8)

method_mare_as_maps
```


Plot age/sex MSE for estimates

```{r method_map_as_mse}
method_mse_as_maps <- br_hexgrid_map(qoivar='geo_mse',
                                     qoiname='MSE',
                                     scale_lims=c(0,50))
      
saveRDS(method_mse_as_maps, file.path(comp_out_dir, "method_mse_agesex_map.rds"))
ggsave(filename=file.path(comp_out_dir, "method_mse_agesex_map.pdf"),
       plot=method_mse_as_maps,
       height=10,
       width=8)
ggsave(filename=file.path(comp_out_dir, "method_mse_agesex_map.png"),
       plot=method_mse_as_maps,
       height=10,
       width=8)

method_mse_as_maps
```



Plot age/sex RMSE for estimates

```{r method_map_as_rmse}
method_rmse_as_maps <- br_hexgrid_map(qoivar='geo_rmse',
                                      qoiname='RMSE',
                                      scale_lims=c(0,10))
      
saveRDS(method_rmse_as_maps, file.path(comp_out_dir, "method_rmse_agesex_map.rds"))
ggsave(filename=file.path(comp_out_dir, "method_rmse_agesex_map.pdf"),
       plot=method_rmse_as_maps,
       height=10,
       width=8)
ggsave(filename=file.path(comp_out_dir, "method_rmse_agesex_map.png"),
       plot=method_rmse_as_maps,
       height=10,
       width=8)

method_rmse_as_maps
```

Plot age/sex RE (not absolute value) for estimates

```{r method_map_as_re}
method_re_as_maps <- br_hexgrid_map(qoivar='geo_re',
                                    qoiname='log(RE)',
                                    logfill=TRUE,
                                    fillscale=scale_fill_distiller(type='div',palette='RdBu'),
                                    #scale_lims=c(0,5))
                                    scale_lims=c(-2,2))
      
saveRDS(method_re_as_maps, file.path(comp_out_dir, "method_re_agesex_map.rds"))
ggsave(filename=file.path(comp_out_dir, "method_re_agesex_map.pdf"),
       plot=method_re_as_maps,
       height=10,
       width=8)

method_re_as_maps
```

Repeat the maps above for age/sex MARE differences

```{r}
#comp_asdrs_bygeoas_wide
#comp_rel_asdrs_bygeoas_wide

as_gps <- expand_grid(agegp10 = unique(comp_asdrs_bygeoas_wide$agegp10),
                      sex = unique(comp_asdrs_bygeoas_wide$sex))

mare_as_maps <- comp_rel_asdrs_bygeoas_wide %>%
  ungroup() %>%
  group_by(agegp10, sex) %>%
  group_map(function(cur_df, key) {
    #cur_sex <- cur_df$sex[1]
    #cur_agegp10 <- cur_df$agegp10[1]
    
    cur_sex <- key$sex[1]
    cur_agegp10 <- key$agegp10[1]
    
    cur_map_mare <- br_compare_choro_map(cur_df,
                                         qoivar='n.minus.s',
                                         title=glue::glue('{cur_sex}, {cur_agegp10}'),
                                         name=glue::glue('Network MARE -\nSibling MARE'),
                                         labels=FALSE)
    
  })

#maxval <- max(abs(range(comp_rel_asdrs_bygeoas_wide$n.minus.s)))
maxval <- 2 

mare_as_maps <- mare_as_maps %>% 
  wrap_plots(mare_as_maps, nrow=5, ncol=2) &
  scale_fill_distiller(name='Network MARE -\nSibling MARE', 
                       limits=c(-maxval, maxval)*1.05,
                       oob=scales::squish,
                       type='div')

mare_as_maps <- mare_as_maps + 
  plot_layout(guides='collect') +
  plot_annotation(caption="Values outside of limits squished to limits.") &
  theme(legend.position='bottom',
        legend.direction='horizontal') 
  
saveRDS(mare_as_maps, file.path(comp_out_dir, "method_compare_mare_agesex_map.rds"))
ggsave(filename=file.path(comp_out_dir, "method_compare_mare_agesex_map.pdf"),
       plot=mare_as_maps,
       height=12,
       width=4)
ggsave(filename=file.path(comp_out_dir, "method_compare_mare_agesex_map.png"),
       plot=mare_as_maps,
       height=12,
       width=4)

mare_as_maps

```

... and for age/sex MSE

```{r}
#comp_asdrs_bygeoas_wide
#comp_rel_asdrs_bygeoas_wide

as_gps <- expand_grid(agegp10 = unique(comp_asdrs_bygeoas_wide$agegp10),
                      sex = unique(comp_asdrs_bygeoas_wide$sex))

mse_as_maps <- comp_asdrs_bygeoas_wide %>%
  ungroup() %>%
  group_by(agegp10, sex) %>%
  group_map(function(cur_df, key) {
    #cur_sex <- cur_df$sex[1]
    #cur_agegp10 <- cur_df$agegp10[1]
    
    cur_sex <- key$sex[1]
    cur_agegp10 <- key$agegp10[1]
    
    cur_map_mare <- br_compare_choro_map(cur_df,
                                         qoivar='n.minus.s',
                                         title=glue::glue('{cur_sex}, {cur_agegp10}'),
                                         name=glue::glue('Network MARE -\nSibling MARE'),
                                         labels=FALSE)
    
  })

#maxval <- max(abs(range(comp_asdrs_bygeoas_wide$n.minus.s)))
maxval <- 50

mse_as_maps <- mse_as_maps %>% 
  wrap_plots(mse_as_maps, nrow=5, ncol=2) &
  scale_fill_distiller(name='Network MSE -\nSibling MSE', 
                       limits=c(-maxval, maxval)*1.05,
                       oob=scales::squish,
                       type='div')

mse_as_maps <- mse_as_maps + 
  plot_layout(guides='collect') +
  plot_annotation(caption="Values outside of limits squished to limits.") &
  theme(legend.position='bottom',
        legend.direction='horizontal') 
  
saveRDS(mse_as_maps, file.path(comp_out_dir, "method_compare_mse_agesex_map.rds"))
ggsave(filename=file.path(comp_out_dir, "method_compare_mse_agesex_map.pdf"),
       plot=mse_as_maps,
       height=12,
       width=4)
ggsave(filename=file.path(comp_out_dir, "method_compare_mse_agesex_map.png"),
       plot=mse_as_maps,
       height=12,
       width=4)

mse_as_maps

```

... and for age/sex RMSE

```{r}
#comp_asdrs_bygeoas_wide
#comp_rel_asdrs_bygeoas_wide

as_gps <- expand_grid(agegp10 = unique(comp_asdrs_bygeoas_wide$agegp10),
                      sex = unique(comp_asdrs_bygeoas_wide$sex))

rmse_as_maps <- comp_rmse_asdrs_bygeoas_wide %>%
  ungroup() %>%
  group_by(agegp10, sex) %>%
  group_map(function(cur_df, key) {
    #cur_sex <- cur_df$sex[1]
    #cur_agegp10 <- cur_df$agegp10[1]
    
    cur_sex <- key$sex[1]
    cur_agegp10 <- key$agegp10[1]
    
    cur_map_rmse <- br_compare_choro_map(cur_df,
                                         qoivar='n.minus.s',
                                         title=glue::glue('{cur_sex}, {cur_agegp10}'),
                                         name=glue::glue('Network RMSE -\nSibling RMSE'),
                                         labels=FALSE)
    
  })

#maxval <- max(abs(range(comp_asdrs_bygeoas_wide$n.minus.s)))
maxval <-7 

rmse_as_maps <- rmse_as_maps %>% 
  wrap_plots(rmse_as_maps, nrow=5, ncol=2) &
  scale_fill_distiller(name='Network RMSE-\nSibling RMSE)', 
                       limits=c(-maxval, maxval)*1.05,
                       oob=scales::squish,
                       type='div')

rmse_as_maps <- rmse_as_maps + 
  plot_layout(guides='collect') +
  plot_annotation(caption="Values outside of limits squished to limits.") &
  theme(legend.position='bottom',
        legend.direction='horizontal') 
  
saveRDS(rmse_as_maps, file.path(comp_out_dir, "method_compare_rmse_agesex_map.rds"))
ggsave(filename=file.path(comp_out_dir, "method_compare_rmse_agesex_map.pdf"),
       plot=rmse_as_maps,
       height=12,
       width=4)
ggsave(filename=file.path(comp_out_dir, "method_compare_rmse_agesex_map.png"),
       plot=rmse_as_maps,
       height=12,
       width=4)

rmse_as_maps

```


## Summarize Geographical relationships with Moran's I

Helper function to calculate Moran's I

```{r}

calculate_moran_I <- function(qoi_df, 
                              qoi_var, 
                              alternative = 'two.sided',
                              # other args for spdep::moran.test
                              ...) {

  mapobj <- readRDS(file.path(out_dir, "brazil_map.rds"))
  
  if(geo_name == 'city') {
    mapraw <- mapobj$map %>%
      mutate(geo = postal) 
  } else {
    mapraw <- mapobj$map %>%
      mutate(geo = region) %>%
      group_by(geo) %>%
      summarize() %>%
      ungroup()
  }
  
  # see
  # https://mgimond.github.io/Spatial/spatial-autocorrelation-in-r.html
  neighbors <- spdep::poly2nb(mapraw) 
  neighbors_weight <- spdep::nb2listw(neighbors, style="W", zero.policy=TRUE)
  
  #comp_rel_asdrs_bygeo_wide,
  #qoivar='n.minus.s'
                                        
  mapdat <- mapraw %>%
    left_join(qoi_df %>% rename(qoi = all_of(qoi_var)))
  
  res <- spdep::moran.test(mapdat[['qoi']], 
                           listw=neighbors_weight,
                           alternative=alternative,
                           ...)
  
  res$moran_I <- round(res$estimate[1],2)
  res$p_value <- round(res$p.value, 2)
  res$desc <- glue::glue("Moran's I, p-value calculated based on {alternative}",
                         .envir = res)
    
  # rename 'method' slot, since we use that for something else
  res$moran_method <- res$method
  res$method <- NULL
  
  return(res)
}

# helper function to coerce results of Moran's I calculation
# to a tibble row
moran_I_to_tibble <- function(res, ...) {
  class(res) <- NULL
  res$estimate <- list(res$estimate)
  return(as_tibble_row(c(res, ...)))
}

```

### Moran's I for MARE values

Calculate Moran's I for MARE values

```{r}
mare_moran_I <- comp_rel_asdrs_bygeoas_wide %>%
  rename(diff = 'n.minus.s') %>%
  pivot_longer(cols=c('Network', 'Sibling', 'diff'),
               names_to = 'method',
               values_to = 'value') %>%
  ungroup() %>%
  group_by(geo, method) %>%
  summarize(value = mean(value)) %>%
  group_by(method) %>%
  group_map(function(cur_df, key) {
    
    cur_method <- key$method[1]
    
    res <- calculate_moran_I(cur_df, 'value')
    
    res$sex <- 'both'
    res$agegp10 <- 'all'
    res$method <- cur_method
    
    return(res)
    
  })

spatial_res_mare <- map_dfr(mare_moran_I,
                            ~ moran_I_to_tibble(.x,
                                                qty = 'MARE'))
```

Calculate Moran's I for MARE values by age/sex group

```{r}
mare_as_moran_I <- comp_rel_asdrs_bygeoas_wide %>%
  rename(diff = 'n.minus.s') %>%
  pivot_longer(cols=c('Network', 'Sibling', 'diff'),
               names_to = 'method',
               values_to = 'value') %>%
  ungroup() %>%
  group_by(sex, method, agegp10) %>%
  group_map(function(cur_df, key) {
    
    cur_sex <- key$sex[1]
    cur_agegp10 <- key$agegp10[1]
    cur_method <- key$method[1]
    
    res <- calculate_moran_I(cur_df, 'value')
    
    res$sex <- cur_sex
    res$agegp10 <- cur_agegp10
    res$method <- cur_method
    
    return(res)
    
  })

spatial_res_mare_as <- map_dfr(mare_as_moran_I,
                               ~ moran_I_to_tibble(.x,
                                                   qty = 'MARE'))
```


### Moran's I for MSE values

Calculate Moran's I for MSE values

```{r}
mse_moran_I <- comp_asdrs_bygeoas_wide %>%
  rename(diff = 'n.minus.s') %>%
  pivot_longer(cols=c('Network', 'Sibling', 'diff'),
               names_to = 'method',
               values_to = 'value') %>%
  ungroup() %>%
  group_by(geo, method) %>%
  summarize(value = mean(value)) %>%
  group_by(method) %>%
  group_map(function(cur_df, key) {
    
    cur_method <- key$method[1]
    
    res <- calculate_moran_I(cur_df, 'value')
    
    res$sex <- 'both'
    res$agegp10 <- 'all'
    res$method <- cur_method
    
    return(res)
    
  })

spatial_res_mse <- map_dfr(mse_moran_I,
                           ~ moran_I_to_tibble(.x,
                                               qty = 'MSE'))
```

Calculate Moran's I for MSE values by age/sex group

```{r}
mse_as_moran_I <- comp_asdrs_bygeoas_wide %>%
  rename(diff = 'n.minus.s') %>%
  pivot_longer(cols=c('Network', 'Sibling', 'diff'),
               names_to = 'method',
               values_to = 'value') %>%
  ungroup() %>%
  group_by(sex, method, agegp10) %>%
  group_map(function(cur_df, key) {
    
    cur_sex <- key$sex[1]
    cur_agegp10 <- key$agegp10[1]
    cur_method <- key$method[1]
    
    res <- calculate_moran_I(cur_df, 'value')
    
    res$sex <- cur_sex
    res$agegp10 <- cur_agegp10
    res$method <- cur_method
    
    return(res)
    
  })

spatial_res_mse_as <- map_dfr(mse_as_moran_I,
                              ~ moran_I_to_tibble(.x,
                                                  qty = 'MSE'))
```

```{r}
moran_I_df <- bind_rows(spatial_res_mare,
                        spatial_res_mare_as,
                        spatial_res_mse,
                        spatial_res_mse_as)


write_csv(moran_I_df %>% unnest_wider(estimate) %>% arrange(p_value),
          file.path(comp_out_dir, "moran_I.csv"))
```

Moran's I values that are significant at $p=0.05$ level

```{r}
moran_I_df %>% filter(p_value < 0.05)
```

## Heatmap figures 

Create a dataset `all_err_diffs_boot`
which has a row for each geo/sex/agegp/boot_idx that has, for Sibling and Network
  - delta = (estimate - truth) [diff between estimate and truth]
  - delta2 = (estimate - truth)^2 [delta squared - used in calculating MSE and RMSE]
  - delta_rel = |estimate - truth| / truth [absolute relative diff between estimate and truth]
  - delta_rel_notabs = (estimate - truth) / truth [relative diff between estimate and truth, with no absolute value taken]
  - estimate (the actual estimate)
  - gs_asdr (the gold standard value)
  
```{r}
all_err_diffs_boot <- comp_asdrs_boot %>%
  rename(estimate = post_mean_asdr) %>%
  pivot_wider(id_cols = c('geo', 'sex', 'agegp10', 'boot_idx', 'gs_asdr'),
              names_from=method,
              values_from=c(starts_with('delta'), 'estimate'))
```

Create a dataset `geo_err_diffs_boot` which summarizes errors within each geographical area;
it has a row for each geo/boot_idx that has, for Network/Sibling
  - mean_delta
  - mean_delta2
  - mean_delta_rel
it also has differences:
  - mean_diff_rel
  - mean_diff_mse
  - mean_diff_rmse = sqrt(mean_delta2_Network) - sqrt(mean_delta2_Sibling)
  
```{r}
## given a dataset assumed to be grouped in some way 
## aggregate errors and calculate rmse after aggregating
summ_estimate_errs <- function(df) {
  df %>%
    summarize(# sibling
              mean_delta_Sibling = mean(delta_Sibling),
              mean_delta2_Sibling = mean(delta2_Sibling),
              mean_delta_rel_Sibling = mean(delta_rel_Sibling),
              mean_delta_rel_notabs_Sibling = mean(delta_rel_notabs_Sibling), 
              # network 
              mean_delta_Network = mean(delta_Network),
              mean_delta2_Network = mean(delta2_Network),
              mean_delta_rel_Network = mean(delta_rel_Network),
              mean_delta_rel_notabs_Network = mean(delta_rel_notabs_Network)) %>%
    ungroup() %>%
    mutate(mean_diff_rel = mean_delta_rel_Network - mean_delta_rel_Sibling,
           mean_diff_rel_notabs = mean_delta_rel_notabs_Network - mean_delta_rel_notabs_Sibling,
           mean_diff_mse = mean_delta2_Network - mean_delta2_Sibling,
           mean_diff_rmse = sqrt(mean_delta2_Network) - sqrt(mean_delta2_Sibling),
           mean_diff_raw = mean_delta_Network - mean_delta_Sibling)
}

## given a summarized and grouped dataset,
## calculate summaries (point ests + cis) for network, sibling, and diffs
calc_ci_errs <- function(df) {
  df %>%
  summarize(
            ## sibling
            sib_mare = mean(mean_delta_rel_Sibling),
            sib_mare_ci_low = quantile(mean_delta_rel_Sibling, .025),
            sib_mare_ci_high = quantile(mean_delta_rel_Sibling, .975),
            sib_mse = mean(mean_delta2_Sibling),
            sib_mse_ci_low = quantile(mean_delta2_Sibling, .025),
            sib_mse_ci_high = quantile(mean_delta2_Sibling, .975),
            sib_rmse = sqrt(mean(mean_delta2_Sibling)),
            sib_rmse_ci_low = sqrt(quantile(mean_delta2_Sibling, .025)),
            sib_rmse_ci_high = sqrt(quantile(mean_delta2_Sibling, .975)),
            sib_raw = mean(mean_delta_Sibling),
            sib_raw_ci_low = quantile(mean_delta_Sibling, .025),
            sib_raw_ci_high = quantile(mean_delta_Sibling, .975),
            sib_rel_notabs = mean(mean_delta_rel_notabs_Sibling),
            sib_rel_notabs_ci_low = quantile(mean_delta_rel_notabs_Sibling, .025),
            sib_rel_notabs_ci_high = quantile(mean_delta_rel_notabs_Sibling, .975),
            ## network 
            net_mare = mean(mean_delta_rel_Network),
            net_mare_ci_low = quantile(mean_delta_rel_Network, .025),
            net_mare_ci_high = quantile(mean_delta_rel_Network, .975),
            net_mse = mean(mean_delta2_Network),
            net_mse_ci_low = quantile(mean_delta2_Network, .025),
            net_mse_ci_high = quantile(mean_delta2_Network, .975),
            net_rmse = sqrt(mean(mean_delta2_Network)),
            net_rmse_ci_low = sqrt(quantile(mean_delta2_Network, .025)),
            net_rmse_ci_high = sqrt(quantile(mean_delta2_Network, .975)),
            net_raw = mean(mean_delta_Network),
            net_raw_ci_low = quantile(mean_delta_Network, .025),
            net_raw_ci_high = quantile(mean_delta_Network, .975),
            net_rel_notabs = mean(mean_delta_rel_notabs_Network),
            net_rel_notabs_ci_low = quantile(mean_delta_rel_notabs_Network, .025),
            net_rel_notabs_ci_high = quantile(mean_delta_rel_notabs_Network, .975),
            ## differences    
            diff_mare = mean(mean_diff_rel),
            diff_mare_ci_low = quantile(mean_diff_rel, .025),
            diff_mare_ci_high = quantile(mean_diff_rel, .975),
            diff_mse = mean(mean_diff_mse),
            diff_mse_ci_low = quantile(mean_diff_mse, .025),
            diff_mse_ci_high = quantile(mean_diff_mse, .975),
            diff_rmse = mean(mean_diff_rmse),
            diff_rmse_ci_low = quantile(mean_diff_rmse, .025),
            diff_rmse_ci_high = quantile(mean_diff_rmse, .975),
            diff_raw = mean(mean_diff_raw),
            diff_raw_ci_low = quantile(mean_diff_raw, .025),
            diff_raw_ci_high = quantile(mean_diff_raw, .975),
            diff_rel_notabs = mean(mean_diff_rel_notabs),
            diff_rel_notabs_ci_low = quantile(mean_diff_rel_notabs, .025),
            diff_rel_notabs_ci_high = quantile(mean_diff_rel_notabs, .975)
            )
}

## given df with errors and grouping vars,
## calculate point ests and cis for those grouping vars,
## based on the general principle of calculating aggregates within
## each bootstrap rep, then summarizing across bootstrap reps
##
## example:
##   if groups is age and sex, then
##       1) calculate mare and rmse for each age and sex group within each boot rep
##       2) then calculate average and 95% CI of these age/sex mare and rmse values across boot reps
calc_summ_errs <- function(df, groups) {
  df %>%
    ## calculate rmse, mare, etc within groups and boot rep
    group_by(across({{groups}}), boot_idx) %>%
    summ_estimate_errs() %>%
    ## now summarize across boot reps, within groups
    group_by(across({{groups}})) %>%
    calc_ci_errs()
}
```

```{r}
geo_err_diffs_summ <-
  all_err_diffs_boot %>%
  calc_summ_errs(geo)

agesex_err_diffs_summ <-
  all_err_diffs_boot %>%
  calc_summ_errs(c(sex, agegp10))

geo_agesex_err_diffs_summ <-
  all_err_diffs_boot %>%
  calc_summ_errs(c(geo, sex, agegp10))

## this should calculate errs across cities for each bootstrap rep,
## then take ci, etc, over bootstrap reps
tot_err_diffs_summ <- all_err_diffs_boot %>%
  group_by(boot_idx) %>%
  summ_estimate_errs() %>%
  mutate(dummy=1) %>%
  group_by(dummy) %>%
  calc_ci_errs() %>%
  ungroup()
```

```{r}
# see
# https://stackoverflow.com/questions/60016390/set-axes-limits-in-patchwork-when-combining-ggplot2-objects
apply_consistent_y_lims <- function(this_plot){
    num_plots <- length(this_plot$layers)
    y_lims <- lapply(1:num_plots, function(x) ggplot_build(this_plot[[x]])$layout$panel_scales_y[[1]]$range$range)
    min_y <- min(unlist(y_lims))
    max_y <- max(unlist(y_lims))
    this_plot & ylim(min_y, max_y)
}
```


```{r}
## NB: this fn assumes that the environment has
##   geo_err_diffs_summ
##   agesex_err_diffs_summ
##   geo_agesex_err_diffs_summ
err_breakdown_plot <- function(err_metric, 
                               err_metric_name, 
                               diff = FALSE) {
  
  if (diff) {
    fill_scale <- scale_fill_gradient2(low='yellow', high='red', midpoint=0)
    vline <- geom_vline(xintercept = 0, color='grey')
    hline <- geom_hline(yintercept = 0, color='grey')
    symm_x <- lemon::scale_x_symmetric(mid=0)
  } else {
    fill_scale <- scale_fill_gradient(low='white', high='red')
    vline <- NULL
    hline <- NULL
    symm_x <- NULL
  }
  
  ## age-sex plot
  as_plot <- agesex_err_diffs_summ %>%
    ## rename current error
    rename_with(~ str_replace(.x, err_metric, 'err'),
                .cols=starts_with(err_metric)) %>%
    ggplot(.) +
    geom_pointrange(aes(x=agegp10, 
                        ymin=err_ci_low,
                        ymax=err_ci_high,
                        y=err)) +
    facet_wrap(~ sex) +
    theme_minimal() +
    xlab("") +
    expand_limits(y = 0) +
    hline + 
    ylab(err_metric_name)

   geo_err_diffs_summ_forplot <- geo_err_diffs_summ %>%
    ## rename current error
    rename_with(~ str_replace(.x, err_metric, 'err'),
                .cols=starts_with(err_metric)) %>%
     mutate(geo = factor(geo)) %>%
     mutate(geo = fct_reorder(geo, err))
   
   geo_lev_order <- levels(geo_err_diffs_summ_forplot$geo)
   
   city_plot <- geo_err_diffs_summ_forplot %>%
     ggplot(.) +
     geom_pointrange(aes(x=err, 
                         xmin=err_ci_low,
                         xmax=err_ci_high,
                         y=geo)) +
     theme_minimal() +
     xlab(err_metric_name) +
     expand_limits(x = 0) +
     symm_x +
     vline +
     ylab("")
   
   ## summarize errors across bootstrap reps within each city/age/sex gp
   hm <- geo_agesex_err_diffs_summ %>%
    ## rename current error
    rename_with(~ str_replace(.x, err_metric, 'err'),
                .cols=starts_with(err_metric)) %>%
     mutate(geo = factor(geo)) %>%
     mutate(geo = fct_relevel(geo, geo_lev_order)) %>%
     ggplot(.) +
     geom_tile(aes(x=agegp10, y=geo, fill=err)) +
     facet_wrap(~ sex) +
     theme_minimal() +
     xlab("") +
     ylab("") +
     theme(legend.position = 'bottom') +
     fill_scale +
     expand_limits(fill = 0) +
     #coord_equal() +
     guides(fill = guide_colorbar(title = err_metric_name,
                                  title.position="top"))
     #scale_fill_gradient(low='black', high='red')   
  
  # 1 : heatmap
  # 2 : city agg errs
  # 3 : age-sex errs
  design <- "
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    111111111112222
    333333333334444
    333333333334444
    333333333334444
    333333333334444
  "
  #p1 <- (hm + ggtitle("City, Probability")) + 
  #      (city_plot + ggtitle("City, Age-specific death rate")) + 
  #      (as_plot + ggtitle("Region, Probability")) +
  test <- (hm) + 
        (city_plot) + 
        (as_plot) +
        guide_area() +
    plot_layout(guides='collect', design=design)   
  
  return(test)
}

```


```{r}
# height / width for saved plots
pheight <- 10
pwidth <- 7.5
```


### MARE

Network MARE

```{r}
err_breakdown_mare_net <- err_breakdown_plot('net_mare', 
                                             'Network\nMARE')

#saveRDS(err_breakdown_mare_net, 
#        file.path(comp_out_dir, "err_breakdown_mare_net.rds"))
ggsave(filename=file.path(comp_out_dir, "err_breakdown_mare_net.pdf"),
       plot=err_breakdown_mare_net,
       height=pheight,
       width=pwidth)

err_breakdown_mare_net
```

Sibling MARE

```{r}
err_breakdown_mare_sib <- err_breakdown_plot('sib_mare', 
                                             'Sibling\nMARE')

#saveRDS(err_breakdown_mare_sib, 
#        file.path(comp_out_dir, "err_breakdown_mare_sib.rds"))
ggsave(filename=file.path(comp_out_dir, "err_breakdown_mare_sib.pdf"),
       plot=err_breakdown_mare_sib,
       height=pheight,
       width=pwidth)

err_breakdown_mare_sib
```

MARE diffs

```{r}
err_breakdown_mare_diff <- err_breakdown_plot('diff_mare', 
                                              'Network MARE -\nSibling MARE', 
                                              diff=TRUE)

#saveRDS(err_breakdown_mare_diff, 
#        file.path(comp_out_dir, "err_breakdown_mare_diff.rds"))
ggsave(filename=file.path(comp_out_dir, "err_breakdown_mare_diff.pdf"),
       plot=err_breakdown_mare_diff,
       height=pheight,
       width=pwidth)

err_breakdown_mare_diff
```

### RMSE


Network RMSE

```{r}
err_breakdown_rmse_net <- err_breakdown_plot('net_rmse', 
                                             'Network\nRMSE')

#saveRDS(err_breakdown_rmse_net, 
#        file.path(comp_out_dir, "err_breakdown_rmse_net.rds"))
ggsave(filename=file.path(comp_out_dir, "err_breakdown_rmse_net.pdf"),
       plot=err_breakdown_rmse_net,
       height=pheight,
       width=pwidth)

err_breakdown_rmse_net
```

Sibling RMSE

```{r}
err_breakdown_rmse_sib <- err_breakdown_plot('sib_rmse', 
                                             'Sibling\nRMSE')

#saveRDS(err_breakdown_rmse_sib, 
#        file.path(comp_out_dir, "err_breakdown_rmse_sib.rds"))
ggsave(filename=file.path(comp_out_dir, "err_breakdown_rmse_sib.pdf"),
       plot=err_breakdown_rmse_sib,
       height=pheight,
       width=pwidth)

err_breakdown_rmse_sib
```

RMSE diffs

```{r}
err_breakdown_rmse_diff <- err_breakdown_plot('diff_rmse', 
                                              'Network RMSE -\nSibling RMSE',
                                              diff=TRUE)

#saveRDS(err_breakdown_mare_diff, 
#        file.path(comp_out_dir, "err_breakdown_mare_diff.rds"))
ggsave(filename=file.path(comp_out_dir, "err_breakdown_rmse_diff.pdf"),
       plot=err_breakdown_rmse_diff,
       height=pheight,
       width=pwidth)

err_breakdown_rmse_diff
```

### Raw errors 

These raw errors could be the basis for estimating bias by
age and sex group

Network raw errors

```{r}
err_breakdown_raw_net <- err_breakdown_plot('net_raw', 
                                            'Network\nError',
                                            diff=TRUE)

ggsave(filename=file.path(comp_out_dir, "err_breakdown_raw_net.pdf"),
       plot=err_breakdown_raw_net,
       height=pheight,
       width=pwidth)

err_breakdown_raw_net
```

Sibling raw error

```{r}
err_breakdown_raw_sib <- err_breakdown_plot('sib_raw', 
                                            'Sibling\nError',
                                            diff=TRUE)

ggsave(filename=file.path(comp_out_dir, "err_breakdown_raw_sib.pdf"),
       plot=err_breakdown_raw_sib,
       height=pheight,
       width=pwidth)

err_breakdown_raw_sib
```

Raw error diffs

```{r}
err_breakdown_raw_diff <- err_breakdown_plot('diff_raw', 
                                             'Network error -\nSibling error',
                                             diff=TRUE)

ggsave(filename=file.path(comp_out_dir, "err_breakdown_raw_diff.pdf"),
       plot=err_breakdown_raw_diff,
       height=pheight,
       width=pwidth)

err_breakdown_raw_diff
```

### Relative (not absolute) errors

Network rel-not-abs errors

```{r}
err_breakdown_rel_notabs_net <- err_breakdown_plot('net_rel_notabs', 
                                                   'Network\nRelative Error (not abs)',
                                                   diff=TRUE)

ggsave(filename=file.path(comp_out_dir, "err_breakdown_rel_notabs_net.pdf"),
       plot=err_breakdown_rel_notabs_net,
       height=pheight,
       width=pwidth)

err_breakdown_rel_notabs_net
```

Sibling raw error

```{r}
err_breakdown_rel_notabs_sib <- err_breakdown_plot('sib_rel_notabs', 
                                                   'Sibling\nRelative Error (not abs)',
                                                   diff=TRUE)

ggsave(filename=file.path(comp_out_dir, "err_breakdown_rel_notabs_sib.pdf"),
       plot=err_breakdown_rel_notabs_sib,
       height=pheight,
       width=pwidth)

err_breakdown_rel_notabs_sib
```

Raw error diffs

```{r}
err_breakdown_rel_notabs_diff <- err_breakdown_plot('diff_rel_notabs', 
                                                    'Network relative error (NA)-\nSibling relative error (NA)',
                                                    diff=TRUE)

ggsave(filename=file.path(comp_out_dir, "err_breakdown_rel_notabs_diff.pdf"),
       plot=err_breakdown_rel_notabs_diff,
       height=pheight,
       width=pwidth)

err_breakdown_rel_notabs_diff
```

```{r}
toc()
```


